### 2017-01-23 paper.tex
init

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8

\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out if you need a4paper

%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper

\IEEEoverridecommandlockouts                              % This command is only needed if 
                                                          % you want to use the \thanks command

\overrideIEEEmargins                                      % Needed to meet printer requirements.

% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

\usepackage{xspace}
\usepackage{amsmath,amssymb,amsfonts,amsfonts}
\usepackage{algorithm}
\usepackage[noend]{algorithmic}
\usepackage{url}
\usepackage{graphicx,subfigure}
\usepackage{color}
\usepackage{hyperref}
%\hypersetup{bookmarksopen,
%bookmarksnumbered,
%pdfpagemode=UseOutlines,
%colorlinks=true,
%linkcolor=blue,
%anchorcolor=blue,
%citecolor=blue,
%filecolor=blue,
%menucolor=blue,
%urlcolor=blue
%}

\title{\LARGE \bf
Informed sampling by Markov chain Monte Carlo methods
}

\author{
Rohan Thakker$^{*}$,
Cole Gulino$^{*}$,
Daqing YI$^{}$,
Oren Salzman$^{}$ and
Siddhartha Srinivasa$^{}$% <-this % stops a space
\thanks{*R. Thakker and C. Gulino contributed equally to this paper.}
\thanks{This work was (partially) funded by the National Science Foundation IIS (\#1409003), Toyota Motor Engineering \& Manufacturing (TEMA), and the Office of Naval Research.}% <-this % stops a space
\thanks{$^{1}${\tt\small \{rthakker, cgulino, daqingy, osalzman, ss5\} @andrew.cmu.edu}}%
%
\\        
Robotics Institute, Carnegie Mellon University$^{1}$
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  macros 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{macros.tex}

\begin{document}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

\section{Related work}
\subsection{planning}

\subsection{sampling}
Hierarchical sampling~\cite{KTC16}.

Informed sampling~\cite{GSB14}

OBPRM~\cite{ABDJV98, YTEA12}

Medial axis~\cite{LTA03, YDLTA14}

heuristic~\cite{US03, SWT09}

\subsection{MCMC}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliography{bibliography}
\bibliographystyle{abbrv}
%\bibliographystyle{IEEEtran}
%\bibliography{IEEEabrv,bibliography}

\end{document}

### 2017-01-24 paper.tex
added refs
add bst
starting intro

@@
 \section{Introduction}
+Sampling-based motion-planning algorithms~\cite{CBHKKLT05, L06} have proven to be an effective tool at solving motion-planning problems.
+They search through the continuous state space~$\calX$ by sampling random states and maintaining a discrete graph~$G$ called a \emph{roadmap}.
+Vertices and edges in $G$ correspond to collision-free states and paths, respectively.
+
+Roughly speaking, all these algorithms iteratively sample new states.
+This is required to ensure that, as the number of samples tends to infinity, 
+(i)~a solution will be found 
+(a property called \emph{probabilistic completeness})
+and that
+(ii)~given some optimization criteria, the quality of the solution will progressively converge to the quality of the optimal solution
+(a property called \emph{asymptotic  optimality}).
+
+While, original sampling-based algorithms such as RRT~\cite{LK01} and PRM~\cite{KSLO96} only guaranteed to asymptotically return \emph{a} solution, if one exists, they did not provide any guarantees on the \emph{quality} of the solution, given some optimization criteria.
+Karaman and Frazzoli~\cite{KF11}, presented variants of PRM and RRT, named PRM* and RRT*, respectively that were shown to produce paths who's cost converges asymptotically to the minimal-cost path.
+Additional algorithms followed, increasing the converges rate by various techniques such as lazy dynamic programming~\cite{GSB15, JSCP15}, relaxing optimality to near-optimality~\cite{DB14, SH16} and more.
+
+In the most basic form, the motion-planning problem calls for computing \emph{a} path between two given states.
+Indeed, 
+However, recent years 
+Original planners such as RRT~\cite{LK01} and PRM~\cite{KSLO96} did not provide any guarantee on the \emph{•}
 
@@
 \subsection{planning}
+Classic:\\
+RRT~\cite{LK01}
+
+PRM~\cite{KSLO96}
+
+AO:\\
+RRT*, PRM*~\cite{KF11}
+
+BIT*~\cite{GSB15}
+
+FMT*~\cite{JSCP15}
+
+Near AO:\\
+LBT-RRT~\cite{SH16}
+
+SPARSE~\cite{DB14}
+
+RGGS~\cite{SSH16}
+
+Kinodynamic works:\\~\cite{SL14, XBPA15, WB13, KF10}
 

### 2017-01-24 paper.tex
more intro

@@
 \title{\LARGE \bf
-Informed sampling by Markov chain Monte Carlo methods
+Informed sampling by Markov Chain Monte Carlo methods
 }
@@
 
+In the initial stages of the algorithm, 
+when no path has yet to be found, 
+the samples need to be drawn from the entire state space~$\calX$.
+However, given a path $\gamma$ , the algorithm can limit its sampling domain to a subset of~$\calX$  containing states that \emph{may} produce higher-quality paths than $\gamma$.
+Following Gammell et al.~\cite{GSB14}, we call this subset the \emph{informed subset} and denote it $\Cinf$.
+
+For systems without differential constraints, \Cinf can be sampled directly~\cite{GSB14}.
+However, for systems with differential constraints, it is not clear how to directly sample \Cinf.
+One approach to produce samples in \Cinf is via \emph{rejection sampling}---sampling a state $x \in \calX$ and testing if $x \in \Cinf$.
+However, when the size of the informed space~$\Cinf$ is much smaller than entire state space~$\calX$, then this procedure may dominate the running time of the algorithm~\cite{KTC16}.
+\emph{Hierarchical rejection sampling} (HRS) is a recently introduced sampling approach that improves the efficiency of rejection sampling.
+This is done by sampling in individual dimensions of the state space and progressively combing these partial samples into larger ones while testing if these combined samples may be in \Cinf or not.
+
 While, original sampling-based algorithms such as RRT~\cite{LK01} and PRM~\cite{KSLO96} only guaranteed to asymptotically return \emph{a} solution, if one exists, they did not provide any guarantees on the \emph{quality} of the solution, given some optimization criteria.
@@
 However, recent years 
-Original planners such as RRT~\cite{LK01} and PRM~\cite{KSLO96} did not provide any guarantee on the \emph{•}
+Original planners such as RRT~\cite{LK01} and PRM~\cite{KSLO96} did not provide any guarantee on the \emph{s}
 
 \section{Related work}
-\subsection{planning}
+
+\subsection{Planning}
+
 Classic:\\
@@
 
-\subsection{sampling}
+\subsection{Sampling}
+
 Hierarchical sampling~\cite{KTC16}.
@@
 
+MCMC~\cite{ADDJ03}
+
+HMC~\cite{N11}
+
+\section{Algorithm}
+
+\section{Results}
+
+\section{Conclusion}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \bibliography{bibliography}
-\bibliographystyle{abbrv}
-%\bibliographystyle{IEEEtran}
+\bibliographystyle{IEEEtran}
 %\bibliography{IEEEabrv,bibliography}

### 2017-01-24 paper.tex
enable hyperlink
add some mcmc

@@
 % on the last page of the document
+
+\makeatletter
+\let\NAT@parse\undefined
+\makeatother
 
@@
 
-MCMC~\cite{ADDJ03}
+Markov Chain Monte Carlo~\cite{ADDJ03} is a framework of sampling from a given probability distribution by constructing a Markov chain of random transition toward a desired distribution.
+A set of samples are generated to approximate the desired distribution.
+Unlike a rejection sampling, MCMC does a random walk in a parametric space and concentrates on an important areas, which usually brings better efficiency.
 

### 2017-01-25 paper.tex
sync

@@
 \section{Introduction}
+\label{sec:intro}
+
 Sampling-based motion-planning algorithms~\cite{CBHKKLT05, L06} have proven to be an effective tool at solving motion-planning problems.
@@
 \section{Related work}
+\label{sec:related_work}
 
@@
 
-Markov Chain Monte Carlo~\cite{ADDJ03} is a framework of sampling from a given probability distribution by constructing a Markov chain of random transition toward a desired distribution.
+Markov Chain Monte Carlo(MCMC)~\cite{ADDJ03} is a framework of sampling from a given probability distribution by constructing a Markov chain of random transition toward a desired distribution.
 A set of samples are generated to approximate the desired distribution.
 Unlike a rejection sampling, MCMC does a random walk in a parametric space and concentrates on an important areas, which usually brings better efficiency.
-
-HMC~\cite{N11}
+Hamiltonian Monte Carlo(HMC)~\cite{N11} is introduced to provide better efficiency in converging to a desired distribution.
+It adopts physical system dynamics to propose future states in the Markov chain.
 
 \section{Algorithm}
+\label{sec:algorithm}
+
+\begin{algorithm}
+	\begin{algorithmic}[1]
+		\STATE
+   	\end{algorithmic}
+	\caption{MCMC Informed Sampling}
+	\label{alg:mcmc_informed_sampling}
+\end{algorithm}
 

### 2017-01-25 paper.tex
add explanation of HMC

@@
 
-Markov Chain Monte Carlo(MCMC)~\cite{ADDJ03} is a framework of sampling from a given probability distribution by constructing a Markov chain of random transition toward a desired distribution.
-A set of samples are generated to approximate the desired distribution.
+Markov Chain Monte Carlo(MCMC)~\cite{ADDJ03} is a framework of sampling from a given probability distribution by constructing a Markov chain of random transition toward a desired distribution $ \pi (x) $ .
+A set of samples are generated to approximate the desired distribution $ \pi (x) $.
 Unlike a rejection sampling, MCMC does a random walk in a parametric space and concentrates on an important areas, which usually brings better efficiency.
@@
 It adopts physical system dynamics to propose future states in the Markov chain.
+The concept origins from Hamiltonian dynamics, which models the movement of an object.
+Given the position $ x $ and the momentum $ q $ of an object, the system energy can be written as $ H(x,q) = U(x) + K(q) $, in which $ U(x) $ is the potential energy and $ K(q) $ is the kinetic energy.
+The movement of the object (how $ x $ and $ q $ change over time) is determined by
+$ \frac{dx}{dt} = \frac{\partial H}{\partial q} $ and $ \frac{dq}{dt} = - \frac{\partial H}{\partial x} $.
+By the association between energy and a canonical distribution, a joint distribution for the states $ x $ and $ q $ can be created from a Hamiltonian dynamics, which is 
+$ P(x, q) = \frac{1}{Z} \exp ( -H(x,q) / T ) = \frac{1}{Z} \exp ( -U(x) / T) \exp (-K(q) / T) $.
+If we define $ U(x) = - \log ( \pi(x) T ) $, $ P(x, q) $ can be rewritten as $ P(x, q) = \pi (x) \frac{1}{Z} \exp (-K(q) / T) $.
+Because the state $ x $ and the the momentum  $ q $ are independent, we can sample $ [ x ,q ] $ from $ P(x, q) $ and discard the momentum $ q $ (as an auxiliary variable).
+The collected set of $ x $ is equivalent to sampling from $ \pi(x) $.
+We are going to integrate this idea into our sampling framework of efficiently generating samples under kinetic constraints.
 

### 2017-01-25 paper.tex
add problem definition

@@
 \usepackage{url}
+\usepackage{bm}
 \usepackage{graphicx,subfigure}
@@
 
+Define the dynamics of a robot as 
+\begin{equation}
+\label{eq:kinematics}
+\dot{\bm{x}}(t) = f( \bm{x}(t) , \bm{u}(t) ), 
+\end{equation}
+in which $ \bm{x} \in \mathcal{X} \subseteq \mathbb{R}^n $ is the state of the robot, and $ \bm{u} \in \mathcal{U} \subseteq \mathbb{R}^m $ is the control input.
+The dynamics determines a state trajectory $ \pi $, given a duration $ T $, an initial state $ \bm{x}(0) $ and an initial input $ \bm{u}(0) $.
+The cost of a trajectory $ \pi $ is defined as the accumulated cost along the path, which is 
+\begin{equation}
+\label{eq:path_cost}
+c(\pi) = \int_0^{T} c( x(t), u(t) ) dt.
+\end{equation}
+Consider the obstacles in a workspace, we have $ \mathcal{X}_{free} \subseteq \mathcal{X} $.
+Consider the bounds of the control input, we have $ \mathcal{U}_{free} \subseteq \mathcal{U} $.
+The dynamics of the robot in Equation~\eqref{eq:kinematics}, free state space $  \mathcal{X}_{free} $ and free control input space $ \mathcal{U}_{free} $ determines a free trajectory space $ \Pi_{free} $, which contains all feasible trajectories $ \pi \in \Pi_{free} $.
+
+We can define an optimal kinodynamic path-planning problem that finds a kinodynamic path minimizing the cost in Definition \ref{defn:optimal_kino_path_planning}.
+\begin{defn}{ \textbf{Optimal Kinodynamic Path-Planning} }
+\label{defn:optimal_kino_path_planning}
+	Find an optimal path $  \pi^* $ that satisfies
+	\begin{itemize}
+	\item $\forall t \in [0,T] $, $ \bm{x} (t) \in \mathcal{X}_{free}  $ and $ \bm{u} (t) \in \mathcal{U}_{free} $;
+	\item $ \bm{x} (0) = x_{init} $, $ \bm{x} (T) = x_{goal} $, $ \bm{u} (0) = u_{init} $ and $ \bm{u} (T) = u_{goal} $; and
+	\item $ \pi^* = \max_{ \pi \in \Pi_{free} } c( \pi ) $. 
+	\end{itemize}
+\end{defn}
+
+\dy{Do we want to set an initial and a goal for the control input? Does this simplify the problem solving?}
+
 \begin{algorithm}

### 2017-01-26 paper.tex
?

--- 2017-01-25 paper.tex
@@
 % on the last page of the document
-
-\makeatletter
-\let\NAT@parse\undefined
-\makeatother
 
@@
 \section{Introduction}
-\label{sec:intro}
-
 Sampling-based motion-planning algorithms~\cite{CBHKKLT05, L06} have proven to be an effective tool at solving motion-planning problems.
@@
 
+In this paper, we suggest an alternative approach to sampling in the informed set \Cinf.
+We call our approach
+
 While, original sampling-based algorithms such as RRT~\cite{LK01} and PRM~\cite{KSLO96} only guaranteed to asymptotically return \emph{a} solution, if one exists, they did not provide any guarantees on the \emph{quality} of the solution, given some optimization criteria.
@@
 \section{Related work}
-\label{sec:related_work}
 
@@
 
-Markov Chain Monte Carlo(MCMC)~\cite{ADDJ03} is a framework of sampling from a given probability distribution by constructing a Markov chain of random transition toward a desired distribution.
-A set of samples are generated to approximate the desired distribution.
-Unlike a rejection sampling, MCMC does a random walk in a parametric space and concentrates on an important areas, which usually brings better efficiency.
-Hamiltonian Monte Carlo(HMC)~\cite{N11} is introduced to provide better efficiency in converging to a desired distribution.
-It adopts physical system dynamics to propose future states in the Markov chain.
+MCMC~\cite{ADDJ03}
+
+HMC~\cite{N11}
 
 \section{Algorithm}
-\label{sec:algorithm}
-
-\begin{algorithm}
-	\begin{algorithmic}[1]
-		\STATE
-   	\end{algorithmic}
-	\caption{MCMC Informed Sampling}
-	\label{alg:mcmc_informed_sampling}
-\end{algorithm}
 

### 2017-01-26 paper.tex
revised intro

--- 2017-01-25 paper.tex
@@
 Sampling-based motion-planning algorithms~\cite{CBHKKLT05, L06} have proven to be an effective tool at solving motion-planning problems.
-They search through the continuous state space~$\calX$ by sampling random states and maintaining a discrete graph~$G$ called a \emph{roadmap}.
+They search through a continuous state space~$\calX$ by sampling random states and maintaining a discrete graph~$G$ called a \emph{roadmap}.
 Vertices and edges in $G$ correspond to collision-free states and paths, respectively.
 
-Roughly speaking, all these algorithms iteratively sample new states.
+Roughly speaking, these algorithms iteratively sample new states.
 This is required to ensure that, as the number of samples tends to infinity, 
@@
 the samples need to be drawn from the entire state space~$\calX$.
-However, given a path $\gamma$ , the algorithm can limit its sampling domain to a subset of~$\calX$  containing states that \emph{may} produce higher-quality paths than $\gamma$.
+However, once a path $\gamma$ is produce,  algorithm that seek \emph{high-quality paths} can limit their sampling domain to a subset of~$\calX$  containing states that may produce higher-quality paths than $\gamma$.
 Following Gammell et al.~\cite{GSB14}, we call this subset the \emph{informed subset} and denote it $\Cinf$.
 
-For systems without differential constraints, \Cinf can be sampled directly~\cite{GSB14}.
-However, for systems with differential constraints, it is not clear how to directly sample \Cinf.
+For Euclidean spaces optimizing for path length, 
+\Cinf can be analytically expresses as a prolate hyperspheroid and can be sampled directly~\cite{GSB14}.
+Indeed, directly sampling in \Cinf has been shown to dramatically improve computation time when compared to sampling in $\calX$, especially in high dimensions.
+
+Unfortunately, in more general settings such as
+for systems with differential constraints,
+it is not clear how to directly sample \Cinf.
+%
 One approach to produce samples in \Cinf is via \emph{rejection sampling}---sampling a state $x \in \calX$ and testing if $x \in \Cinf$.
 However, when the size of the informed space~$\Cinf$ is much smaller than entire state space~$\calX$, then this procedure may dominate the running time of the algorithm~\cite{KTC16}.
-\emph{Hierarchical rejection sampling} (HRS) is a recently introduced sampling approach that improves the efficiency of rejection sampling.
-This is done by sampling in individual dimensions of the state space and progressively combing these partial samples into larger ones while testing if these combined samples may be in \Cinf or not.
+Recently, Kunz et al.~\cite{KTC16} showed, under some technical assumptions, how to efficiently produce samples in~$\Cinf$ by \emph{Hierarchical rejection sampling} (HRS). 
+Here, individual dimensions are sampled recursively 
+and then combined. Rejection sampling is performed for these partial samples until a suitable sample has been produced. The novelty of HRS is the ability to fail fast.
 
-While, original sampling-based algorithms such as RRT~\cite{LK01} and PRM~\cite{KSLO96} only guaranteed to asymptotically return \emph{a} solution, if one exists, they did not provide any guarantees on the \emph{quality} of the solution, given some optimization criteria.
-Karaman and Frazzoli~\cite{KF11}, presented variants of PRM and RRT, named PRM* and RRT*, respectively that were shown to produce paths who's cost converges asymptotically to the minimal-cost path.
-Additional algorithms followed, increasing the converges rate by various techniques such as lazy dynamic programming~\cite{GSB15, JSCP15}, relaxing optimality to near-optimality~\cite{DB14, SH16} and more.
+Unfortunately, both rejection sampling and HRS may produce a large number of rejected samples especially in high-dimensional spaces.
+This may cause the search algorithm to spend most of its time trying to produces samples in~$\Cinf$ rather than explore it.
+In this paper, we suggest an alternative approach to sampling in the informed set \Cinf for a wide range of settings.
+Our main insight is 
+\os{this is a very important sentence!!!}
+Specifically, our approach consists of two stages:
+in the first, a random sample $x \in \calX$ is retracted to the boundary of~$\Cinf$ by running a gradient-descent algorithm;
+in the second stage, this retracted sample $\tilde{x}$ is used to seed a Monte Carlo sampling chain which allows us to approximately produce samples uniformly \emph{within}~$\Cinf$.
 
-In the most basic form, the motion-planning problem calls for computing \emph{a} path between two given states.
-Indeed, 
-However, recent years 
-Original planners such as RRT~\cite{LK01} and PRM~\cite{KSLO96} did not provide any guarantee on the \emph{s}
+Our approach requires that the system has a solution to the two-point boundary value problem (2pBVP)~\cite{} and that a gradient can be defined over the cost function.
+Indeed, we demonstrate the efficiency of our approach on a wide variety of systems and show that it enables reducing the planning time by several orders of magnitute when compared to algorithms using rejection sampling or HRS.
+
+%While, original sampling-based algorithms such as RRT~\cite{LK01} and PRM~\cite{KSLO96} only guaranteed to asymptotically return \emph{a} solution, if one exists, they did not provide any guarantees on the \emph{quality} of the solution, given some optimization criteria.
+%Karaman and Frazzoli~\cite{KF11}, presented variants of PRM and RRT, named PRM* and RRT*, respectively that were shown to produce paths who's cost converges asymptotically to the minimal-cost path.
+%Additional algorithms followed, increasing the converges rate by various techniques such as lazy dynamic programming~\cite{GSB15, JSCP15}, relaxing optimality to near-optimality~\cite{DB14, SH16} and more.
+%
+
+%In the most basic form, the motion-planning problem calls for computing \emph{a} path between two given states.
+%Indeed, 
+%However, recent years 
+%Original planners such as RRT~\cite{LK01} and PRM~\cite{KSLO96} did not provide any guarantee on the \emph{s}
 
@@
 
+\os{can our method be applied to produce samples on the medial axis?}
+
+S. A. Wilmarth, N. M. Amato, and P. F. Stiller. MAPRM: A prob-
+abilistic roadmap planner with sampling on the medial axis of the
+free space. In Proc. IEEE Int. Conf. Robot. Autom. (ICRA), pages
+1024–1031, 1999.
+
+S. A. Wilmarth, N. M. Amato, and P. F. Stiller. Motion planning for
+a rigid body using random networks on the medial axis of the free
+space. In Proc. ACM Symp. on Computational Geometry (SoCG),
+pages 173–180, 1999
+
 heuristic~\cite{US03, SWT09}
@@
 We are going to integrate this idea into our sampling framework of efficiently generating samples under kinetic constraints.
+
+\section{Problem definition}
+\label{sec:pdef}
+
+\subsection{general}
+
+\subsection{double integrator}
+Discuss how the informed set looks like
 

### 2017-01-27 paper.tex
for merge
additional refs

@@
 
-In the initial stages of the algorithm, 
+Initially, 
 when no path has yet to be found, 
 the samples need to be drawn from the entire state space~$\calX$.
-However, once a path $\gamma$ is produce,  algorithm that seek \emph{high-quality paths} can limit their sampling domain to a subset of~$\calX$  containing states that may produce higher-quality paths than $\gamma$.
+However, once a path $\gamma$ is produced,  algorithms that seek \emph{high-quality paths} can limit their sampling domain to a subset of~$\calX$  containing states that may produce higher-quality paths than~$\gamma$.
 Following Gammell et al.~\cite{GSB14}, we call this subset the \emph{informed subset} and denote it $\Cinf$.
@@
 Here, individual dimensions are sampled recursively 
-and then combined. Rejection sampling is performed for these partial samples until a suitable sample has been produced. The novelty of HRS is the ability to fail fast.
+and then combined. Rejection sampling is performed for these partial samples until a suitable sample has been produced. 
+%The novelty of HRS is the ability to fail fast.
 
@@
 \label{sec:related_work}
+We start in Sec.~\ref{subsec:planning} by giving an overview of relevant sampling-based motion-planning algorithms.
+We then continue in Sec.~\ref{subsec:sampling} to describe different approaches used to sample~$\calX$.
+We conclude our literature review in Sec.~\ref{subsec:mcmc} with a brief overview of Markov Chain Monte Carlo methods.
 
 \subsection{Planning}
+\label{subsec:planning}
+Initial sampling-based algorithms such as RRT~\cite{LK01} and PRM~\cite{KSLO96} did not take into account the \emph{quality} of a path, given some optimization criteria, and only guaranteed to asymptotically return \emph{a} solution, if one exists.
+Karaman and Frazzoli~\cite{KF11}, presented variants of PRM and RRT, named PRM* and RRT*, respectively that were shown to produce paths who's cost converges asymptotically to the minimal-cost path.
+Additional algorithms followed, increasing the converges rate by various techniques such as lazy dynamic programming~\cite{GSB15, JSCP15}, relaxing optimality to near-optimality~\cite{DB14, SH16} and more.
 
-Classic:\\
-RRT~\cite{LK01}
+Many of the algorithms mentioned require solving a two-point boundary value problem (2pBVP) to perform exact connections between vertices in the roadmap.
 
-PRM~\cite{KSLO96}
+Xie et al.~\cite{XBPA15} use a variant of sequential quadratic programming (SQP) to solve 2pBVP and integrate it with BIT*~\cite{GSB15}.
 
-AO:\\
-RRT*, PRM*~\cite{KF11}
-
-BIT*~\cite{GSB15}
-
-FMT*~\cite{JSCP15}
-
-Near AO:\\
-LBT-RRT~\cite{SH16}
-
-SPARSE~\cite{DB14}
+Webb and van den Berg~\cite{WB13} use a fixed-final-state-free-final-time controller to solve the 2pBVP  with respect to a cost function that is allows for balancing between the duration of the trajectory and the expended control effort.
 
@@
 
-Kinodynamic works:\\~\cite{SL14, XBPA15, WB13, KF10}
+Kinodynamic works:\\~\cite{KF10}
+
+Perez et al.~\cite{PPKKL12} propose a variant of RRT* that automatically defines a distance metric and node extension method by locally linearizing
+the domain dynamics and applying linear quadratic regulation (LQR).
+
+Goretkin et al.~\cite{GPPK13}
 
 \subsection{Sampling}
-
+\label{subsec:sampling}
 Hierarchical sampling~\cite{KTC16}.
@@
 \subsection{MCMC}
-
+\label{subsec:mcmc}
 Markov Chain Monte Carlo(MCMC)~\cite{ADDJ03} is a framework of sampling from a given probability distribution by constructing a Markov chain of random transition toward a desired distribution $ \pi (x) $ .

### 2017-01-28 paper.tex
new

@@
 
+We
+
 \section{Results}
+
+\subsection{Uniformity}
+
+(Give a set of parameters)
+We firstly need to propose a way of measuring uniformity.
+Then we can apply it to compare MCMC approach with rejection sampling and hierarchical rejection sampling.
+We are interested with
+\begin{itemize}
+	\item asymptotic behavior (assumption: MCMC converge to a close uniformity)
+	\item convergence rate (assumption: MCMC converge faster)
+\end{itemize}
+
+\subsection{Efficiency}
+
+The efficiency is shown by how the time is needed when the number of nodes are increased.
+(Y: time spent) and (X: number of nodes).
+
+\subsection{Integration}
+
+We're going to test with RRT*, which falls into a informed RRT*.
+
+We are going to show how the solution cost falls along time.
+(Y: solution cost) and (X: time spent).
+
+\begin{itemize}
+\item DIMT (double integrator minimum time)
+\item Dubins car
+\item Airplane
+\end{itemize}
 

### 2017-01-30 paper.tex
related work

@@
 the samples need to be drawn from the entire state space~$\calX$.
-However, once a path $\gamma$ is produced,  algorithms that seek \emph{high-quality paths} can limit their sampling domain to a subset of~$\calX$  containing states that may produce higher-quality paths than~$\gamma$.
-Following Gammell et al.~\cite{GSB14}, we call this subset the \emph{informed subset} and denote it $\Cinf$.
+However, once a path $\gamma$ is produced,  algorithms that seek \emph{high-quality paths}, which is the focus of this paper, can limit their sampling domain to a subset of~$\calX$  containing states that may produce higher-quality paths than~$\gamma$.
+Following Gammell et al.~\cite{GSB14}, we call this subset the \emph{informed subset} and denote it~$\Cinf$.
 
@@
 This may cause the search algorithm to spend most of its time trying to produces samples in~$\Cinf$ rather than explore it.
-In this paper, we suggest an alternative approach to sampling in the informed set \Cinf for a wide range of settings.
+In this paper, we suggest an alternative approach to produce samples in the informed set \Cinf for a wide range of settings.
 Our main insight is 
@@
 in the first, a random sample $x \in \calX$ is retracted to the boundary of~$\Cinf$ by running a gradient-descent algorithm;
-in the second stage, this retracted sample $\tilde{x}$ is used to seed a Monte Carlo sampling chain which allows us to approximately produce samples uniformly \emph{within}~$\Cinf$.
+in the second stage, this retracted sample $\tilde{x}$ is used to seed a Monte Carlo sampling chain which allows us to  produce samples that (approximately) cover~$\Cinf$  uniformly.
 
-Our approach requires that the system has a solution to the two-point boundary value problem (2pBVP)~\cite{} and that a gradient can be defined over the cost function.
+Our approach requires that the system has a solution to the two-point boundary value problem (2pBVP)~\cite{L06, H02} and that a gradient can be defined over the cost function.
 Indeed, we demonstrate the efficiency of our approach on a wide variety of systems and show that it enables reducing the planning time by several orders of magnitute when compared to algorithms using rejection sampling or HRS.
@@
 Karaman and Frazzoli~\cite{KF11}, presented variants of PRM and RRT, named PRM* and RRT*, respectively that were shown to produce paths who's cost converges asymptotically to the minimal-cost path.
+This is done by recognizing the underlying connections between stochastic sampling-based motion planning and the theory of random geometric graphs (see also~\cite{SSH16}).
 Additional algorithms followed, increasing the converges rate by various techniques such as lazy dynamic programming~\cite{GSB15, JSCP15}, relaxing optimality to near-optimality~\cite{DB14, SH16} and more.
 
-Many of the algorithms mentioned require solving a two-point boundary value problem (2pBVP) to perform exact connections between vertices in the roadmap.
+Many of the algorithms mentioned require solving a two-point boundary value problem (2pBVP) to perform exact and optimal connections between vertices in the roadmap.
+For holonomic robots, these are simply straight lines in the state space, but for kinodynamic sytems with arbitrary cost functions,  computing an optimal trajectory between two states is non-trivial in general.
 
 Xie et al.~\cite{XBPA15} use a variant of sequential quadratic programming (SQP) to solve 2pBVP and integrate it with BIT*~\cite{GSB15}.
-
-Webb and van den Berg~\cite{WB13} use a fixed-final-state-free-final-time controller to solve the 2pBVP  with respect to a cost function that is allows for balancing between the duration of the trajectory and the expended control effort.
-
-RGGS~\cite{SSH16}
-
-Kinodynamic works:\\~\cite{KF10}
-
+Webb and van den Berg~\cite{WB13} use a fixed-final-state-free-final-time controller to solve the 2pBVP  with respect to a cost function that allows for balancing between the duration of the trajectory and the expended control effort.
 Perez et al.~\cite{PPKKL12} propose a variant of RRT* that automatically defines a distance metric and node extension method by locally linearizing
@@
 
-Goretkin et al.~\cite{GPPK13}
+%Finally, we note that there have been many papers presenting solutions to the 2pBVP for specific systems such as
+%
+%Jeong Hwan Jeon, Raghvendra V.
+Cowlagi, Steven C.
+Peters, Sertac Karaman, Emilio Frazzoli, Panagiotis Tsiotras, Karl Iagnemma: Optimal motion planning with the half-car dynamical model for autonomous high-speed driving.
+ACC 2013: 188-193
+%Dubins cars optimizng for both time and energy (RSS submission 107 by Shammas, Elie)
+
+%possible additional papers on Kinodynamic RRT*:~\cite{KF10, GPPK13}
 
@@
 \label{subsec:sampling}
-Hierarchical sampling~\cite{KTC16}.
+There is a rich body of literature on how to produce samples that increase the efficiency of the planner in terms of finding a solution or producing high-quality solutions.
+Heuristic approaches include
+sampling on the medial axis~\cite{WAS99a, WAS99b, LTA03, YDLTA14},
+sampling near the boundary of the obstacles~\cite{ABDJV98, YTEA12},
+resampling along a given trajectory~\cite{APD11, AS11}
+and more~\cite{US03, SWT09}
 
-Informed sampling~\cite{GSB14}
-
-OBPRM~\cite{ABDJV98, YTEA12}
-
-Medial axis~\cite{LTA03, YDLTA14}
-
-\os{can our method be applied to produce samples on the medial axis?}
-
-S. A. Wilmarth, N. M. Amato, and P. F. Stiller. MAPRM: A prob-
-abilistic roadmap planner with sampling on the medial axis of the
-free space. In Proc. IEEE Int. Conf. Robot. Autom. (ICRA), pages
-1024–1031, 1999.
-
-S. A. Wilmarth, N. M. Amato, and P. F. Stiller. Motion planning for
-a rigid body using random networks on the medial axis of the free
-space. In Proc. ACM Symp. on Computational Geometry (SoCG),
-pages 173–180, 1999
-
-heuristic~\cite{US03, SWT09}
+Of specific interest to our work are approaches that produce samples in the informed set~\Cinf.
+As mentioned in Sec.~\ref{sec:intro} Gammel et al.~\cite{GSB14} describe an approach to sample uniformly in~\Cinf for the specific case of where $\calX = \R^d$ and when optimizing for path length.
+To the best of our knowledge, the only method to produce samples in non-Euclidean spaces (other than rejection sampling) is HRS by Kunz et al.~\cite{KTC16}.
 
@@
 \label{subsec:mcmc}
-Markov Chain Monte Carlo(MCMC)~\cite{ADDJ03} is a framework of sampling from a given probability distribution by constructing a Markov chain of random transition toward a desired distribution $ \pi (x) $ .
+Markov Chain Monte Carlo (MCMC)~\cite{ADDJ03} is a framework of sampling from a given probability distribution by constructing a Markov chain of random transition toward a desired distribution $ \pi (x) $.
 A set of samples are generated to approximate the desired distribution $ \pi (x) $.
@@
 
+\section{Motivating example---Minimal Time Double Integrator}
+We start by considering a simple yet important motion-planning problem
+
+The double integrator is a simple yet im-
+portant example that nicely illustrates the phase space. Suppose that a second-
+order differential equation is given as q  ̈ = u, in which q and u are chosen from R
+
 \section{Problem definition}
 \label{sec:pdef}
+
+\subsection{Minimal Time Double Integrator (MTDI)}
+In this paper we demonstrate our approach for the specific case of a double integrator system when the objective function is minimizing the trajectory execution time.
+
+Minimal Time Double Integrator
 

### 2017-01-30 paper.tex
rewrite MCMC

@@
 It adopts physical system dynamics to propose future states in the Markov chain.
-The concept origins from Hamiltonian dynamics, which models the movement of an object.
-Given the position $ x $ and the momentum $ q $ of an object, the system energy can be written as $ H(x,q) = U(x) + K(q) $, in which $ U(x) $ is the potential energy and $ K(q) $ is the kinetic energy.
-The movement of the object (how $ x $ and $ q $ change over time) is determined by
+The concept origins from Hamiltonian dynamics, which models the movement of an object, the position $ x $ and the momentum $ q $ over time $ t $.
+Define a system energy $ H $ of an object that consists of kinetic energy $ K $ and potential energy $ U $, which is written as $ H(x,q) = U(x) + K(q) $.
+The kinetic energy $ K(q) $ is determined by the momentum $ q $ of the object, while the potential energy $ U(x) $ is determined by the position $ x $ of the object.
+By the Hamiltonian equation, the movement of the object can be predicted by
 $ \frac{dx}{dt} = \frac{\partial H}{\partial q} $ and $ \frac{dq}{dt} = - \frac{\partial H}{\partial x} $.
-By the association between energy and a canonical distribution, a joint distribution for the states $ x $ and $ q $ can be created from a Hamiltonian dynamics, which is 
-$ P(x, q) = \frac{1}{Z} \exp ( -H(x,q) / T ) = \frac{1}{Z} \exp ( -U(x) / T) \exp (-K(q) / T) $.
-If we define $ U(x) = - \log ( \pi(x) T ) $, $ P(x, q) $ can be rewritten as $ P(x, q) = \pi (x) \frac{1}{Z} \exp (-K(q) / T) $.
-Because the state $ x $ and the the momentum  $ q $ are independent, we can sample $ [ x ,q ] $ from $ P(x, q) $ and discard the momentum $ q $ (as an auxiliary variable).
+This provides an approach of the gradient descent by following the decrease of an associated potential energy.
+Thus, HMC simulates the Hamiltonian dynamics that moves samples towards a target distribution while avoiding random walks.
+
+A canonical distribution bridges an energy with a probability distribution.
+If two different states have the same energy, the probabilities of them are equivalent.
+A set of samples from such a distribution can be equivalent to a set of samples driven by an associated energy.
+By using the system energy $ H(x, q) $, we can defines a canonical distribution $ P(x, q) = \frac{1}{Z} \exp ( -H(x,q) / T ) $.
+Because $ H(x,q) = U(x) + K(q) $, $ P(x, q) $ can be factorized into two independent terms, which is written as $ P(x, q) = \frac{1}{Z} \exp ( -U(x) / T) \exp (-K(q) / T) $.
+The independence implies that we can sample $ [ x ,q ] $ from $ P(x, q) $ and discard the momentum $ q $ (as an auxiliary variable) in order to sample from a canonical distribution $ \propto \exp ( -U(x) / T) $.
+If we have a target distribution $ \pi(x) $ of state $ x $ and define a potential energy in the form $  U(x) = - \log ( \pi(x) T ) $, we can have the canonical distribution equal to $ \pi(x) $.
 The collected set of $ x $ is equivalent to sampling from $ \pi(x) $.
+Thus, we can use simulating the Hamiltonian dynamics to generate a set of samples from a target distribution $ \pi (x) $.
+
 We are going to integrate this idea into our sampling framework of efficiently generating samples under kinetic constraints. 
+We define a target distribution as a uniform distribution subject to kinetic constraints and cost budgets.
 

### 2017-01-30 paper.tex
MTDI

--- 2017-01-30 paper.tex
@@
 
-\section{Motivating example---Minimal Time Double Integrator}
-We start by considering a simple yet important motion-planning problem
+\section{Motivating example---Minimal-Time Double Integrator}
+We start by considering a simple yet important motion-planning problem---the double integrator.
+We are given a one-dimensional point robot  with bounded velocity and bounded acceleration moving amid obstacles. We wish to compute the minimal-time trajectory between two states $x_s, x_g$.
+A state in this model is described by 
+the position $q \in \R$
+and
+the velocity $\dot{q}\in \R$ of the position
+%each coordinate axis.
+The dynamics of the system is described by:
+$$
+x = (q, \dot{q}); 
+\hspace{5mm}
+u = \ddot{q}.
+$$
+Here, the control $u [u_{\text{min}}, u_{\text{max}}]$ is the (bounded) acceleration.
 
-The double integrator is a simple yet im-
-portant example that nicely illustrates the phase space. Suppose that a second-
-order differential equation is given as q  ̈ = u, in which q and u are chosen from R
+Notice that 
+(i)~this is model can be seen as a simplified one-dimensional instance of a robot manipulator with many degrees of freedom and that
+(ii)~closed form solutions exist to the 2pBVP for this specific case (as well as the generalized instance)~\cite{HN10}.
 
-\section{Problem definition}
-\label{sec:pdef}
+Let $T(x_1, x_2)$ denote the minimal time to move the robot from state $x_1$ to $x_2$.
+Further, set
+$$
+T(x) = T(x_s, x) + T(x, x_g).
+$$ 
+Namely, $T(x)$ is the minimal time to reach the goal from the start subject to passing through the state $x$.
 
-\subsection{Minimal Time Double Integrator (MTDI)}
-In this paper we demonstrate our approach for the specific case of a double integrator system when the objective function is minimizing the trajectory execution time.
+\subsection{Informed set}
+Recall that for Euclidean spaces minimizing path length, the informed set is a prolate hyperspheroid.
+Moreover, this ellipsoid is defined only be the cost $\hat{c}$ of the current best solution and not by the location of the start and goal.
 
-Minimal Time Double Integrator
+For the case of a double integrator, this is not the case:
+\os{show the explicit math and that it depends on the location of the start and goal}
 
-\subsection{general}
-
-\subsection{double integrator}
-Discuss how the informed set looks like
+See Fig.~\ref{fig:informed_1d_di}.
+\begin{figure}[tb]
+  \centering
+  	\includegraphics[height = 4.cm ]{level_set.jpg}
+  \caption{
+    \captionstyle
+  	Level sets for the case of minimal-time double integrator.
+A point $x = (q, \dot{q})$  denote the position and velocity of the robot while the color at $x$ denotes the cost to reach $x_t$ from $x_s$ subject to passing through the state $x$.
+  	}
+   	\label{fig:informed_1d_di}
+	\vspace{-5.5mm}
+\end{figure}
 

### 2017-02-01 paper.tex
merge:
trim
fix some writing

@@
 By using the system energy $ H(x, q) $, we can defines a canonical distribution $ P(x, q) = \frac{1}{Z} \exp ( -H(x,q) / T ) $.
-Because $ H(x,q) = U(x) + K(q) $, $ P(x, q) $ can be factorized into two independent terms, which is written as $ P(x, q) = \frac{1}{Z} \exp ( -U(x) / T) \exp (-K(q) / T) $.
-The independence implies that we can sample $ [ x ,q ] $ from $ P(x, q) $ and discard the momentum $ q $ (as an auxiliary variable) in order to sample from a canonical distribution $ \propto \exp ( -U(x) / T) $.
+We can sample $ [ x ,q ] $ from $ P(x, q) $ and discard the momentum $ q $ (as an auxiliary variable) in order to sample from a marginal distribution $ P(x) $.
 If we have a target distribution $ \pi(x) $ of state $ x $ and define a potential energy in the form $  U(x) = - \log ( \pi(x) T ) $, we can have the canonical distribution equal to $ \pi(x) $.
@@
 Thus, we can use simulating the Hamiltonian dynamics to generate a set of samples from a target distribution $ \pi (x) $.
+The properties of Hamiltonian dynamics guarantees so that the proposals will always be accepted, which accelerates the convergence rate.
 

### 2017-02-01 paper.tex
minor changes

--- 2017-01-30 paper.tex
@@
 \title{\LARGE \bf
-Informed sampling by Markov Chain Monte Carlo methods
+Informed sampling for kinodynamic planning by \\ Markov Chain Monte Carlo methods
 }
@@
 the samples need to be drawn from the entire state space~$\calX$.
-However, once a path $\gamma$ is produced,  algorithms that seek \emph{high-quality paths}, which is the focus of this paper, can limit their sampling domain to a subset of~$\calX$  containing states that may produce higher-quality paths than~$\gamma$.
+However, once a path $\gamma$ is produced,  algorithms that seek \emph{high-quality paths} can limit their sampling domain to a subset of~$\calX$ only  containing states that may produce higher-quality paths than~$\gamma$.
 Following Gammell et al.~\cite{GSB14}, we call this subset the \emph{informed subset} and denote it~$\Cinf$.
+\textbf{In this work we address the problem of efficiently producing samples in informed subset for systems with differential constraints}.
 
@@
 In this paper, we suggest an alternative approach to produce samples in the informed set \Cinf for a wide range of settings.
-Our main insight is 
-\os{this is a very important sentence!!!}
+\textbf{Our main insight is to formulate the problem as the problem of sampling uniformly below a level set of an implicit function and then apply optimization and statistical tools.}
 Specifically, our approach consists of two stages:
@@
 $$
-Here, the control $u [u_{\text{min}}, u_{\text{max}}]$ is the (bounded) acceleration.
+Here, the control $u \in [u_{\text{min}}, u_{\text{max}}]$ is the (bounded) acceleration.
 

### 2017-02-01 paper.tex
rewrite some of MCMC

--- 2017-02-01 paper.tex
@@
 \label{subsec:mcmc}
+
 Markov Chain Monte Carlo (MCMC)~\cite{ADDJ03} is a framework of sampling from a given probability distribution by constructing a Markov chain of random transition toward a desired distribution $ \pi (x) $.
 A set of samples are generated to approximate the desired distribution $ \pi (x) $.
-Unlike a rejection sampling, MCMC does a random walk in a parametric space and concentrates on an important areas, which usually brings better efficiency.
+A approximated desired distribution $ \hat{\pi} (x) $ can be used in any problem that states are modeled random variable, e.g.
+motion tracking~\cite{KBD04}, data regression~\cite{TL11} and state estimation~\cite{ASC13}.
+Unlike a rejection sampling, MCMC does a random walk in a parametric space and concentrates on an important area, which usually brings better efficiency.
 Hamiltonian Monte Carlo(HMC)~\cite{N11} is introduced to provide better efficiency in converging to a desired distribution.
@@
 \section{Motivating example---Minimal-Time Double Integrator}
-We start by considering a simple yet important motion-planning problem---the double integrator.
+
+We start by considering a simple yet important dynamical system---the double integrator. 
 We are given a one-dimensional point robot with bounded velocity and bounded acceleration moving amid obstacles. We wish to compute the minimal-time trajectory between two states $x_s, x_g$.

### 2017-02-02 paper.tex
?
key sentences

--- 2017-02-01 paper.tex
@@
 \title{\LARGE \bf
-Informed sampling for kinodynamic planning by \\ Markov Chain Monte Carlo methods
+Informed sampling by Markov Chain Monte Carlo methods
 }
@@
 Cole Gulino$^{*}$,
-Daqing YI$^{}$,
+Daqing Yi$^{}$,
 Oren Salzman$^{}$ and
@@
 %
-
-%In the most basic form, the motion-planning problem calls for computing \emph{a} path between two given states.
-%Indeed, 
 %However, recent years 

### 2017-02-06 paper.tex
polishing

@@
 Following Gammell et al.~\cite{GSB14}, we call this subset the \emph{informed subset} and denote it~$\Cinf$.
-\textbf{In this work we address the problem of efficiently producing samples in informed subset for systems with differential constraints}.
+\textbf{In this work we address the problem of efficiently producing samples in the informed subset for systems with differential constraints}.
 
@@
 %
-One approach to produce samples in \Cinf is via \emph{rejection sampling}---sampling a state $x \in \calX$ and testing if $x \in \Cinf$.
+One approach to produce samples in \Cinf is via \emph{rejection sampling}---sampling a state $x \in \calX$ and then testing if $x \in \Cinf$.
 However, when the size of the informed space~$\Cinf$ is much smaller than entire state space~$\calX$, then this procedure may dominate the running time of the algorithm~\cite{KTC16}.
@@
 in the first, a random sample $x \in \calX$ is retracted to the boundary of~$\Cinf$ by running a gradient-descent algorithm;
-in the second stage, this retracted sample $\tilde{x}$ is used to seed a Monte Carlo sampling chain which allows us to  produce samples that (approximately) cover~$\Cinf$  uniformly.
+in the second stage, this retracted sample~$\tilde{x}$ is used to seed a Monte Carlo sampling chain which allows us to  produce samples that (approximately) cover~$\Cinf$  uniformly.
 
@@
 Karaman and Frazzoli~\cite{KF11}, presented variants of PRM and RRT, named PRM* and RRT*, respectively that were shown to produce paths who's cost converges asymptotically to the minimal-cost path.
-This is done by recognizing the underlying connections between stochastic sampling-based motion planning and the theory of random geometric graphs (see also~\cite{SSH16}).
-Additional algorithms followed, increasing the converges rate by various techniques such as lazy dynamic programming~\cite{GSB15, JSCP15}, relaxing optimality to near-optimality~\cite{DB14, SH16} and more.
+This was done by recognizing the underlying connections between stochastic sampling-based motion planning and the theory of random geometric graphs (see also~\cite{SSH16}).
+Additional algorithms followed, increasing the converges rate by using various techniques such as lazy dynamic programming~\cite{GSB15, JSCP15}, relaxing optimality to near-optimality~\cite{DB14, SH16} and more.
 
@@
 Notice that 
-(i)~this is model can be seen as a simplified one-dimensional instance of a robot manipulator with many degrees of freedom and that
+(i)~this model can be seen as a simplified one-dimensional instance of a robot manipulator with many degrees of freedom and that
 (ii)~closed form solutions exist to the 2pBVP for this specific case (as well as the generalized instance)~\cite{HN10}.
@@
 Let $T(x_1, x_2)$ denote the minimal time to move the robot from state $x_1$ to $x_2$.
-Further, set
+Furthermore, set
 $$

### 2017-02-06 paper.tex
rewrite mcmc

@@
 
-Markov Chain Monte Carlo (MCMC)~\cite{ADDJ03} is a framework of sampling from a given probability distribution by constructing a Markov chain of random transition toward a desired distribution $ \pi (x) $.
-A set of samples are generated to approximate the desired distribution $ \pi (x) $.
+An alternative sampling framework, which is widely used in statistical machine learning, is Monte Carlo Simulation~\cite{M97}.
+It uses the numerical experimental power of computers to generate samples toward a desired distribution $ \pi (x) $.
+The generated set of samples are a discrete approximation $ \hat{\pi} (x) $ of the desired distribution $ \pi (x) $.
 A approximated desired distribution $ \hat{\pi} (x) $ can be used in any problem that states are modeled random variable, e.g.
 motion tracking~\cite{KBD04}, data regression~\cite{TL11} and state estimation~\cite{ASC13}.
-Unlike a rejection sampling, MCMC does a random walk in a parametric space and concentrates on an important area, which usually brings better efficiency.
-Hamiltonian Monte Carlo(HMC)~\cite{N11} is introduced to provide better efficiency in converging to a desired distribution.
-It adopts physical system dynamics to propose future states in the Markov chain.
-The concept origins from Hamiltonian dynamics, which models the movement of an object, the position $ x $ and the momentum $ q $ over time $ t $.
-Define a system energy $ H $ of an object that consists of kinetic energy $ K $ and potential energy $ U $, which is written as $ H(x,q) = U(x) + K(q) $.
+
+Markov Chain Monte Carlo (MCMC)~\cite{ADDJ03} is one most popular class that constructs a Markov chain of random transition that moves samples from an original proposed distribution to a desired distribution $ \pi (x) $.
+Unlike a rejection sampling, MCMC does a random walk in a parametric space and concentrates on an important area.
+Though the convergence to the desired distribution is proved to be guaranteed, the nature of random walk determines that the convergence of MCMC can be slow in a high-dimensional space.
+Hamiltonian Monte Carlo(HMC)~\cite{N11} is thus introduced to reduce the random walk but directly moving to the target by heuristic.
+
+HMC adopts physical system dynamics to propose future states in the Markov chain~\cite{N11}.
+It is named ``Hamiltonian, because the concept origins from Hamiltonian dynamics, which associates the system energy with the resulting dynamics.
+Define the system dynamics of an object as the position $ x $ and the momentum $ q $ over time $ t $.
+We can have a system energy $ H $ of the object that consists of kinetic energy $ K $ and potential energy $ U $, which is written as $ H(x,q) = U(x) + K(q) $.
 The kinetic energy $ K(q) $ is determined by the momentum $ q $ of the object, while the potential energy $ U(x) $ is determined by the position $ x $ of the object.
-By the Hamiltonian equation, the movement of the object can be predicted by
+The Hamiltonian dynamics is determined by the gradients of the system energy, which is
 $ \frac{dx}{dt} = \frac{\partial H}{\partial q} $ and $ \frac{dq}{dt} = - \frac{\partial H}{\partial x} $.
-This provides an approach of the gradient descent by following the decrease of an associated potential energy.
-Thus, HMC simulates the Hamiltonian dynamics that moves samples towards a target distribution while avoiding random walks.
+In HMC, the state to be sampled is used as the position $ x $, and the associated probability $ P(x) $ is defined as the kinematic energy $ K(x) $.
+An auxiliary variable is used as the momentum $ q $, which is associated with another probability that is defined as the potential energy $ U(q) $.
+Thus, the system energy $ H(x, q) $ is associated with a joint probability $ P(x, q) $. 
+As we are interested with sampling from marginal probability $ P(x) $ is interested, we will sample $ [ x ,q ] $ from $ P(x, q) $ and discard the momentum $ q $ as an indirect way of sampling.
 
-A canonical distribution bridges an energy with a probability distribution.
+The canonical distribution is often choose to bridge a system energy with a probability distribution, which is written as $ P(x, q) = \frac{1}{Z} \exp ( -H(x,q) / T ) $.
 If two different states have the same energy, the probabilities of them are equivalent.
-A set of samples from such a distribution can be equivalent to a set of samples driven by an associated energy.
-By using the system energy $ H(x, q) $, we can defines a canonical distribution $ P(x, q) = \frac{1}{Z} \exp ( -H(x,q) / T ) $.
-We can sample $ [ x ,q ] $ from $ P(x, q) $ and discard the momentum $ q $ (as an auxiliary variable) in order to sample from a marginal distribution $ P(x) $.
-If we have a target distribution $ \pi(x) $ of state $ x $ and define a potential energy in the form $  U(x) = - \log ( \pi(x) T ) $, we can have the canonical distribution equal to $ \pi(x) $.
+Given a target distribution $ \pi(x) $, the potential energy is defined in the form $  U(x) = - \log ( \pi(x) T ) $.
+
+If we have of state $ x $ and define a potential energy , we can have the canonical distribution equal to $ \pi(x) $.
 The collected set of $ x $ is equivalent to sampling from $ \pi(x) $.

### 2017-02-07 paper.tex
Merge Cole's commit

@@
 Initially, 
-when no path has yet to be found, 
+when a path has yet to be found, 
 the samples need to be drawn from the entire state space~$\calX$.
@@
 Following Gammell et al.~\cite{GSB14}, we call this subset the \emph{informed subset} and denote it~$\Cinf$.
-\textbf{In this work we address the problem of efficiently producing samples in the informed subset for systems with differential constraints}.
+\textbf{In this work we address the problem of efficiently producing samples in informed subset for systems with differential constraints}.
 
 For Euclidean spaces optimizing for path length, 
-\Cinf can be analytically expresses as a prolate hyperspheroid and can be sampled directly~\cite{GSB14}.
+\Cinf can be analytically expressed as a prolate hyperspheroid and can be sampled directly using a closed form solution~\cite{GSB14}.
 Indeed, directly sampling in \Cinf has been shown to dramatically improve computation time when compared to sampling in $\calX$, especially in high dimensions.
@@
 %
-One approach to produce samples in \Cinf is via \emph{rejection sampling}---sampling a state $x \in \calX$ and then testing if $x \in \Cinf$.
+One approach to produce samples in \Cinf is via \emph{rejection sampling}---sampling a state $x \in \calX$ and testing if $x \in \Cinf$.
 However, when the size of the informed space~$\Cinf$ is much smaller than entire state space~$\calX$, then this procedure may dominate the running time of the algorithm~\cite{KTC16}.
@@
 in the first, a random sample $x \in \calX$ is retracted to the boundary of~$\Cinf$ by running a gradient-descent algorithm;
-in the second stage, this retracted sample~$\tilde{x}$ is used to seed a Monte Carlo sampling chain which allows us to  produce samples that (approximately) cover~$\Cinf$  uniformly.
+in the second stage, this retracted sample $\tilde{x}$ is used to seed a Monte Carlo sampling chain which allows us to  produce samples that (approximately) cover~$\Cinf$  uniformly.
 
@@
 Karaman and Frazzoli~\cite{KF11}, presented variants of PRM and RRT, named PRM* and RRT*, respectively that were shown to produce paths who's cost converges asymptotically to the minimal-cost path.
-This was done by recognizing the underlying connections between stochastic sampling-based motion planning and the theory of random geometric graphs (see also~\cite{SSH16}).
-Additional algorithms followed, increasing the converges rate by using various techniques such as lazy dynamic programming~\cite{GSB15, JSCP15}, relaxing optimality to near-optimality~\cite{DB14, SH16} and more.
+This is done by recognizing the underlying connections between stochastic sampling-based motion planning and the theory of random geometric graphs (see also~\cite{SSH16}).
+Additional algorithms followed, increasing the converges rate by various techniques such as lazy dynamic programming~\cite{GSB15, JSCP15}, relaxing optimality to near-optimality~\cite{DB14, SH16} and more.
 
@@
 and
-the velocity $\dot{q}\in \R$ of the position
+the velocity $\dot{q}\in \R$ of the position.
 %each coordinate axis.
 The dynamics of the system is described by:
-$$
+
+\begin{equation}
 x = (q, \dot{q}); 
@@
 u = \ddot{q}.
-$$
+\end{equation}
+
 Here, the control $u \in [u_{\text{min}}, u_{\text{max}}]$ is the (bounded) acceleration.
@@
 Notice that 
-(i)~this model can be seen as a simplified one-dimensional instance of a robot manipulator with many degrees of freedom and that
+(i)~this is model can be seen as a simplified one-dimensional instance of a robot manipulator with many degrees of freedom and that
 (ii)~closed form solutions exist to the 2pBVP for this specific case (as well as the generalized instance)~\cite{HN10}.
@@
 Let $T(x_1, x_2)$ denote the minimal time to move the robot from state $x_1$ to $x_2$.
-Furthermore, set
-$$
+
+Further, set
+\begin{equation}
 T(x) = T(x_s, x) + T(x, x_g).
-$$ 
+\end{equation}
+
 Namely, $T(x)$ is the minimal time to reach the goal from the start subject to passing through the state $x$.
@@
 
-For the case of a double integrator, this is not the case:
-\os{show the explicit math and that it depends on the location of the start and goal}
+For the case of a double integrator, this is not the case.
+Intuitively, one can see why.
+According the the double-integrator minimum time model, maximum acceleration is applied in one direction to a point, and then maximum acceleration in the other direction is applied to complete the motion.
+The direction of the first and second acceleration depends on the start and goal state.
 
-See Fig.~\ref{fig:informed_1d_di}.
+See Fig. ~\ref{fig:sample_dimt} for an example motion of one joint through the $\left(x,\dot{x}\right)$ space.
+
 \begin{figure}[tb]
   \centering
-  	\includegraphics[height = 4.cm ]{level_set.jpg}
+  	\includegraphics[width=0.3\textwidth]{fig/example_motion.png}
+  \caption{
+    \captionstyle
+  	Example possible motion using the double-integrator minimum time model between start state $(x_1, \dot{x_1}$ and goal state $(x_2, \dot{x_2}$ through some intermediate state $(x_i, \dot{x_i})$.
+  	}
+   	\label{fig:sample_dimt}
+\end{figure}
+
+In order to find the minimum time, $T\left(x\right)$, of a motion like Fig.
+~\ref{fig:sample_dimt}, we can examine the paths separately with one corresponding to a motion with acceleration $a_1$ from $\left(x_1, \dot{x}_1\right)$ to $\left(x_i, \dot{x}_i\right)$ and another corresponding to motion with acceleration $a_2$ from $\left(x_i, \dot{x}_i\right)$ to $\left(x_2, \dot{x}_2\right)$.
+
+\ref{} shows that we can express total distance travelled in the joint space $x$ can be expressed in this way as:
+
+\begin{equation}
+x_2 - x_1 = d_{a_1} + d_{a_2}
+\end{equation}
+where $d_{a_1}$ is the distance travelled at max acceleration from the first path and $d_{a_2}$ is the distance travelled at max acceleration in the opposite direction.
+
+Using simple constant acceleration equations we can express this in the form:
+
+\begin{equation}
+x_2 - x_1 = \left(\dot{x}_1 t_{a_1} + \frac{1}{2} a_1 t_{a_1}^2\right) + \left(\frac{\dot{x}_2^2 - \dot{x}_i^2}{2a_2}\right)
+\end{equation}
+where $t_{a_1}$ is the time it takes to make the path from $\left(x_1, \dot{x}_1\right)$ to $\left(x_i, \dot{x}_i\right)$ at acceleration $a_1$ and $t_{a_2}$ is the time it takes to make the path from $\left(x_i, \dot{x_i}\right)$ to $\left(x_2, \dot{x}_2\right)$ at acceleration $a_2$.
+
+We can further expand the equation in order to put it into the canonical quadratic equation as follows:
+
+\begin{equation}
+a_1 t_{a_1}^2 + 2 \dot{x}_1 t_{a_1} + \frac{\dot{x}_2^2 - \dot{x}_1^2}{2a_2} - \left(x_2 - x_1\right) = 0
+\end{equation}
+
+Following ~\ref{} we solve a quadratic equation of the form $at^2+bt+c=0$ as follows:
+
+$$
+q = -\frac{1}{2}\left(b + \text{sign}\left(b\right)\sqrt{b^2 - 4ac}\right)
+$$
+$$
+t_1 = \frac{q}{a}; \hspace{5mm} t_2 = \frac{c}{q}
+$$
+where $t_1$ and $t_2$ are the two solutions to the quadratic equation.
+
+As we know, time must be positive and we are looking for minimum time.
+This leads to the fact that there is only one correct solution to the quadratic equation.
+Because of this, depending on the start and goal states, the sign of the acceleration on each path will change.
+
+Again following ~\ref{}, we programatically solve for the sign of the sign of the acceleration by analysing the start and goal position.
+Fig.
+~\ref{fig:sample_dimt} shows the determining term $\Delta x_{acc}$, which is the distance from $x_1$ to the point where $\dot{x} = \dot{x}_2$.
+
+And using constant acceleration equations with ~\ref{} again, we find that:
+
+\begin{equation}
+\Delta x_{acc} = \frac{1}{2} \left(\dot{x}_1 + \dot{x}_2\right) \frac{|\dot{x}_2 - \dot{x}_1|}{a_{max}}
+\end{equation}
+
+\begin{equation}
+a_1 = - a_2 = \text{sign}\left(x_2 - x_2 - \Delta x_{acc}\right) a_{max}
+\end{equation}
+
+From these equations it shows a fundamental difference of a kinodynamic state space compared to a geometric state space.
+Because of this the minimum time path can vary in shape depending on the start and goal state.
+The consequence of this is that the shape of the informed subset can change dramatically depending on the start and goal state of the problem definition.
+Because of this, finding a closed form solution to sampling in the informed space is not feasible.
+
+See Fig.~\ref{fig:informed_1d_di} for a visualization of the cost surface for a specific start and goal state for one degree of freedom (two dimensions $\left(x, \dot{x}\right)$).
+Lower costs are represented with cooler colors with warmer colors representing higher costs.
+One can see the minimum cost path from start to goal as the dark blue curve.
+
+\begin{figure}[tb]
+  \centering
+  	\includegraphics[height = 4.cm ]{fig/level_set.jpg}
   \caption{
@@
 \end{figure}
+
+\begin{figure}[tb]
+  \centering
+  	\includegraphics[width=0.5\textwidth]{fig/kino_space.png}
+  \caption{
+    \captionstyle
+  	Side view of the cost surface for the case of minimal-time double integrator. The side view showcases the discontinuous nature of the cost surface.
+  	}
+   	\label{fig:cost_surface_1d}
+	\vspace{-5.5mm}
+\end{figure}
+
+See Fig.
+~\ref{fig:cost_surface_1d} for a side view of the cost surface for one degree of freedom ($\left(x, \dot{x}\right)$).
+One can see a key property of the cost surface that cause serious concerns is the discontinuous nature of the surface.
+As mentioned before, finding the minimum time problem amounts to solving a quadratic equation.
+Because the nature of this equation changes with the start and end goal, there is a curve in the input space that amounts to a switching surface that represents the boundary for the decision of the sign of $a_1$.
+This surface causes a discontinuous cost surface as shown in Fig.
+~\ref{fig:cost_surface_1d}.
 
@@
 
+\dy{I am not sure what we want to put into here, but I am going to continue on the discussion of the algorithm and talk about some of the probability stuff.}
+
+One of the major difficulties of sampling the informed level set is that the shape of the cost function can change dramatically with the start and goal states.
+Because of this, there is not a principled way to sample from the informed set for each possible start and goal combination.
+
+Following the example of recent work in path planning algorithms such as ~\ref{} (CHOMP?), we propose to solve the problem of efficiently sampling uniformly in the level set by using Monte Carlo sampling methods.
+Monte Carlo sampling methods have been used in the statics and machine learning fields to sample from intractable posteriors.
+Monte Carlo methods have the desirable property that they are guaranteed to sample the true posterior as the number of steps goes toward infinity.
+
+In order to take advantage of these powerful methods, we propose to reformulate the cost surface as a probability density.
+Specifically, we consider a Boltzmann distribution in order to formulate the cost function using flexible energy based methods.
+Because Monte Carlo methods only consider the ratio of the probabilities, we do not need to consider the problem of estimating the intractable partition function.
+
+Formally, we consider the probability distribution to be a Boltzmann distribution in the form of:
+
+\begin{equation}
+P\left(t,t_0\right) = \frac{1}{Z}\exp\left(-E\left(t,t_0\right)\right)
+\end{equation}
+where $Z$ is the intractable partition function that denotes the normalizing constant of the distribution and  $E\left(t,t_0\right)$ is the energy function which is dependent on the current best cost, $t_0$, and the cost of the path in question $t$.
+
+The flexibility of the energy function is in the ability to specify desired or more probable states (by presenting lower energies) without the need to use a formal and restrictive model.
+Specifically for our problem, we defined the energy function to be:
+
+\begin{equation}
+E\left(t, t_0\right) = E_{\text{grad}}\left(t\right) + E_{\text{informed}}\left(t,t_0\right) + E_{\text{region}}\left(\mathbf{x}\right)
+\end{equation}
+
+\begin{equation}
+E_{\text{grad}}\left(t\right) = \sigma\left(t\right)
+\end{equation}
+where $\sigma\left(\cdot\right)$ is some function that controls the flatness of the distribution.
+Intuitively, this function prefers states with smaller costs.
+The flatter the function, the less pronounced this becomes.
+We experimented with using $\log\left(1 + \log\left(t\right)\right)$ and $\tanh\left(t\right)$.
+$\tanh$ resorts in a flatter distribution which may result in more uniform samples, but contains less gradient information for methods that use them such as Hamiltonian Monte Carlo.
+
+\begin{equation}
+E_{\text{informed}}\left(t,t_0\right) = \beta_{\text{informed}} \text{sigm}\left(t_0 - t\right)
+\end{equation}
+where $\text{sigm}\left(\cdot\right)$ represents a tight sigmoid function that can be seen as a differentiable $\text{sign}\left(\cdot\right)$ function.
+$\beta_{\text{informed}}$ is some large number that controls how much we want to penalize states outside of the level set.
+In theory, the energy should be infinity (which represents zero probability).
+In practice, however, setting $\beta_{\text{informed}}$ to be some high number such as $100$ works well and is more stable.
+
+\begin{equation}
+E_{\text{region}}\left(\mathbf{x}\right) = \beta_{\text{region}}||\mathbf{x}_{\text{limits}} - \mathbf{x}||_2
+\end{equation}
+where $||\mathbf{x}_{\text{limits}} - \mathbf{x}||_2$ represents the L2 distance between the current state $\mathbf{x}$ and the state limits $\mathbf{x}_{\text{limits}}$ and $\beta_{\text{region}}$ is some high number that controls how much to penalize states close to the limits.
+The same intuition for values of $\beta_{\text{region}}$ is the same as for $\beta_{\text{informed}}$.
+
+In order to ensure that the span the set of all possible states
+
 \begin{algorithm}
@@
 \end{algorithm}
-
-We
 

### 2017-02-07 paper.tex
need to check the last part of mcmc in related work
rewrite mcmc

@@
 Markov Chain Monte Carlo (MCMC)~\cite{ADDJ03} is one most popular class that constructs a Markov chain of random transition that moves samples from an original proposed distribution to a desired distribution $ \pi (x) $.
-Unlike a rejection sampling, MCMC does a random walk in a parametric space and concentrates on an important area.
-Though the convergence to the desired distribution is proved to be guaranteed, the nature of random walk determines that the convergence of MCMC can be slow in a high-dimensional space.
-Hamiltonian Monte Carlo(HMC)~\cite{N11} is thus introduced to reduce the random walk but directly moving to the target by heuristic.
+The random movement is driven by a jumping distribution $ g(x' \mid x) $, which samples a new state $ x' $ by a given state $ x $.
+The idea of MCMC is designing a jumping distribution $ g $ that makes the desired distribution a stationary distribution $ \pi = \pi * g $.
+\emph{Ergodic theorem} shows that if the jumping distribution is aperiodic, irreducible and positive recurrent~\cite{AG11}, samples generated from arbitrary distributions will gradually converge to the stationary (desired) distribution $ \pi $.
+In practice, samples are initially generated from an arbitrary distribution.
+They shall converge to the samples generated from the desired distribution () 
+A few MCMC algorithms, e.g. Gibbs sampling and Metropolis-Hastings, have been widely used in sampling from distributions that are difficult to directly sample.
 
-HMC adopts physical system dynamics to propose future states in the Markov chain~\cite{N11}.
-It is named ``Hamiltonian, because the concept origins from Hamiltonian dynamics, which associates the system energy with the resulting dynamics.
+The nature of random walk in MCMC sometimes requires too many iterations to converge, especially in high-dimension state spaces.
+In consider of efficiency, Hamiltonian Monte Carlo(HMC)~\cite{N11} is thus introduced to replace random walk with Hamiltonian dynamics, which means that future states in the Markov chain is proposed from simulating system dynamics instead of sampling from a jumping distribution.
+It is named ``Hamiltonian, because the concept origins from Hamiltonian dynamics, which defines how system dynamics is determined by system energy.
 Define the system dynamics of an object as the position $ x $ and the momentum $ q $ over time $ t $.
-We can have a system energy $ H $ of the object that consists of kinetic energy $ K $ and potential energy $ U $, which is written as $ H(x,q) = U(x) + K(q) $.
+We have a system energy $ H $ of the object that consists of kinetic energy $ K $ and potential energy $ U $, which is written as $ H(x,q) = U(x) + K(q) $.
 The kinetic energy $ K(q) $ is determined by the momentum $ q $ of the object, while the potential energy $ U(x) $ is determined by the position $ x $ of the object.
@@
 $ \frac{dx}{dt} = \frac{\partial H}{\partial q} $ and $ \frac{dq}{dt} = - \frac{\partial H}{\partial x} $.
-In HMC, the state to be sampled is used as the position $ x $, and the associated probability $ P(x) $ is defined as the kinematic energy $ K(x) $.
-An auxiliary variable is used as the momentum $ q $, which is associated with another probability that is defined as the potential energy $ U(q) $.
-Thus, the system energy $ H(x, q) $ is associated with a joint probability $ P(x, q) $. 
-As we are interested with sampling from marginal probability $ P(x) $ is interested, we will sample $ [ x ,q ] $ from $ P(x, q) $ and discard the momentum $ q $ as an indirect way of sampling.
 
@@
 If two different states have the same energy, the probabilities of them are equivalent.
+It has been proved that properties of Hamiltonian dynamics ``leaves the canonical distribution invariant"~\cite{N11}, which means $ P(x, q) $ equals to a stationary distribution in MCMC.
+Thus, we can generate samples $ [ x , q ]^T $ from joint distribution $ p(x, q) $.
+
 Given a target distribution $ \pi(x) $, the potential energy is defined in the form $  U(x) = - \log ( \pi(x) T ) $.
+We can have $ P(x, q) = \pi(x) \frac{1}{Z'} \exp ( -K(q) / T ) $, which indicates that $ pi(x) $ is a marginal distribution of $ P(x, q) $.
+In HMC, we sample $ [ x ,q ] $ from $ P(x, q) $ and discard the momentum $ q $ so that the set of samples $ x $ equals to sampling from the marginal distribution $ \pi(x) $.
+The momentum $ q $ is used as an auxiliary variable.
 
-If we have of state $ x $ and define a potential energy , we can have the canonical distribution equal to $ \pi(x) $.
-The collected set of $ x $ is equivalent to sampling from $ \pi(x) $.
 Thus, we can use simulating the Hamiltonian dynamics to generate a set of samples from a target distribution $ \pi (x) $.
@@
 
-We are going to integrate this idea into our sampling framework of efficiently generating samples under kinetic constraints. 
+We are going to integrate this idea into our sampling framework of efficiently generating samples under system dynamic constraints. 
 We define a target distribution as a uniform distribution subject to kinetic constraints and cost budgets.

### 2017-02-07 paper.tex
rewrite mcmc

@@
 The momentum $ q $ is used as an auxiliary variable.
-
-Thus, we can use simulating the Hamiltonian dynamics to generate a set of samples from a target distribution $ \pi (x) $.
-The properties of Hamiltonian dynamics guarantees so that the proposals will always be accepted, which accelerates the convergence rate.
-
-We are going to integrate this idea into our sampling framework of efficiently generating samples under system dynamic constraints. 
-We define a target distribution as a uniform distribution subject to kinetic constraints and cost budgets.
+Avoiding random walk helps samplings converge to the desired distribution $ \pi(x) $ in higher rate~\cite{N11}.
 

### 2017-02-08 paper.tex
small fix

@@
     \captionstyle
-  	Example possible motion using the double-integrator minimum time model between start state $(x_1, \dot{x_1}$ and goal state $(x_2, \dot{x_2}$ through some intermediate state $(x_i, \dot{x_i})$.
+  	Example possible motion using the double-integrator minimum time model between start state $(x_1, \dot{x_1})$ and goal state $(x_2, \dot{x_2})$ through some intermediate state $(x_i, \dot{x_i})$.
   	}
@@
 
-Following the example of recent work in path planning algorithms such as ~\ref{} (CHOMP?), we propose to solve the problem of efficiently sampling uniformly in the level set by using Monte Carlo sampling methods.
+Following the example of recent work in path planning algorithms such as CHOMP~\cite{RZBS09}, we propose to solve the problem of efficiently sampling uniformly in the level set by using Monte Carlo sampling methods.
 Monte Carlo sampling methods have been used in the statics and machine learning fields to sample from intractable posteriors.

### 2017-02-08 paper.tex
high-level description of MCMC

@@
 
-\subsection{Planning}
+\subsection{Sampling-based motion-planning algorithms}
 \label{subsec:planning}
@@
 
-\subsection{Sampling}
+\subsection{State-space sampling}
 \label{subsec:sampling}
-There is a rich body of literature on how to produce samples that increase the efficiency of the planner in terms of finding a solution or producing high-quality solutions.
+There is a rich body of literature on how to produce samples that increase the efficiency of a planner in terms of finding a solution or producing high-quality solutions.
 Heuristic approaches include
@@
 
-\subsection{MCMC}
+\subsection{Markov Chain Monte Carlo (MCMC)}
 \label{subsec:mcmc}
+Monte Carlo simulation is a general sampling framework widely used in various domains such as
+statistical machine learning~\cite{M97},
+motion tracking~\cite{KBD04}, 
+data regression~\cite{TL11} and 
+state estimation~\cite{ASC13}.
+Roughly speaking, Monte Carlo simulation repeatedly samples a domain at random to approximate some value or function.
+One specific domain where Monte Carlo simulation is used which is of specific interest to us is generating draws from a desired distribution which is hard to sample directly.
 
+One of the popular classes of Monte Carlo simulation is 
+\emph{Markov Chain Monte Carlo} (MCMC)~\cite{ADDJ03}.
+Here, the samples are drawn by generating a Markov chain such that the distribution of points on the chain converges to the desired distribution.
+The Markov Chain can be generated by performing a random walk such as
+in Metropolis-Hastings~\cite{}
+or Gibbs sampling~\cite{}.
+Alternatively, samples on the chain can be generated by simulating Hamiltonian dynamics~\cite{} (instead of performing the random walk).
+This approach, termed Hybrid or Hamiltonian Monte Carlo (HMC)~\cite{} was shown to converge faster to the desired distribution, when compared to random-walk based MCMC algorithms.
+
+%\deprecated{
+\ignore{ which means that future states in the Markov chain is proposed from simulating system dynamics instead of sampling from a jumping distribution.
+%
+%
 An alternative sampling framework, which is widely used in statistical machine learning, is Monte Carlo Simulation~\cite{M97}.
+%
 It uses the numerical experimental power of computers to generate samples toward a desired distribution $ \pi (x) $.
@@
 motion tracking~\cite{KBD04}, data regression~\cite{TL11} and state estimation~\cite{ASC13}.
-
+%
 Markov Chain Monte Carlo (MCMC)~\cite{ADDJ03} is one most popular class that constructs a Markov chain of random transition that moves samples from an original proposed distribution to a desired distribution $ \pi (x) $.
@@
 A few MCMC algorithms, e.g. Gibbs sampling and Metropolis-Hastings, have been widely used in sampling from distributions that are difficult to directly sample.
-
+%
 The nature of random walk in MCMC sometimes requires too many iterations to converge, especially in high-dimension state spaces.
@@
 $ \frac{dx}{dt} = \frac{\partial H}{\partial q} $ and $ \frac{dq}{dt} = - \frac{\partial H}{\partial x} $.
-
+%
 The canonical distribution is often choose to bridge a system energy with a probability distribution, which is written as $ P(x, q) = \frac{1}{Z} \exp ( -H(x,q) / T ) $.
@@
 Thus, we can generate samples $ [ x , q ]^T $ from joint distribution $ p(x, q) $.
-
+%
 Given a target distribution $ \pi(x) $, the potential energy is defined in the form $  U(x) = - \log ( \pi(x) T ) $.
@@
 Avoiding random walk helps samplings converge to the desired distribution $ \pi(x) $ in higher rate~\cite{N11}.
+%
+}
 
@@
 We start by considering a simple yet important dynamical system---the double integrator. 
-We are given a one-dimensional point robot with bounded velocity and bounded acceleration moving amid obstacles. We wish to compute the minimal-time trajectory between two states $x_s, x_g$.
+We are given a one-dimensional point robot with bounded acceleration moving amid obstacles. We wish to compute the minimal-time trajectory between two states $x_s, x_g$.
 A state in this model is described by 
@@
 and
-the velocity $\dot{q}\in \R$ of the position.
+the velocity $\dot{q}\in \R$ of the robot.
 %each coordinate axis.
-The dynamics of the system is described by:
-
+The system dynamics are described by:
 \begin{equation}
@@
 \end{equation}
-
-Here, the control $u \in [u_{\text{min}}, u_{\text{max}}]$ is the (bounded) acceleration.
+Here, the control $u \in [u_{\text{min}}, u_{\text{max}}]$ is the (bounded) acceleration\footnote{One can also bound the velocity of the system.
+However, to simplify the exposition, we only constrain the system with acceleration bounds.}.
 
@@
 (i)~this is model can be seen as a simplified one-dimensional instance of a robot manipulator with many degrees of freedom and that
-(ii)~closed form solutions exist to the 2pBVP for this specific case (as well as the generalized instance)~\cite{HN10}.
+(ii)~closed form solutions exist to the 2pBVP for this specific case (as well as the multi-dimensional setting)~\cite{HN10, KS14}.
 
 Let $T(x_1, x_2)$ denote the minimal time to move the robot from state $x_1$ to $x_2$.
-
-Further, set
+Furthermore, set
+%
 \begin{equation}
@@
 \end{equation}
-
+%
 Namely, $T(x)$ is the minimal time to reach the goal from the start subject to passing through the state $x$.
@@
 
+\os{
+Roughly speaking, HMC views the system as an energy function for which Hamiltonian dynamics are simulated in fixed time steps.
+Thus, to sample from a desired distribution~$P$ using HMC, we need to convert the distribution to an energy function and vice-versa.
+This is done using the concept of a canonical distribution from statistical mechanics~\cite{}. 
+Given some energy function,~$E$, the canonical distribution over states has probability density function $P = \frac{1}{Z}\exp (-E/T)$, where $Z$ is a normalizing constant and $T$ is the temperature of the system.
+%Viewing this the opposite way, if we are interested in some distribution with density function $P$, we can obtain it as a canonical distribution with $T = 1$ by setting $E = -\log P - \log Z$, where $Z$ is any convenient positive constant
+Simulating Hamiltonian dynamics requires that the energy function defined is differentiable.
+}
+
 One of the major difficulties of sampling the informed level set is that the shape of the cost function can change dramatically with the start and goal states.

### 2017-02-08 paper.tex
continue some mcmc

@@
 The Markov Chain can be generated by performing a random walk such as
-in Metropolis-Hastings~\cite{}
-or Gibbs sampling~\cite{}.
-Alternatively, samples on the chain can be generated by simulating Hamiltonian dynamics~\cite{} (instead of performing the random walk).
-This approach, termed Hybrid or Hamiltonian Monte Carlo (HMC)~\cite{} was shown to converge faster to the desired distribution, when compared to random-walk based MCMC algorithms.
+in Metropolis-Hastings~\cite{ADDJ03} or Gibbs sampling~\cite{ADDJ03}.
+Alternatively, samples on the chain can be generated by simulating Hamiltonian dynamics~\cite{N11} (instead of performing the random walk).
+This approach, termed Hybrid or Hamiltonian Monte Carlo (HMC)~\cite{N11} was shown to converge faster to the desired distribution, when compared to random-walk based MCMC algorithms.
 
@@
 
-\section{Algorithm}
+\dy{add a math description}
+
+\section{Informed Sampling}
 \label{sec:algorithm}

### 2017-02-09 paper.tex
add problem definition and start mcmc sampling

@@
 The Markov Chain can be generated by performing a random walk such as
-in Metropolis-Hastings~\cite{ADDJ03} or Gibbs sampling~\cite{ADDJ03}.
-Alternatively, samples on the chain can be generated by simulating Hamiltonian dynamics~\cite{N11} (instead of performing the random walk).
+in Metropolis-Hastings~\cite{CG95} or Gibbs sampling~\cite{CK94}.
+Alternatively, samples on the chain can be generated by simulating Hamiltonian dynamics~\cite{N92} (instead of performing the random walk).
 This approach, termed Hybrid or Hamiltonian Monte Carlo (HMC)~\cite{N11} was shown to converge faster to the desired distribution, when compared to random-walk based MCMC algorithms.
@@
 
+\section{Informed Sampling}
+\label{sec:algorithm}
+
+Define the dynamics of a robot as 
+\begin{equation}
+\label{eq:kinematics}
+\dot{\bm{x}}(t) = f( \bm{x}(t) , \bm{u}(t) ), 
+\end{equation}
+in which $ \bm{x} \in \mathcal{X} \subseteq \mathbb{R}^n $ is the state of the robot, and $ \bm{u} \in \mathcal{U} \subseteq \mathbb{R}^m $ is the control input.
+The dynamics determines a state trajectory $ \pi $, given a duration $ T $, an initial state $ \bm{x}(0) $ and an initial input $ \bm{u}(0) $.
+The cost of a trajectory $ \pi $ is defined as the accumulated cost along the path, which is 
+\begin{equation}
+\label{eq:path_cost}
+c(\pi) = \int_0^{T} c( x(t), u(t) ) dt.
+\end{equation}
+Consider the obstacles in a workspace, we have $ \mathcal{X}_{free} \subseteq \mathcal{X} $.
+Consider the bounds of the control input, we have $ \mathcal{U}_{free} \subseteq \mathcal{U} $.
+The dynamics of the robot in Equation~\eqref{eq:kinematics}, free state space $  \mathcal{X}_{free} $ and free control input space $ \mathcal{U}_{free} $ determines a free trajectory space $ \Pi_{free} $, which contains all feasible trajectories $ \pi \in \Pi_{free} $.
+An optimal kinodynamic path-planning problem that finds a kinodynamic path minimizing the cost $ \pi^* = \max_{ \pi \in \Pi_{free} } c( \pi ) $ subject to constraints $ \bm{x} (t) \in \mathcal{X}_{free}  $ and $ \bm{u} (t) \in \mathcal{U}_{free} $.
+
+Informed sampling-based planning algorithms (e.g. Informed RRT*~\cite{GSB14}, BIT*~\cite{GSB15}) samples new states only from an \emph{informed set}.
+An informed set is a subspace $ X_f \subseteq \mathcal{X}_{free} $  that is possible to provide better solution than the current best $  X_f = \{ x \in \mathcal{X}_{free} \mid c ( \pi^*(x) ) < c_{best} \} $~\cite{GSB14}, in which $ \pi^*(x) $ means the optimal path from $ x_{init} $ to $ x_{goal} $ constrained to pass through $ x $ and $ c_{best} $ is the cost of the current best found.
+The current best $ c_{best} $ constrains eligible $ x $ indirectly by an implicit $ \pi^*(x) $.
+In an optimal kinodynamic path-planning problem, more constraints are considered in defining an informed set, which include the system dynamic constraint and the boundary of control input.
+If we consider a manifold that is defined by an informed set $ X_f $, the informed sampling becomes how to sample on this manifold in a high-dimensional space.
+
 \section{Motivating example---Minimal-Time Double Integrator}
@@
 \begin{equation}
-T(x) = T(x_s, x) + T(x, x_g).
+T(x_s, x, x_g) = T(x_s, x) + T(x, x_g).
 \end{equation}
 %
-Namely, $T(x)$ is the minimal time to reach the goal from the start subject to passing through the state $x$.
+Namely, $T(x_s, x, x_g)$ is the minimal time to reach the goal from the start subject to passing through the state $x$.
 
@@
 Recall that for Euclidean spaces minimizing path length, the informed set is a prolate hyperspheroid.
-Moreover, this ellipsoid is defined only be the cost $\hat{c}$ of the current best solution and not by the location of the start and goal.
+Moreover, this hyperspheroid is defined only be the cost $\hat{c}$ of the current best solution and not by the location of the start and goal.
 
@@
 
-See Fig. ~\ref{fig:sample_dimt} for an example motion of one joint through the $\left(x,\dot{x}\right)$ space.
+See Fig. ~\ref{fig:sample_dimt} for an example motion of one joint through the $\left(q,\dot{q}\right)$ space.
 
@@
 
-\dy{add a math description}
-
-\section{Informed Sampling}
-\label{sec:algorithm}
-
-Define the dynamics of a robot as 
-\begin{equation}
-\label{eq:kinematics}
-\dot{\bm{x}}(t) = f( \bm{x}(t) , \bm{u}(t) ), 
-\end{equation}
-in which $ \bm{x} \in \mathcal{X} \subseteq \mathbb{R}^n $ is the state of the robot, and $ \bm{u} \in \mathcal{U} \subseteq \mathbb{R}^m $ is the control input.
-The dynamics determines a state trajectory $ \pi $, given a duration $ T $, an initial state $ \bm{x}(0) $ and an initial input $ \bm{u}(0) $.
-The cost of a trajectory $ \pi $ is defined as the accumulated cost along the path, which is 
-\begin{equation}
-\label{eq:path_cost}
-c(\pi) = \int_0^{T} c( x(t), u(t) ) dt.
-\end{equation}
-Consider the obstacles in a workspace, we have $ \mathcal{X}_{free} \subseteq \mathcal{X} $.
-Consider the bounds of the control input, we have $ \mathcal{U}_{free} \subseteq \mathcal{U} $.
-The dynamics of the robot in Equation~\eqref{eq:kinematics}, free state space $  \mathcal{X}_{free} $ and free control input space $ \mathcal{U}_{free} $ determines a free trajectory space $ \Pi_{free} $, which contains all feasible trajectories $ \pi \in \Pi_{free} $.
-
-We can define an optimal kinodynamic path-planning problem that finds a kinodynamic path minimizing the cost in Definition \ref{defn:optimal_kino_path_planning}.
-\begin{defn}{ \textbf{Optimal Kinodynamic Path-Planning} }
-\label{defn:optimal_kino_path_planning}
-	Find an optimal path $  \pi^* $ that satisfies
-	\begin{itemize}
-	\item $\forall t \in [0,T] $, $ \bm{x} (t) \in \mathcal{X}_{free}  $ and $ \bm{u} (t) \in \mathcal{U}_{free} $;
-	\item $ \bm{x} (0) = x_{init} $, $ \bm{x} (T) = x_{goal} $, $ \bm{u} (0) = u_{init} $ and $ \bm{u} (T) = u_{goal} $; and
-	\item $ \pi^* = \max_{ \pi \in \Pi_{free} } c( \pi ) $. 
-	\end{itemize}
-\end{defn}
-
-\dy{Do we want to set an initial and a goal for the control input? Does this simplify the problem solving?}
+\section{MCMC-based Informed Sampling}
 
 \dy{I am not sure what we want to put into here, but I am going to continue on the discussion of the algorithm and talk about some of the probability stuff.}
+
+Rejection sampling is the simplest ways of constrained sampling~\cite{}, but is also known for high rejection-rate on a manifold in a high-dimensional space.
+Hierarchical Rejection Sampling (HRS) is thus proposed .... 
+However, the rejection rate is still relatively high~\cite{}.
+In this paper, we propose an informed sampling by an MCMC approach.
+In order to obtained uniformly sampling on a manifold, MCMC provides an approach that samples from a high-dimensional uniform distribution subject to a manifold constraint.
 

### 2017-02-09 paper.tex
move hmc
add intro paragraph for algorithm section

@@
 
-\dy{I am not sure what we want to put into here, but I am going to continue on the discussion of the algorithm and talk about some of the probability stuff.}
+%\dy{I am not sure what we want to put into here, but I am going to continue on the discussion of the algorithm and talk about some of the probability stuff.}
 
-Rejection sampling is the simplest ways of constrained sampling~\cite{}, but is also known for high rejection-rate on a manifold in a high-dimensional space.
-Hierarchical Rejection Sampling (HRS) is thus proposed .... 
-However, the rejection rate is still relatively high~\cite{}.
+Rejection sampling is the simplest ways of constrained sampling~\cite{CRCW04}, but is also known for high rejection-rate on a manifold in a high-dimensional space~\cite{KTC16}.
+Hierarchical Rejection Sampling (HRS)~\cite{KTC16} is thus proposed that sequentially samples each dimension so that an unqualified candidate can be rejected before all dimensions are sampled. 
+However, the rejection rate is still relatively high~\cite{KTC16}.
 In this paper, we propose an informed sampling by an MCMC approach.
 In order to obtained uniformly sampling on a manifold, MCMC provides an approach that samples from a high-dimensional uniform distribution subject to a manifold constraint.
-
-\os{
-Roughly speaking, HMC views the system as an energy function for which Hamiltonian dynamics are simulated in fixed time steps.
-Thus, to sample from a desired distribution~$P$ using HMC, we need to convert the distribution to an energy function and vice-versa.
-This is done using the concept of a canonical distribution from statistical mechanics~\cite{}. 
-Given some energy function,~$E$, the canonical distribution over states has probability density function $P = \frac{1}{Z}\exp (-E/T)$, where $Z$ is a normalizing constant and $T$ is the temperature of the system.
-%Viewing this the opposite way, if we are interested in some distribution with density function $P$, we can obtain it as a canonical distribution with $T = 1$ by setting $E = -\log P - \log Z$, where $Z$ is any convenient positive constant
-Simulating Hamiltonian dynamics requires that the energy function defined is differentiable.
-}
+Instead of rejecting samplings, original samples are purposefully driven onto a manifold.
 
@@
 Because Monte Carlo methods only consider the ratio of the probabilities, we do not need to consider the problem of estimating the intractable partition function.
+
+\os{
+	Roughly speaking, HMC views the system as an energy function for which Hamiltonian dynamics are simulated in fixed time steps.
+	Thus, to sample from a desired distribution~$P$ using HMC, we need to convert the distribution to an energy function and vice-versa.
+	This is done using the concept of a canonical distribution from statistical mechanics~\cite{N11}. 
+	Given some energy function,~$E$, the canonical distribution over states has probability density function $P = \frac{1}{Z}\exp (-E/T)$, where $Z$ is a normalizing constant and $T$ is the temperature of the system.
+	%Viewing this the opposite way, if we are interested in some distribution with density function $P$, we can obtain it as a canonical distribution with $T = 1$ by setting $E = -\log P - \log Z$, where $Z$ is any convenient positive constant
+	Simulating Hamiltonian dynamics requires that the energy function defined is differentiable.
+}
 

### 2017-02-10 paper.tex
fix bib
minor edits

@@
 \Cinf can be analytically expressed as a prolate hyperspheroid and can be sampled directly using a closed form solution~\cite{GSB14}.
-Indeed, directly sampling in \Cinf has been shown to dramatically improve computation time when compared to sampling in $\calX$, especially in high dimensions.
+Indeed, directly sampling in \Cinf has been shown to dramatically improve computation time when compared to sampling in~$\calX$, especially in high dimensions.
 
@@
 Unfortunately, both rejection sampling and HRS may produce a large number of rejected samples especially in high-dimensional spaces.
-This may cause the search algorithm to spend most of its time trying to produces samples in~$\Cinf$ rather than explore it.
+This may cause the planning algorithm to spend most of its time trying to produces samples in~$\Cinf$ rather than explore it.
 In this paper, we suggest an alternative approach to produce samples in the informed set \Cinf for a wide range of settings.
@@
 We start in Sec.~\ref{subsec:planning} by giving an overview of relevant sampling-based motion-planning algorithms.
-We then continue in Sec.~\ref{subsec:sampling} to describe different approaches used to sample~$\calX$.
+We then continue in Sec.~\ref{subsec:sampling} to describe different approaches that can be used these algorithms to sample~$\calX$.
 We conclude our literature review in Sec.~\ref{subsec:mcmc} with a brief overview of Markov Chain Monte Carlo methods.
@@
 This is done by recognizing the underlying connections between stochastic sampling-based motion planning and the theory of random geometric graphs (see also~\cite{SSH16}).
-Additional algorithms followed, increasing the converges rate by various techniques such as lazy dynamic programming~\cite{GSB15, JSCP15}, relaxing optimality to near-optimality~\cite{DB14, SH16} and more.
+Additional algorithms followed, increasing the converges rate by various techniques such as 
+lazy dynamic programming~\cite{GSB15, JSCP15, SH15},
+relaxing optimality to near-optimality~\cite{DB14, SH16} 
+and more.
 
@@
 in Metropolis-Hastings~\cite{CG95} or Gibbs sampling~\cite{CK94}.
-Alternatively, samples on the chain can be generated by simulating Hamiltonian dynamics~\cite{N92} (instead of performing the random walk).
+Alternatively, samples on the chain can be generated by simulating Hamiltonian dynamics~\cite{N94} (instead of performing the random walk).
 This approach, termed Hybrid or Hamiltonian Monte Carlo (HMC)~\cite{N11} was shown to converge faster to the desired distribution, when compared to random-walk based MCMC algorithms.
@@
 Informed sampling-based planning algorithms (e.g. Informed RRT*~\cite{GSB14}, BIT*~\cite{GSB15}) samples new states only from an \emph{informed set}.
-An informed set is a subspace $ X_f \subseteq \mathcal{X}_{free} $  that is possible to provide better solution than the current best $  X_f = \{ x \in \mathcal{X}_{free} \mid c ( \pi^*(x) ) < c_{best} \} $~\cite{GSB14}, in which $ \pi^*(x) $ means the optimal path from $ x_{init} $ to $ x_{goal} $ constrained to pass through $ x $ and $ c_{best} $ is the cost of the current best found.
+An informed set is a subspace $ \Cinf \subseteq \calX $   that is possible to provide better solution than the current best $  \Cinf = \{ x \in \calX \mid c ( \pi^*(x) ) < c_{best} \} $~\cite{GSB14}, in which $ \pi^*(x) $ means the optimal path from $ x_{init} $ to $ x_{goal} $ constrained to pass through $ x $ and $ c_{best} $ is the cost of the current best found.
 The current best $ c_{best} $ constrains eligible $ x $ indirectly by an implicit $ \pi^*(x) $.

### 2017-02-10 paper.tex
work in progress and macros

@@
 	This is done using the concept of a canonical distribution from statistical mechanics~\cite{N11}. 
-	Given some energy function,~$E$, the canonical distribution over states has probability density function $P = \frac{1}{Z}\exp (-E/T)$, where $Z$ is a normalizing constant and $T$ is the temperature of the system.
+	Given some energy function,~$E$, the canonical distribution over states has the Boltzman probability distribution $P = \frac{1}{Z}\exp (-E/T)$, where $Z$ is a normalizing constant and $T$ is the temperature of the system.
 	%Viewing this the opposite way, if we are interested in some distribution with density function $P$, we can obtain it as a canonical distribution with $T = 1$ by setting $E = -\log P - \log Z$, where $Z$ is any convenient positive constant
-	Simulating Hamiltonian dynamics requires that the energy function defined is differentiable.
+}
+
+\os{
+The energy function's definition provides the flexibility to specify desired or more probable states (by presenting lower energies) without the need to use a formal and restrictive model. 
+Specifically, in our setting we want to approximate 
+a uniform distribution over points inside the informed set~\Cinf.
+Note that simulating Hamiltonian dynamics requires that the energy function defined is differentiable.
+}
+
+\os{
+Our energy for any given time $t$, 
+denoted by~$E\left(t,\Cbest \right)$, 
+is a function of $t$ and the current best cost~$\Cbest$.
 }

### 2017-02-10 paper.tex
fix informed sampling definition

--- 2017-02-10 paper.tex
@@
 \label{eq:kinematics}
-\dot{\bm{x}}(t) = f( \bm{x}(t) , \bm{u}(t) ), 
+\dot{x}(t) = f( x(t) , u(t) ), 
 \end{equation}
-in which $ \bm{x} \in \mathcal{X} \subseteq \mathbb{R}^n $ is the state of the robot, and $ \bm{u} \in \mathcal{U} \subseteq \mathbb{R}^m $ is the control input.
-The dynamics determines a state trajectory $ \pi $, given a duration $ T $, an initial state $ \bm{x}(0) $ and an initial input $ \bm{u}(0) $.
-The cost of a trajectory $ \pi $ is defined as the accumulated cost along the path, which is 
+in which $ x \in \calX \subseteq \mathbb{R}^n $ is the state of the robot, and $ u \in \calU \subseteq \mathbb{R}^m $ is the control input.
+The dynamics determines how a state trajectory $ \gamma $ is like given duration $ T $, state $ x(t) $ and input $ u(t) $.
+The cost of a trajectory $ \gamma $ is defined as the accumulated cost $ c( x(t), u(t) ) $ along the path, which is 
 \begin{equation}
 \label{eq:path_cost}
-c(\pi) = \int_0^{T} c( x(t), u(t) ) dt.
+c(\gamma) = \int_0^{T} c( x(t), u(t) ) dt.
 \end{equation}
-Consider the obstacles in a workspace, we have $ \mathcal{X}_{free} \subseteq \mathcal{X} $.
-Consider the bounds of the control input, we have $ \mathcal{U}_{free} \subseteq \mathcal{U} $.
-The dynamics of the robot in Equation~\eqref{eq:kinematics}, free state space $  \mathcal{X}_{free} $ and free control input space $ \mathcal{U}_{free} $ determines a free trajectory space $ \Pi_{free} $, which contains all feasible trajectories $ \pi \in \Pi_{free} $.
-An optimal kinodynamic path-planning problem that finds a kinodynamic path minimizing the cost $ \pi^* = \max_{ \pi \in \Pi_{free} } c( \pi ) $ subject to constraints $ \bm{x} (t) \in \mathcal{X}_{free}  $ and $ \bm{u} (t) \in \mathcal{U}_{free} $.
+Consider the obstacles in a workspace, we have $ \Cfree \subseteq \calX $.
+Consider the bounds of the control input, we have $ \Ufree \subseteq \calU $.
+The dynamics of the robot in Equation~\eqref{eq:kinematics}, free state space $  \Cfree $ and free control input space $ \Ufree $ determines a free trajectory space $ \Pi_{free} $, which contains all feasible trajectories $ \gamma \in \Gamma_{\rm free} $.
+An optimal kinodynamic path-planning problem that finds a kinodynamic path minimizing the cost $ \pi^* = \min_{ \pi \in \Gamma_{free} } c( \gamma ) $ subject to constraints $ x(t) \in \Cfree  $ and $ u(t) \in \Ufree $.
 
 Informed sampling-based planning algorithms (e.g. Informed RRT*~\cite{GSB14}, BIT*~\cite{GSB15}) samples new states only from an \emph{informed set}.
-An informed set is a subspace $ \Cinf \subseteq \calX $   that is possible to provide better solution than the current best $  \Cinf = \{ x \in \calX \mid c ( \pi^*(x) ) < c_{best} \} $~\cite{GSB14}, in which $ \pi^*(x) $ means the optimal path from $ x_{init} $ to $ x_{goal} $ constrained to pass through $ x $ and $ c_{best} $ is the cost of the current best found.
-The current best $ c_{best} $ constrains eligible $ x $ indirectly by an implicit $ \pi^*(x) $.
+An informed set is a subspace $ \Cinf \subseteq \calX $   that is possible to provide better solution than the current best $  \Cinf = \{ x \in \calX \mid c ( \gamma^*(x) ) < \cbest \} $~\cite{GSB14}, in which $ \gamma^*(x) $ means the optimal path from $ x_s $ to $ x_g $ constrained to pass through $ x $ without considering collision checking, and $ \cbest $ is the cost of the current best found.
+The current best $ \cbest $ constrains eligible $ x $ indirectly by an implicit $ \gamma^*(x) $.
 In an optimal kinodynamic path-planning problem, more constraints are considered in defining an informed set, which include the system dynamic constraint and the boundary of control input.
-If we consider a manifold that is defined by an informed set $ X_f $, the informed sampling becomes how to sample on this manifold in a high-dimensional space.
+If we consider a manifold that is defined by an informed set $ \Cinf $, the informed sampling becomes how to sample on this manifold in a high-dimensional space.
 

### 2017-02-10 paper.tex
fix informed sampling definition

@@
 The dynamics determines how a state trajectory $ \gamma $ is like given duration $ T $, state $ x(t) $ and input $ u(t) $.
+There exists a free trajectory space $ \Pi_{free} $ that contains all feasible trajectories $ \gamma \in \Gamma_{\rm free} $.
+It is determined by the system dynamics,$ \Cfree $ and $ \Ufree $, in which $ \Cfree \subseteq \calX $ is a free state space considering the obstacles in a workspace, and $ \Ufree \subseteq \calU $ is a free control space considering the bounds of control input.
 The cost of a trajectory $ \gamma $ is defined as the accumulated cost $ c( x(t), u(t) ) $ along the path, which is 
@@
 \end{equation}
-Consider the obstacles in a workspace, we have $ \Cfree \subseteq \calX $.
-Consider the bounds of the control input, we have $ \Ufree \subseteq \calU $.
-The dynamics of the robot in Equation~\eqref{eq:kinematics}, free state space $  \Cfree $ and free control input space $ \Ufree $ determines a free trajectory space $ \Pi_{free} $, which contains all feasible trajectories $ \gamma \in \Gamma_{\rm free} $.
-An optimal kinodynamic path-planning problem that finds a kinodynamic path minimizing the cost $ \pi^* = \min_{ \pi \in \Gamma_{free} } c( \gamma ) $ subject to constraints $ x(t) \in \Cfree  $ and $ u(t) \in \Ufree $.
+An optimal kinodynamic path-planning problem that finds a kinodynamic path minimizing the cost $ \pi^* = \min_{ \pi \in \Gamma_{free} } c( \gamma ) $.
 

### 2017-02-10 paper.tex
reordering

@@
 \label{eq:kinematics}
-\dot{x}(t) = f( x(t) , u(t) ), 
+\dot{\bm{x}}(t) = f( \bm{x}(t) , \bm{u}(t) ), 
 \end{equation}
-in which $ x \in \calX \subseteq \mathbb{R}^n $ is the state of the robot, and $ u \in \calU \subseteq \mathbb{R}^m $ is the control input.
-The dynamics determines how a state trajectory $ \gamma $ is like given duration $ T $, state $ x(t) $ and input $ u(t) $.
-There exists a free trajectory space $ \Pi_{free} $ that contains all feasible trajectories $ \gamma \in \Gamma_{\rm free} $.
-It is determined by the system dynamics,$ \Cfree $ and $ \Ufree $, in which $ \Cfree \subseteq \calX $ is a free state space considering the obstacles in a workspace, and $ \Ufree \subseteq \calU $ is a free control space considering the bounds of control input.
-The cost of a trajectory $ \gamma $ is defined as the accumulated cost $ c( x(t), u(t) ) $ along the path, which is 
+in which $ \bm{x} \in \mathcal{X} \subseteq \mathbb{R}^n $ is the state of the robot, and $ \bm{u} \in \mathcal{U} \subseteq \mathbb{R}^m $ is the control input.
+The dynamics determines a state trajectory $ \pi $, given a duration $ T $, an initial state $ \bm{x}(0) $ and an initial input $ \bm{u}(0) $.
+The cost of a trajectory $ \pi $ is defined as the accumulated cost along the path, which is 
 \begin{equation}
 \label{eq:path_cost}
-c(\gamma) = \int_0^{T} c( x(t), u(t) ) dt.
+c(\pi) = \int_0^{T} c( x(t), u(t) ) dt.
 \end{equation}
-An optimal kinodynamic path-planning problem that finds a kinodynamic path minimizing the cost $ \pi^* = \min_{ \pi \in \Gamma_{free} } c( \gamma ) $.
+Consider the obstacles in a workspace, we have $ \mathcal{X}_{free} \subseteq \mathcal{X} $.
+Consider the bounds of the control input, we have $ \mathcal{U}_{free} \subseteq \mathcal{U} $.
+The dynamics of the robot in Equation~\eqref{eq:kinematics}, free state space $  \mathcal{X}_{free} $ and free control input space $ \mathcal{U}_{free} $ determines a free trajectory space $ \Pi_{free} $, which contains all feasible trajectories $ \pi \in \Pi_{free} $.
+An optimal kinodynamic path-planning problem that finds a kinodynamic path minimizing the cost $ \pi^* = \max_{ \pi \in \Pi_{free} } c( \pi ) $ subject to constraints $ \bm{x} (t) \in \mathcal{X}_{free}  $ and $ \bm{u} (t) \in \mathcal{U}_{free} $.
 
 Informed sampling-based planning algorithms (e.g. Informed RRT*~\cite{GSB14}, BIT*~\cite{GSB15}) samples new states only from an \emph{informed set}.
-An informed set is a subspace $ \Cinf \subseteq \calX $   that is possible to provide better solution than the current best $  \Cinf = \{ x \in \calX \mid c ( \gamma^*(x) ) < \cbest \} $~\cite{GSB14}, in which $ \gamma^*(x) $ means the optimal path from $ x_s $ to $ x_g $ constrained to pass through $ x $ without considering collision checking, and $ \cbest $ is the cost of the current best found.
-The current best $ \cbest $ constrains eligible $ x $ indirectly by an implicit $ \gamma^*(x) $.
+An informed set is a subspace $ \Cinf \subseteq \calX $   that is possible to provide better solution than the current best $  \Cinf = \{ x \in \calX \mid c ( \pi^*(x) ) < c_{best} \} $~\cite{GSB14}, in which $ \pi^*(x) $ means the optimal path from $ x_{init} $ to $ x_{goal} $ constrained to pass through $ x $ and $ c_{best} $ is the cost of the current best found.
+The current best $ c_{best} $ constrains eligible $ x $ indirectly by an implicit $ \pi^*(x) $.
 In an optimal kinodynamic path-planning problem, more constraints are considered in defining an informed set, which include the system dynamic constraint and the boundary of control input.
-If we consider a manifold that is defined by an informed set $ \Cinf $, the informed sampling becomes how to sample on this manifold in a high-dimensional space.
+If we consider a manifold that is defined by an informed set $ X_f $, the informed sampling becomes how to sample on this manifold in a high-dimensional space.
 
@@
 
+\ignore{
 See Fig. ~\ref{fig:sample_dimt} for an example motion of one joint through the $\left(q,\dot{q}\right)$ space.
@@
 Because of this, finding a closed form solution to sampling in the informed space is not feasible.
+}
 
@@
    	\label{fig:cost_surface_1d}
-	\vspace{-5.5mm}
+%	\vspace{-5.5mm}
 \end{figure}
 
-See Fig.
-~\ref{fig:cost_surface_1d} for a side view of the cost surface for one degree of freedom ($\left(x, \dot{x}\right)$).
+See Fig.~\ref{fig:cost_surface_1d} for a side view of the cost surface for one degree of freedom ($\left(x, \dot{x}\right)$).
 One can see a key property of the cost surface that cause serious concerns is the discontinuous nature of the surface.
@@
 \section{MCMC-based Informed Sampling}
+	Roughly speaking, HMC views the system as an energy function for which Hamiltonian dynamics are simulated in fixed time steps.
+	Thus, to sample from a desired distribution~$P$ using HMC, we need to convert the distribution to an energy function and vice-versa.
+	This is done using the concept of a canonical distribution from statistical mechanics~\cite{N11}. 
+	Given some energy function,~$E$, the canonical distribution over states has the Boltzman probability distribution $P = \frac{1}{Z}\exp (-E/T)$, where $Z$ is a normalizing constant and $T$ is the temperature of the system.
+	%Viewing this the opposite way, if we are interested in some distribution with density function $P$, we can obtain it as a canonical distribution with $T = 1$ by setting $E = -\log P - \log Z$, where $Z$ is any convenient positive constant
 
-%\dy{I am not sure what we want to put into here, but I am going to continue on the discussion of the algorithm and talk about some of the probability stuff.}
+The energy function's definition provides the flexibility to specify desired or more probable states (by presenting lower energies) without the need to use a formal and restrictive model. 
+Specifically, in our setting we want to approximate 
+a uniform distribution over points inside the informed set~\Cinf.
+
+Our energy for any given time $t$, 
+denoted by~$E\left(t,\Cbest \right)$, 
+is a function of $t$ and the current best cost~$\Cbest$.
+To consider only points in the informed set, all with equal energy, one may consider taking 
+$$
+E\left(t,\Cbest \right) = 
+\begin{cases}
+    1,	& \text{if } t \leq \Cbest\\        
+    0,  	& \text{otherwise}.
+\end{cases}
+$$
+However, simulating Hamiltonian dynamics requires that the energy function defined is differentiable.
+This function has a discontinuity at $t = \Cbest$ 
+and contains no gradient information for $t \leq \Cbest$.
+Thus, we define our energy function\footnote{In practice we add another term to the energy function which we discuss in our experiments (see Sec.~\ref{sec:eval}).
+We omit this term here for clarity of exposition.} as
+\begin{equation}
+\label{eq:energy}
+E\left( t, \Cbest \right) 
+= 
+E_{\text{grad}} \left( t \right) + 
+E_{\text{informed}} \left( t,\Cbest \right).
+\end{equation}
+Here, $E_{\text{grad}}$ is a user-defined function that
+controls the ``flatness`` of the distribution.
+Intuitively, this term biases the distribution towards states with smaller cost and balances between the uniformity of the distribution and the gradient information provided to the HMC algorithm.
+%
+%In our setting we experimented with using 
+%$\log\left(1 + \log\left(t\right)\right)$ and $\tanh\left(t\right)$. 
+%
+The term 
+$E_{\text{informed}} \left( t,\Cbest \right) 
+= \beta_{\text{informed}} \cdot \text{sigm}\left(t_0 - t\right)
+$
+penalizes states outside the informed set~$\Cinf$ using a tight sigmoid function~$\text{sigm}$ scaled by some constant~$\beta_{\text{informed}}$.
+The sigmoid can be seen as a differentiable function smoothing the boundary of~$\Cinf$.
+
+\subsection{Implementation details}
+In our implementation we add another term to our energy function (Eq.~\ref{eq:energy}) relating to system parameters that induce known bounds on states.
+Specifically, our robot has predefined joint limits. 
+The flexibility of the energy function allows us to incorporate these limits  to penalize states \emph{within} the informed set that are close to, or violate these limits.
+
+Specifically, we add to Eq.~\ref{eq:energy} the term 
+$
+E_{\text{limits}}\left(\mathbf{x}\right) = \beta_{\text{limits}} \cdot ||\mathbf{x}_{\text{limits}} - \mathbf{x}||_2
+$
+where $||\mathbf{x}_{\text{limits}} - \mathbf{x}||_2$ represents the L2 distance between the current state $\mathbf{x}$ and the state limits~$\mathbf{x}_{\text{limits}}$ and~$\beta_{\text{limits}}$ is some constant controlling how much to penalize states close to the limits.
+
+\section{MCMC-based Informed Sampling}
 
@@
 
+\begin{algorithm}
+	\begin{algorithmic}[1]
+		\STATE
+   	\end{algorithmic}
+	\caption{MCMC Informed Sampling}
+	\label{alg:mcmc_informed_sampling}
+\end{algorithm}
+
+\section{Evaluation}
+\label{sec:eval}
+
+\subsection{Uniformity}
+
+(Give a set of parameters)
+We firstly need to propose a way of measuring uniformity.
+Then we can apply it to compare MCMC approach with rejection sampling and hierarchical rejection sampling.
+We are interested with
+\begin{itemize}
+	\item asymptotic behavior (assumption: MCMC converge to a close uniformity)
+	\item convergence rate (assumption: MCMC converge faster)
+\end{itemize}
+
+\subsection{Efficiency}
+
+The efficiency is shown by how the time is needed when the number of nodes are increased.
+(Y: time spent) and (X: number of nodes).
+
+\subsection{Integration}
+
+We're going to test with RRT*, which falls into a informed RRT*.
+
+We are going to show how the solution cost falls along time.
+(Y: solution cost) and (X: time spent).
+
+\begin{itemize}
+\item DIMT (double integrator minimum time)
+\item Dubins car
+\item Airplane
+\end{itemize}
+
+\section{Conclusion}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Old text that may be re-used
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\ignore{
 In order to take advantage of these powerful methods, we propose to reformulate the cost surface as a probability density.
@@
 
-\os{
-	Roughly speaking, HMC views the system as an energy function for which Hamiltonian dynamics are simulated in fixed time steps.
-	Thus, to sample from a desired distribution~$P$ using HMC, we need to convert the distribution to an energy function and vice-versa.
-	This is done using the concept of a canonical distribution from statistical mechanics~\cite{N11}. 
-	Given some energy function,~$E$, the canonical distribution over states has the Boltzman probability distribution $P = \frac{1}{Z}\exp (-E/T)$, where $Z$ is a normalizing constant and $T$ is the temperature of the system.
-	%Viewing this the opposite way, if we are interested in some distribution with density function $P$, we can obtain it as a canonical distribution with $T = 1$ by setting $E = -\log P - \log Z$, where $Z$ is any convenient positive constant
-}
-
-\os{
-The energy function's definition provides the flexibility to specify desired or more probable states (by presenting lower energies) without the need to use a formal and restrictive model. 
-Specifically, in our setting we want to approximate 
-a uniform distribution over points inside the informed set~\Cinf.
-Note that simulating Hamiltonian dynamics requires that the energy function defined is differentiable.
-}
-
-\os{
-Our energy for any given time $t$, 
-denoted by~$E\left(t,\Cbest \right)$, 
-is a function of $t$ and the current best cost~$\Cbest$.
-}
+\begin{equation}
+E_{\text{informed}}\left(t,t_0\right) = \beta_{\text{informed}} \text{sigm}\left(t_0 - t\right)
+\end{equation}
+where $\text{sigm}\left(\cdot\right)$ represents a tight sigmoid function that can be seen as a differentiable $\text{sign}\left(\cdot\right)$ function.
+$\beta_{\text{informed}}$ is some large number that controls how much we want to penalize states outside of the level set.
+In theory, the energy should be infinity (which represents zero probability).
+In practice, however, setting $\beta_{\text{informed}}$ to be some high number such as $100$ works well and is more stable.
 
@@
 
-In order to ensure that the span the set of all possible states
-
-\begin{algorithm}
-	\begin{algorithmic}[1]
-		\STATE
-   	\end{algorithmic}
-	\caption{MCMC Informed Sampling}
-	\label{alg:mcmc_informed_sampling}
-\end{algorithm}
-
-\section{Results}
-
-\subsection{Uniformity}
-
-(Give a set of parameters)
-We firstly need to propose a way of measuring uniformity.
-Then we can apply it to compare MCMC approach with rejection sampling and hierarchical rejection sampling.
-We are interested with
-\begin{itemize}
-	\item asymptotic behavior (assumption: MCMC converge to a close uniformity)
-	\item convergence rate (assumption: MCMC converge faster)
-\end{itemize}
-
-\subsection{Efficiency}
-
-The efficiency is shown by how the time is needed when the number of nodes are increased.
-(Y: time spent) and (X: number of nodes).
-
-\subsection{Integration}
-
-We're going to test with RRT*, which falls into a informed RRT*.
-
-We are going to show how the solution cost falls along time.
-(Y: solution cost) and (X: time spent).
-
-\begin{itemize}
-\item DIMT (double integrator minimum time)
-\item Dubins car
-\item Airplane
-\end{itemize}
-
-\section{Conclusion}
+}
 

### 2017-02-10 paper.tex

@@
 \label{eq:kinematics}
-\dot{\bm{x}}(t) = f( \bm{x}(t) , \bm{u}(t) ), 
+\dot{x}(t) = f( x(t) , u(t) ), 
 \end{equation}
-in which $ \bm{x} \in \mathcal{X} \subseteq \mathbb{R}^n $ is the state of the robot, and $ \bm{u} \in \mathcal{U} \subseteq \mathbb{R}^m $ is the control input.
-The dynamics determines a state trajectory $ \pi $, given a duration $ T $, an initial state $ \bm{x}(0) $ and an initial input $ \bm{u}(0) $.
-The cost of a trajectory $ \pi $ is defined as the accumulated cost along the path, which is 
+in which $ x \in \calX \subseteq \mathbb{R}^n $ is the state of the robot, and $ u \in \calU \subseteq \mathbb{R}^m $ is the control input.
+The dynamics determines how a state trajectory $ \gamma $ is like given duration $ T $, state $ x(t) $ and input $ u(t) $.
+There exists a free trajectory space $ \Pi_{free} $ that contains all feasible trajectories $ \gamma \in \Gamma_{\rm free} $.
+It is determined by the system dynamics,$ \Cfree $ and $ \Ufree $, in which $ \Cfree \subseteq \calX $ is a free state space considering the obstacles in a workspace, and $ \Ufree \subseteq \calU $ is a free control space considering the bounds of control input.
+The cost of a trajectory $ \gamma $ is defined as the accumulated cost $ c( x(t), u(t) ) $ along the path, which is 
 \begin{equation}
 \label{eq:path_cost}
-c(\pi) = \int_0^{T} c( x(t), u(t) ) dt.
+c(\gamma) = \int_0^{T} c( x(t), u(t) ) dt.
 \end{equation}
-Consider the obstacles in a workspace, we have $ \mathcal{X}_{free} \subseteq \mathcal{X} $.
-Consider the bounds of the control input, we have $ \mathcal{U}_{free} \subseteq \mathcal{U} $.
-The dynamics of the robot in Equation~\eqref{eq:kinematics}, free state space $  \mathcal{X}_{free} $ and free control input space $ \mathcal{U}_{free} $ determines a free trajectory space $ \Pi_{free} $, which contains all feasible trajectories $ \pi \in \Pi_{free} $.
-An optimal kinodynamic path-planning problem that finds a kinodynamic path minimizing the cost $ \pi^* = \max_{ \pi \in \Pi_{free} } c( \pi ) $ subject to constraints $ \bm{x} (t) \in \mathcal{X}_{free}  $ and $ \bm{u} (t) \in \mathcal{U}_{free} $.
+An optimal kinodynamic path-planning problem that finds a kinodynamic path minimizing the cost $ \pi^* = \min_{ \pi \in \Gamma_{free} } c( \gamma ) $.
 
 Informed sampling-based planning algorithms (e.g. Informed RRT*~\cite{GSB14}, BIT*~\cite{GSB15}) samples new states only from an \emph{informed set}.
-An informed set is a subspace $ \Cinf \subseteq \calX $   that is possible to provide better solution than the current best $  \Cinf = \{ x \in \calX \mid c ( \pi^*(x) ) < c_{best} \} $~\cite{GSB14}, in which $ \pi^*(x) $ means the optimal path from $ x_{init} $ to $ x_{goal} $ constrained to pass through $ x $ and $ c_{best} $ is the cost of the current best found.
-The current best $ c_{best} $ constrains eligible $ x $ indirectly by an implicit $ \pi^*(x) $.
+An informed set is a subspace $ \Cinf \subseteq \calX $   that is possible to provide better solution than the current best $  \Cinf = \{ x \in \calX \mid c ( \gamma^*(x) ) < \cbest \} $~\cite{GSB14}, in which $ \gamma^*(x) $ means the optimal path from $ x_s $ to $ x_g $ constrained to pass through $ x $ without considering collision checking, and $ \cbest $ is the cost of the current best found.
+The current best $ \cbest $ constrains eligible $ x $ indirectly by an implicit $ \gamma^*(x) $.
 In an optimal kinodynamic path-planning problem, more constraints are considered in defining an informed set, which include the system dynamic constraint and the boundary of control input.
-If we consider a manifold that is defined by an informed set $ X_f $, the informed sampling becomes how to sample on this manifold in a high-dimensional space.
+If we consider a manifold that is defined by an informed set $ \Cinf $, the informed sampling becomes how to sample on this manifold in a high-dimensional space.
 

### 2017-02-10 paper.tex
typo

@@
 There exists a free trajectory space $ \Pi_{free} $ that contains all feasible trajectories $ \gamma \in \Gamma_{\rm free} $.
-It is determined by the system dynamics,$ \Cfree $ and $ \Ufree $, in which $ \Cfree \subseteq \calX $ is a free state space considering the obstacles in a workspace, and $ \Ufree \subseteq \calU $ is a free control space considering the bounds of control input.
+It is determined by the system dynamics, $\Cfree $ and $ \Ufree $, in which $ \Cfree \subseteq \calX $ is a free state space considering the obstacles in a workspace, and $ \Ufree \subseteq \calU $ is a free control space considering the bounds of control input.
 The cost of a trajectory $ \gamma $ is defined as the accumulated cost $ c( x(t), u(t) ) $ along the path, which is 

### 2017-02-13 paper.tex
new fig

@@
 
-\section{Motivating example---Minimal-Time Double Integrator}
+\section{Motivating example---Minimal-Time Double Integrator (MTDI)}
 
@@
 \subsection{Informed set}
-Recall that for Euclidean spaces minimizing path length, the informed set is a prolate hyperspheroid.
+Recall that for Euclidean spaces minimizing path length, the informed set~\Cinf is a prolate hyperspheroid.
 Moreover, this hyperspheroid is defined only be the cost $\hat{c}$ of the current best solution and not by the location of the start and goal.
 
-For the case of a double integrator, this is not the case.
+For the case of a MTDI, this is not the case. 
+Specifically, we have that 
+(i)~the structure of~\Cinf changes not only with~$\hat{c}$ but also according to the specific values of the start~$x_s$ and goal~$x_g$ states
+and that
+(ii)~the cost map that implicitly defines~\Cinf can contain discontinuities (in contrast to Euclidean spaces minimizing path length where the cost map is continuous and differentiable at every point).
+
+To understand the differences recall that optimal paths for MTDI follows a ``bang-bang`` controller.
+Namely, we first apply maximal (or minimal) acceleration for some duration and then switch to applying minimal (or maximal, respectively) acceleration.
+It is straightforward to see that both the type and the amount of acceleration applied (and hence the structure of~\Cinf) depend on the specific values of~$x_s$ and~$x_g$. 
+Fig~\ref{fig:informed_sets} 
+depicts two informed sets defined using the same cost~$\hat{c}$ using different start and goal states. Notice the difference in structure of~\Cinf.
+
+To understand why the cost map may not be continuous consider the simple example in Fig~\ref{fig:discont}
+
+First, the informed
+
 Intuitively, one can see why.

### 2017-02-15 paper.tex
updated figure

@@
 the samples need to be drawn from the entire state space~$\calX$.
-However, once a path $\gamma$ is produced,  algorithms that seek \emph{high-quality paths} can limit their sampling domain to a subset of~$\calX$ only  containing states that may produce higher-quality paths than~$\gamma$.
+However, once a path $\gamma$ is produced,  algorithms that seek \emph{high-quality paths} can limit their sampling domain to a subset of~$\calX$ only  containing states that may be used to produce higher-quality paths than~$\gamma$.
 Following Gammell et al.~\cite{GSB14}, we call this subset the \emph{informed subset} and denote it~$\Cinf$.
@@
 \textbf{Our main insight is to formulate the problem as the problem of sampling uniformly below a level set of an implicit function and then apply optimization and statistical tools.}
+\os{do we really care about uniformity?}
 Specifically, our approach consists of two stages:
@@
 Indeed, we demonstrate the efficiency of our approach on a wide variety of systems and show that it enables reducing the planning time by several orders of magnitute when compared to algorithms using rejection sampling or HRS.
+
+\os{structure}
 
@@
 We start in Sec.~\ref{subsec:planning} by giving an overview of relevant sampling-based motion-planning algorithms.
-We then continue in Sec.~\ref{subsec:sampling} to describe different approaches that can be used these algorithms to sample~$\calX$.
+We then continue in Sec.~\ref{subsec:sampling} to describe different approaches that can be used by  these algorithms to sample~$\calX$.
 We conclude our literature review in Sec.~\ref{subsec:mcmc} with a brief overview of Markov Chain Monte Carlo methods.
@@
 Karaman and Frazzoli~\cite{KF11}, presented variants of PRM and RRT, named PRM* and RRT*, respectively that were shown to produce paths who's cost converges asymptotically to the minimal-cost path.
-This is done by recognizing the underlying connections between stochastic sampling-based motion planning and the theory of random geometric graphs (see also~\cite{SSH16}).
+This was done by recognizing the underlying connections between stochastic sampling-based motion planning and the theory of random geometric graphs (see also~\cite{SSH16}).
 Additional algorithms followed, increasing the converges rate by various techniques such as 
@@
 
-\section{Informed Sampling}
+\section{Problem definition}
 \label{sec:algorithm}
+Let $\calX, \calU$ denote the state and controls spaces, respectively and set $\Cfree \subset \calX$ to be the set of states where the robot is collision free.
+A \emph{trajectory} $\gamma$ is a timed path through~$\calX$ obtained by applying at time $t$ control $u(t) \in \calU$ and satisfying the system dynamics 
+$\dot{x}(t) = f( x(t) , u(t) )$.
+A trajectory is collision free if $\forall t,~\gamma(t) \in \Cfree$
 
+Given a cost function $C : \calX \times \calU \rightarrow \R$, the cost of a trajectory $ \gamma $ is defined as the accumulated cost along the path
+$c(\gamma) = \int_0^{T} c( x(t), u(t) ) dt$, 
+where $T$ is the duration of~$\gamma$.
+
+Given start and target states $x_s, x_g \in \calX$, we wish to find a collision free trajectory $\gamma*$ connecting $x_s$ to $x_g$ such that 
+$c(\gamma*) = \min_{\gamma \in \Gamma} c(\gamma)$, where $\Gamma$ is the set of all collision-free trajectories.
+
+Given a trajectory $\gamma_{\text{best}}$ with cost $c_{\text{best}} = c(\gamma_{\text{best}})$ the \emph{informed set}~\Cinf is defined to be all states $x$  which may be on trajectories with lower cost than $c_{\text{best}}$.
+Specifically,
+$
+\Cinf = \{ x \in \calX \mid  
+		c ( \gamma^*(x) ) < \cbest \} $~\cite{GSB14}.
+Here~$ \gamma^*(x) $ denotes the optimal trajectory  from $ x_s $ to $ x_g $ constrained to pass through $ x $.
+Notice that~$ \gamma^*(x) $ is not required to be collision free.
+
+\ignore{
 Define the dynamics of a robot as 
@@
 In an optimal kinodynamic path-planning problem, more constraints are considered in defining an informed set, which include the system dynamic constraint and the boundary of control input.
-If we consider a manifold that is defined by an informed set $ \Cinf $, the informed sampling becomes how to sample on this manifold in a high-dimensional space.
+If we consider a manifold that is defined by an informed set $ \Cinf $, the informed sampling becomes how to sample on this manifold in a high-dimensional space. }
 
@@
 
-We start by considering a simple yet important dynamical system---the double integrator. 
-We are given a one-dimensional point robot with bounded acceleration moving amid obstacles. We wish to compute the minimal-time trajectory between two states $x_s, x_g$.
-A state in this model is described by 
+To understand why we resort to optimization-based methods and do not attempt to provide a closed-form solution to sample $\Cinf$ we study the structure of the informed set for a simple yet important dynamical system---the double integrator.
+Here, we are given a one-dimensional point robot with bounded acceleration moving amid obstacles. We wish to compute the minimal-time trajectory between two states $x_s, x_g$.
+A state $x \in \calX$ in this model is defined by 
 the position $q \in \R$
@@
 
-Let $T(x_1, x_2)$ denote the minimal time to move the robot from state $x_1$ to $x_2$.
-Furthermore, set
+%Let $T(x_1, x_2)$ denote the minimal time to move the robot from state $x_1$ to $x_2$.
+%Furthermore, set
+%%
+%\begin{equation}
+%T(x_s, x, x_g) = T(x_s, x) + T(x, x_g).
+%\end{equation}
+%%
+%Namely, $T(x_s, x, x_g)$ is the minimal time to reach the goal from the start subject to passing through the state $x$.
 %
-\begin{equation}
-T(x_s, x, x_g) = T(x_s, x) + T(x, x_g).
-\end{equation}
 %
-Namely, $T(x_s, x, x_g)$ is the minimal time to reach the goal from the start subject to passing through the state $x$.
-
-\subsection{Informed set}
+%\subsection{Informed set}
 Recall that for Euclidean spaces minimizing path length, the informed set~\Cinf is a prolate hyperspheroid.
@@
 
-To understand the differences recall that optimal paths for MTDI follows a ``bang-bang`` controller.
+To understand the differences recall that optimal paths for MTDI follow a ``bang-bang`` controller.
 Namely, we first apply maximal (or minimal) acceleration for some duration and then switch to applying minimal (or maximal, respectively) acceleration.
@@
 depicts two informed sets defined using the same cost~$\hat{c}$ using different start and goal states. Notice the difference in structure of~\Cinf. 
+Fig~\ref{fig:discont} depicts a simple example where the cost map may is discontinuous.
 
-To understand why the cost map may not be continuous consider the simple example in Fig~\ref{fig:discont}
-
-First, the informed
-
-Intuitively, one can see why.
-According the the double-integrator minimum time model, maximum acceleration is applied in one direction to a point, and then maximum acceleration in the other direction is applied to complete the motion.
-The direction of the first and second acceleration depends on the start and goal state.
+To summarize, the structure of \Cinf can change given different start and goal states.
+Furthermore,  its boundary may not even be smooth or differentiable due to the aforementioned discontinuous.
 
@@
 
+\ignore{
 See Fig.~\ref{fig:informed_1d_di} for a visualization of the cost surface for a specific start and goal state for one degree of freedom (two dimensions $\left(x, \dot{x}\right)$).
@@
 One can see the minimum cost path from start to goal as the dark blue curve.
+}
 
+\begin{figure}[tb]
+  \centering
+  	\includegraphics[height = 5.25cm ]{fig/cost_discontinuity.pdf}
+  \caption{
+    \captionstyle
+  	Visualization of the discontinuity in the cost function of MTDI (right) as a function of the controls applied (left). 
+  	Given state~$x_s$ and fixed position $q_0$, we depict the cost (time) as a function of the velocity~$\dot{q}$. 
+  	The minimal cost is attained at $\dot{q}_{\min}$ by applying maximal acceleration (blue curves~$(i), (ii)$). 
+  	To reach states such as~$\dot{q}_1$, where $\dot{q}_1 < \dot{q}_{\min}$ we need to apply maximal acceleration (curve~$(i)$) followed by minimal acceleration (green curve~$(iii)$), which result in a continuous increase in cost.
+  	However, for states such as $\dot{q}_2$, where $\dot{q}_2 > \dot{q}_{\min}$, we need to apply minimal acceleration  followed by maximal acceleration (curves~$(iv), (v)$), which result in the cost discontinuity.
+  	}
+   	\label{fig:discont}
+\end{figure}
+
+\ignore{
 \begin{figure}[tb]
@@
 ~\ref{fig:cost_surface_1d}.
+}
 
 \section{MCMC-based Informed Sampling}
+\os{missing intro here}
+
 	Roughly speaking, HMC views the system as an energy function for which Hamiltonian dynamics are simulated in fixed time steps.
@@
 The sigmoid can be seen as a differentiable function smoothing the boundary of~$\Cinf$.
+
+\os{add visualization}
 

### 2017-02-21 paper.tex
added refs
polishing

@@
 (i)~a solution will be found 
-(a property called \emph{probabilistic completeness})
+%(a property called \emph{probabilistic completeness})
 and that
-(ii)~given some optimization criteria, the quality of the solution will progressively converge to the quality of the optimal solution
-(a property called \emph{asymptotic  optimality}).
+(ii)~given some optimization criteria, the quality of the solution will progressively converge to the quality of the optimal solution.
+%(a property called \emph{asymptotic  optimality}).
 
@@
 the domain dynamics and applying linear quadratic regulation (LQR).
+Finally, reachability-guided sampling~\cite{SWT09, PLAEFRA17} focuses on sampling regions of the state space that are most likely to promote expansion under the differential constraints.
 
@@
 
-Given a cost function $C : \calX \times \calU \rightarrow \R$, the cost of a trajectory $ \gamma $ is defined as the accumulated cost along the path
+Given a cost function $C : \calX \times \calU \rightarrow \R$, the cost of a trajectory $ \gamma $ is the accumulated cost along the path
 $c(\gamma) = \int_0^{T} c( x(t), u(t) ) dt$, 
@@
 
-Given start and target states $x_s, x_g \in \calX$, we wish to find a collision free trajectory $\gamma*$ connecting $x_s$ to $x_g$ such that 
-$c(\gamma*) = \min_{\gamma \in \Gamma} c(\gamma)$, where $\Gamma$ is the set of all collision-free trajectories.
+Given start and target states $x_s, x_g \in \calX$, we wish to find a collision free trajectory $\gamma^*$ connecting $x_s$ to $x_g$ such that 
+$c(\gamma^*) = \min_{\gamma \in \Gamma} c(\gamma)$, where $\Gamma$ is the set of all collision-free trajectories.
 
@@
 Here~$ \gamma^*(x) $ denotes the optimal trajectory  from $ x_s $ to $ x_g $ constrained to pass through $ x $.
-Notice that~$ \gamma^*(x) $ is not required to be collision free.
+Notice that we do not require that~$ \gamma^*(x) $ is collision free.
+
+The informed set induces a probability distribution $\Pinf$. 
+Here, points in \Cinf are distributed uniformly
+while 
+the probability of sampling any configuration $x \in \calX \setminus \Cinf$ is zero.
+Our goal is to efficiently produce samples (approximately) from \Pinf.
 
@@
 \section{Motivating example---Minimal-Time Double Integrator (MTDI)}
+\label{sec:mtdi}
 
-To understand why we resort to optimization-based methods and do not attempt to provide a closed-form solution to sample $\Cinf$ we study the structure of the informed set for a simple yet important dynamical system---the double integrator.
+To understand why we resort to optimization-based methods and do not attempt to provide a closed-form solution to sample $\Cinf$ we study the structure of the informed set for a simple yet important dynamical system---the double integrator minimizing time (MTDI).
 Here, we are given a one-dimensional point robot with bounded acceleration moving amid obstacles. We wish to compute the minimal-time trajectory between two states $x_s, x_g$.
@@
 (i)~this is model can be seen as a simplified one-dimensional instance of a robot manipulator with many degrees of freedom and that
-(ii)~closed form solutions exist to the 2pBVP for this specific case (as well as the multi-dimensional setting)~\cite{HN10, KS14}.
+(ii)~closed-form solutions exist to the 2pBVP for this specific case (as well as the multi-dimensional setting)~\cite{HN10, KS14}.
 
@@
 Recall that for Euclidean spaces minimizing path length, the informed set~\Cinf is a prolate hyperspheroid.
-Moreover, this hyperspheroid is defined only be the cost $\hat{c}$ of the current best solution and not by the location of the start and goal.
+Moreover, this hyperspheroid is defined only be the cost $c_{\text{best}}$ of the current best solution and not by the location of the start~$x_s$ and goal~$x_g$.
 
@@
 Specifically, we have that 
-(i)~the structure of~\Cinf changes not only with~$\hat{c}$ but also according to the specific values of the start~$x_s$ and goal~$x_g$ states
+(i)~the structure of~\Cinf changes not only with~$c_{\text{best}}$ but also according to the specific values of~$x_s$ and~$x_g$ 
 and that
@@
 
-To understand the differences recall that optimal paths for MTDI follow a ``bang-bang`` controller.
+To understand the differences recall that optimal paths for MTDI follow a ``bang-bang`` controller~\cite{HN10, KS14}.
 Namely, we first apply maximal (or minimal) acceleration for some duration and then switch to applying minimal (or maximal, respectively) acceleration.
@@
 Fig~\ref{fig:informed_sets} 
-depicts two informed sets defined using the same cost~$\hat{c}$ using different start and goal states. Notice the difference in structure of~\Cinf. 
+depicts two informed sets defined using the same cost~$c_{\text{best}}$ but different start and goal states. Notice the difference in structure of~\Cinf. 
 Fig~\ref{fig:discont} depicts a simple example where the cost map may is discontinuous.
@@
     \captionstyle
-  	Visualization of the discontinuity in the cost function of MTDI (right) as a function of the controls applied (left). 
+  	Visualization of the discontinuity in the cost function of MTDI (right) related to the types of controls applied (left). 
   	Given state~$x_s$ and fixed position $q_0$, we depict the cost (time) as a function of the velocity~$\dot{q}$. 
@@
   	To reach states such as~$\dot{q}_1$, where $\dot{q}_1 < \dot{q}_{\min}$ we need to apply maximal acceleration (curve~$(i)$) followed by minimal acceleration (green curve~$(iii)$), which result in a continuous increase in cost.
-  	However, for states such as $\dot{q}_2$, where $\dot{q}_2 > \dot{q}_{\min}$, we need to apply minimal acceleration  followed by maximal acceleration (curves~$(iv), (v)$), which result in the cost discontinuity.
+  	However, for states such as $\dot{q}_2$, where $\dot{q}_2 > \dot{q}_{\min}$, we need to apply minimal acceleration  followed by maximal acceleration (curves~$(iv), (v)$), which result in the discontinuity.
   	}
@@
 \section{MCMC-based Informed Sampling}
-\os{missing intro here}
+In this section we describe our approach to efficiently produce samples in the informed set~\Cinf given a specific cost~$c_{\text{best}}$.
+We start  by randomly sampling a configuration~$x_\text{rand} \in \calX$.
+This sample~$x_\text{rand}$ is used to initialize a gradient-descent algorithm which produces a sample~$x_\text{boundary} \in \partial\Cinf$ which lies (approximately) on the boundary of the informed set (Sec.~\ref{subsec:grad}).
+We then use~$x_\text{boundary}$ to initialize an MCMC algorithm which produces a series of samples within \Cinf (Sec.~\ref{subsec:mcmc}).
+Specifically, we chose to use HMC due to its favourable properties (see Sec.~\ref{sec:intro}).
 
+\subsection{Gradient descent}
+\label{subsec:grad}
+In theory, MCMC methods converge to the desired distribution regardless of the initial sample used to seed the chain.
+However, in practice it is common to discard an initial set of samples (a process referred to as ``burn-in'') to avoid starting biases~\cite{ADDJ03}. 
+In our setting, we chose to skip this
+
+Recall (Sec.~\ref{sec:mtdi}) that our cost function is nor necessarily continuous
+
+\subsection{Hamiltonian Monte Carlo (HMC)}
+\label{subsec:mcmc}
 	Roughly speaking, HMC views the system as an energy function for which Hamiltonian dynamics are simulated in fixed time steps.
@@
 	This is done using the concept of a canonical distribution from statistical mechanics~\cite{N11}. 
-	Given some energy function,~$E$, the canonical distribution over states has the Boltzman probability distribution $P = \frac{1}{Z}\exp (-E/T)$, where $Z$ is a normalizing constant and $T$ is the temperature of the system.
+	Given some energy function,~$E$, the canonical distribution over states has the Boltzman probability distribution $P = \frac{1}{Z}\exp (-E/T)$, where $Z$ is a normalizing constant and~$T$ is the temperature of the system.
 	%Viewing this the opposite way, if we are interested in some distribution with density function $P$, we can obtain it as a canonical distribution with $T = 1$ by setting $E = -\log P - \log Z$, where $Z$ is any convenient positive constant
@@
 \begin{cases}
-    1,	& \text{if } t \leq \Cbest\\        
-    0,  	& \text{otherwise}.
+    0,	& \text{if } t \leq \Cbest\\        
+    \infty,  	& \text{otherwise}.
 \end{cases}
@@
 Intuitively, this term biases the distribution towards states with smaller cost and balances between the uniformity of the distribution and the gradient information provided to the HMC algorithm.
-%
-%In our setting we experimented with using 
-%$\log\left(1 + \log\left(t\right)\right)$ and $\tanh\left(t\right)$. 
-%
+
+In our setting we experimented with using 
+$\log\left(1 + \log\left(t\right)\right)$ and $\tanh\left(t\right)$.
+
 The term 
@@
 $
-penalizes states outside the informed set~$\Cinf$ using a tight sigmoid function~$\text{sigm}$ scaled by some constant~$\beta_{\text{informed}}$.
+penalizes states outside the informed set~$\Cinf$ using a tight sigmoid function~$\text{sigm}$ scaled by some (large\footnote{The constant~$\beta_{\text{informed}}$ gives points out of~\Cinf a large energy value which in turn implies a low probability of being sampled.
+In theory, we would like to have~$\beta_{\text{informed}} \approx \infty$.
+However, choosing~$\beta_{\text{informed}}$ to be to large may cause numerical instabilities.}) constant~$\beta_{\text{informed}}$.
 The sigmoid can be seen as a differentiable function smoothing the boundary of~$\Cinf$.
@@
 
+\subsection{Probabilistic completeness}
+
+%\newpage
+%\begin{thm}
+%For each node $u$ that was removed from the priority $\calQ$, $g(u) = \delta(u)$, where $\delta(u)$ denotes the shortest path to reach $u$ from $s$.
+%\end{thm}
+%
+%The proof is by induction on the order of vertices removed from $\calQ$. 
+%
+%\textbf{Base} holds trivially for $s$.
+%
+%\textbf{Step:}
+%Let $v$ be the current node on the top of the priority queue and let $u$ be its parent.
+%Notice that by the induction hypothesis we have that $g(u) = \delta(u)$.
+%
+%We have two case to consider: 
+%(i) the shortest path does not pass through $u$ but through some other node $u'$ which is not in $\calQ$,
+%and
+%(i) the shortest path does not pass through $u$ but through some other node $y$ which is in $\calQ$.
+%
+%For case (i), we have that when $u'$ was removed from $\calQ$, then $v$'s cost was $g(v) \leq g(u') + c(u',v)$.
+%Since $g(u') = \delta(u')$ this is equal to $\delta(v)$.
+%
+%For case (ii), let $x$ be $y$'s parent which was already removed from $\calQ$.
+%Note that $g(x) = \delta(x)$ and (similar to the previous case) we have that $g(y) < g(x) + c(x,y)$.
+%Furthermore notice that $v$ was before $y$ in $\calQ$ thus $g(v) \leq g(y)$.
+%Purring everything together we have that
+%$$
+%\delta(v)   > \delta(x) + c(x,y)
+%			\geq g(y)
+%			\geq g(v).
+%$$
+%Here, the first transition is due to the assumption that the shortest path goes from $s$ to $v$ through the edge $(x,y)$.
+%The second (which I got confused about in class) is due to the fact that when $x$ was popped from $\calQ$ it updated $y$'s cost.
+% \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\
+% 
+%\vspace{20cm}
+
+\ignore{
 \section{MCMC-based Informed Sampling}
@@
 \end{algorithm}
+}
 
@@
 
+What MCMC algorithm is the best to use?
+
+Parameter tuning
+
+Application to different state spaces
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-02-22 paper.tex
updated energy and Newton

@@
 the domain dynamics and applying linear quadratic regulation (LQR).
-Finally, reachability-guided sampling~\cite{SWT09, PLAEFRA17} focuses on sampling regions of the state space that are most likely to promote expansion under the differential constraints.
+
+Finally, we note that we are not the first to integrate Monte Carlo sampling into planning algorithms.
+T-RRT~\cite{JCS10} and its variants~\cite{DSC13} are inspired by Monte Carlo optimization techniques and use notions such as the Metropolis criterion to guide the exploration of the configuration space.
 
@@
 resampling along a given trajectory~\cite{APD11, AS11}
-and more~\cite{US03, SWT09}
+and more~\cite{US03, SWT09}.
+For planning under the differential constraints,
+reachability-guided sampling~\cite{SWT09, PLAEFRA17} focuses on sampling regions of the state space that are most likely to promote expansion under the differential constraints.
 
@@
 \label{subsec:mcmc}
+\os{This section puts a lot of emphasis on HMC. If we end up choosing an alternative method, we should change the relevant weight}
+
 Monte Carlo simulation is a general sampling framework widely used in various domains such as
@@
 Recall that for Euclidean spaces minimizing path length, the informed set~\Cinf is a prolate hyperspheroid.
-Moreover, this hyperspheroid is defined only be the cost $c_{\text{best}}$ of the current best solution and not by the location of the start~$x_s$ and goal~$x_g$.
+Moreover, the size and shape of the hyperspheroid is defined only be the cost $c_{\text{best}}$ of the current best solution and not by the location of the start~$x_s$ and goal~$x_g$.
 
@@
 
-To understand the differences recall that optimal paths for MTDI follow a ``bang-bang`` controller~\cite{HN10, KS14}.
+To understand the differences recall that optimal trajectories  for MTDI follow a ``bang-bang`` controller~\cite{HN10, KS14}.
 Namely, we first apply maximal (or minimal) acceleration for some duration and then switch to applying minimal (or maximal, respectively) acceleration.
@@
 depicts two informed sets defined using the same cost~$c_{\text{best}}$ but different start and goal states. Notice the difference in structure of~\Cinf. 
-Fig~\ref{fig:discont} depicts a simple example where the cost map may is discontinuous.
+Fig~\ref{fig:discont} depicts a simple example where the cost map is discontinuous.
 
 To summarize, the structure of \Cinf can change given different start and goal states.
-Furthermore,  its boundary may not even be smooth or differentiable due to the aforementioned discontinuous.
+Furthermore,  its boundary may not be  differentiable due to the aforementioned discontinuous.
 
@@
 In this section we describe our approach to efficiently produce samples in the informed set~\Cinf given a specific cost~$c_{\text{best}}$.
-We start  by randomly sampling a configuration~$x_\text{rand} \in \calX$.
-This sample~$x_\text{rand}$ is used to initialize a gradient-descent algorithm which produces a sample~$x_\text{boundary} \in \partial\Cinf$ which lies (approximately) on the boundary of the informed set (Sec.~\ref{subsec:grad}).
+We start  by randomly sampling a state~$x_\text{rand} \in \calX$ and use it
+to produces a sample~$x_\text{boundary} \in \partial\Cinf$ which lies (approximately) on the boundary of the informed set (Sec.~\ref{subsec:grad}).
+This is done by applying Newton–Raphson method~\cite{RT06}.
 We then use~$x_\text{boundary}$ to initialize an MCMC algorithm which produces a series of samples within \Cinf (Sec.~\ref{subsec:mcmc}).
@@
 
-\subsection{Gradient descent}
+\subsection{Sampling the boundary of \Cinf via Newton–Raphson}
 \label{subsec:grad}
@@
 However, in practice it is common to discard an initial set of samples (a process referred to as ``burn-in'') to avoid starting biases~\cite{ADDJ03}.
-In our setting, we chose to skip this
 
-Recall (Sec.~\ref{sec:mtdi}) that our cost function is nor necessarily continuous
+In our setting, we are only interested in points in~\Cinf, thus we can start the Markov Chain in~\Cinf and avoid this burn-in stage. 
+To do so we apply  Newton–Raphson's method to obtain a sample on $\partial \Cinf$. 
+However, our cost function is not necessarily continuous (see Sec.~\ref{sec:mtdi}), thus if no sample was produced on $\partial \Cinf$ after a predefined number of steps, we restart the algorithm using a different random state~$x_\text{rand}$.
 
-\subsection{Hamiltonian Monte Carlo (HMC)}
+\subsection{Sampling the interior of \Cinf via
+MCMC}
 \label{subsec:mcmc}
+\os{once we have results we need to discuss here (or in the implementation details), how is this used: Do we use one chain? Do we restart from scratch? Do we use every sample on the chain?}
+
 	Roughly speaking, HMC views the system as an energy function for which Hamiltonian dynamics are simulated in fixed time steps.
@@
 Intuitively, this term biases the distribution towards states with smaller cost and balances between the uniformity of the distribution and the gradient information provided to the HMC algorithm.
-
-In our setting we experimented with using 
-$\log\left(1 + \log\left(t\right)\right)$ and $\tanh\left(t\right)$.
+We used $E_{\text{grad}} (t) = \tanh(t + 3 )$ which whose gradient is close to zero for $t>0$.
 
@@
 $E_{\text{informed}} \left( t,\Cbest \right) 
-= \beta_{\text{informed}} \cdot \text{sigm}\left(t_0 - t\right)
+= \beta \cdot \text{sigm}\left(t_0 - t\right)
 $
-penalizes states outside the informed set~$\Cinf$ using a tight sigmoid function~$\text{sigm}$ scaled by some (large\footnote{The constant~$\beta_{\text{informed}}$ gives points out of~\Cinf a large energy value which in turn implies a low probability of being sampled.
-In theory, we would like to have~$\beta_{\text{informed}} \approx \infty$.
-However, choosing~$\beta_{\text{informed}}$ to be to large may cause numerical instabilities.}) constant~$\beta_{\text{informed}}$.
+penalizes states outside the informed set~$\Cinf$ using a tight sigmoid function~$\text{sigm}$ scaled by some (large\footnote{The constant~$\beta$ gives points out of~\Cinf a large energy value which in turn implies a low probability of being sampled.
+In theory, we would like to have~$\beta \approx \infty$.
+However, choosing~$\beta$ to be to large may cause numerical instabilities.}) constant~$\beta$.
 The sigmoid can be seen as a differentiable function smoothing the boundary of~$\Cinf$.
@@
 Specifically, our robot has predefined joint limits. 
-The flexibility of the energy function allows us to incorporate these limits  to penalize states \emph{within} the informed set that are close to, or violate these limits.
+The flexibility of the energy function allows us to incorporate these limits  to penalize states \emph{within} the informed set that are violating these limits.
 
@@
 $
-E_{\text{limits}}\left(\mathbf{x}\right) = \beta_{\text{limits}} \cdot ||\mathbf{x}_{\text{limits}} - \mathbf{x}||_2
+E_{\text{limits}}\left(\mathbf{x}\right) = \beta\cdot \text{sigm} ( ||\mathbf{x}_{\text{limits}} - \mathbf{x}||_2 )
 $
-where $||\mathbf{x}_{\text{limits}} - \mathbf{x}||_2$ represents the L2 distance between the current state $\mathbf{x}$ and the state limits~$\mathbf{x}_{\text{limits}}$ and~$\beta_{\text{limits}}$ is some constant controlling how much to penalize states close to the limits.
+where $||\mathbf{x}_{\text{limits}} - \mathbf{x}||_2$ represents the L2 distance between the current state $\mathbf{x}$ and the state limits~$\mathbf{x}_{\text{limits}}$.
 

### 2017-02-22 paper.tex
added alg

@@
 to produces a sample~$x_\text{boundary} \in \partial\Cinf$ which lies (approximately) on the boundary of the informed set (Sec.~\ref{subsec:grad}).
-This is done by applying Newton–Raphson method~\cite{RT06}.
+This is done by applying Newton-Raphson method~\cite{RT06}.
 We then use~$x_\text{boundary}$ to initialize an MCMC algorithm which produces a series of samples within \Cinf (Sec.~\ref{subsec:mcmc}).
@@
 
-\subsection{Sampling the boundary of \Cinf via Newton–Raphson}
+\begin{algorithm}[t]
+	\begin{algorithmic}[1]
+		\STATE $x_{\text{rand}} \leftarrow \texttt{sample\_uniform(\calX)}$
+		\STATE $x_{\text{boundary}} \leftarrow
+		 \texttt{newton\_raphson}(x_{\text{rand}}, c_{\text{best}})$
+		\STATE $x_{0} \leftarrow x_{\text{boundary}}$
+		\FOR {$i = 1$ to $N$}
+			\STATE $x_{i} \leftarrow \texttt{MCMC} (x_{i-1}, c_{\text{best}})$
+			\RETURN $x_{i}$
+		\ENDFOR
+
+   	\end{algorithmic}
+	\caption{MCMC Informed Sampling $(c_{\text{best}})$}
+	\label{alg:mcmc_informed_sampling}	
+\end{algorithm}
+
+\subsection{Sampling the boundary of \Cinf via Newton-Raphson}
 \label{subsec:grad}
@@
 In our setting, we are only interested in points in~\Cinf, thus we can start the Markov Chain in~\Cinf and avoid this burn-in stage. 
-To do so we apply  Newton–Raphson's method to obtain a sample on $\partial \Cinf$. 
+To do so we apply  Newton-Raphson's method to obtain a sample on $\partial \Cinf$. 
 However, our cost function is not necessarily continuous (see Sec.~\ref{sec:mtdi}), thus if no sample was produced on $\partial \Cinf$ after a predefined number of steps, we restart the algorithm using a different random state~$x_\text{rand}$.
@@
 The sigmoid can be seen as a differentiable function smoothing the boundary of~$\Cinf$.
+See Fig.~\ref{fig:energy} for a visualization.
 
-\os{add visualization}
+\begin{figure}[tb]
+  \centering
+  	\includegraphics[height = 4.5cm ]{fig/energy.pdf}
+  \caption{
+    \captionstyle
+  	Energy function used by HMC to obtain samples~$x \in \Cinf$.
+  	}
+   	\label{fig:energy}
+\end{figure}
 

### 2017-02-22 paper.tex
minor edits

@@
 and contains no gradient information for $t \leq \Cbest$.
-Thus, we define our energy function\footnote{In practice we add another term to the energy function which we discuss in our experiments (see Sec.~\ref{sec:eval}).
-We omit this term here for clarity of exposition.} as
+Thus, we define our energy function\footnote{In practice we add another term to the energy function which we discuss in Sec.~\ref{sec:eval}. We omit the term here for clarity of exposition.} as  
 \begin{equation}
@@
 In theory, we would like to have~$\beta \approx \infty$.
-However, choosing~$\beta$ to be to large may cause numerical instabilities.}) constant~$\beta$.
+However, choosing~$\beta$ to be too large may cause numerical instabilities.}) constant~$\beta$.
 The sigmoid can be seen as a differentiable function smoothing the boundary of~$\Cinf$.
@@
 Application to different state spaces
+
+Parallel chains
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-02-23 paper.tex
backup
added todo

@@
 \usepackage{color}
+\usepackage{cite}
 \usepackage{hyperref}
@@
 when a path has yet to be found, 
-the samples need to be drawn from the entire state space~$\calX$.
+the samples are drawn from the entire state space~$\calX$.
 However, once a path $\gamma$ is produced,  algorithms that seek \emph{high-quality paths} can limit their sampling domain to a subset of~$\calX$ only  containing states that may be used to produce higher-quality paths than~$\gamma$.
 Following Gammell et al.~\cite{GSB14}, we call this subset the \emph{informed subset} and denote it~$\Cinf$.
-\textbf{In this work we address the problem of efficiently producing samples in informed subset for systems with differential constraints}.
+\textbf{In this work we address the problem of efficiently producing samples in informed subset for systems with arbitrary complex costs}.
 
@@
 Unfortunately, in more general settings such as
-for systems with differential constraints,
+for systems,
 it is not clear how to directly sample \Cinf.
@@
 One approach to produce samples in \Cinf is via \emph{rejection sampling}---sampling a state $x \in \calX$ and testing if $x \in \Cinf$.
-However, when the size of the informed space~$\Cinf$ is much smaller than entire state space~$\calX$, then this procedure may dominate the running time of the algorithm~\cite{KTC16}.
-Recently, Kunz et al.~\cite{KTC16} showed, under some technical assumptions, how to efficiently produce samples in~$\Cinf$ by \emph{Hierarchical rejection sampling} (HRS). 
+However, when the size of the informed space~$\Cinf$ is much smaller than entire state space~$\calX$, then this procedure is highly inefficient, dominating the running time of the algorithm~\cite{KTC16}.
+Recently, Kunz et al.~\cite{KTC16} showed, under some technical assumptions, how to partially ameliorate this efficiently by \emph{Hierarchical rejection sampling} (HRS). 
 Here, individual dimensions are sampled recursively 
@@
 %The novelty of HRS is the ability to fail fast. 
+Unfortunately, HRS may still produce a large number of rejected samples especially in high-dimensional spaces~\cite{KTC16}.
+This may cause the planning algorithm to spend most of its time trying to produces samples in~$\Cinf$ rather than explore it.
 
-Unfortunately, both rejection sampling and HRS may produce a large number of rejected samples especially in high-dimensional spaces.
-This may cause the planning algorithm to spend most of its time trying to produces samples in~$\Cinf$ rather than explore it.
 In this paper, we suggest an alternative approach to produce samples in the informed set \Cinf for a wide range of settings.
-\textbf{Our main insight is to formulate the problem as the problem of sampling uniformly below a level set of an implicit function and then apply optimization and statistical tools.}
+\textbf{
+Our main insight is to recast this problem of sampling uniformly within a level set of an implicit function.
+This recasting enables us to apply Monte Carlo sampling methods, used very effectively in the optimization community, to solve our problem.
+}
+%
+%\textbf{Our main insight is to formulate the problem as the problem of sampling uniformly below a level set of an implicit function and then apply optimization and statistical tools.}
 \os{do we really care about uniformity?}
 Specifically, our approach consists of two stages:
-in the first, a random sample $x \in \calX$ is retracted to the boundary of~$\Cinf$ by running a gradient-descent algorithm;
+in the first, a random sample $x \in \calX$ is retracted to the boundary of~$\Cinf$ by running a root-finding algorithm;
 in the second stage, this retracted sample~$\tilde{x}$ is used to seed a Monte Carlo sampling chain which allows us to  produce samples that (approximately) cover~$\Cinf$  uniformly.
@@
 The nature of random walk in MCMC sometimes requires too many iterations to converge, especially in high-dimension state spaces.
-In consider of efficiency, Hamiltonian Monte Carlo(HMC)~\cite{N11} is thus introduced to replace random walk with Hamiltonian dynamics, which means that future states in the Markov chain is proposed from simulating system dynamics instead of sampling from a jumping distribution.
-It is named ``Hamiltonian, because the concept origins from Hamiltonian dynamics, which defines how system dynamics is determined by system energy.
-Define the system dynamics of an object as the position $ x $ and the momentum $ q $ over time $ t $.
-We have a system energy $ H $ of the object that consists of kinetic energy $ K $ and potential energy $ U $, which is written as $ H(x,q) = U(x) + K(q) $.
-The kinetic energy $ K(q) $ is determined by the momentum $ q $ of the object, while the potential energy $ U(x) $ is determined by the position $ x $ of the object.
-The Hamiltonian dynamics is determined by the gradients of the system energy, which is
-$ \frac{dx}{dt} = \frac{\partial H}{\partial q} $ and $ \frac{dq}{dt} = - \frac{\partial H}{\partial x} $.
-%
-The canonical distribution is often choose to bridge a system energy with a probability distribution, which is written as $ P(x, q) = \frac{1}{Z} \exp ( -H(x,q) / T ) $.
-If two different states have the same energy, the probabilities of them are equivalent.
-It has been proved that properties of Hamiltonian dynamics ``leaves the canonical distribution invariant"~\cite{N11}, which means $ P(x, q) $ equals to a stationary distribution in MCMC.
-Thus, we can generate samples $ [ x , q ]^T $ from joint distribution $ p(x, q) $.
-%
-Given a target distribution $ \pi(x) $, the potential energy is defined in the form $  U(x) = - \log ( \pi(x) T ) $.
-We can have $ P(x, q) = \pi(x) \frac{1}{Z'} \exp ( -K(q) / T ) $, which indicates that $ pi(x) $ is a marginal distribution of $ P(x, q) $.
-In HMC, we sample $ [ x ,q ] $ from $ P(x, q) $ and discard the momentum $ q $ so that the set of samples $ x $ equals to sampling from the marginal distribution $ \pi(x) $.
-The momentum $ q $ is used as an auxiliary variable.
-Avoiding random walk helps samplings converge to the desired distribution $ \pi(x) $ in higher rate~\cite{N11}.
-%
 }
@@
 Given a cost function $C : \calX \times \calU \rightarrow \R$, the cost of a trajectory $ \gamma $ is the accumulated cost along the path
-$c(\gamma) = \int_0^{T} c( x(t), u(t) ) dt$, 
+$c(\gamma) = \int_0^{T} c( x(t), u(t) ) |\dot{\gamma}(t)|dt$, 
 where $T$ is the duration of~$\gamma$.
@@
 Notice that we do not require that~$ \gamma^*(x) $ is collision free.
-
-The informed set induces a probability distribution $\Pinf$. 
-Here, points in \Cinf are distributed uniformly
-while 
-the probability of sampling any configuration $x \in \calX \setminus \Cinf$ is zero.
-Our goal is to efficiently produce samples (approximately) from \Pinf.
 
@@
 \begin{equation}
-x = (q, \dot{q}); 
-\hspace{5mm}
-u = \ddot{q}.
+\begin{bmatrix}
+	\dot{q} \\
+	\ddot{q}
+\end{bmatrix}
+=
+\begin{bmatrix}
+	0 & 1 \\
+	0 & 0
+\end{bmatrix}
+\begin{bmatrix}
+	{q} \\
+	\dot{q}
+\end{bmatrix}
++
+\begin{bmatrix}
+	0 \\
+	1
+\end{bmatrix}
+u
 \end{equation}
-Here, the control $u \in [u_{\text{min}}, u_{\text{max}}]$ is the (bounded) acceleration\footnote{One can also bound the velocity of the system.
-However, to simplify the exposition, we only constrain the system with acceleration bounds.}.
+%\begin{equation}
+%x = (q, \dot{q}); 
+%\hspace{5mm}
+%u = \ddot{q}.
+%\end{equation}
+Here, the control 
+%$u \in [u_{\text{min}}, u_{\text{max}}]$ 
+$u \in [\underline{u}, \overline{u}]$ 
+is the (bounded) acceleration\footnote{One can also bound the velocity of the system. However, to simplify the exposition, we only constrain the system with acceleration bounds.}.
 
@@
 \section{MCMC-based Informed Sampling}
+The informed set induces a probability distribution $\Pinf$. 
+Here, points in \Cinf are distributed uniformly
+while 
+the probability of sampling any configuration $x \in \calX \setminus \Cinf$ is zero.
+Our goal is to efficiently produce samples (approximately) from \Pinf.
+
+\os{connect previous par}
+
 In this section we describe our approach to efficiently produce samples in the informed set~\Cinf given a specific cost~$c_{\text{best}}$.
@@
 Specifically, we chose to use HMC due to its favourable properties (see Sec.~\ref{sec:intro}).
+For a visualization of the approach, see Fig.~\ref{fig:alg}.
+
+\begin{figure}[tb]
+  \centering
+  	\includegraphics[trim={4.5cm 0 4cm 2cm},clip,height = 5.25cm ]{fig/alg.pdf}
+  \caption{
+    \captionstyle
+  	Algorithmic approach.
+  	Cost function is depicted using isocontours (darker shades reflect lower cost) while the boundary of the informed set is depicted in purple. 
+  	The root-finding and MCMC algorithms are depicted in blue and green respectively.
+  	}
+   	\label{fig:alg}
+\end{figure}
 
@@
 
+\os{change section to use c instead of t}
 	Roughly speaking, HMC views the system as an energy function for which Hamiltonian dynamics are simulated in fixed time steps.
@@
 Intuitively, this term biases the distribution towards states with smaller cost and balances between the uniformity of the distribution and the gradient information provided to the HMC algorithm.
-We used $E_{\text{grad}} (t) = \tanh(t + 3 )$ which whose gradient is close to zero for $t>0$.
+We used $E_{\text{grad}} (t) = \tanh(t + \alpha )$,  which whose gradient is close to zero for $t>0$.
+Here, $\alpha$ is some constant that controls the slope of the function\footnote{In our implementation we use $\alpha=3$.}.
 
@@
 Parallel chains
+
+\appendix
+\section{HMC}
+\os{polish}
+
+In consider of efficiency, Hamiltonian Monte Carlo(HMC)~\cite{N11} is thus introduced to replace random walk with Hamiltonian dynamics, which means that future states in the Markov chain is proposed from simulating system dynamics instead of sampling from a jumping distribution.
+It is named ``Hamiltonian, because the concept origins from Hamiltonian dynamics, which defines how system dynamics is determined by system energy.
+Define the system dynamics of an object as the position $ x $ and the momentum $ q $ over time $ t $.
+We have a system energy $ H $ 
+\os{change to E}
+of the object that consists of kinetic energy $ K $ and potential energy $ U $, which is written as $ H(x,q) = U(x) + K(q) $.
+The kinetic energy $ K(q) $ is determined by the momentum $ q $ of the object, while the potential energy $ U(x) $ is determined by the position $ x $ of the object.
+The Hamiltonian dynamics is determined by the gradients of the system energy, which is
+$ \frac{dx}{dt} = \frac{\partial H}{\partial q} $ and $ \frac{dq}{dt} = - \frac{\partial H}{\partial x} $.
+%
+The canonical distribution is often choose to bridge a system energy with a probability distribution, which is written as $ P(x, q) = \frac{1}{Z} \exp ( -H(x,q) / T ) $.
+If two different states have the same energy, the probabilities of them are equivalent.
+It has been proved that properties of Hamiltonian dynamics ``leaves the canonical distribution invariant"~\cite{N11}, which means $ P(x, q) $ equals to a stationary distribution in MCMC.
+Thus, we can generate samples $ [ x , q ]^T $ from joint distribution $ p(x, q) $.
+%
+Given a target distribution $ \pi(x) $, the potential energy is defined in the form $  U(x) = - \log ( \pi(x) T ) $.
+We can have $ P(x, q) = \pi(x) \frac{1}{Z'} \exp ( -K(q) / T ) $, which indicates that $ pi(x) $ is a marginal distribution of $ P(x, q) $.
+In HMC, we sample $ [ x ,q ] $ from $ P(x, q) $ and discard the momentum $ q $ so that the set of samples $ x $ equals to sampling from the marginal distribution $ \pi(x) $.
+The momentum $ q $ is used as an auxiliary variable.
+Avoiding random walk helps samplings converge to the desired distribution $ \pi(x) $ in higher rate~\cite{N11}.
+%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2017-02-24 paper.tex
note

@@
 \os{do we really care about uniformity?}
+\dy{Is it fair to say that uniformity guarantee each state has equal opportunity of being selected?}
 Specifically, our approach consists of two stages:
@@
 \os{This section puts a lot of emphasis on HMC. If we end up choosing an alternative method, we should change the relevant weight}
-
 Monte Carlo simulation is a general sampling framework widely used in various domains such as
@@
 
+\dy{should the ``return'' in Algorithm 1 \ref{alg:mcmc_informed_sampling} be ``yield"?}
+
 \subsection{Sampling the boundary of \Cinf via Newton-Raphson}

### 2017-02-24 paper.tex
change H to E

@@
 Define the system dynamics of an object as the position $ x $ and the momentum $ q $ over time $ t $.
-We have a system energy $ H $ 
-\os{change to E}
-of the object that consists of kinetic energy $ K $ and potential energy $ U $, which is written as $ H(x,q) = U(x) + K(q) $.
+We have a system energy $ E $ 
+%\os{change to E}
+of the object that consists of kinetic energy $ K $ and potential energy $ U $, which is written as $ E(x,q) = U(x) + K(q) $.
 The kinetic energy $ K(q) $ is determined by the momentum $ q $ of the object, while the potential energy $ U(x) $ is determined by the position $ x $ of the object.
 The Hamiltonian dynamics is determined by the gradients of the system energy, which is
-$ \frac{dx}{dt} = \frac{\partial H}{\partial q} $ and $ \frac{dq}{dt} = - \frac{\partial H}{\partial x} $.
+$ \frac{dx}{dt} = \frac{\partial E}{\partial q} $ and $ \frac{dq}{dt} = - \frac{\partial E}{\partial x} $.
 %
-The canonical distribution is often choose to bridge a system energy with a probability distribution, which is written as $ P(x, q) = \frac{1}{Z} \exp ( -H(x,q) / T ) $.
+The canonical distribution is often choose to bridge a system energy with a probability distribution, which is written as $ P(x, q) = \frac{1}{Z} \exp ( -E(x,q) / T ) $.
 If two different states have the same energy, the probabilities of them are equivalent.

### 2017-02-24 paper.tex
added appendix

@@
 \section{HMC}
-\os{polish}
+In this section we provide background on Hamiltonian Monte Carlo (HMC). 
+For a comprehensive description, see~\cite{N11},
+for intuition, see~\cite{ZRDPKDBS13}.
+%Some of the notation in this section
 
-In consider of efficiency, Hamiltonian Monte Carlo(HMC)~\cite{N11} is thus introduced to replace random walk with Hamiltonian dynamics, which means that future states in the Markov chain is proposed from simulating system dynamics instead of sampling from a jumping distribution.
-It is named ``Hamiltonian, because the concept origins from Hamiltonian dynamics, which defines how system dynamics is determined by system energy.
-Define the system dynamics of an object as the position $ x $ and the momentum $ q $ over time $ t $.
-We have a system energy $ E $ 
-%\os{change to E}
-of the object that consists of kinetic energy $ K $ and potential energy $ U $, which is written as $ E(x,q) = U(x) + K(q) $.
-The kinetic energy $ K(q) $ is determined by the momentum $ q $ of the object, while the potential energy $ U(x) $ is determined by the position $ x $ of the object.
-The Hamiltonian dynamics is determined by the gradients of the system energy, which is
-$ \frac{dx}{dt} = \frac{\partial E}{\partial q} $ and $ \frac{dq}{dt} = - \frac{\partial E}{\partial x} $.
+MCMC algorithms typically make use of random-walks to convergence to a target stationary distribution.
+This is often inefficient, resulting in slow mixing\footnote{The \emph{mixing time} of a Markov chain is the time until it is ``close'' to its steady state distribution.}.
+HMC is an MCMC method that adopts physical-system dynamics (specifically Hamiltonian dynamics) rather than a probability distribution to produce the next state in the Markov chain.
+
+\subsection{Hamiltonian dynamics}
+Hamiltonian dynamics describe an object's motion in terms of its position $x$ and momentum $q$ at some time $t$. 
+Each position is associated with a potential energy $U(x)$.
+Similarly, each momentum is associated with a kinetic energy $K(q)$.
+The total energy (also called the Hamiltonian) of the system is constant and is defined as
+$$
+E(x, p) = U(x) + K(q).
+$$
+Hamiltonian dynamics describe how the kinetic and potential energies are converted one to the other as the object moves throughout a system in time. 
+This is done via a set of differential equations known as the Hamiltonian equations:
+$$
+\frac{dx}{dt} = \frac{\partial E}{\partial q}, 
+\hspace{5mm}
+\frac{dq}{dt} = - \frac{\partial E}{\partial x}. $$
 %
-The canonical distribution is often choose to bridge a system energy with a probability distribution, which is written as $ P(x, q) = \frac{1}{Z} \exp ( -E(x,q) / T ) $.
-If two different states have the same energy, the probabilities of them are equivalent.
-It has been proved that properties of Hamiltonian dynamics ``leaves the canonical distribution invariant"~\cite{N11}, which means $ P(x, q) $ equals to a stationary distribution in MCMC.
-Thus, we can generate samples $ [ x , q ]^T $ from joint distribution $ p(x, q) $.
-%
-Given a target distribution $ \pi(x) $, the potential energy is defined in the form $  U(x) = - \log ( \pi(x) T ) $.
-We can have $ P(x, q) = \pi(x) \frac{1}{Z'} \exp ( -K(q) / T ) $, which indicates that $ pi(x) $ is a marginal distribution of $ P(x, q) $.
-In HMC, we sample $ [ x ,q ] $ from $ P(x, q) $ and discard the momentum $ q $ so that the set of samples $ x $ equals to sampling from the marginal distribution $ \pi(x) $.
-The momentum $ q $ is used as an auxiliary variable.
-Avoiding random walk helps samplings converge to the desired distribution $ \pi(x) $ in higher rate~\cite{N11}.
+%The Hamiltonian equations describe an object’s motion in time, which is a continuous variable. In order to simulate Hamiltonian dynamics numerically, the Leapfrog method is typically used.
+
+\subsection{From Hamiltonian dynamics to probability distribution}
+To sample from a desired distribution~$P$ using HMC, we need to convert the distribution to an energy function and vice-versa.
+This is done using the concept of a canonical distribution from statistical mechanics~\cite{N11}.
+Given some energy function,~$E$, the canonical distribution over states has the Boltzman probability distribution $P = \frac{1}{Z}\exp (-E/T)$, where $Z$ is a normalizing constant and~$T$ is the temperature of the system.
+Notice that in our setting
+$$
+P(x,q) 
+\propto e^{-E(x,q)} 
+= e^{-U(x)} \cdot e^{-K(q)}
+\propto P(x) \cdot P(q).
+$$
+This means that the distributions $P(x)$ and $P(q)$ are independent.
+Therefore, we can use Hamiltonian dynamics to sample from the joint distribution over $q$ and $x$ and ignore the momentum contributions.
+Because the two distributions are independent, we can introducing auxiliary variables to represent the momentum and choose any distribution from which to sample the momentum variables.
+A common choice is to use a zero-mean Normal distribution with unit variance.
+
+\subsection{Hamiltonian Monte Carlo}
+HMC uses Hamiltonian dynamics to explore the distribution $P(x)$ defined by $U(x)$. 
+Starting at an initial state $(x_0, q_0)$, 
+(here, $q_0$ is the axillary variable used to simulate the momentum), Hamiltonian dynamics are simulated for a short time using the Leap Frog method. 
+Let $(x^*, q^*)$ be the state at the end of the simulation. 
+This state is accepted using an update rule analogous to the Metropolis acceptance criterion~\cite{CG95}. 
+Specifically, if the probability of $(x^*, q^*)$ after Hamiltonian dynamics is greater than probability of the state prior to the Hamiltonian dynamics, then $(x^*, q^*)$ is accepted.
+Otherwise, $(x^*, q^*)$ is accepted randomly. 
+If $(x^*, q^*)$ is rejected, the next state of the Markov chain is set as the state at $(t-1)$.
+
+To explore the entire space, the dynamics are randomly perturbed.
+This is done by drawing a random momentum from $p(q)$ before running the dynamics prior to each sampling iteration $t$.
+Combining these steps, sampling random momentum, followed by Hamiltonian dynamics and Metropolis acceptance criterion defines the HMC algorithm.
 %

### 2017-02-24 paper.tex
updated fig and polishing

@@
 For Euclidean spaces optimizing for path length, 
-\Cinf can be analytically expressed as a prolate hyperspheroid and can be sampled directly using a closed form solution~\cite{GSB14}.
+\Cinf can be analytically expressed as a prolate hyperspheroid and can be sampled directly using a closed-form solution~\cite{GSB14}.
 Indeed, directly sampling in \Cinf has been shown to dramatically improve computation time when compared to sampling in~$\calX$, especially in high dimensions.
 
-Unfortunately, in more general settings such as
-for systems,
+Unfortunately, in more general settings,
 it is not clear how to directly sample \Cinf.
@@
 One approach to produce samples in \Cinf is via \emph{rejection sampling}---sampling a state $x \in \calX$ and testing if $x \in \Cinf$.
-However, when the size of the informed space~$\Cinf$ is much smaller than entire state space~$\calX$, then this procedure is highly inefficient, dominating the running time of the algorithm~\cite{KTC16}.
-Recently, Kunz et al.~\cite{KTC16} showed, under some technical assumptions, how to partially ameliorate this efficiently by \emph{Hierarchical rejection sampling} (HRS). 
+However, when the size of the informed space~$\Cinf$ is much smaller than entire state space~$\calX$, this procedure is highly inefficient, dominating the running time of the algorithm~\cite{KTC16}.
+Recently, Kunz et al.~\cite{KTC16} showed, under some technical assumptions, how to partially ameliorate this inefficiently by \emph{Hierarchical rejection sampling} (HRS). 
 Here, individual dimensions are sampled recursively 
@@
 \textbf{
-Our main insight is to recast this problem of sampling uniformly within a level set of an implicit function.
+Our main insight is to recast this problem as one of sampling uniformly within a level set of an implicit function.
 This recasting enables us to apply Monte Carlo sampling methods, used very effectively in the optimization community, to solve our problem.
@@
 in the first, a random sample $x \in \calX$ is retracted to the boundary of~$\Cinf$ by running a root-finding algorithm;
-in the second stage, this retracted sample~$\tilde{x}$ is used to seed a Monte Carlo sampling chain which allows us to  produce samples that (approximately) cover~$\Cinf$  uniformly.
+in the second stage, this retracted sample  is used to seed a Monte Carlo sampling chain which allows us to  produce samples that (approximately) cover~$\Cinf$  uniformly.
 
@@
 Many of the algorithms mentioned require solving a two-point boundary value problem (2pBVP) to perform exact and optimal connections between vertices in the roadmap.
-For holonomic robots, these are simply straight lines in the state space, but for kinodynamic sytems with arbitrary cost functions,  computing an optimal trajectory between two states is non-trivial in general.
+For holonomic robots, these are simply straight lines in the configuration space, but for kinodynamic sytems with arbitrary cost functions,  computing an optimal trajectory between two states is non-trivial in general.
 
@@
 Finally, we note that we are not the first to integrate Monte Carlo sampling into planning algorithms.
-T-RRT~\cite{JCS10} and its variants~\cite{DSC13} are inspired by Monte Carlo optimization techniques and use notions such as the Metropolis criterion to guide the exploration of the configuration space.
+T-RRT~\cite{JCS10} and its variants~\cite{DSC13} are inspired by Monte Carlo optimization techniques and use notions such as the Metropolis criterion~\cite{CG95} to guide the exploration of the configuration space.
 
@@
 For planning under the differential constraints,
-reachability-guided sampling~\cite{SWT09, PLAEFRA17} focuses on sampling regions of the state space that are most likely to promote expansion under the differential constraints.
+reachability-guided sampling~\cite{SWT09, PLAEFRA17} focuses on sampling regions of the state space that are most likely to promote expansion for the given constraints.
 
@@
 Roughly speaking, Monte Carlo simulation repeatedly samples a domain at random to approximate some value or function.
-One specific domain where Monte Carlo simulation is used which is of specific interest to us is generating draws from a desired distribution which is hard to sample directly.
+One specific domain where Monte Carlo simulation is used which is relevant to this work is generating draws from a desired distribution which is hard to sample directly.
 
@@
 Notice that we do not require that~$ \gamma^*(x) $ is collision free.
+\os{add fig}
 
@@
   	Cost function is depicted using isocontours (darker shades reflect lower cost) while the boundary of the informed set is depicted in purple. 
-  	The root-finding and MCMC algorithms are depicted in blue and green respectively.
+  	The root-finding and MCMC algorithms are depicted in blue and green, respectively.
   	}
@@
 			\STATE $x_{i} \leftarrow \texttt{MCMC} (x_{i-1}, c_{\text{best}})$
-			\RETURN $x_{i}$
+			\STATE \textbf{output} $x_{i}$
 		\ENDFOR
@@
 
-\os{change section to use c instead of t}
-	Roughly speaking, HMC views the system as an energy function for which Hamiltonian dynamics are simulated in fixed time steps.
-	Thus, to sample from a desired distribution~$P$ using HMC, we need to convert the distribution to an energy function and vice-versa.
+	Roughly speaking, HMC views the system as an energy function for which Hamiltonian dynamics are simulated in fixed time steps (for additional background on HMC see Appendix).
+	Thus, to sample from a desired distribution~$\pi$ using HMC, we need to convert the distribution to an energy function and vice-versa.
 	This is done using the concept of a canonical distribution from statistical mechanics~\cite{N11}. 
-	Given some energy function,~$E$, the canonical distribution over states has the Boltzman probability distribution $P = \frac{1}{Z}\exp (-E/T)$, where $Z$ is a normalizing constant and~$T$ is the temperature of the system.
+	Given some energy function,~$E$, the canonical distribution over states has the Boltzman probability distribution $\pi = \frac{1}{Z}\exp (-E/T)$, where $Z$ is a normalizing constant and~$T$ is the temperature of the system.
 	%Viewing this the opposite way, if we are interested in some distribution with density function $P$, we can obtain it as a canonical distribution with $T = 1$ by setting $E = -\log P - \log Z$, where $Z$ is any convenient positive constant
@@
 
-Our energy for any given time $t$, 
-denoted by~$E\left(t,\Cbest \right)$, 
-is a function of $t$ and the current best cost~$\Cbest$.
+Our energy for any given cost $c$, 
+denoted by~$E\left(c,\Cbest \right)$, 
+is a function of $c$ and the current best cost~$\Cbest$.
 To consider only points in the informed set, all with equal energy, one may consider taking 
@@
 \begin{cases}
-    0,	& \text{if } t \leq \Cbest\\        
+    0,	& \text{if } c \leq \Cbest\\        
     \infty,  	& \text{otherwise}.
@@
 However, simulating Hamiltonian dynamics requires that the energy function defined is differentiable.
-This function has a discontinuity at $t = \Cbest$ 
-and contains no gradient information for $t \leq \Cbest$.
+This function has a discontinuity at $c = \Cbest$ 
+and contains no gradient information for $c \leq \Cbest$.
 Thus, we define our energy function\footnote{In practice we add another term to the energy function which we discuss in Sec.~\ref{sec:eval}. We omit the term here for clarity of exposition.} as  
@@
 \label{eq:energy}
-E\left( t, \Cbest \right) 
+E\left( c, \Cbest \right) 
 = 
-E_{\text{grad}} \left( t \right) + 
-E_{\text{informed}} \left( t,\Cbest \right).
+E_{\text{grad}} \left( c \right) + 
+E_{\text{informed}} \left( c,\Cbest \right).
 \end{equation}
@@
 Intuitively, this term biases the distribution towards states with smaller cost and balances between the uniformity of the distribution and the gradient information provided to the HMC algorithm.
-We used $E_{\text{grad}} (t) = \tanh(t + \alpha )$,  which whose gradient is close to zero for $t>0$.
+We used $E_{\text{grad}} (c) = \tanh(c + \alpha )$,  which whose gradient is close to zero for $c>0$.
 Here, $\alpha$ is some constant that controls the slope of the function\footnote{In our implementation we use $\alpha=3$.}.
@@
 The term 
-$E_{\text{informed}} \left( t,\Cbest \right) 
-= \beta \cdot \text{sigm}\left(t_0 - t\right)
+$E_{\text{informed}} \left( c,\Cbest \right) 
+= \beta \cdot \text{sigm}\left(\Cbest - c\right)
 $
@@
 \section{HMC}
+%base on https://theclevermachine.wordpress.com/2012/11/18/mcmc-hamiltonian-monte-carlo-a-k-a-hybrid-monte-carlo/
+
 In this section we provide background on Hamiltonian Monte Carlo (HMC). 
@@
 for intuition, see~\cite{ZRDPKDBS13}.
-%Some of the notation in this section
+Note that some of the notation in this section slightly differ from the ones used in the main body such as replacing the cost~$c$ with time~$t$.
 
 MCMC algorithms typically make use of random-walks to convergence to a target stationary distribution.
-This is often inefficient, resulting in slow mixing\footnote{The \emph{mixing time} of a Markov chain is the time until it is ``close'' to its steady state distribution.}.
+This is often inefficient, resulting in slow mixing\footnote{Informally, the \emph{mixing time} of a Markov chain is the time until it is ``close'' to its steady-state distribution.}.
 HMC is an MCMC method that adopts physical-system dynamics (specifically Hamiltonian dynamics) rather than a probability distribution to produce the next state in the Markov chain.
@@
 \subsection{From Hamiltonian dynamics to probability distribution}
-To sample from a desired distribution~$P$ using HMC, we need to convert the distribution to an energy function and vice-versa.
+To sample from a desired distribution~$\pi$ using HMC, we need to convert the distribution to an energy function and vice-versa.
 This is done using the concept of a canonical distribution from statistical mechanics~\cite{N11}.
-Given some energy function,~$E$, the canonical distribution over states has the Boltzman probability distribution $P = \frac{1}{Z}\exp (-E/T)$, where $Z$ is a normalizing constant and~$T$ is the temperature of the system.
+Given some energy function,~$E$, the canonical distribution over states has the Boltzman probability distribution $\pi = \frac{1}{Z}\exp (-E/T)$, where $Z$ is a normalizing constant and~$T$ is the temperature of the system.
 Notice that in our setting
 $$
-P(x,q) 
+\pi(x,q) 
 \propto e^{-E(x,q)} 
 = e^{-U(x)} \cdot e^{-K(q)}
-\propto P(x) \cdot P(q).
+\propto \pi(x) \cdot \pi(q).
 $$
-This means that the distributions $P(x)$ and $P(q)$ are independent.
+This means that the distributions $\pi(x)$ and $\pi(q)$ are independent.
 Therefore, we can use Hamiltonian dynamics to sample from the joint distribution over $q$ and $x$ and ignore the momentum contributions.
-Because the two distributions are independent, we can introducing auxiliary variables to represent the momentum and choose any distribution from which to sample the momentum variables.
+This is done by introducing auxiliary variables to represent the momentum and choosing any distribution from which to sample the momentum variables.
 A common choice is to use a zero-mean Normal distribution with unit variance.
@@
 \subsection{Hamiltonian Monte Carlo}
-HMC uses Hamiltonian dynamics to explore the distribution $P(x)$ defined by $U(x)$. 
-Starting at an initial state $(x_0, q_0)$, 
-(here, $q_0$ is the axillary variable used to simulate the momentum), Hamiltonian dynamics are simulated for a short time using the Leap Frog method. 
-Let $(x^*, q^*)$ be the state at the end of the simulation. 
+HMC uses Hamiltonian dynamics to explore the distribution $\pi(x)$ defined by $U(x)$. 
+Starting at an initial state~$(x_0, q_0)$, 
+(here, $q_0$ is the axillary variable used to simulate the momentum), Hamiltonian dynamics are simulated for a short time using the Leap-Frog method~\cite{S82}. 
+Let $(x', q')$ be the state at the end of the simulation. 
 This state is accepted using an update rule analogous to the Metropolis acceptance criterion~\cite{CG95}. 
-Specifically, if the probability of $(x^*, q^*)$ after Hamiltonian dynamics is greater than probability of the state prior to the Hamiltonian dynamics, then $(x^*, q^*)$ is accepted.
-Otherwise, $(x^*, q^*)$ is accepted randomly. 
-If $(x^*, q^*)$ is rejected, the next state of the Markov chain is set as the state at $(t-1)$.
+Specifically, if the probability of $(x', q')$ after Hamiltonian dynamics is greater than probability of the state prior to the Hamiltonian dynamics, then $(x', q')$ is accepted.
+Otherwise, $(x', q')$ is accepted randomly. 
+If~$(x', q')$ is rejected, the next state of the Markov chain is set as the state at the previous time step.
 
 To explore the entire space, the dynamics are randomly perturbed.
-This is done by drawing a random momentum from $p(q)$ before running the dynamics prior to each sampling iteration $t$.
+This is done by drawing a random momentum from $\pi(q)$ before running the dynamics prior to each sampling iteration $t$.
 Combining these steps, sampling random momentum, followed by Hamiltonian dynamics and Metropolis acceptance criterion defines the HMC algorithm.

### 2017-02-27 code/time_efficiency/diff_level_set/plot_time.m
new

@@ -1,0 +1,33 @@
+load('testtime')
+
+testtimelvlhmc1=log(testtimelvlhmc1)
+testtimelvlhmc2=log(testtimelvlhmc2)
+testtimelvlmcmc=log(testtimelvlmcmc)
+testtimelvlrs=log(testtimelvlrs)
+testtimelvlhrs=log(testtimelvlhrs)
+
+figure;
+hold on;
+X = 1:1:6
+mean_hmc1 = mean(testtimelvlhmc1')
+mean_hmc2 = mean(testtimelvlhmc2')
+mean_mcmc = mean(testtimelvlmcmc')
+mean_rs = mean(testtimelvlrs')
+mean_hrs = mean(testtimelvlhrs')
+plot(X,mean_hmc1,'b.-')
+%boxplot(testtimelvlhmc1', 'Notch', 'on', 'Labels', {100, 200, 500, 1000, 3000, 5000},'Colors','b')
+plot(X,mean_hmc2,'g*-')
+%boxplot(testtimelvlhmc2', 'Notch', 'on', 'Labels', {100, 200, 500, 1000, 3000, 5000},'Colors','g')
+plot(X,mean_mcmc,'ys-')
+%boxplot(testtimelvlmcmc', 'Notch', 'on', 'Labels', {100, 200, 500, 1000, 3000, 5000},'Colors','y')
+plot(X,mean_rs,'ro-')
+%boxplot(testtimelvlrs', 'Notch', 'on', 'Labels', {100, 200, 500, 1000, 3000, 5000},'Colors','r')
+plot(X,mean_hrs,'c+-')
+%boxplot(testtimelvlhrs', 'Notch', 'on', 'Labels', {100, 200, 500, 1000, 3000, 5000},'Colors','c')
+legend('HMC1','HMC2','MCMC','RS','HRS')
+
+set(gca, 'XTick', 1:6, 'XTickLabel', {'2.29', '1.94', '1.35', '0.955', '0.84', '0.609'})
+xlabel('Level set')
+ylabel('log time')
+title('Sampling efficiency')
+hold off;

### 2017-02-27 code/time_efficiency/diff_sample_num/calc_ratio.m

@@ -1,0 +1,5 @@
+function y = calc_ratio(x)
+
+ratio = 0.1
+n = 4
+y = x* (x^2 - 0.5^2)^((n-1)/2.) * (pi^2/2) - ratio * 2^n * 2^n

### 2017-02-27 code/time_efficiency/diff_sample_num/find_level_set.m

@@ -1,0 +1,7 @@
+fun = @calc_ratio
+X = [0.5 1]
+
+
+y1 = calc_ratio(0.6)
+y2 = calc_ratio(1)
+level_set = fzero(fun, X)

### 2017-02-27 code/time_efficiency/diff_sample_num/plot_time.m

@@ -1,0 +1,25 @@
+set(groot,'DefaultFigureRenderer','painters')
+
+figure;
+hold on;
+X = 1:1:6
+mean_hmc1 = mean(testtimesnhmc1')
+mean_hmc2 = mean(testtimesnhmc2')
+mean_mcmc = mean(testtimesnmcmc')
+mean_rs = mean(testtimesnrs')
+mean_hrs = mean(testtimesnhrs')
+plot(X,mean_hmc1,'b.-')
+%boxplot(testtimesnhmc1', 'Notch', 'on', 'Labels', {100, 200, 500, 1000, 3000, 5000},'Colors','b')
+plot(X,mean_hmc2,'g*-')
+%boxplot(testtimesnhmc2', 'Notch', 'on', 'Labels', {100, 200, 500, 1000, 3000, 5000},'Colors','g')
+plot(X,mean_mcmc,'ys-')
+%boxplot(testtimesnmcmc', 'Notch', 'on', 'Labels', {100, 200, 500, 1000, 3000, 5000},'Colors','y')
+plot(X,mean_rs,'ro-')
+%boxplot(testtimesnrs', 'Notch', 'on', 'Labels', {100, 200, 500, 1000, 3000, 5000},'Colors','r')
+plot(X,mean_hrs,'c+-')
+%boxplot(testtimesnhrs', 'Notch', 'on', 'Labels', {100, 200, 500, 1000, 3000, 5000},'Colors','c')
+legend('HMC1','HMC2','MCMC','RS','HRS')
+xlabel('Number of samples')
+ylabel('ms')
+title('Sampling efficiency')
+hold off;

### 2017-02-27 code/time_efficiency/plot_time.m

@@ -1,0 +1,4 @@
+boxplot(testtime', 'Notch', 'on', 'Labels', {'HMC'; 'HMC-M'; 'MCMC'; 'RS'; 'HRS'})
+ylabel('ms')
+title('Sampling efficiency')
+

### 2017-02-28 paper.tex
new
?

@@
 \section{MCMC-based Informed Sampling}
-The informed set induces a probability distribution $\Pinf$. 
-Here, points in \Cinf are distributed uniformly
+In this section we describe our approach to efficiently produce samples in the informed set~\Cinf given a specific cost~$c_{\text{best}}$.
+Our algorithm (see Alg.~\ref{alg:mcmc_informed_sampling}) starts by randomly sampling a state~$x_\text{rand} \in \calX$ (line~1).
+This sample is used to produces a 
+sample~$x_0 \in \partial\Cinf$ 
+%sample~$x_\text{boundary} \in \partial\Cinf$ 
+which lies (approximately) on the boundary of the informed set (Sec.~\ref{subsec:grad})by applying Newton-Raphson method~\cite{RT06} (line~2).
+Finally,~$x_0$ 
+%use~$x_\text{boundary}$ 
+is used (lines~3-5)
+to initialize an MCMC algorithm which produces a series of samples within \Cinf (Sec.~\ref{subsec:mcmc}).
+Specifically, we chose to use HMC due to its favourable properties (see Sec.~\ref{sec:intro}).
+For a visualization of the approach, see Fig.~\ref{fig:alg}.
+
+We apply MCMC by using the cost function to define a probability distribution \Pinf.
+Specifically, points in \Cinf are distributed uniformly
 while 
 the probability of sampling any configuration $x \in \calX \setminus \Cinf$ is zero.
-Our goal is to efficiently produce samples (approximately) from \Pinf.
-
-\os{connect previous par}
-
-In this section we describe our approach to efficiently produce samples in the informed set~\Cinf given a specific cost~$c_{\text{best}}$.
-We start  by randomly sampling a state~$x_\text{rand} \in \calX$ and use it
-to produces a sample~$x_\text{boundary} \in \partial\Cinf$ which lies (approximately) on the boundary of the informed set (Sec.~\ref{subsec:grad}).
-This is done by applying Newton-Raphson method~\cite{RT06}.
-We then use~$x_\text{boundary}$ to initialize an MCMC algorithm which produces a series of samples within \Cinf (Sec.~\ref{subsec:mcmc}).
-Specifically, we chose to use HMC due to its favourable properties (see Sec.~\ref{sec:intro}).
-For a visualization of the approach, see Fig.~\ref{fig:alg}.
+The MCMC algorithm will allow us to  efficiently produce samples (approximately) from \Pinf.
 
@@
 		\STATE $x_{\text{rand}} \leftarrow \texttt{sample\_uniform(\calX)}$
-		\STATE $x_{\text{boundary}} \leftarrow
+%		\STATE $x_{\text{boundary}} 
+		\STATE $x_{0} 
+		 \leftarrow
 		 \texttt{newton\_raphson}(x_{\text{rand}}, c_{\text{best}})$
-		\STATE $x_{0} \leftarrow x_{\text{boundary}}$
+%		\STATE $x_{0} \leftarrow x_{\text{boundary}}$
 		\FOR {$i = 1$ to $N$}
@@
 \end{algorithm}
-
-\dy{should the ``return'' in Algorithm 1 \ref{alg:mcmc_informed_sampling} be ``yield"?}
 
@@
 
+\begin{figure}[tb]
+	\centering
+	\includegraphics[height = 4.5cm ]{fig/sampling_efficiency.pdf}
+	\caption{
+		\captionstyle
+		Compare time efficiency of generating 1000 samplings.
+	}
+	\label{fig:compare_time_efficiency}
+\end{figure}
+
 \subsection{Integration}

### 2017-03-02 paper.tex
future work
?

@@
 The Markov Chain can be generated by performing a random walk such as
-in Metropolis-Hastings~\cite{CG95} or Gibbs sampling~\cite{CK94}.
+in Metropolis-Hastings~\cite{CG95}, 
+Gibbs sampling~\cite{CK94},
+hit-and-run~\cite{S84,KSZ11} and their many variants.
 Alternatively, samples on the chain can be generated by simulating Hamiltonian dynamics~\cite{N94} (instead of performing the random walk).
@@
 
-\appendix
+estimating volume of informed space
+
+%\appendix
+\appendices
 \section{HMC}
@@
 Combining these steps, sampling random momentum, followed by Hamiltonian dynamics and Metropolis acceptance criterion defines the HMC algorithm.
+
+\section{Gibbs sampling and Hit-and-run}
+Gibbs sampling is a simple MCMC algorithm which samples each dimension (or variable) from its \emph{conditional distribution} with the remaining variables fixed to their current values.
+Specifically,
+
 %

### 2017-09-08 code/planning efficiency/3d/merge_planning_data2.m
sync data

@@ -1,0 +1,70 @@
+datasetSize = 5;
+maxtimes = zeros(datasetSize,1);
+minvals = zeros(datasetSize,1);
+for i = 0:1:datasetSize-1
+  mcmc_filename = sprintf('data/120s2/simple_MCMC_%d.csv', i);
+  rs_filename = sprintf('data/120s2/simple_RS_%d.csv', i);
+  hrs_filename = sprintf('data/120s2/simple_HRS_%d.csv', i);
+  hnr_filename = sprintf('data/120s2/simple_HNR_%d.csv', i);
+  
+  MCMC = csvread(mcmc_filename);
+  RS = csvread(rs_filename);
+  HRS = csvread(hrs_filename);
+  HNR = csvread(hnr_filename);
+  
+  allTime = vertcat(MCMC(:,1), RS(:,1), HRS(:,1), HNR(:,1));
+  allVal = vertcat(MCMC(:,2), RS(:,2), HRS(:,2), HNR(:,2));
+  maxtimes(i+1,1) = max(allTime);
+  minvals(i+1,1) = min(allVal);
+end
+
+maxT = max(maxtimes);
+minVal = min(minvals);
+
+stepNum = 20;
+MCMC1 = zeros(datasetSize, stepNum+1);
+RS1 = zeros(datasetSize, stepNum+1);
+HRS1 = zeros(datasetSize, stepNum+1);
+HNR1 = zeros(datasetSize, stepNum+1);
+
+stepSize = maxT / stepNum;
+deltaStepSize = stepSize / 5;
+T1 = 0:stepSize:maxT;
+T2 = T1 + deltaStepSize; T2(1) = 0;
+T3 = T1 + deltaStepSize*2; T3(1) = 0;
+T4 = T1 + deltaStepSize*3; T4(1) = 0; 
+
+for i = 0:1:datasetSize-1
+  mcmc_filename = sprintf('data/120s2/simple_MCMC_%d.csv', i);
+  rs_filename = sprintf('data/120s2/simple_RS_%d.csv', i);
+  hrs_filename = sprintf('data/120s2/simple_HRS_%d.csv', i);
+  hnr_filename = sprintf('data/120s2/simple_HNR_%d.csv', i);
+  
+  MCMC = csvread(mcmc_filename);
[…]

### 2017-09-08 code/planning efficiency/3d/plot_data2.m

@@ -1,0 +1,29 @@
+figure(100);
+hold on;
+
+%HMC2 = log(HMC1);
+%HNR2 = log(HNR1);
+%RS2 = log(RS1);
+%HRS2 = log(HRS1);
+
+MCMC2 = MCMC1;
+RS2 = RS1;
+HRS2 = HRS1;
+HNR2 = HNR1;
+
+errorbar(T2, mean(MCMC2,1), std(MCMC2), 'g', 'LineWidth',2);
+errorbar(T3, mean(RS2,1), std(RS2), 'b', 'LineWidth',2);
+errorbar(T4, mean(HRS2,1), std(HRS2), 'c', 'LineWidth',2);
+errorbar(T1, mean(HNR2,1), std(HNR2)', 'r', 'LineWidth',2);
+
+
+plot(T1, mean(MCMC2,1), 'o', 'MarkerFaceColor', 'g', 'MarkerEdgeColor', 'g', 'MarkerSize', 4);
+plot(T2, mean(RS2,1), 'o', 'MarkerFaceColor', 'b', 'MarkerEdgeColor', 'b', 'MarkerSize', 4);
+plot(T3, mean(HRS2,1), 'o', 'MarkerFaceColor', 'c', 'MarkerEdgeColor', 'c', 'MarkerSize', 4);
+plot(T4, mean(HNR2,1), 'o', 'MarkerFaceColor', 'r', 'MarkerEdgeColor', 'r', 'MarkerSize', 4);
+
+xlim([0, 120]);
+legend('MCMC', 'RS', 'HRS', 'HNR');
+xlabel('Time - s');
+ylabel('Ratio to minimum');
+hold off;

### 2017-09-08 code/planning efficiency/6d/merge_planning_data2.m

@@ -1,0 +1,70 @@
+datasetSize = 10;
+maxtimes = zeros(datasetSize,1);
+minvals = zeros(datasetSize,1);
+for i = 0:1:datasetSize-1
+  mcmc_filename = sprintf('data/120s/simple_MCMC_%d.csv', i);
+  rs_filename = sprintf('data/120s/simple_RS_%d.csv', i);
+  hrs_filename = sprintf('data/120s/simple_HRS_%d.csv', i);
+  hnr_filename = sprintf('data/120s/simple_HNR_%d.csv', i);
+  
+  MCMC = csvread(mcmc_filename);
+  RS = csvread(rs_filename);
+  HRS = csvread(hrs_filename);
+  HNR = csvread(hnr_filename);
+  
+  allTime = vertcat(MCMC(:,1), RS(:,1), HRS(:,1), HNR(:,1));
+  allVal = vertcat(MCMC(:,2), RS(:,2), HRS(:,2), HNR(:,2));
+  maxtimes(i+1,1) = max(allTime);
+  minvals(i+1,1) = min(allVal);
+end
+
+maxT = max(maxtimes);
+minVal = min(minvals);
+
+stepNum = 20;
+MCMC1 = zeros(datasetSize, stepNum+1);
+RS1 = zeros(datasetSize, stepNum+1);
+HRS1 = zeros(datasetSize, stepNum+1);
+HNR1 = zeros(datasetSize, stepNum+1);
+
+stepSize = maxT / stepNum;
+deltaStepSize = stepSize / 5;
+T1 = 0:stepSize:maxT;
+T2 = T1 + deltaStepSize; T2(1) = 0;
+T3 = T1 + deltaStepSize*2; T3(1) = 0;
+T4 = T1 + deltaStepSize*3; T4(1) = 0; 
+
+for i = 0:1:datasetSize-1
+  mcmc_filename = sprintf('data/120s/simple_MCMC_%d.csv', i);
+  rs_filename = sprintf('data/120s/simple_RS_%d.csv', i);
+  hrs_filename = sprintf('data/120s/simple_HRS_%d.csv', i);
+  hnr_filename = sprintf('data/120s/simple_HNR_%d.csv', i);
+  
+  MCMC = csvread(mcmc_filename);
+  RS = csvread(rs_filename);
[…]

### 2017-09-08 code/planning efficiency/6dof_snake/problem1/plot_data2.m

@@ -1,0 +1,29 @@
+figure(100);
+hold on;
+
+%HMC2 = log(HMC1);
+%HNR2 = log(HNR1);
+%RS2 = log(RS1);
+%HRS2 = log(HRS1);
+
+MCMC2 = MCMC1;
+RS2 = RS1;
+HRS2 = HRS1;
+HNR2 = HNR1;
+
+errorbar(T2, mean(MCMC2,1), std(MCMC2), 'g', 'LineWidth',2);
+errorbar(T3, mean(RS2,1), std(RS2), 'b', 'LineWidth',2);
+errorbar(T4, mean(HRS2,1), std(HRS2), 'c', 'LineWidth',2);
+errorbar(T1, mean(HNR2,1), std(HNR2)', 'r', 'LineWidth',2);
+
+
+plot(T1, mean(MCMC2,1), 'o', 'MarkerFaceColor', 'g', 'MarkerEdgeColor', 'g', 'MarkerSize', 4);
+plot(T2, mean(RS2,1), 'o', 'MarkerFaceColor', 'b', 'MarkerEdgeColor', 'b', 'MarkerSize', 4);
+plot(T3, mean(HRS2,1), 'o', 'MarkerFaceColor', 'c', 'MarkerEdgeColor', 'c', 'MarkerSize', 4);
+plot(T4, mean(HNR2,1), 'o', 'MarkerFaceColor', 'r', 'MarkerEdgeColor', 'r', 'MarkerSize', 4);
+
+xlim([0, 4]);
+legend('MCMC', 'RS', 'HRS', 'HNR');
+xlabel('Time - s');
+ylabel('Ratio to minimum');
+hold off;

### 2017-09-08 code/planning efficiency/6dof_snake/problem1/resample_data.m

@@ -1,0 +1,20 @@
+function [ new_Y ] = resample_data( Y, X, new_X )
+
+  [new_numX, dim] = size(new_X);
+  [numY,dim] = size(Y);
+  new_Y = zeros(new_numX,dim);
+  
+  idx = 1;
+  for i=1:1:new_numX
+    if idx == 1 && X(idx,1) > new_X(i,1)
+       new_Y(i,1) = inf;
+       continue;
+    end
+    while X(idx,1) < new_X(i,1) && idx < numY  
+         idx = idx + 1;
+    end
+    new_Y(i,1) = Y(idx,1);
+  end
+
+end
+

### 2017-09-08 code/planning efficiency/8dof_snake/problem1/merge_planning_data2.m

@@ -1,0 +1,70 @@
+datasetSize = 10;
+maxtimes = zeros(datasetSize,1);
+minvals = zeros(datasetSize,1);
+for i = 0:1:datasetSize-1
+  mcmc_filename = sprintf('data/10s/simple_MCMC_%d.csv', i);
+  rs_filename = sprintf('data/10s/simple_RS_%d.csv', i);
+  hrs_filename = sprintf('data/10s/simple_HRS_%d.csv', i);
+  hnr_filename = sprintf('data/10s/simple_HNR_%d.csv', i);
+  
+  MCMC = csvread(mcmc_filename);
+  RS = csvread(rs_filename);
+  HRS = csvread(hrs_filename);
+  HNR = csvread(hnr_filename);
+  
+  allTime = vertcat(MCMC(:,1), RS(:,1), HRS(:,1), HNR(:,1));
+  allVal = vertcat(MCMC(:,2), RS(:,2), HRS(:,2), HNR(:,2));
+  maxtimes(i+1,1) = max(allTime);
+  minvals(i+1,1) = min(allVal);
+end
+
+maxT = max(maxtimes);
+minVal = min(minvals);
+
+stepNum = 20;
+MCMC1 = zeros(datasetSize, stepNum+1);
+RS1 = zeros(datasetSize, stepNum+1);
+HRS1 = zeros(datasetSize, stepNum+1);
+HNR1 = zeros(datasetSize, stepNum+1);
+
+stepSize = maxT / stepNum;
+deltaStepSize = stepSize / 5;
+T1 = 0:stepSize:maxT;
+T2 = T1 + deltaStepSize; T2(1) = 0;
+T3 = T1 + deltaStepSize*2; T3(1) = 0;
+T4 = T1 + deltaStepSize*3; T4(1) = 0; 
+
+for i = 0:1:datasetSize-1
+  mcmc_filename = sprintf('data/10s/simple_MCMC_%d.csv', i);
+  rs_filename = sprintf('data/10s/simple_RS_%d.csv', i);
+  hrs_filename = sprintf('data/10s/simple_HRS_%d.csv', i);
+  hnr_filename = sprintf('data/10s/simple_HNR_%d.csv', i);
+  
+  MCMC = csvread(mcmc_filename);
+  RS = csvread(rs_filename);
[…]

### 2017-09-08 code/planning efficiency/8dof_snake/problem2/plot_data2.m

@@ -1,0 +1,29 @@
+figure(100);
+hold on;
+
+%HMC2 = log(HMC1);
+%HNR2 = log(HNR1);
+%RS2 = log(RS1);
+%HRS2 = log(HRS1);
+
+MCMC2 = MCMC1;
+RS2 = RS1;
+HRS2 = HRS1;
+HNR2 = HNR1;
+
+errorbar(T2, mean(MCMC2,1), std(MCMC2), 'g', 'LineWidth',2);
+errorbar(T3, mean(RS2,1), std(RS2), 'b', 'LineWidth',2);
+errorbar(T4, mean(HRS2,1), std(HRS2), 'c', 'LineWidth',2);
+errorbar(T1, mean(HNR2,1), std(HNR2)', 'r', 'LineWidth',2);
+
+
+plot(T1, mean(MCMC2,1), 'o', 'MarkerFaceColor', 'g', 'MarkerEdgeColor', 'g', 'MarkerSize', 4);
+plot(T2, mean(RS2,1), 'o', 'MarkerFaceColor', 'b', 'MarkerEdgeColor', 'b', 'MarkerSize', 4);
+plot(T3, mean(HRS2,1), 'o', 'MarkerFaceColor', 'c', 'MarkerEdgeColor', 'c', 'MarkerSize', 4);
+plot(T4, mean(HNR2,1), 'o', 'MarkerFaceColor', 'r', 'MarkerEdgeColor', 'r', 'MarkerSize', 4);
+
+xlim([0, 10]);
+legend('MCMC', 'RS', 'HRS', 'HNR');
+xlabel('Time - s');
+ylabel('Ratio to minimum');
+hold off;

### 2017-09-08 code/planning efficiency/planar_manipulator/merge_planning_data.m

@@ -1,0 +1,68 @@
+datasetSize = 10;
+maxtimes = zeros(datasetSize,1);
+minvals = zeros(datasetSize,1);
+for i = 0:1:datasetSize-1
+  hnr_filename = sprintf('data/3d/3s/simple_HNR_%d.csv', i);
+  mcmc_filename = sprintf('data/3d/3s/simple_MCMC_%d.csv', i);
+  rs_filename = sprintf('data/3d/3s/simple_RS_%d.csv', i);
+  hrs_filename = sprintf('data/3d/3s/simple_HRS_%d.csv', i);
+  
+  HNR = csvread(hnr_filename);
+  MCMC = csvread(mcmc_filename);
+  RS = csvread(rs_filename);
+  HRS = csvread(hrs_filename);
+  
+  allTime = vertcat(HNR(:,1), MCMC(:,1), RS(:,1), HRS(:,1));
+  allVal = vertcat(HNR(:,2), MCMC(:,2), RS(:,2), HRS(:,2));
+  maxtimes(i+1,1) = max(allTime);
+  minvals(i+1,1) = min(allVal);
+end
+
+maxT = max(maxtimes);
+minVal = min(minvals);
+
+stepNum = 20;
+HNR1 = zeros(datasetSize, stepNum+1);
+MCMC1 = zeros(datasetSize, stepNum+1);
+RS1 = zeros(datasetSize, stepNum+1);
+HRS1 = zeros(datasetSize, stepNum+1);
+
+stepSize = maxT / stepNum;
+deltaStepSize = stepSize / 5;
+T1 = 0:stepSize:maxT;
+T2 = T1 + deltaStepSize; T2(1) = 0;
+T3 = T1 + deltaStepSize*2; T3(1) = 0;
+T4 = T1 + deltaStepSize*3; T4(1) = 0; 
+
+for i = 0:1:datasetSize-1
+  hnr_filename = sprintf('data/3d/3s/simple_HNR_%d.csv', i);
+  mcmc_filename = sprintf('data/3d/3s/simple_MCMC_%d.csv', i);
+  rs_filename = sprintf('data/3d/3s/simple_RS_%d.csv', i);
+  hrs_filename = sprintf('data/3d/3s/simple_HRS_%d.csv', i);
+  
+  HNR = csvread(hnr_filename);
[…]

### 2017-09-08 code/planning efficiency/planar_manipulator/plot_data.m

@@ -1,0 +1,28 @@
+figure(100);
+hold on;
+
+%HMC2 = log(HMC1);
+%HNR2 = log(HNR1);
+%RS2 = log(RS1);
+%HRS2 = log(HRS1);
+
+HNR2 = HNR1;
+MCMC2 = MCMC1;
+RS2 = RS1;
+HRS2 = HRS1;
+
+errorbar(T1, mean(HNR2,1), std(HNR2)', 'r', 'LineWidth',2);
+errorbar(T2, mean(MCMC2,1), std(MCMC2), 'g', 'LineWidth',2);
+errorbar(T3, mean(RS2,1), std(RS2), 'b', 'LineWidth',2);
+errorbar(T4, mean(HRS2,1), std(HRS2), 'c', 'LineWidth',2);
+
+plot(T1, mean(HNR2,1), 'o', 'MarkerFaceColor', 'r', 'MarkerEdgeColor', 'r', 'MarkerSize', 4);
+plot(T2, mean(MCMC2,1), 'o', 'MarkerFaceColor', 'g', 'MarkerEdgeColor', 'g', 'MarkerSize', 4);
+plot(T3, mean(RS2,1), 'o', 'MarkerFaceColor', 'b', 'MarkerEdgeColor', 'b', 'MarkerSize', 4);
+plot(T4, mean(HRS2,1), 'o', 'MarkerFaceColor', 'c', 'MarkerEdgeColor', 'c', 'MarkerSize', 4);
+
+xlim([0, 3]);
+legend('HNR', 'MCMC', 'RS', 'HRS');
+xlabel('Time - s');
+ylabel('Ratio to minimum');
+hold off;

### 2017-09-11 paper.tex
sync

--- 2017-02-28 paper.tex
@@
 \usepackage{bm}
-\usepackage{graphicx,subfigure}
+\usepackage{graphicx}
+\usepackage[font=footnotesize]{caption} % incompatible with aaai.sty?
+\usepackage[font=footnotesize]{subcaption}
 \usepackage{color}
@@
 Following Gammell et al.~\cite{GSB14}, we call this subset the \emph{informed subset} and denote it~$\Cinf$.
-\textbf{In this work we address the problem of efficiently producing samples in informed subset for systems with arbitrary complex costs}.
+In this work we address the problem of efficiently producing samples in informed subset for systems with arbitrary complex costs.
 
@@
 %
-One approach to produce samples in \Cinf is via \emph{rejection sampling}---sampling a state $x \in \calX$ and testing if $x \in \Cinf$.
+One approach to produce samples in~\Cinf is via \emph{rejection sampling}---sampling a state $x \in \calX$ and testing if $x \in \Cinf$.
 However, when the size of the informed space~$\Cinf$ is much smaller than entire state space~$\calX$, this procedure is highly inefficient, dominating the running time of the algorithm~\cite{KTC16}.
@@
 
+\begin{figure}[tb]
+  \centering
+  	\includegraphics[trim={4.5cm 0 4cm 2cm},clip,height = 5.25cm ]{fig/alg.pdf}
+  \caption{
+    \captionstyle
+  	Algorithmic approach.
+  	Cost function is depicted using isocontours (darker shades reflect lower cost) while the boundary of the informed set is depicted in purple. 
+  	The root-finding and MCMC algorithms are depicted in blue and green, respectively.
+  	}
+   	\label{fig:alg}
+\end{figure}
+
 In this paper, we suggest an alternative approach to produce samples in the informed set \Cinf for a wide range of settings.
@@
 Our main insight is to recast this problem as one of sampling uniformly within a level set of an implicit function.
-This recasting enables us to apply Monte Carlo sampling methods, used very effectively in the optimization community, to solve our problem.
+This recasting enables us to apply Monte Carlo sampling methods, used very effectively in the Machine Learning and Optimization communities, to solve our problem.
 }
-%
-%\textbf{Our main insight is to formulate the problem as the problem of sampling uniformly below a level set of an implicit function and then apply optimization and statistical tools.}
-\os{do we really care about uniformity?}
-\dy{Is it fair to say that uniformity guarantee each state has equal opportunity of being selected?}
-Specifically, our approach consists of two stages:
+Specifically, our approach, depicted in Fig~\ref{fig:alg} consists of two stages:
 in the first, a random sample $x \in \calX$ is retracted to the boundary of~$\Cinf$ by running a root-finding algorithm;
@@
 
+While our approach can be used with any Markov chain Monte Carlo (MCMC) method, it is especially suited to be used with hit and run~\cite{S84,KSZ11}.
+Roughly speaking, this is because hit and run (detailed in Sec~\ref{sec:related_work})
+performs a series of one-dimensional rejection samples which are extremely fast to compute, even in high-dimensional spaces.
+
 Our approach requires that the system has a solution to the two-point boundary value problem (2pBVP)~\cite{L06, H02} and that a gradient can be defined over the cost function.
-Indeed, we demonstrate the efficiency of our approach on a wide variety of systems and show that it enables reducing the planning time by several orders of magnitute when compared to algorithms using rejection sampling or HRS.
+Indeed, we demonstrate the efficiency of our approach on a wide variety of systems and show that it enables reducing the planning time by several orders of magnitude when compared to algorithms using rejection sampling or HRS.
 
 \os{structure}
-
-%While, original sampling-based algorithms such as RRT~\cite{LK01} and PRM~\cite{KSLO96} only guaranteed to asymptotically return \emph{a} solution, if one exists, they did not provide any guarantees on the \emph{quality} of the solution, given some optimization criteria.
-%Karaman and Frazzoli~\cite{KF11}, presented variants of PRM and RRT, named PRM* and RRT*, respectively that were shown to produce paths who's cost converges asymptotically to the minimal-cost path.
-%Additional algorithms followed, increasing the converges rate by various techniques such as lazy dynamic programming~\cite{GSB15, JSCP15}, relaxing optimality to near-optimality~\cite{DB14, SH16} and more.
-%
-%However, recent years 
-%Original planners such as RRT~\cite{LK01} and PRM~\cite{KSLO96} did not provide any guarantee on the \emph{s}
 
@@
 
-%Finally, we note that there have been many papers presenting solutions to the 2pBVP for specific systems such as
-%
-%Jeong Hwan Jeon, Raghvendra V.
-Cowlagi, Steven C.
-Peters, Sertac Karaman, Emilio Frazzoli, Panagiotis Tsiotras, Karl Iagnemma: Optimal motion planning with the half-car dynamical model for autonomous high-speed driving.
-ACC 2013: 188-193
-%Dubins cars optimizng for both time and energy (RSS submission 107 by Shammas, Elie)
-
-%possible additional papers on Kinodynamic RRT*:~\cite{KF10, GPPK13}
-
 \subsection{State-space sampling}
@@
 \label{subsec:mcmc}
-\os{This section puts a lot of emphasis on HMC. If we end up choosing an alternative method, we should change the relevant weight}
 Monte Carlo simulation is a general sampling framework widely used in various domains such as
@@
 The Markov Chain can be generated by performing a random walk such as
-in Metropolis-Hastings~\cite{CG95} or Gibbs sampling~\cite{CK94}.
-Alternatively, samples on the chain can be generated by simulating Hamiltonian dynamics~\cite{N94} (instead of performing the random walk).
-This approach, termed Hybrid or Hamiltonian Monte Carlo (HMC)~\cite{N11} was shown to converge faster to the desired distribution, when compared to random-walk based MCMC algorithms.
+in Metropolis-Hastings~\cite{CG95}, 
+Gibbs sampling~\cite{CK94}
+or by simulating simulating Hamiltonian dynamics~\cite{N94} (instead of performing the random walk).
 
-%\deprecated{
-\ignore{ which means that future states in the Markov chain is proposed from simulating system dynamics instead of sampling from a jumping distribution.
-%
-%
-An alternative sampling framework, which is widely used in statistical machine learning, is Monte Carlo Simulation~\cite{M97}.
-%
-It uses the numerical experimental power of computers to generate samples toward a desired distribution $ \pi (x) $.
-The generated set of samples are a discrete approximation $ \hat{\pi} (x) $ of the desired distribution $ \pi (x) $.
-A approximated desired distribution $ \hat{\pi} (x) $ can be used in any problem that states are modeled random variable, e.g.
-motion tracking~\cite{KBD04}, data regression~\cite{TL11} and state estimation~\cite{ASC13}.
-%
-Markov Chain Monte Carlo (MCMC)~\cite{ADDJ03} is one most popular class that constructs a Markov chain of random transition that moves samples from an original proposed distribution to a desired distribution $ \pi (x) $.
-The random movement is driven by a jumping distribution $ g(x' \mid x) $, which samples a new state $ x' $ by a given state $ x $.
-The idea of MCMC is designing a jumping distribution $ g $ that makes the desired distribution a stationary distribution $ \pi = \pi * g $.
-\emph{Ergodic theorem} shows that if the jumping distribution is aperiodic, irreducible and positive recurrent~\cite{AG11}, samples generated from arbitrary distributions will gradually converge to the stationary (desired) distribution $ \pi $.
-In practice, samples are initially generated from an arbitrary distribution.
-They shall converge to the samples generated from the desired distribution () 
-A few MCMC algorithms, e.g. Gibbs sampling and Metropolis-Hastings, have been widely used in sampling from distributions that are difficult to directly sample.
-%
-The nature of random walk in MCMC sometimes requires too many iterations to converge, especially in high-dimension state spaces.
-}
+One variant, which is of special interest to us is 
+hit-and-run~\cite{S84,KSZ11}.
+Here, given the current point $x_i$ the next point~$x_{i+1}$ in the Markov chain is produced by sampling a random direction~$\theta$ on the surface of the unit sphere centered at $x_{i+1}$.
+This defines a ray $r_i$ rooted at $x_i$ and passing through~$\theta$.
+The point $x_{i+1}$ is chosen by randomly sampling a point on $r_i$.
+This algorithm is considered to be one of the most efficient algorithms for generating an asymptotically uniform point if the set under consideration is convex~\cite{L99, LV06}
+and it can also be extended to sample points that converge to an arbitrary target distribution in total variation~\cite{BRS93, RS94}.
+
+The attractiveness of hit and run for our problem domain stems from the fact that it performs a series of one-dimensional rejection samples which are extremely fast to compute, even in high-dimensional spaces.
+Finally, it is worth noting that we are not the first to apply hit and run for motion-planning problems.
+Recently~\cite{YPVA17} was used as an alternative to RRT to produce \emph{feasible motions} (and not high-quality paths). 
+Interestingly the paper concludes with the statement ``\emph{One drawback is that the sample paths for Hit and-Run have no pruning and are therefore longer than the RRT paths.
+Hybrid approaches that yield short paths but also explore quickly are a promising future direction.}''
+Our paper can be seen as a hybrid approach marrying sampling-based planning with MCM-based approaches.
 
@@
 Notice that we do not require that~$ \gamma^*(x) $ is collision free.
-\os{add fig}
-
-\ignore{
-Define the dynamics of a robot as 
-\begin{equation}
-\label{eq:kinematics}
-\dot{x}(t) = f( x(t) , u(t) ), 
-\end{equation}
-in which $ x \in \calX \subseteq \mathbb{R}^n $ is the state of the robot, and $ u \in \calU \subseteq \mathbb{R}^m $ is the control input.
-The dynamics determines how a state trajectory $ \gamma $ is like given duration $ T $, state $ x(t) $ and input $ u(t) $.
-There exists a free trajectory space $ \Pi_{free} $ that contains all feasible trajectories $ \gamma \in \Gamma_{\rm free} $.
-It is determined by the system dynamics, $\Cfree $ and $ \Ufree $, in which $ \Cfree \subseteq \calX $ is a free state space considering the obstacles in a workspace, and $ \Ufree \subseteq \calU $ is a free control space considering the bounds of control input.
-The cost of a trajectory $ \gamma $ is defined as the accumulated cost $ c( x(t), u(t) ) $ along the path, which is 
-\begin{equation}
-\label{eq:path_cost}
-c(\gamma) = \int_0^{T} c( x(t), u(t) ) dt.
-\end{equation}
-An optimal kinodynamic path-planning problem that finds a kinodynamic path minimizing the cost $ \pi^* = \min_{ \pi \in \Gamma_{free} } c( \gamma ) $.
-
-Informed sampling-based planning algorithms (e.g. Informed RRT*~\cite{GSB14}, BIT*~\cite{GSB15}) samples new states only from an \emph{informed set}.
-An informed set is a subspace $ \Cinf \subseteq \calX $   that is possible to provide better solution than the current best $  \Cinf = \{ x \in \calX \mid c ( \gamma^*(x) ) < \cbest \} $~\cite{GSB14}, in which $ \gamma^*(x) $ means the optimal path from $ x_s $ to $ x_g $ constrained to pass through $ x $ without considering collision checking, and $ \cbest $ is the cost of the current best found.
-The current best $ \cbest $ constrains eligible $ x $ indirectly by an implicit $ \gamma^*(x) $.
-In an optimal kinodynamic path-planning problem, more constraints are considered in defining an informed set, which include the system dynamic constraint and the boundary of control input.
-If we consider a manifold that is defined by an informed set $ \Cinf $, the informed sampling becomes how to sample on this manifold in a high-dimensional space. }
 
@@
 It is straightforward to see that both the type and the amount of acceleration applied (and hence the structure of~\Cinf) depend on the specific values of~$x_s$ and~$x_g$. 
-Fig~\ref{fig:informed_sets} 
-depicts two informed sets defined using the same cost~$c_{\text{best}}$ but different start and goal states. Notice the difference in structure of~\Cinf. 
+%Fig~\ref{fig:informed_sets} depicts two informed sets defined using the same cost~$c_{\text{best}}$ but different start and goal states. Notice the difference in structure of~\Cinf. 
 Fig~\ref{fig:discont} depicts a simple example where the cost map is discontinuous.
@@
 
-\begin{figure}[tb]
-  \centering
-  	\includegraphics[trim={4.5cm 0 4cm 2cm},clip,height = 5.25cm ]{fig/alg.pdf}
-  \caption{
-    \captionstyle
-  	Algorithmic approach.
-  	Cost function is depicted using isocontours (darker shades reflect lower cost) while the boundary of the informed set is depicted in purple. 
-  	The root-finding and MCMC algorithms are depicted in blue and green, respectively.
-  	}
-   	\label{fig:alg}
-\end{figure}
-
 \begin{algorithm}[t]
@@
    	\end{algorithmic}
-	\caption{MCMC Informed Sampling $(c_{\text{best}})$}
+	\caption{MCMC-based Informed Sampling $(c_{\text{best}})$}
 	\label{alg:mcmc_informed_sampling}	
@@
 
-\subsection{Sampling the interior of \Cinf via
-MCMC}
+\subsection{Sampling the interior of \Cinf via MCMC}
 \label{subsec:mcmc}
-\os{once we have results we need to discuss here (or in the implementation details), how is this used: Do we use one chain? Do we restart from scratch? Do we use every sample on the chain?}
-
-	Roughly speaking, HMC views the system as an energy function for which Hamiltonian dynamics are simulated in fixed time steps (for additional background on HMC see Appendix).
-	Thus, to sample from a desired distribution~$\pi$ using HMC, we need to convert the distribution to an energy function and vice-versa.
-	This is done using the concept of a canonical distribution from statistical mechanics~\cite{N11}. 
-	Given some energy function,~$E$, the canonical distribution over states has the Boltzman probability distribution $\pi = \frac{1}{Z}\exp (-E/T)$, where $Z$ is a normalizing constant and~$T$ is the temperature of the system.
-	%Viewing this the opposite way, if we are interested in some distribution with density function $P$, we can obtain it as a canonical distribution with $T = 1$ by setting $E = -\log P - \log Z$, where $Z$ is any convenient positive constant
-
-The energy function's definition provides the flexibility to specify desired or more probable states (by presenting lower energies) without the need to use a formal and restrictive model. 
-Specifically, in our setting we want to approximate 
-a uniform distribution over points inside the informed set~\Cinf.
-
-Our energy for any given cost $c$, 
-denoted by~$E\left(c,\Cbest \right)$, 
-is a function of $c$ and the current best cost~$\Cbest$.
-To consider only points in the informed set, all with equal energy, one may consider taking 
-$$
-E\left(t,\Cbest \right) = 
-\begin{cases}
-    0,	& \text{if } c \leq \Cbest\\        
-    \infty,  	& \text{otherwise}.
-\end{cases}
-$$
-However, simulating Hamiltonian dynamics requires that the energy function defined is differentiable.
-This function has a discontinuity at $c = \Cbest$ 
-and contains no gradient information for $c \leq \Cbest$.
-Thus, we define our energy function\footnote{In practice we add another term to the energy function which we discuss in Sec.~\ref{sec:eval}. We omit the term here for clarity of exposition.} as  
-\begin{equation}
-\label{eq:energy}
-E\left( c, \Cbest \right) 
-= 
-E_{\text{grad}} \left( c \right) + 
-E_{\text{informed}} \left( c,\Cbest \right).
-\end{equation}
-Here, $E_{\text{grad}}$ is a user-defined function that
-controls the ``flatness`` of the distribution.
-Intuitively, this term biases the distribution towards states with smaller cost and balances between the uniformity of the distribution and the gradient information provided to the HMC algorithm.
-We used $E_{\text{grad}} (c) = \tanh(c + \alpha )$,  which whose gradient is close to zero for $c>0$.
-Here, $\alpha$ is some constant that controls the slope of the function\footnote{In our implementation we use $\alpha=3$.}.
-
-The term 
-$E_{\text{informed}} \left( c,\Cbest \right) 
-= \beta \cdot \text{sigm}\left(\Cbest - c\right)
-$
-penalizes states outside the informed set~$\Cinf$ using a tight sigmoid function~$\text{sigm}$ scaled by some (large\footnote{The constant~$\beta$ gives points out of~\Cinf a large energy value which in turn implies a low probability of being sampled.
-In theory, we would like to have~$\beta \approx \infty$.
-However, choosing~$\beta$ to be too large may cause numerical instabilities.}) constant~$\beta$.
-The sigmoid can be seen as a differentiable function smoothing the boundary of~$\Cinf$.
-See Fig.~\ref{fig:energy} for a visualization.
-
-\begin{figure}[tb]
-  \centering
-  	\includegraphics[height = 4.5cm ]{fig/energy.pdf}
-  \caption{
-    \captionstyle
-  	Energy function used by HMC to obtain samples~$x \in \Cinf$.
-  	}
-   	\label{fig:energy}
-\end{figure}
-
-\subsection{Implementation details}
-In our implementation we add another term to our energy function (Eq.~\ref{eq:energy}) relating to system parameters that induce known bounds on states.
-Specifically, our robot has predefined joint limits. 
-The flexibility of the energy function allows us to incorporate these limits  to penalize states \emph{within} the informed set that are violating these limits.
-
-Specifically, we add to Eq.~\ref{eq:energy} the term 
-$
-E_{\text{limits}}\left(\mathbf{x}\right) = \beta\cdot \text{sigm} ( ||\mathbf{x}_{\text{limits}} - \mathbf{x}||_2 )
-$
-where $||\mathbf{x}_{\text{limits}} - \mathbf{x}||_2$ represents the L2 distance between the current state $\mathbf{x}$ and the state limits~$\mathbf{x}_{\text{limits}}$.
 
@@
 
-\begin{figure}[tb]
+\begin{figure}[t!]
 	\centering
-	\includegraphics[height = 4.5cm ]{fig/sampling_efficiency.pdf}
-	\caption{
-		\captionstyle
-		Compare time efficiency of generating 1000 samplings.
-	}
-	\label{fig:compare_time_efficiency}
+	\begin{subfigure}[b]{0.5\textwidth}
+		\includegraphics[width=\linewidth]{fig/sampling_efficiency/sample_efficiency_2d}
+		\caption{2D}
+		\label{fig:sampling_efficiency:2d}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.5\textwidth}
+		\includegraphics[width=\linewidth]{fig/sampling_efficiency/sample_efficiency_4d}
+		\caption{4D}
+		\label{fig:sampling_efficiency:4d}
+	\end{subfigure}	
+	\begin{subfigure}[b]{0.5\textwidth}
+		\includegraphics[width=\linewidth]{fig/sampling_efficiency/sample_efficiency_6d}
+		\caption{6D}
+		\label{fig:sampling_efficiency:6d}
+	\end{subfigure}
+	\caption{\captionstyle Compare the sampling efficiency of different sampling methods.}
+	\label{fig:sampling_efficiency}
 \end{figure}
@@
 
+\begin{figure}[t!]
+	\centering
+	\begin{subfigure}[b]{0.5\textwidth}
+		\includegraphics[width=\linewidth]{fig/planning_efficiency/3dof_example}
+		\caption{3DOF planar}
+		\label{fig:planning_efficiency:3dof:example}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.5\textwidth}
+		\includegraphics[width=\linewidth]{fig/planning_efficiency/3dof_general}
+		\caption{Obstacle avoiding}
+		\label{fig:planning_efficiency:3dof:general}
+	\end{subfigure}	
+	\begin{subfigure}[b]{0.5\textwidth}
+		\includegraphics[width=\linewidth]{fig/planning_efficiency/3dof_hammering}
+		\caption{Hammering}
+		\label{fig:planning_efficiency:3dof:hammering}
+	\end{subfigure}
+	\caption{\captionstyle An example of a 3DOF planar manipulator.}
+	\label{fig:planning_efficiency:3dof}
+\end{figure}
+
+\begin{figure}[t!]
+	\centering
+	\begin{subfigure}[b]{0.5\textwidth}
+		\includegraphics[width=\linewidth]{fig/planning_efficiency/6dof_example}
+		\caption{6DOF snake}
+		\label{fig:planning_efficiency:6dof:example}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.5\textwidth}
+		\includegraphics[width=\linewidth]{fig/planning_efficiency/6dof_general}
+		\caption{Obstacle avoiding}
+		\label{fig:planning_efficiency:6dof:general}
+	\end{subfigure}	
+	\begin{subfigure}[b]{0.5\textwidth}
+		\includegraphics[width=\linewidth]{fig/planning_efficiency/6dof_hammering}
+		\caption{Hammering}
+		\label{fig:planning_efficiency:6dof:hammering}
+	\end{subfigure}
+	\caption{\captionstyle An example of a 6DOF 3D snake.}
+	\label{fig:planning_efficiency:3dof}
+\end{figure}
+
 \section{Conclusion}
@@
 
-\appendix
-\section{HMC}
-%base on https://theclevermachine.wordpress.com/2012/11/18/mcmc-hamiltonian-monte-carlo-a-k-a-hybrid-monte-carlo/
-
-In this section we provide background on Hamiltonian Monte Carlo (HMC). 
-For a comprehensive description, see~\cite{N11},
-for intuition, see~\cite{ZRDPKDBS13}.
-Note that some of the notation in this section slightly differ from the ones used in the main body such as replacing the cost~$c$ with time~$t$.
-
-MCMC algorithms typically make use of random-walks to convergence to a target stationary distribution.
-This is often inefficient, resulting in slow mixing\footnote{Informally, the \emph{mixing time} of a Markov chain is the time until it is ``close'' to its steady-state distribution.}.
-HMC is an MCMC method that adopts physical-system dynamics (specifically Hamiltonian dynamics) rather than a probability distribution to produce the next state in the Markov chain.
-
-\subsection{Hamiltonian dynamics}
-Hamiltonian dynamics describe an object's motion in terms of its position $x$ and momentum $q$ at some time $t$. 
-Each position is associated with a potential energy $U(x)$.
-Similarly, each momentum is associated with a kinetic energy $K(q)$.
-The total energy (also called the Hamiltonian) of the system is constant and is defined as
-$$
-E(x, p) = U(x) + K(q).
-$$
-Hamiltonian dynamics describe how the kinetic and potential energies are converted one to the other as the object moves throughout a system in time. 
-This is done via a set of differential equations known as the Hamiltonian equations:
-$$
-\frac{dx}{dt} = \frac{\partial E}{\partial q}, 
-\hspace{5mm}
-\frac{dq}{dt} = - \frac{\partial E}{\partial x}. $$
-%
-%The Hamiltonian equations describe an object’s motion in time, which is a continuous variable. In order to simulate Hamiltonian dynamics numerically, the Leapfrog method is typically used.
-
-\subsection{From Hamiltonian dynamics to probability distribution}
-To sample from a desired distribution~$\pi$ using HMC, we need to convert the distribution to an energy function and vice-versa.
-This is done using the concept of a canonical distribution from statistical mechanics~\cite{N11}.
-Given some energy function,~$E$, the canonical distribution over states has the Boltzman probability distribution $\pi = \frac{1}{Z}\exp (-E/T)$, where $Z$ is a normalizing constant and~$T$ is the temperature of the system.
-Notice that in our setting
-$$
-\pi(x,q) 
-\propto e^{-E(x,q)} 
-= e^{-U(x)} \cdot e^{-K(q)}
-\propto \pi(x) \cdot \pi(q).
-$$
-This means that the distributions $\pi(x)$ and $\pi(q)$ are independent.
-Therefore, we can use Hamiltonian dynamics to sample from the joint distribution over $q$ and $x$ and ignore the momentum contributions.
-This is done by introducing auxiliary variables to represent the momentum and choosing any distribution from which to sample the momentum variables.
-A common choice is to use a zero-mean Normal distribution with unit variance.
-
-\subsection{Hamiltonian Monte Carlo}
-HMC uses Hamiltonian dynamics to explore the distribution $\pi(x)$ defined by $U(x)$. 
-Starting at an initial state~$(x_0, q_0)$, 
-(here, $q_0$ is the axillary variable used to simulate the momentum), Hamiltonian dynamics are simulated for a short time using the Leap-Frog method~\cite{S82}. 
-Let $(x', q')$ be the state at the end of the simulation. 
-This state is accepted using an update rule analogous to the Metropolis acceptance criterion~\cite{CG95}. 
-Specifically, if the probability of $(x', q')$ after Hamiltonian dynamics is greater than probability of the state prior to the Hamiltonian dynamics, then $(x', q')$ is accepted.
-Otherwise, $(x', q')$ is accepted randomly. 
-If~$(x', q')$ is rejected, the next state of the Markov chain is set as the state at the previous time step.
-
-To explore the entire space, the dynamics are randomly perturbed.
-This is done by drawing a random momentum from $\pi(q)$ before running the dynamics prior to each sampling iteration $t$.
-Combining these steps, sampling random momentum, followed by Hamiltonian dynamics and Metropolis acceptance criterion defines the HMC algorithm.
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Old text that may be re-used
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\ignore{
-In order to take advantage of these powerful methods, we propose to reformulate the cost surface as a probability density.
-Specifically, we consider a Boltzmann distribution in order to formulate the cost function using flexible energy based methods.
-Because Monte Carlo methods only consider the ratio of the probabilities, we do not need to consider the problem of estimating the intractable partition function.
-
-\begin{equation}
-E_{\text{informed}}\left(t,t_0\right) = \beta_{\text{informed}} \text{sigm}\left(t_0 - t\right)
-\end{equation}
-where $\text{sigm}\left(\cdot\right)$ represents a tight sigmoid function that can be seen as a differentiable $\text{sign}\left(\cdot\right)$ function.
-$\beta_{\text{informed}}$ is some large number that controls how much we want to penalize states outside of the level set.
-In theory, the energy should be infinity (which represents zero probability).
-In practice, however, setting $\beta_{\text{informed}}$ to be some high number such as $100$ works well and is more stable.
-
-Formally, we consider the probability distribution to be a Boltzmann distribution in the form of:
-
-\begin{equation}
-P\left(t,t_0\right) = \frac{1}{Z}\exp\left(-E\left(t,t_0\right)\right)
-\end{equation}
-where $Z$ is the intractable partition function that denotes the normalizing constant of the distribution and  $E\left(t,t_0\right)$ is the energy function which is dependent on the current best cost, $t_0$, and the cost of the path in question $t$.
-
-The flexibility of the energy function is in the ability to specify desired or more probable states (by presenting lower energies) without the need to use a formal and restrictive model.
-Specifically for our problem, we defined the energy function to be:
-
-\begin{equation}
-E\left(t, t_0\right) = E_{\text{grad}}\left(t\right) + E_{\text{informed}}\left(t,t_0\right) + E_{\text{region}}\left(\mathbf{x}\right)
-\end{equation}
-
-\begin{equation}
-E_{\text{grad}}\left(t\right) = \sigma\left(t\right)
-\end{equation}
-where $\sigma\left(\cdot\right)$ is some function that controls the flatness of the distribution.
-Intuitively, this function prefers states with smaller costs.
-The flatter the function, the less pronounced this becomes.
-We experimented with using $\log\left(1 + \log\left(t\right)\right)$ and $\tanh\left(t\right)$.
-$\tanh$ resorts in a flatter distribution which may result in more uniform samples, but contains less gradient information for methods that use them such as Hamiltonian Monte Carlo.
-
-\begin{equation}
-E_{\text{informed}}\left(t,t_0\right) = \beta_{\text{informed}} \text{sigm}\left(t_0 - t\right)
-\end{equation}
-where $\text{sigm}\left(\cdot\right)$ represents a tight sigmoid function that can be seen as a differentiable $\text{sign}\left(\cdot\right)$ function.
-$\beta_{\text{informed}}$ is some large number that controls how much we want to penalize states outside of the level set.
-In theory, the energy should be infinity (which represents zero probability).
-In practice, however, setting $\beta_{\text{informed}}$ to be some high number such as $100$ works well and is more stable.
-
-\begin{equation}
-E_{\text{region}}\left(\mathbf{x}\right) = \beta_{\text{region}}||\mathbf{x}_{\text{limits}} - \mathbf{x}||_2
-\end{equation}
-where $||\mathbf{x}_{\text{limits}} - \mathbf{x}||_2$ represents the L2 distance between the current state $\mathbf{x}$ and the state limits $\mathbf{x}_{\text{limits}}$ and $\beta_{\text{region}}$ is some high number that controls how much to penalize states close to the limits.
-The same intuition for values of $\beta_{\text{region}}$ is the same as for $\beta_{\text{informed}}$.
-
-}
+estimating volume of informed space
 

### 2017-09-11 code/planning efficiency/6dof_snake/Hammer/merge_planning_data2.m

@@ -1,0 +1,70 @@
+datasetSize = 10;
+maxtimes = zeros(datasetSize,1);
+minvals = zeros(datasetSize,1);
+for i = 0:1:datasetSize-1
+  mcmc_filename = sprintf('data/5s/simple_MCMC_%d.csv', i);
+  rs_filename = sprintf('data/5s/simple_RS_%d.csv', i);
+  hrs_filename = sprintf('data/5s/simple_HRS_%d.csv', i);
+  hnr_filename = sprintf('data/5s/simple_HNR_%d.csv', i);
+  
+  MCMC = csvread(mcmc_filename);
+  RS = csvread(rs_filename);
+  HRS = csvread(hrs_filename);
+  HNR = csvread(hnr_filename);
+  
+  allTime = vertcat(MCMC(:,1), RS(:,1), HRS(:,1), HNR(:,1));
+  allVal = vertcat(MCMC(:,2), RS(:,2), HRS(:,2), HNR(:,2));
+  maxtimes(i+1,1) = max(allTime);
+  minvals(i+1,1) = min(allVal);
+end
+
+maxT = max(maxtimes);
+minVal = min(minvals);
+
+stepNum = 20;
+MCMC1 = zeros(datasetSize, stepNum+1);
+RS1 = zeros(datasetSize, stepNum+1);
+HRS1 = zeros(datasetSize, stepNum+1);
+HNR1 = zeros(datasetSize, stepNum+1);
+
+stepSize = maxT / stepNum;
+deltaStepSize = stepSize / 5;
+T1 = 0:stepSize:maxT;
+T2 = T1 + deltaStepSize; T2(1) = 0;
+T3 = T1 + deltaStepSize*2; T3(1) = 0;
+T4 = T1 + deltaStepSize*3; T4(1) = 0; 
+
+for i = 0:1:datasetSize-1
+  mcmc_filename = sprintf('data/5s/simple_MCMC_%d.csv', i);
+  rs_filename = sprintf('data/5s/simple_RS_%d.csv', i);
+  hrs_filename = sprintf('data/5s/simple_HRS_%d.csv', i);
+  hnr_filename = sprintf('data/5s/simple_HNR_%d.csv', i);
+  
+  MCMC = csvread(mcmc_filename);
+  RS = csvread(rs_filename);
[…]

### 2017-09-11 code/planning efficiency/6dof_snake/Hammer/plot_data2.m

@@ -1,0 +1,29 @@
+figure(100);
+hold on;
+
+%HMC2 = log(HMC1);
+%HNR2 = log(HNR1);
+%RS2 = log(RS1);
+%HRS2 = log(HRS1);
+
+MCMC2 = MCMC1;
+RS2 = RS1;
+HRS2 = HRS1;
+HNR2 = HNR1;
+
+errorbar(T2, mean(MCMC2,1), std(MCMC2), 'g', 'LineWidth',2);
+errorbar(T3, mean(RS2,1), std(RS2), 'b', 'LineWidth',2);
+errorbar(T4, mean(HRS2,1), std(HRS2), 'c', 'LineWidth',2);
+errorbar(T1, mean(HNR2,1), std(HNR2)', 'r', 'LineWidth',2);
+
+
+plot(T1, mean(MCMC2,1), 'o', 'MarkerFaceColor', 'g', 'MarkerEdgeColor', 'g', 'MarkerSize', 4);
+plot(T2, mean(RS2,1), 'o', 'MarkerFaceColor', 'b', 'MarkerEdgeColor', 'b', 'MarkerSize', 4);
+plot(T3, mean(HRS2,1), 'o', 'MarkerFaceColor', 'c', 'MarkerEdgeColor', 'c', 'MarkerSize', 4);
+plot(T4, mean(HNR2,1), 'o', 'MarkerFaceColor', 'r', 'MarkerEdgeColor', 'r', 'MarkerSize', 4);
+
+xlim([0, 8]);
+legend('MCMC', 'RS', 'HRS', 'HNR');
+xlabel('Time - s');
+ylabel('Ratio to minimum');
+hold off;

### 2017-09-11 code/sample efficiency/4d/plot1.m

@@ -1,0 +1,19 @@
+data = sortrows(data05, 9);
+
+data(:,1) = log(data(:,1));
+data(:,3) = log(data(:,3));
+data(:,5) = log(data(:,5));
+data(:,7) = log(data(:,7));
+
+
+figure;
+hold on;
+scatter(log(data(:,9)),data(:,1)./data(:,2),'MarkerFaceColor','r', 'Marker', 'h');
+scatter(log(data(:,9)),data(:,3)./data(:,4),'MarkerFaceColor','g', 'Marker', 'd');
+scatter(log(data(:,9)),data(:,5)./data(:,6),'MarkerFaceColor','b', 'Marker', 'o');
+scatter(log(data(:,9)),data(:,7)./data(:,8),'MarkerFaceColor','c', 'Marker', 's');
+xlabel('informed set volume ratio');
+ylabel('time per sample (ms)');
+legend('HMC', 'HRS', 'Hit&Run', 'Rejection');
+hold off;
+

### 2017-09-11 paper.tex
add pseudo code

@@
 \section{MCMC-based Informed Sampling}
+
 In this section we describe our approach to efficiently produce samples in the informed set~\Cinf given a specific cost~$c_{\text{best}}$.
@@
 to initialize an MCMC algorithm which produces a series of samples within \Cinf (Sec.~\ref{subsec:mcmc}). 
-Specifically, we chose to use HMC due to its favourable properties (see Sec.~\ref{sec:intro}).
+%Specifically, we chose to use HMC due to its favourable properties (see Sec.~\ref{sec:intro}). 
 For a visualization of the approach, see Fig.~\ref{fig:alg}.
@@
 The MCMC algorithm will allow us to  efficiently produce samples (approximately) from \Pinf.
+
+\dy{Basically we follows a MCMC framework for informed sampling, which takes the advantage of a balanced exploration and exploitation.
+Under the MCMC framework, we use both Metropolis-Hastings and Hit-And-Run to generate samples.
+}
 
@@
 \label{subsec:mcmc}
+
+(a) we use Metropolis-Hasting
+
+\begin{algorithm}[t]
+	\begin{algorithmic}[1]
+		\STATE $ x'_{i+1} \leftarrow g( x'_{i+1} \mid x_{i} ) $
+		\STATE $ \alpha = \frac{ P( x'_{i} ) }{ P( x_{i} ) } $ 
+		\IF{ $ random() \leq \alpha $ \AND \textsc{Cost}($ x'_{i+1} $) $ < c_{\text{best}} $  }
+		  \STATE $ x_{i+1} \leftarrow x'_{i+1} $ 
+		\ELSE
+		  \STATE $ x_{i+1} \leftarrow x_{i} $
+		\ENDIF 
+	\end{algorithmic}
+	\caption{Metropolis-Hastings MCMC $(x_{i}, c_{\text{best}})$}
+	\label{alg:mh_mcmc}	
+\end{algorithm}
+
+\subsection{Sampling using Hit-And-Run Sampler}
+
+\begin{algorithm}[t]
+	\begin{algorithmic}[1]
+		\STATE Sample random direction in $ d_i $
+		\STATE Find the line set $ L = \{  x \mid x = x_i + \lambda d_i \} $
+		\STATE $ \lambda^{+} \leftarrow \sup L $, $ \lambda^{-} \leftarrow \inf L $
+		\STATE $ \lambda'_{i} \leftarrow ( \lambda^{-} , \lambda^{+} ) $
+		\STATE $ x'_{i+1} = x_{i} + \lambda'_{i} d_i $
+		\IF{ \textsc{Cost}($ x'_{i+1} $) $ < c_{\text{best}} $ }
+		  \STATE $ x_{i+1} = x'_{i+1} $
+ 		\ELSE
+		  \IF{ $ \lambda'_{i} > 0 $ }
+			  \STATE $ \lambda^{+} \leftarrow \lambda'_{i} $
+		  \ELSE
+			  \STATE $ \lambda^{-} \leftarrow \lambda'_{i} $
+		  \ENDIF 
+		  \STATE go back to line 4
+		\ENDIF 	
+	\end{algorithmic}
+	\caption{Hit-And-Run MCMC $(x_{i}, c_{\text{best}})$}
+	\label{alg:hit_and_run_mcmc}	
+\end{algorithm}
 

### 2017-09-11 code/planning efficiency/6dof_snake/Hammer/plot_data2.m
update

@@ -6,21 +6,28 @@ hold on;
 %RS2 = log(RS1);
 %HRS2 = log(HRS1);
 
+green = [49,163,84]/255;
+red = [222 45 38]/255;
+blue = [49,130,189]/255;
+orange = [230,85,13]/255;
+purple = [117,107,177]/255;
+pink = [197,27,138]/255;
+
 MCMC2 = MCMC1;
 RS2 = RS1;
 HRS2 = HRS1;
 HNR2 = HNR1;
 
-errorbar(T2, mean(MCMC2,1), std(MCMC2), 'g', 'LineWidth',2);
-errorbar(T3, mean(RS2,1), std(RS2), 'b', 'LineWidth',2);
-errorbar(T4, mean(HRS2,1), std(HRS2), 'c', 'LineWidth',2);
-errorbar(T1, mean(HNR2,1), std(HNR2)', 'r', 'LineWidth',2);
+errorbar(T2, mean(RS2,1), std(RS2), 'color', blue, 'LineWidth',2);
+errorbar(T3, mean(HRS2,1), std(HRS2), 'color', red, 'LineWidth',2);
+errorbar(T1, mean(MCMC2,1), std(MCMC2), 'color', green, 'LineWidth',2);
+errorbar(T4, mean(HNR2,1), std(HNR2), 'color', purple, 'LineWidth',2);
 
 
-plot(T1, mean(MCMC2,1), 'o', 'MarkerFaceColor', 'g', 'MarkerEdgeColor', 'g', 'MarkerSize', 4);
-plot(T2, mean(RS2,1), 'o', 'MarkerFaceColor', 'b', 'MarkerEdgeColor', 'b', 'MarkerSize', 4);
-plot(T3, mean(HRS2,1), 'o', 'MarkerFaceColor', 'c', 'MarkerEdgeColor', 'c', 'MarkerSize', 4);
-plot(T4, mean(HNR2,1), 'o', 'MarkerFaceColor', 'r', 'MarkerEdgeColor', 'r', 'MarkerSize', 4);
+plot(T2, mean(RS2,1), 'o', 'MarkerFaceColor', blue, 'MarkerEdgeColor', blue, 'MarkerSize', 4);
+plot(T3, mean(HRS2,1), 'o', 'MarkerFaceColor', red, 'MarkerEdgeColor', red, 'MarkerSize', 4);
[…]

### 2017-09-11 code/planning efficiency/6dof_snake/problem1/plot_data2.m

@@ -6,21 +6,28 @@ hold on;
 %RS2 = log(RS1);
 %HRS2 = log(HRS1);
 
+green = [49,163,84]/255;
+red = [222 45 38]/255;
+blue = [49,130,189]/255;
+orange = [230,85,13]/255;
+purple = [117,107,177]/255;
+pink = [197,27,138]/255;
+
 MCMC2 = MCMC1;
 RS2 = RS1;
 HRS2 = HRS1;
 HNR2 = HNR1;
 
-errorbar(T2, mean(MCMC2,1), std(MCMC2), 'g', 'LineWidth',2);
-errorbar(T3, mean(RS2,1), std(RS2), 'b', 'LineWidth',2);
-errorbar(T4, mean(HRS2,1), std(HRS2), 'c', 'LineWidth',2);
-errorbar(T1, mean(HNR2,1), std(HNR2)', 'r', 'LineWidth',2);
+errorbar(T2, mean(RS2,1), std(RS2), 'color', blue, 'LineWidth',2);
+errorbar(T3, mean(HRS2,1), std(HRS2), 'color', red, 'LineWidth',2);
+errorbar(T1, mean(MCMC2,1), std(MCMC2), 'color', green, 'LineWidth',2);
+errorbar(T4, mean(HNR2,1), std(HNR2), 'color', purple, 'LineWidth',2);
 
 
-plot(T1, mean(MCMC2,1), 'o', 'MarkerFaceColor', 'g', 'MarkerEdgeColor', 'g', 'MarkerSize', 4);
-plot(T2, mean(RS2,1), 'o', 'MarkerFaceColor', 'b', 'MarkerEdgeColor', 'b', 'MarkerSize', 4);
-plot(T3, mean(HRS2,1), 'o', 'MarkerFaceColor', 'c', 'MarkerEdgeColor', 'c', 'MarkerSize', 4);
-plot(T4, mean(HNR2,1), 'o', 'MarkerFaceColor', 'r', 'MarkerEdgeColor', 'r', 'MarkerSize', 4);
+plot(T2, mean(RS2,1), 'o', 'MarkerFaceColor', blue, 'MarkerEdgeColor', blue, 'MarkerSize', 4);
+plot(T3, mean(HRS2,1), 'o', 'MarkerFaceColor', red, 'MarkerEdgeColor', red, 'MarkerSize', 4);
[…]

### 2017-09-11 code/planning efficiency/planar_manipulator/general/plot_data2.m

@@ -6,21 +6,28 @@ hold on;
 %RS2 = log(RS1);
 %HRS2 = log(HRS1);
 
+green = [49,163,84]/255;
+red = [222 45 38]/255;
+blue = [49,130,189]/255;
+orange = [230,85,13]/255;
+purple = [117,107,177]/255;
+pink = [197,27,138]/255;
+
 MCMC2 = MCMC1;
 RS2 = RS1;
 HRS2 = HRS1;
 HNR2 = HNR1;
 
-errorbar(T2, mean(MCMC2,1), std(MCMC2), 'g', 'LineWidth',2);
-errorbar(T3, mean(RS2,1), std(RS2), 'b', 'LineWidth',2);
-errorbar(T4, mean(HRS2,1), std(HRS2), 'c', 'LineWidth',2);
-errorbar(T1, mean(HNR2,1), std(HNR2)', 'r', 'LineWidth',2);
+errorbar(T2, mean(RS2,1), std(RS2), 'color', blue, 'LineWidth',2);
+errorbar(T3, mean(HRS2,1), std(HRS2), 'color', red, 'LineWidth',2);
+errorbar(T1, mean(MCMC2,1), std(MCMC2), 'color', green, 'LineWidth',2);
+errorbar(T4, mean(HNR2,1), std(HNR2), 'color', purple, 'LineWidth',2);
 
 
-plot(T1, mean(MCMC2,1), 'o', 'MarkerFaceColor', 'g', 'MarkerEdgeColor', 'g', 'MarkerSize', 4);
-plot(T2, mean(RS2,1), 'o', 'MarkerFaceColor', 'b', 'MarkerEdgeColor', 'b', 'MarkerSize', 4);
-plot(T3, mean(HRS2,1), 'o', 'MarkerFaceColor', 'c', 'MarkerEdgeColor', 'c', 'MarkerSize', 4);
-plot(T4, mean(HNR2,1), 'o', 'MarkerFaceColor', 'r', 'MarkerEdgeColor', 'r', 'MarkerSize', 4);
+plot(T2, mean(RS2,1), 'o', 'MarkerFaceColor', blue, 'MarkerEdgeColor', blue, 'MarkerSize', 4);
+plot(T3, mean(HRS2,1), 'o', 'MarkerFaceColor', red, 'MarkerEdgeColor', red, 'MarkerSize', 4);
[…]

### 2017-09-11 code/planning efficiency/planar_manipulator/plot_data.m

@@ -6,23 +6,31 @@ hold on;
 %RS2 = log(RS1);
 %HRS2 = log(HRS1);
 
-HNR2 = HNR1;
+green = [49,163,84]/255;
+red = [222 45 38]/255;
+blue = [49,130,189]/255;
+orange = [230,85,13]/255;
+purple = [117,107,177]/255;
+pink = [197,27,138]/255;
+
 MCMC2 = MCMC1;
 RS2 = RS1;
 HRS2 = HRS1;
+HNR2 = HNR1;
 
-errorbar(T1, mean(HNR2,1), std(HNR2)', 'r', 'LineWidth',2);
-errorbar(T2, mean(MCMC2,1), std(MCMC2), 'g', 'LineWidth',2);
-errorbar(T3, mean(RS2,1), std(RS2), 'b', 'LineWidth',2);
-errorbar(T4, mean(HRS2,1), std(HRS2), 'c', 'LineWidth',2);
+errorbar(T2, mean(RS2,1), std(RS2), 'color', blue, 'LineWidth',2);
+errorbar(T3, mean(HRS2,1), std(HRS2), 'color', red, 'LineWidth',2);
+errorbar(T1, mean(MCMC2,1), std(MCMC2), 'color', green, 'LineWidth',2);
+errorbar(T4, mean(HNR2,1), std(HNR2), 'color', purple, 'LineWidth',2);
 
-plot(T1, mean(HNR2,1), 'o', 'MarkerFaceColor', 'r', 'MarkerEdgeColor', 'r', 'MarkerSize', 4);
-plot(T2, mean(MCMC2,1), 'o', 'MarkerFaceColor', 'g', 'MarkerEdgeColor', 'g', 'MarkerSize', 4);
-plot(T3, mean(RS2,1), 'o', 'MarkerFaceColor', 'b', 'MarkerEdgeColor', 'b', 'MarkerSize', 4);
-plot(T4, mean(HRS2,1), 'o', 'MarkerFaceColor', 'c', 'MarkerEdgeColor', 'c', 'MarkerSize', 4);
 
-xlim([0, 3]);
-legend('HNR', 'MCMC', 'RS', 'HRS');
+plot(T2, mean(RS2,1), 'o', 'MarkerFaceColor', blue, 'MarkerEdgeColor', blue, 'MarkerSize', 4);
[…]

### 2017-09-11 code/sample efficiency/3d/plot1.m

@@ -1,4 +1,4 @@
-data = sortrows(dim2, 5);
+data = sortrows(dim3, 5);
 
 data(:,1) = log(data(:,1));
 data(:,2) = log(data(:,2));
@@ -24,4 +24,3 @@ xlabel('informed set volume ratio');
 ylabel('time per sample (ms)');
 legend('Rejection', 'HRS', 'MCMC', 'Hit&Run');
 hold off;
-

### 2017-09-11 code/sample efficiency/4d/plot1.m

@@ -1,19 +1,0 @@
-data = sortrows(data05, 9);
-
-data(:,1) = log(data(:,1));
-data(:,3) = log(data(:,3));
-data(:,5) = log(data(:,5));
-data(:,7) = log(data(:,7));
-
-
-figure;
-hold on;
-scatter(log(data(:,9)),data(:,1)./data(:,2),'MarkerFaceColor','r', 'Marker', 'h');
-scatter(log(data(:,9)),data(:,3)./data(:,4),'MarkerFaceColor','g', 'Marker', 'd');
-scatter(log(data(:,9)),data(:,5)./data(:,6),'MarkerFaceColor','b', 'Marker', 'o');
-scatter(log(data(:,9)),data(:,7)./data(:,8),'MarkerFaceColor','c', 'Marker', 's');
-xlabel('informed set volume ratio');
-ylabel('time per sample (ms)');
-legend('HMC', 'HRS', 'Hit&Run', 'Rejection');
-hold off;
-

### 2017-09-11 code/sample efficiency/6d/plot1.m

@@ -1,19 +1,26 @@
-data = sortrows(data05, 9);
+data = sortrows(dim6, 5);
 
 data(:,1) = log(data(:,1));
+data(:,2) = log(data(:,2));
 data(:,3) = log(data(:,3));
-data(:,5) = log(data(:,5));
-data(:,7) = log(data(:,7));
+data(:,4) = log(data(:,4));
 
+green = [49,163,84]/255;
+red = [222 45 38]/255;
+blue = [49,130,189]/255;
+orange = [230,85,13]/255;
+purple = [117,107,177]/255;
+pink = [197,27,138]/255;
 
 figure;
 hold on;
-scatter(log(data(:,9)),data(:,1)./data(:,2),'MarkerFaceColor','r', 'Marker', 'h');
-scatter(log(data(:,9)),data(:,3)./data(:,4),'MarkerFaceColor','g', 'Marker', 'd');
-scatter(log(data(:,9)),data(:,5)./data(:,6),'MarkerFaceColor','b', 'Marker', 'o');
-scatter(log(data(:,9)),data(:,7)./data(:,8),'MarkerFaceColor','c', 'Marker', 's');
+marker_size = 20;
+scatter(log(data(:,5)),data(:,4)./data(:,6), marker_size, 'MarkerFaceColor', blue, 'MarkerEdgeColor', blue, 'Marker', 's');
+scatter(log(data(:,5)),data(:,2)./data(:,6), marker_size, 'MarkerFaceColor', red, 'MarkerEdgeColor', red, 'Marker', 'd');
+scatter(log(data(:,5)),data(:,1)./data(:,6), marker_size, 'MarkerFaceColor', green, 'MarkerEdgeColor', green, 'Marker', 'h');
+scatter(log(data(:,5)),data(:,3)./data(:,6), marker_size, 'MarkerFaceColor', purple, 'MarkerEdgeColor', purple, 'Marker', 'o');
+
 xlabel('informed set volume ratio');
 ylabel('time per sample (ms)');
-legend('HMC', 'HRS', 'Hit&Run', 'Rejection');
+legend('Rejection', 'HRS', 'MCMC', 'Hit&Run');
 hold off;
-

### 2017-09-12 paper.tex
updated pseudo code
update
updates on sec V - alg

--- 2017-09-11 paper.tex
@@
 \usepackage{hyperref}
+\usepackage{eqparbox}
 %\hypersetup{bookmarksopen,
@@
 \section{MCMC-based Informed Sampling}
-In this section we describe our approach to efficiently produce samples in the informed set~\Cinf given a specific cost~$c_{\text{best}}$.
-Our algorithm (see Alg.~\ref{alg:mcmc_informed_sampling}) starts by randomly sampling a state~$x_\text{rand} \in \calX$ (line~1).
+
+In this section we describe our approach to efficiently produce a sequence of samples in the informed set~\Cinf given a specific cost~$c_{\text{best}}$.
+Our algorithm (see Alg.~\ref{alg:mcmc_informed_sampling}) starts by randomly sampling a state~$x_\text{rand} \in \calX$ (line~2).
 This sample is used to produces a 
@@
 %sample~$x_\text{boundary} \in \partial\Cinf$ 
-which lies (approximately) on the boundary of the informed set (Sec.~\ref{subsec:grad})by applying Newton-Raphson method~\cite{RT06} (line~2).
+which lies (approximately) on the boundary of the informed set (Sec.~\ref{subsec:grad}) by applying Newton-Raphson method~\cite{RT06} (line~3).
 Finally,~$x_0$ 
 %use~$x_\text{boundary}$ 
-is used (lines~3-5)
-to initialize an MCMC algorithm which produces a series of samples within \Cinf (Sec.~\ref{subsec:mcmc}).
-Specifically, we chose to use HMC due to its favourable properties (see Sec.~\ref{sec:intro}).
+is used (lines~4-6)
+to initialize an MCMC algorithm which produces a series of samples within \Cinf until some termination criterion is met.
+This process is then repeated (Sec.~\ref{subsec:mcmc}). 
+%Specifically, we chose to use HMC due to its favourable properties (see Sec.~\ref{sec:intro}). 
 For a visualization of the approach, see Fig.~\ref{fig:alg}.
+
+It is important to note that at each iteration, we will query our algorithm for one sample.
+However, this sample depends on the previous iterations of the algorithm which is why we describe it as a method to produce a sequence of samples.
+Furthermore, the value~$c_{\text{best}}$ can decrease between consecutive iterations.
+This will occur if the search algorithm that uses our sampler finds a path to the goal whose cost is lower than~$c_{\text{best}}$.
 
@@
 the probability of sampling any configuration $x \in \calX \setminus \Cinf$ is zero.
-The MCMC algorithm will allow us to  efficiently produce samples (approximately) from \Pinf.
+MCMC algorithms allow us to  efficiently produce samples (approximately) from \Pinf.
 
@@
 	\begin{algorithmic}[1]
+		\LOOP
 			\STATE $x_{\text{rand}} \leftarrow \texttt{sample\_uniform(\calX)}$
-%		\STATE $x_{\text{boundary}} 
 			\STATE $x_{0} 
 		 \leftarrow
-		 \texttt{newton\_raphson}(x_{\text{rand}}, c_{\text{best}})$
-%		\STATE $x_{0} \leftarrow x_{\text{boundary}}$
-		\FOR {$i = 1$ to $N$}
-			\STATE $x_{i} \leftarrow \texttt{MCMC} (x_{i-1}, c_{\text{best}})$
+		 \texttt{newton\_raphson}(x_{\text{rand}}, c_{\text{best}})$ ; \hspace{3mm} $i\leftarrow 0$
+			\WHILE {\texttt{MCMC\_continue\_chain()}}
+			\STATE $x_{i} \leftarrow \texttt{MCMC\_sample} (x_{i-1}, c_{\text{best}})$
 			\STATE \textbf{output} $x_{i}$
-		\ENDFOR
+			\ENDWHILE
 
+		\ENDLOOP 
+%		\STATE $x_{\text{rand}} \leftarrow \texttt{sample\_uniform(\calX)}$
+%%		\STATE $x_{\text{boundary}} 
+%		\STATE $x_{0} 
+%		 \leftarrow
+%		 \texttt{newton\_raphson}(x_{\text{rand}}, c_{\text{best}})$ ; \hspace{3mm} $i\leftarrow 0$
+%%		\STATE $x_{0} \leftarrow x_{\text{boundary}}$
+%		\WHILE {\texttt{MCMC\_continue\_chain()}}
+%			\STATE $x_{i} \leftarrow \texttt{MCMC} (x_{i-1}, c_{\text{best}})$; \hspace{3mm} $i\leftarrow i+1$
+%			\STATE \textbf{output} $x_{i}$
+%		\ENDWHILE		
+%		\FOR {$i = 1$ to $N$}
+%			\STATE $x_{i} \leftarrow \texttt{MCMC} (x_{i-1}, c_{\text{best}})$
+%			\STATE \textbf{output} $x_{i}$
+%		\ENDFOR
+%		 
    	\end{algorithmic}
@@
 \label{subsec:mcmc}
+
+Our approach is general and can be applied to any MCMC algorithm (see Sec.~\ref{sec:related_work}).
+We demonstrate how to instantiate it with two different algorithms: 
+Hit and Run and Metropolis-Hastings.
+
+For each algorithm, 
+one has to describe how it is used to (i)~sample points 
+(\texttt{MCMC\_sample, line 5})
+and 
+(ii)~decide if to continue sampling along the Markov Chain or to restart the entire process 
+(\texttt{MCMC\_continue\_chain, line 5}).
+
+\subsubsection{Hit and Run}
+
+\subsubsection{Metropolis-Hasting}
+
+\begin{algorithm}[t]
+	\begin{algorithmic}[1]
+		\STATE $ x'_{i+1} \leftarrow g( x'_{i+1} \mid x_{i} ) $
+		\COMMENT {$g$~is a Gaussian}		
+		\IF{ \textsc{Cost}($ x'_{i+1} $) $ < c_{\text{best}} $  }
+		  \STATE $ x_{i+1} \leftarrow x'_{i+1} $ 
+		\ELSE
+		  \STATE $ x_{i+1} \leftarrow x_{i} $
+		\ENDIF 
+	\end{algorithmic}
+	\caption{Metropolis-Hastings MCMC $(x_{i}, c_{\text{best}})$}
+	\label{alg:mh_mcmc}	
+\end{algorithm}
+
+\begin{algorithm}[t]
+	\begin{algorithmic}[1]
+		\STATE $d \leftarrow$ \texttt{sample\_random\_direction}$()$
+		\STATE $ L(\lambda) = \{  x \mid x = x_i + \lambda d_i \} $
+		\STATE $ \lambda^{+} \leftarrow \sup L(\lambda) $; 
+				\hspace{3mm} 
+			   $ \lambda^{-} \leftarrow \inf L(\lambda) $
+
+		\LOOP
+
+		\STATE $ \lambda' \leftarrow$ \texttt{sample\_random}$ (\lambda^{-} , \lambda^{+})$
+		\STATE $ x_{i+1} \leftarrow x_{i} + \lambda'_{i} d_i $
+
+		\IF{ \textsc{Cost}($ x_{i+1} $) $ < c_{\text{best}} $ }
+		  \RETURN $ x_{i+1}$
+		\ENDIF
+
+		\IF{ $ \lambda' > 0 $ }
+			\STATE $ \lambda^{+} \leftarrow \lambda' $
+		\ELSE
+			\STATE $ \lambda^{-} \leftarrow \lambda'$
+		\ENDIF
+
+		\ENDLOOP
+  	\end{algorithmic}
+	\caption{Hit-And-Run MCMC $(x_{i}, c_{\text{best}})$}
+	\label{alg:hit_and_run_mcmc}	
+\end{algorithm}
 
@@
 	\begin{subfigure}[b]{0.5\textwidth}
-		\includegraphics[width=\linewidth]{fig/sampling_efficiency/sample_efficiency_4d}
-		\caption{4D}
+		\includegraphics[width=\linewidth]{fig/sampling_efficiency/sample_efficiency_3d}
+		\caption{3D}
 		\label{fig:sampling_efficiency:4d}

### 2017-09-12 paper.tex
finished text for alg sec

@@
 We then continue in Sec.~\ref{subsec:sampling} to describe different approaches that can be used by  these algorithms to sample~$\calX$.
-We conclude our literature review in Sec.~\ref{subsec:mcmc} with a brief overview of Markov Chain Monte Carlo methods.
+We conclude our literature review in Sec.~\ref{subsec:mcmc0} with a brief overview of Markov Chain Monte Carlo methods.
 
@@
 \subsection{Markov Chain Monte Carlo (MCMC)}
-\label{subsec:mcmc}
+\label{subsec:mcmc0}
 Monte Carlo simulation is a general sampling framework widely used in various domains such as
@@
 Here, given the current point $x_i$ the next point~$x_{i+1}$ in the Markov chain is produced by sampling a random direction~$\theta$ on the surface of the unit sphere centered at $x_{i+1}$.
-This defines a ray $r_i$ rooted at $x_i$ and passing through~$\theta$.
-The point $x_{i+1}$ is chosen by randomly sampling a point on $r_i$.
+This defines a line $\ell_i$ rooted at $x_i$ and passing through~$\theta$.
+The point $x_{i+1}$ is chosen by randomly sampling a point on $\ell_i$ (see also Sec.~\ref{sec:algorithm}).
 This algorithm is considered to be one of the most efficient algorithms for generating an asymptotically uniform point if the set under consideration is convex~\cite{L99, LV06}
@@
 \section{Problem definition}
-\label{sec:algorithm}
+\label{sec:pdef}
 Let $\calX, \calU$ denote the state and controls spaces, respectively and set $\Cfree \subset \calX$ to be the set of states where the robot is collision free.
@@
 \section{MCMC-based Informed Sampling}
+\label{sec:algorithm}
 
@@
 is used (lines~4-6)
-to initialize an MCMC algorithm which produces a series of samples within \Cinf until some termination criterion is met.
-This process is then repeated (Sec.~\ref{subsec:mcmc}). 
+to initialize an MCMC algorithm which outputs a series of samples within \Cinf by constructing a Markov Chain.
+This is done until some termination criterion is met and the entire process is repeated (Sec.~\ref{subsec:mcmc}). 
 %Specifically, we chose to use HMC due to its favourable properties (see Sec.~\ref{sec:intro}). 
@@
 This will occur if the search algorithm that uses our sampler finds a path to the goal whose cost is lower than~$c_{\text{best}}$.
-
-We apply MCMC by using the cost function to define a probability distribution \Pinf.
-Specifically, points in \Cinf are distributed uniformly
-while 
-the probability of sampling any configuration $x \in \calX \setminus \Cinf$ is zero.
-MCMC algorithms allow us to  efficiently produce samples (approximately) from \Pinf.
 
@@
 In theory, MCMC methods converge to the desired distribution regardless of the initial sample used to seed the chain.
-However, in practice it is common to discard an initial set of samples (a process referred to as ``burn-in'') to avoid starting biases~\cite{ADDJ03}.
+In our setting, the probability distribution~\Pinf is defined by having all points in \Cinf distributed uniformly
+while 
+the probability of sampling any configuration $x \in \calX \setminus \Cinf$ is zero.
+A common practice to avoid starting biases in MCMC-type algorithm is to discard an initial set of samples (a process referred to as ``burn-in'')~\cite{ADDJ03}.
 
@@
 To do so we apply  Newton-Raphson's method to obtain a sample on $\partial \Cinf$. 
-However, our cost function is not necessarily continuous (see Sec.~\ref{sec:mtdi}), thus if no sample was produced on $\partial \Cinf$ after a predefined number of steps, we restart the algorithm using a different random state~$x_\text{rand}$.
+However, our cost function is not necessarily continuous (see Sec.~\ref{sec:mtdi}), thus if no sample was produced on $\partial \Cinf$ after a predefined number of steps, we restart the algorithm using a different random state~$x_\text{rand}$
+(see also Sec.~\ref{subsec:mcmc}).
 
@@
 For each algorithm, 
-one has to describe how it is used to (i)~sample points 
+we describe how it is used to 
+(i)~sample points 
 (\texttt{MCMC\_sample, line 5})
@@
 (ii)~decide if to continue sampling along the Markov Chain or to restart the entire process 
-(\texttt{MCMC\_continue\_chain, line 5}).
+(\texttt{MCMC\_continue\_chain, line 4}).
 
 \subsubsection{Hit and Run}
-
-\subsubsection{Metropolis-Hasting}
-
-\begin{algorithm}[t]
-	\begin{algorithmic}[1]
-		\STATE $ x'_{i+1} \leftarrow g( x'_{i+1} \mid x_{i} ) $
-		\COMMENT {$g$~is a Gaussian}		
-		\IF{ \textsc{Cost}($ x'_{i+1} $) $ < c_{\text{best}} $  }
-		  \STATE $ x_{i+1} \leftarrow x'_{i+1} $ 
-		\ELSE
-		  \STATE $ x_{i+1} \leftarrow x_{i} $
-		\ENDIF 
-	\end{algorithmic}
-	\caption{Metropolis-Hastings MCMC $(x_{i}, c_{\text{best}})$}
-	\label{alg:mh_mcmc}	
-\end{algorithm}
-
 \begin{algorithm}[t]
@@
 
-\subsection{Probabilistic completeness}
+Hit and Run, described in Alg.~\ref{alg:hit_and_run_mcmc} produces a series of samples $x_0, \ldots$.
+Given the previous sample~$x_i$ it first  samples a random direction on the unit sphere (line 1).
+This induces a line~$L(\lambda)$ passing through~$x_i$  in the direction sampled (line 2) parametrized by a scalar~$\lambda$.
+We obtain upper and lower bounds on~$\lambda$ (line 3) that are problem dependant (e.g. these can relate to joint limits of the robot, bounds on maximum velocity etc.).
+We then sample a point along~$L(\lambda)$ by sampling a scalar~$\lambda'$ within our bounds (line 5).
+This defines a point~$x_{i+1}$ which is a candidate for the next sample along the Markov Chain (line 6).
+We then check if the point lies in the informed set (line 7) and if it does we return it.
+If not, we update our bounds (lines~9-12) and repeat the process.
+The algorithm can be view as an efficient method to perform rejection sampling around the previous sample using in a one-dimensional search space parametrized by $\lambda$.
 
-%\newpage
-%\begin{thm}
-%For each node $u$ that was removed from the priority $\calQ$, $g(u) = \delta(u)$, where $\delta(u)$ denotes the shortest path to reach $u$ from $s$.
-%\end{thm}
+For this algorithm, we continue sampling along the Markov Chain until either 
+(i)~the difference between the lower and upper bounds ($\lambda^-$ and $\lambda^+)$ 
+that define our sampling domain is below a predefined threshold or
+(ii)~a predefined number of samples was exceeded.
+
+\subsubsection{Metropolis-Hasting}
+
+\begin{algorithm}[t]
+	\begin{algorithmic}[1]
+		\STATE $ x'_{i+1} \leftarrow g( x'_{i+1} \mid x_{i} ) $
+		\COMMENT {$g$~is a Gaussian}		
+		\IF{ \textsc{Cost}($ x'_{i+1} $) $ < c_{\text{best}} $  }
+		  \RETURN $ x_{i+1} \leftarrow x'_{i+1} $ 
+		\ELSE
+		  \RETURN $ x_{i+1} \leftarrow x_{i} $
+		\ENDIF 
+	\end{algorithmic}
+	\caption{Metropolis-Hastings MCMC $(x_{i}, c_{\text{best}})$}
+	\label{alg:mh_mcmc}	
+\end{algorithm}
+
+The Metropolis-Hastings algorithm, describe in Alg.~\ref{alg:mh_mcmc}, also uses rejection sampling around the previously generated sample to propose the next sample of the Markov Chain.
+While the general algorithm is slightly more complex, for our setting it can be described as follows:
+We generate a new sample $ x_{i+1}$ around the previous sample $ x_{i}$ using a Gaussian distribution (line~1).
+We then check if the point lies in the informed set (lines 2-5) and if it does we return it.
+If not, we return the previous sample.
 %
-%The proof is by induction on the order of vertices removed from $\calQ$. 
-%
-%\textbf{Base} holds trivially for $s$.
-%
-%\textbf{Step:}
-%Let $v$ be the current node on the top of the priority queue and let $u$ be its parent.
-%Notice that by the induction hypothesis we have that $g(u) = \delta(u)$.
-%
-%We have two case to consider: 
-%(i) the shortest path does not pass through $u$ but through some other node $u'$ which is not in $\calQ$,
-%and
-%(i) the shortest path does not pass through $u$ but through some other node $y$ which is in $\calQ$.
-%
-%For case (i), we have that when $u'$ was removed from $\calQ$, then $v$'s cost was $g(v) \leq g(u') + c(u',v)$.
-%Since $g(u') = \delta(u')$ this is equal to $\delta(v)$.
-%
-%For case (ii), let $x$ be $y$'s parent which was already removed from $\calQ$.
-%Note that $g(x) = \delta(x)$ and (similar to the previous case) we have that $g(y) < g(x) + c(x,y)$.
-%Furthermore notice that $v$ was before $y$ in $\calQ$ thus $g(v) \leq g(y)$.
-%Purring everything together we have that
-%$$
-%\delta(v)   > \delta(x) + c(x,y)
-%			\geq g(y)
-%			\geq g(v).
-%$$
-%Here, the first transition is due to the assumption that the shortest path goes from $s$ to $v$ through the edge $(x,y)$.
-%The second (which I got confused about in class) is due to the fact that when $x$ was popped from $\calQ$ it updated $y$'s cost.
-% \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\ \\
-% 
-%\vspace{20cm}
+For this algorithm, we continue sampling along the Markov Chain as long as new samples are produced.
 
-\ignore{
-\section{MCMC-based Informed Sampling}
-
-Rejection sampling is the simplest ways of constrained sampling~\cite{CRCW04}, but is also known for high rejection-rate on a manifold in a high-dimensional space~\cite{KTC16}.
-Hierarchical Rejection Sampling (HRS)~\cite{KTC16} is thus proposed that sequentially samples each dimension so that an unqualified candidate can be rejected before all dimensions are sampled. 
-However, the rejection rate is still relatively high~\cite{KTC16}.
-In this paper, we propose an informed sampling by an MCMC approach.
-In order to obtained uniformly sampling on a manifold, MCMC provides an approach that samples from a high-dimensional uniform distribution subject to a manifold constraint.
-Instead of rejecting samplings, original samples are purposefully driven onto a manifold.
-
-One of the major difficulties of sampling the informed level set is that the shape of the cost function can change dramatically with the start and goal states.
-Because of this, there is not a principled way to sample from the informed set for each possible start and goal combination.
-
-Following the example of recent work in path planning algorithms such as CHOMP~\cite{RZBS09}, we propose to solve the problem of efficiently sampling uniformly in the level set by using Monte Carlo sampling methods.
-Monte Carlo sampling methods have been used in the statics and machine learning fields to sample from intractable posteriors.
-Monte Carlo methods have the desirable property that they are guaranteed to sample the true posterior as the number of steps goes toward infinity.
-
-\begin{algorithm}
-	\begin{algorithmic}[1]
-		\STATE
-   	\end{algorithmic}
-	\caption{MCMC Informed Sampling}
-	\label{alg:mcmc_informed_sampling}
-\end{algorithm}
-}
+%\subsection{Probabilistic completeness}
 

### 2017-09-12 code/sample efficiency/2d/plot1.m
new figures

@@ -1,9 +1,9 @@
 data = sortrows(dim2, 5);
 
-data(:,1) = log(data(:,1));
-data(:,2) = log(data(:,2));
-data(:,3) = log(data(:,3));
-data(:,4) = log(data(:,4));
+%data(:,1) = log(data(:,1));
+%data(:,2) = log(data(:,2));
+%data(:,3) = log(data(:,3));
+%data(:,4) = log(data(:,4));
 
 green = [49,163,84]/255;
 red = [222 45 38]/255;
@@ -15,13 +15,13 @@ pink = [197,27,138]/255;
 figure;
 hold on;
 marker_size = 20;
-scatter(log(data(:,5)),data(:,4)./data(:,6), marker_size, 'MarkerFaceColor', blue, 'MarkerEdgeColor', blue, 'Marker', 's');
-scatter(log(data(:,5)),data(:,2)./data(:,6), marker_size, 'MarkerFaceColor', red, 'MarkerEdgeColor', red, 'Marker', 'd');
-scatter(log(data(:,5)),data(:,1)./data(:,6), marker_size, 'MarkerFaceColor', green, 'MarkerEdgeColor', green, 'Marker', 'h');
-scatter(log(data(:,5)),data(:,3)./data(:,6), marker_size, 'MarkerFaceColor', purple, 'MarkerEdgeColor', purple, 'Marker', 'o');
+scatter(log10(data(:,5)), log10(data(:,4)./data(:,6)), marker_size, 'MarkerFaceColor', blue, 'MarkerEdgeColor', blue, 'Marker', 's');
+scatter(log10(data(:,5)),log10(data(:,2)./data(:,6)), marker_size, 'MarkerFaceColor', red, 'MarkerEdgeColor', red, 'Marker', 'd');
+scatter(log10(data(:,5)),log10(data(:,1)./data(:,6)), marker_size, 'MarkerFaceColor', green, 'MarkerEdgeColor', green, 'Marker', 'h');
+scatter(log10(data(:,5)),log10(data(:,3)./data(:,6)), marker_size, 'MarkerFaceColor', purple, 'MarkerEdgeColor', purple, 'Marker', 'o');
 
-xlabel('informed set volume ratio');
-ylabel('time per sample (ms)');
+xlabel('informed set volume ratio - log_1_0');
+ylabel('time per sample - log_1_0(ms)');
 legend('Rejection', 'HRS', 'MCMC', 'Hit&Run');
 hold off;
 

### 2017-09-12 code/sample efficiency/3d/plot1.m

@@ -1,9 +1,9 @@
 data = sortrows(dim3, 5);
 
-data(:,1) = log(data(:,1));
-data(:,2) = log(data(:,2));
-data(:,3) = log(data(:,3));
-data(:,4) = log(data(:,4));
+%data(:,1) = log(data(:,1));
+%data(:,2) = log(data(:,2));
+%data(:,3) = log(data(:,3));
+%data(:,4) = log(data(:,4));
 
 green = [49,163,84]/255;
 red = [222 45 38]/255;
@@ -15,12 +15,13 @@ pink = [197,27,138]/255;
 figure;
 hold on;
 marker_size = 20;
-scatter(log(data(:,5)),data(:,4)./data(:,6), marker_size, 'MarkerFaceColor', blue, 'MarkerEdgeColor', blue, 'Marker', 's');
-scatter(log(data(:,5)),data(:,2)./data(:,6), marker_size, 'MarkerFaceColor', red, 'MarkerEdgeColor', red, 'Marker', 'd');
-scatter(log(data(:,5)),data(:,1)./data(:,6), marker_size, 'MarkerFaceColor', green, 'MarkerEdgeColor', green, 'Marker', 'h');
-scatter(log(data(:,5)),data(:,3)./data(:,6), marker_size, 'MarkerFaceColor', purple, 'MarkerEdgeColor', purple, 'Marker', 'o');
+scatter(log10(data(:,5)), log10(data(:,4)./data(:,6)), marker_size, 'MarkerFaceColor', blue, 'MarkerEdgeColor', blue, 'Marker', 's');
+scatter(log10(data(:,5)),log10(data(:,2)./data(:,6)), marker_size, 'MarkerFaceColor', red, 'MarkerEdgeColor', red, 'Marker', 'd');
+scatter(log10(data(:,5)),log10(data(:,1)./data(:,6)), marker_size, 'MarkerFaceColor', green, 'MarkerEdgeColor', green, 'Marker', 'h');
+scatter(log10(data(:,5)),log10(data(:,3)./data(:,6)), marker_size, 'MarkerFaceColor', purple, 'MarkerEdgeColor', purple, 'Marker', 'o');
 
-xlabel('informed set volume ratio');
-ylabel('time per sample (ms)');
+%xlim([-5, -2.4]);
+xlabel('informed set volume ratio - log_1_0');
+ylabel('time per sample - log_1_0(ms)');
 legend('Rejection', 'HRS', 'MCMC', 'Hit&Run');
 hold off;

### 2017-09-12 code/sample efficiency/6d/plot1.m

@@ -1,9 +1,9 @@
 data = sortrows(dim6, 5);
 
-data(:,1) = log(data(:,1));
-data(:,2) = log(data(:,2));
-data(:,3) = log(data(:,3));
-data(:,4) = log(data(:,4));
+%data(:,1) = log(data(:,1));
+%data(:,2) = log(data(:,2));
+%data(:,3) = log(data(:,3));
+%data(:,4) = log(data(:,4));
 
 green = [49,163,84]/255;
 red = [222 45 38]/255;
@@ -15,12 +15,13 @@ pink = [197,27,138]/255;
 figure;
 hold on;
 marker_size = 20;
-scatter(log(data(:,5)),data(:,4)./data(:,6), marker_size, 'MarkerFaceColor', blue, 'MarkerEdgeColor', blue, 'Marker', 's');
-scatter(log(data(:,5)),data(:,2)./data(:,6), marker_size, 'MarkerFaceColor', red, 'MarkerEdgeColor', red, 'Marker', 'd');
-scatter(log(data(:,5)),data(:,1)./data(:,6), marker_size, 'MarkerFaceColor', green, 'MarkerEdgeColor', green, 'Marker', 'h');
-scatter(log(data(:,5)),data(:,3)./data(:,6), marker_size, 'MarkerFaceColor', purple, 'MarkerEdgeColor', purple, 'Marker', 'o');
+scatter(log10(data(:,5)), log10(data(:,4)./data(:,6)), marker_size, 'MarkerFaceColor', blue, 'MarkerEdgeColor', blue, 'Marker', 's');
+scatter(log10(data(:,5)),log10(data(:,2)./data(:,6)), marker_size, 'MarkerFaceColor', red, 'MarkerEdgeColor', red, 'Marker', 'd');
+scatter(log10(data(:,5)),log10(data(:,1)./data(:,6)), marker_size, 'MarkerFaceColor', green, 'MarkerEdgeColor', green, 'Marker', 'h');
+scatter(log10(data(:,5)),log10(data(:,3)./data(:,6)), marker_size, 'MarkerFaceColor', purple, 'MarkerEdgeColor', purple, 'Marker', 'o');
 
-xlabel('informed set volume ratio');
-ylabel('time per sample (ms)');
+xlim([-5, -2.4]);
+xlabel('informed set volume ratio - log_1_0');
+ylabel('time per sample - log_1_0(ms)');
 legend('Rejection', 'HRS', 'MCMC', 'Hit&Run');
 hold off;

### 2017-09-12 paper.tex
new figures
sync

@@
 We then continue in Sec.~\ref{subsec:sampling} to describe different approaches that can be used by  these algorithms to sample~$\calX$.
-We conclude our literature review in Sec.~\ref{subsec:mcmc0} with a brief overview of Markov Chain Monte Carlo methods.
+We conclude our literature review in Sec.~\ref{subsec:mcmc} with a brief overview of Markov Chain Monte Carlo methods.
 
@@
 \subsection{Markov Chain Monte Carlo (MCMC)}
-\label{subsec:mcmc0}
+\label{subsec:mcmc}
 Monte Carlo simulation is a general sampling framework widely used in various domains such as
@@
 Here, given the current point $x_i$ the next point~$x_{i+1}$ in the Markov chain is produced by sampling a random direction~$\theta$ on the surface of the unit sphere centered at $x_{i+1}$.
-This defines a line $\ell_i$ rooted at $x_i$ and passing through~$\theta$.
-The point $x_{i+1}$ is chosen by randomly sampling a point on $\ell_i$ (see also Sec.~\ref{sec:algorithm}).
+This defines a ray $r_i$ rooted at $x_i$ and passing through~$\theta$.
+The point $x_{i+1}$ is chosen by randomly sampling a point on $r_i$.
 This algorithm is considered to be one of the most efficient algorithms for generating an asymptotically uniform point if the set under consideration is convex~\cite{L99, LV06}
@@
 Hybrid approaches that yield short paths but also explore quickly are a promising future direction.}''
-Our paper can be seen as a hybrid approach marrying sampling-based planning with MCM-based approaches.
+Our paper can be seen as a hybrid approach marrying sampling-based planning with MCMC-based approaches.
 
@@
 
-%\subsection{Probabilistic completeness}
+\label{sec:eval}
+% \subsection{Uniformity}
 
-\section{Evaluation}
-\label{sec:eval}
+% (Give a set of parameters)
+% We firstly need to propose a way of measuring uniformity.
+% Then we can apply it to compare MCMC approach with rejection sampling and hierarchical rejection sampling.
+% We are interested with
+% \begin{itemize}
+% 	\item asymptotic behavior (assumption: MCMC converge to a close uniformity)
+% 	\item convergence rate (assumption: MCMC converge faster)
+% \end{itemize}
 
-\subsection{Uniformity}
+\subsection{Sampling Efficiency}
 
-(Give a set of parameters)
-We firstly need to propose a way of measuring uniformity.
-Then we can apply it to compare MCMC approach with rejection sampling and hierarchical rejection sampling.
-We are interested with
-\begin{itemize}
-	\item asymptotic behavior (assumption: MCMC converge to a close uniformity)
-	\item convergence rate (assumption: MCMC converge faster)
-\end{itemize}
+Fig.
+\ref{fig:sampling_efficiency} shows the semi-log plot of the average time taken to generate one sample in the informed space vs.
+informed set volume ratio, i.e.
+the ratio of the volume of informed space to the volume of entire state space for 5000 samples.
+The informed set volume ratio is approximated by the ratio of the number of accepted to the total number samples obtained while running rejection sampling.
+Efficiency of rejection sampling based methods is very low for high dimesions because this ratio decreases exponentially w.r.t the dimension of the space due to the curse of dimensionality.
+The Fig.
+\ref{fig:sampling_efficiency} shows that MCMC and Hit\&Run have a better sampling efficiency compared to HRS and RS with decrease in informed set ratio or increase in dimensions.
+TODO: Brag about order of magnitude improvement (mostly for 6 DoF example)
 
-\subsection{Efficiency}
+\begin{figure*}[t!]
+	\centering
+	\begin{subfigure}[b]{0.32\textwidth}
+		\includegraphics[width=\linewidth]{fig/sampling_efficiency/sample_efficiency_2d}
+		\caption{2DoF - 4D TODO: rescale x axis}
+		\label{fig:sampling_efficiency:2d}
+	\end{subfigure}
+% 	\begin{subfigure}[b]{0.32\textwidth}
+% 		\includegraphics[width=\linewidth]{fig/sampling_efficiency/sample_efficiency_3d}
+% 		\caption{3DoF - 6D}
+% 		\label{fig:sampling_efficiency:3d}
+% 	\end{subfigure}	
+	\begin{subfigure}[b]{0.32\textwidth}
+		\includegraphics[width=\linewidth]{fig/sampling_efficiency/sample_efficiency_6d}
+		\caption{6DoF - 12D. TODO: rescale x axis}
+		\label{fig:sampling_efficiency:6d}
+	\end{subfigure}\\
+	\begin{subfigure}[b]{0.32\textwidth}
+		\includegraphics[width=\linewidth]{fig/sampling_efficiency/sample_efficiency_6d}
+		\caption{2DoF - 4D. TODO:Time per sample vs level set}
+		\label{fig:sampling_efficiency:6d}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.32\textwidth}
+		\includegraphics[width=\linewidth]{fig/sampling_efficiency/sample_efficiency_6d}
+		\caption{6DoF - 12D. TODO:Time per sample vs level set}
+		\label{fig:sampling_efficiency:6d}
+	\end{subfigure}
+	\caption{\captionstyle Sampling efficiency of different sampling methods}
+	\label{fig:sampling_efficiency}
+\end{figure*}
 
-The efficiency is shown by how the time is needed when the number of nodes are increased.
-(Y: time spent) and (X: number of nodes).
+\subsection{Planning Efficiency}
+
+To test the planning efficiency we run the samplers with the informed RRT* planner on 3 different problems described below and shown in Fig.
+\ref{fig:problems}.
+For each problem the start and goal states (positions and velocities) are known in the joint space.
+
+\subsubsection{Problem 1: 3 DoF Planar Manipulator}
+
+\subsubsection{Problem 2: 6 DoF Snake Arm}
+
+\subsubsection{Problem 3: 7 DoF HERB}
+
+\begin{figure*}[t!]
+	\centering
+	\begin{subfigure}[b]{\textwidth}
+	    \centering
+		\includegraphics[height=3cm]{fig/planning_efficiency/3dof_example}
+		\includegraphics[height=3cm]{fig/planning_efficiency/3dof_example}
+		\includegraphics[height=3cm]{fig/planning_efficiency/3dof_example}
+		\includegraphics[height=3cm]{fig/planning_efficiency/3dof_example}
+		\caption{3DOF planar}
+		\label{fig:planning_efficiency:3dof:example}
+	\end{subfigure}
+	\begin{subfigure}[b]{\textwidth}
+	    \centering
+		\includegraphics[height=3cm]{fig/planning_efficiency/6dof_example}
+		\includegraphics[height=3cm]{fig/planning_efficiency/6dof_example}
+		\includegraphics[height=3cm]{fig/planning_efficiency/6dof_example}
+		\includegraphics[height=3cm]{fig/planning_efficiency/6dof_example}
+		\caption{6DOF snake}
+		\label{fig:planning_efficiency:6dof:example}
+	\end{subfigure}
+	\begin{subfigure}[b]{\textwidth}
+    \centering
+    \includegraphics[height=3cm]{fig/planning_efficiency/6dof_example}
+	\caption{HERB}
+	\label{fig:planning_efficiency:6dof:example}
+	\end{subfigure}
+	\caption{Test problems to evaluate planning efficiency. TODO: Add herb and update figures}
+	\label{fig:problems}
+\end{figure*}
 
@@
 	\begin{subfigure}[b]{0.5\textwidth}
-		\includegraphics[width=\linewidth]{fig/sampling_efficiency/sample_efficiency_2d}
-		\caption{2D}
-		\label{fig:sampling_efficiency:2d}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.5\textwidth}
-		\includegraphics[width=\linewidth]{fig/sampling_efficiency/sample_efficiency_3d}
-		\caption{3D}
-		\label{fig:sampling_efficiency:4d}
-	\end{subfigure}	
-	\begin{subfigure}[b]{0.5\textwidth}
-		\includegraphics[width=\linewidth]{fig/sampling_efficiency/sample_efficiency_6d}
-		\caption{6D}
-		\label{fig:sampling_efficiency:6d}
-	\end{subfigure}
-	\caption{\captionstyle Compare the sampling efficiency of different sampling methods.}
-	\label{fig:sampling_efficiency}
-\end{figure}
-
-\subsection{Integration}
-
-We're going to test with RRT*, which falls into a informed RRT*.
-
-We are going to show how the solution cost falls along time.
-(Y: solution cost) and (X: time spent).
-
-\begin{itemize}
-\item DIMT (double integrator minimum time)
-\item Dubins car
-\item Airplane
-\end{itemize}
-
-\begin{figure}[t!]
-	\centering
-	\begin{subfigure}[b]{0.5\textwidth}
-		\includegraphics[width=\linewidth]{fig/planning_efficiency/3dof_example}
-		\caption{3DOF planar}
-		\label{fig:planning_efficiency:3dof:example}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.5\textwidth}
 		\includegraphics[width=\linewidth]{fig/planning_efficiency/3dof_general}
-		\caption{Obstacle avoiding}
+		\caption{\captionstyle Planning Efficiency for Problem 1: 3 DoF Manipulator}
 		\label{fig:planning_efficiency:3dof:general}
 	\end{subfigure}	
-	\begin{subfigure}[b]{0.5\textwidth}
-		\includegraphics[width=\linewidth]{fig/planning_efficiency/3dof_hammering}
-		\caption{Hammering}
-		\label{fig:planning_efficiency:3dof:hammering}
-	\end{subfigure}
-	\caption{\captionstyle An example of a 3DOF planar manipulator.}
-	\label{fig:planning_efficiency:3dof}
-\end{figure}
-
-\begin{figure}[t!]
-	\centering
-	\begin{subfigure}[b]{0.5\textwidth}
-		\includegraphics[width=\linewidth]{fig/planning_efficiency/6dof_example}
-		\caption{6DOF snake}
-		\label{fig:planning_efficiency:6dof:example}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.5\textwidth}
-		\includegraphics[width=\linewidth]{fig/planning_efficiency/6dof_general}
-		\caption{Obstacle avoiding}
-		\label{fig:planning_efficiency:6dof:general}
-	\end{subfigure}	
+% 	\begin{subfigure}[b]{0.5\textwidth}
+% 		\includegraphics[width=\linewidth]{fig/planning_efficiency/3dof_hammering}
+% 		\caption{Hammering}
+% 		\label{fig:planning_efficiency:3dof:hammering}
+% 	\end{subfigure}
+% 	\begin{subfigure}[b]{0.5\textwidth}
+% 		\includegraphics[width=\linewidth]{fig/planning_efficiency/6dof_general}
+% 		\caption{Obstacle avoiding}
+% 		\label{fig:planning_efficiency:6dof:general}
+% 	\end{subfigure}	
 	\begin{subfigure}[b]{0.5\textwidth}
 		\includegraphics[width=\linewidth]{fig/planning_efficiency/6dof_hammering}
-		\caption{Hammering}
-		\label{fig:planning_efficiency:6dof:hammering}
+		\caption{Planning Efficiency for Problem 2: 6DoF Hammering Task}
+		\label{\captionstyle An example of a 6DOF 3D snake.}
 	\end{subfigure}
-	\caption{\captionstyle An example of a 6DOF 3D snake.}
-	\label{fig:planning_efficiency:3dof}
+	\caption{Planning Efficiency}
+	\label{fig:planning_efficiency}
 \end{figure}

### 2017-09-12 paper.tex
sync

@@
 
+\section{Evaluation}
+
 \label{sec:eval}
@@
 	    \centering
-		\includegraphics[height=3cm]{fig/planning_efficiency/3dof_example}
-		\includegraphics[height=3cm]{fig/planning_efficiency/3dof_example}
-		\includegraphics[height=3cm]{fig/planning_efficiency/3dof_example}
-		\includegraphics[height=3cm]{fig/planning_efficiency/3dof_example}
+		\includegraphics[height=2.7cm]{fig/planning_efficiency/3dof_1}
+		\includegraphics[height=2.7cm]{fig/planning_efficiency/3dof_2}
+		\includegraphics[height=2.7cm]{fig/planning_efficiency/3dof_3}
+		\includegraphics[height=2.7cm]{fig/planning_efficiency/3dof_4}
+		\includegraphics[height=2.7cm]{fig/planning_efficiency/3dof_5}
 		\caption{3DOF planar}
@@
 	    \centering
-		\includegraphics[height=3cm]{fig/planning_efficiency/6dof_example}
-		\includegraphics[height=3cm]{fig/planning_efficiency/6dof_example}
-		\includegraphics[height=3cm]{fig/planning_efficiency/6dof_example}
-		\includegraphics[height=3cm]{fig/planning_efficiency/6dof_example}
+		\includegraphics[height=3cm]{fig/planning_efficiency/6dof_1}
+		\includegraphics[height=3cm]{fig/planning_efficiency/6dof_2}
+		\includegraphics[height=3cm]{fig/planning_efficiency/6dof_3}
+		\includegraphics[height=3cm]{fig/planning_efficiency/6dof_4}
+		\includegraphics[height=3cm]{fig/planning_efficiency/6dof_5}
 		\caption{6DOF snake}
@@
     \centering
-    \includegraphics[height=3cm]{fig/planning_efficiency/6dof_example}
+    \includegraphics[height=2.7cm]{fig/planning_efficiency/herb_batting_1}
+    \includegraphics[height=2.7cm]{fig/planning_efficiency/herb_batting_2}
+    \includegraphics[height=2.7cm]{fig/planning_efficiency/herb_batting_3}
+    \includegraphics[height=2.7cm]{fig/planning_efficiency/herb_batting_4}
+    \includegraphics[height=2.7cm]{fig/planning_efficiency/herb_batting_5}
 	\caption{HERB}
-	\label{fig:planning_efficiency:6dof:example}
+	\label{fig:planning_efficiency:herb:example}
 	\end{subfigure}
@@
 	\end{subfigure}	
-% 	\begin{subfigure}[b]{0.5\textwidth}
-% 		\includegraphics[width=\linewidth]{fig/planning_efficiency/3dof_hammering}
-% 		\caption{Hammering}
-% 		\label{fig:planning_efficiency:3dof:hammering}
-% 	\end{subfigure}
-% 	\begin{subfigure}[b]{0.5\textwidth}
-% 		\includegraphics[width=\linewidth]{fig/planning_efficiency/6dof_general}
-% 		\caption{Obstacle avoiding}
-% 		\label{fig:planning_efficiency:6dof:general}
-% 	\end{subfigure}	
 	\begin{subfigure}[b]{0.5\textwidth}
 		\includegraphics[width=\linewidth]{fig/planning_efficiency/6dof_hammering}
-		\caption{Planning Efficiency for Problem 2: 6DoF Hammering Task}
-		\label{\captionstyle An example of a 6DOF 3D snake.}
+		\caption{\captionstyle Planning Efficiency for Problem 2: 6DoF Hammering Task}
+		\label{fig:planning_efficiency:6dof:hammering}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.5\textwidth}
+	\includegraphics[width=\linewidth]{fig/planning_efficiency/herb_batting_efficiency}
+	\caption{\captionstyle Planning Efficiency for Problem 3: 7DoF HERB Batting Task}
+	\label{fig:planning_efficiency:herb:batting}
     \end{subfigure}

### 2017-09-12 code/planning efficiency/herb/batting/merge_planning_data2.m

@@ -1,0 +1,70 @@
+datasetSize = 10;
+maxtimes = zeros(datasetSize,1);
+minvals = zeros(datasetSize,1);
+for i = 0:1:datasetSize-1
+  mcmc_filename = sprintf('data/60s/simple_MCMC_%d.csv', i);
+  rs_filename = sprintf('data/60s/simple_RS_%d.csv', i);
+  hrs_filename = sprintf('data/60s/simple_HRS_%d.csv', i);
+  hnr_filename = sprintf('data/60s/simple_HNR_%d.csv', i);
+  
+  MCMC = csvread(mcmc_filename);
+  RS = csvread(rs_filename);
+  HRS = csvread(hrs_filename);
+  HNR = csvread(hnr_filename);
+  
+  allTime = vertcat(MCMC(:,1), RS(:,1), HRS(:,1), HNR(:,1));
+  allVal = vertcat(MCMC(:,2), RS(:,2), HRS(:,2), HNR(:,2));
+  maxtimes(i+1,1) = max(allTime);
+  minvals(i+1,1) = min(allVal);
+end
+
+maxT = max(maxtimes);
+minVal = min(minvals);
+
+stepNum = 20;
+MCMC1 = zeros(datasetSize, stepNum+1);
+RS1 = zeros(datasetSize, stepNum+1);
+HRS1 = zeros(datasetSize, stepNum+1);
+HNR1 = zeros(datasetSize, stepNum+1);
+
+stepSize = maxT / stepNum;
+deltaStepSize = stepSize / 5;
+T1 = 0:stepSize:maxT;
+T2 = T1 + deltaStepSize; T2(1) = 0;
+T3 = T1 + deltaStepSize*2; T3(1) = 0;
+T4 = T1 + deltaStepSize*3; T4(1) = 0; 
+
+for i = 0:1:datasetSize-1
+  mcmc_filename = sprintf('data/20s/simple_MCMC_%d.csv', i);
+  rs_filename = sprintf('data/20s/simple_RS_%d.csv', i);
+  hrs_filename = sprintf('data/20s/simple_HRS_%d.csv', i);
+  hnr_filename = sprintf('data/20s/simple_HNR_%d.csv', i);
+  
+  MCMC = csvread(mcmc_filename);
+  RS = csvread(rs_filename);
[…]

### 2017-09-12 code/planning efficiency/herb/batting/plot_data2.m

@@ -29,7 +29,7 @@ plot(T3, mean(HRS2,1), 'o', 'MarkerFaceColor', red, 'MarkerEdgeColor', red, 'Mar
 plot(T1, mean(MCMC2,1), 'o', 'MarkerFaceColor', green, 'MarkerEdgeColor', green, 'MarkerSize', 4);
 plot(T4, mean(HNR2,1), 'o', 'MarkerFaceColor', purple, 'MarkerEdgeColor', purple, 'MarkerSize', 4);
 
-xlim([0, 8]);
+xlim([0, 20]);
 legend('RS', 'HRS', 'MCMC', 'HNR');
 xlabel('Time - s');
 ylabel('Ratio to minimum');

### 2017-09-12 code/planning efficiency/planar_manipulator/general/plot_data2.m

@@ -30,7 +30,7 @@ plot(T1, mean(MCMC2,1), 'o', 'MarkerFaceColor', green, 'MarkerEdgeColor', green,
 plot(T4, mean(HNR2,1), 'o', 'MarkerFaceColor', purple, 'MarkerEdgeColor', purple, 'MarkerSize', 4);
 
 xlim([0, 10]);
-legend('MCMC', 'RS', 'HRS', 'HNR');
+legend('RS', 'HRS', 'MCMC', 'HNR');
 xlabel('Time - s');
 ylabel('Ratio to minimum');
 hold off;

### 2017-09-12 code/planning efficiency/planar_manipulator/plot_data.m

@@ -30,7 +30,7 @@ plot(T1, mean(MCMC2,1), 'o', 'MarkerFaceColor', green, 'MarkerEdgeColor', green,
 plot(T4, mean(HNR2,1), 'o', 'MarkerFaceColor', purple, 'MarkerEdgeColor', purple, 'MarkerSize', 4);
 
 xlim([0, 2.5]);
-legend('MCMC', 'RS', 'HRS', 'HNR');
+legend('RS', 'HRS', 'MCMC', 'HNR');
 xlabel('Time - s');
 ylabel('Ratio to minimum');
 hold off;

### 2017-09-13 paper.tex
sync

@@
 \author{
+Daqing Yi$^{*}$,
 Rohan Thakker$^{*}$,
-Cole Gulino$^{*}$,
-Daqing Yi$^{}$,
-Oren Salzman$^{}$ and
+Cole Gulino$^{}$, 
+Oren Salzman$^{}$, and
 Siddhartha Srinivasa$^{}$% <-this % stops a space
-\thanks{*R. Thakker and C. Gulino contributed equally to this paper.}
+\thanks{*Daqing Yi and R. Thakker contributed equally to this paper.}
 \thanks{This work was (partially) funded by the National Science Foundation IIS (\#1409003), Toyota Motor Engineering \& Manufacturing (TEMA), and the Office of Naval Research.}% <-this % stops a space
@@
 As mentioned in Sec.~\ref{sec:intro} Gammel et al.~\cite{GSB14} describe an approach to sample uniformly in~\Cinf for the specific case of where $\calX = \R^d$ and when optimizing for path length.
-To the best of our knowledge, the only method to produce samples in non-Euclidean spaces (other than rejection sampling) is HRS by Kunz et al.~\cite{KTC16}.
+To the best of our knowledge, the only method to produce samples in non-Euclidean spaces that are applied to motion planning problems (other than rejection sampling) is HRS by Kunz et al.~\cite{KTC16}.
 
@@
 
-In this section we describe our approach to efficiently produce a sequence of samples in the informed set~\Cinf given a specific cost~$c_{\text{best}}$.
+In this section we describe our approach to efficiently produce a sequence of samples in the informed set~\Cinf given a specific cost~$c_{\text{best}}$ of trajectory $x_{best}(t)$.
 Our algorithm (see Alg.~\ref{alg:mcmc_informed_sampling}) starts by randomly sampling a state~$x_\text{rand} \in \calX$ (line~2).
@@
 		\LOOP
-			\STATE $x_{\text{rand}} \leftarrow \texttt{sample\_uniform(\calX)}$
-			\STATE $x_{0} 
-		 \leftarrow
-		 \texttt{newton\_raphson}(x_{\text{rand}}, c_{\text{best}})$ ; \hspace{3mm} $i\leftarrow 0$
+			\STATE $x_{0} \leftarrow \texttt{sample\_in\_informed\_space}( method )$
 			\WHILE {\texttt{MCMC\_continue\_chain()}}
@@
 			\ENDWHILE
-
 		\ENDLOOP 
@@
 %		\ENDFOR
-%		 
    	\end{algorithmic}
@@
 
-\subsection{Sampling the boundary of \Cinf via Newton-Raphson}
+\subsection{Sampling the boundary of \Cinf}
 \label{subsec:grad}
+We can use either of the following two approaches to sample points in the informed space:
+\subsubsection{Newton-Raphson Method}
 In theory, MCMC methods converge to the desired distribution regardless of the initial sample used to seed the chain.
@@
 (see also Sec.~\ref{subsec:mcmc}).
+
+\subsubsection{Previous-Trajectory Method}
 
@@
 		\STATE $d \leftarrow$ \texttt{sample\_random\_direction}$()$
-		\STATE $ L(\lambda) = \{  x \mid x = x_i + \lambda d_i \} $
+		\STATE $ L(\lambda) = \{  x \mid x = x_{i-1} + \lambda d_i \} $
 		\STATE $ \lambda^{+} \leftarrow \sup L(\lambda) $; 
@@
 		\STATE $ \lambda' \leftarrow$ \texttt{sample\_random}$ (\lambda^{-} , \lambda^{+})$
-		\STATE $ x_{i+1} \leftarrow x_{i} + \lambda'_{i} d_i $
+		\STATE $ x_{i} \leftarrow x_{i-1} + \lambda'_{i} d_i $
 
-		\IF{ \textsc{Cost}($ x_{i+1} $) $ < c_{\text{best}} $ }
-		  \RETURN $ x_{i+1}$
+		\IF{ \textsc{Cost}($ x_{i} $) $ < c_{\text{best}} $ }
+		  \RETURN $ x_{i}$
 		\ENDIF
@@
   	\end{algorithmic}
-	\caption{Hit-And-Run MCMC $(x_{i}, c_{\text{best}})$}
+	\caption{Hit-And-Run MCMC $(x_{i-1}, c_{\text{best}})$}
 	\label{alg:hit_and_run_mcmc}	
@@
 
-Hit and Run, described in Alg.~\ref{alg:hit_and_run_mcmc} produces a series of samples $x_0, \ldots$.
-Given the previous sample~$x_i$ it first  samples a random direction on the unit sphere (line 1).
-This induces a line~$L(\lambda)$ passing through~$x_i$  in the direction sampled (line 2) parametrized by a scalar~$\lambda$.
-We obtain upper and lower bounds on~$\lambda$ (line 3) that are problem dependant (e.g. these can relate to joint limits of the robot, bounds on maximum velocity etc.).
+We use the Accelerated Hit and Run algorithm \cite{KSZ11}, described in Alg.~\ref{alg:hit_and_run_mcmc} that produces a series of samples $x_0, \ldots$.
+Given the previous sample~$x_{i-1}$ it first  samples a random direction on the unit sphere (line 1).
+This induces a line~$L(\lambda)$ passing through~$x_{i-1}$  in the direction sampled (line 2) parametrized by a scalar~$\lambda$.
+We obtain upper and lower bounds on $\lambda$ (line 3) that are problem dependant.
+For example, if we have box constraints on joint limits of the robot and on maximum velocity, then bounds are given by $\lambda^{+} = -\lambda^{-} = l_{diag}$; where $l_{diag}$ is the length of the longest diagonal of the box.
 We then sample a point along~$L(\lambda)$ by sampling a scalar~$\lambda'$ within our bounds (line 5).
-This defines a point~$x_{i+1}$ which is a candidate for the next sample along the Markov Chain (line 6).
+This defines a point~$x_{i}$ which is a candidate for the next sample along the Markov Chain (line 6).
 We then check if the point lies in the informed set (line 7) and if it does we return it.
 If not, we update our bounds (lines~9-12) and repeat the process.
-The algorithm can be view as an efficient method to perform rejection sampling around the previous sample using in a one-dimensional search space parametrized by $\lambda$.
+The algorithm can be viewed as an efficient method that performs rejection sampling along a one-dimensional line passing through the previous sample parametrized by $\lambda$.
 
@@
 
-\subsubsection{Metropolis-Hasting}
+\begin{algorithm}[t]
+	\begin{algorithmic}[1]
+	    \LOOP
+		\STATE $ x_{i} \leftarrow \texttt{sample\_normal}(x_{i-1},\Sigma) $ 
+		\label{start}
+		\IF{ \textsc{Cost}($ x_{i} $) $ < c_{\text{best}} $  }
+		  \RETURN $x_{i}$
+		\ENDIF 
+		\ENDLOOP
+	\end{algorithmic}
+	\caption{Metropolis-Hastings MCMC $(x_{i-1}, c_{\text{best}})$}
+	\label{alg:mh_mcmc}	
+\end{algorithm}
 
@@
 	\begin{algorithmic}[1]
-		\STATE $ x'_{i+1} \leftarrow g( x'_{i+1} \mid x_{i} ) $
-		\COMMENT {$g$~is a Gaussian}		
-		\IF{ \textsc{Cost}($ x'_{i+1} $) $ < c_{\text{best}} $  }
-		  \RETURN $ x_{i+1} \leftarrow x'_{i+1} $ 
-		\ELSE
-		  \RETURN $ x_{i+1} \leftarrow x_{i} $
+	\IF{ $method = \texttt{Newton-Rapson}$  }
+		\STATE $x_{\text{rand}} \leftarrow \texttt{sample\_uniform(\calX)}$
+		\STATE $x_{0} \leftarrow \texttt{newton\_raphson}(x_{\text{rand}}, c_{\text{best}})$ ; \hspace{3mm} $i\leftarrow 0$
+	\ELSIF{ $method = \texttt{Previous-Trajectory}$ }
+	    \STATE $t_{rand} \leftarrow \texttt{sample\_random\_time()}$
+	    \STATE $x_{0} \leftarrow x_{best}(t_{rand})$
 	\ENDIF
+	\RETURN $x_0$
 	\end{algorithmic}
-	\caption{Metropolis-Hastings MCMC $(x_{i}, c_{\text{best}})$}
-	\label{alg:mh_mcmc}	
+	\caption{sample\_in\_informed\_space$(method, c_{best})$}
+	\label{alg:sample_inf}	
 \end{algorithm}
+
+\subsubsection{Metropolis-Hasting}
 
@@
 While the general algorithm is slightly more complex, for our setting it can be described as follows:
-We generate a new sample $ x_{i+1}$ around the previous sample $ x_{i}$ using a Gaussian distribution (line~1).
+We generate a new sample $ x_{i}$ around the previous sample $ x_{i-1}$ using a Gaussian distribution (line~1).
 We then check if the point lies in the informed set (lines 2-5) and if it does we return it.
@@
 \section{Evaluation}
+\label{sec:eval}
 
-\label{sec:eval}
 % \subsection{Uniformity}
@@
 Fig.
-\ref{fig:sampling_efficiency} shows the semi-log plot of the average time taken to generate one sample in the informed space vs.
+\ref{fig:sampling_efficiency} shows the log plot of the average time taken to generate one sample in the informed space vs.
 informed set volume ratio, i.e.
@@
 Efficiency of rejection sampling based methods is very low for high dimesions because this ratio decreases exponentially w.r.t the dimension of the space due to the curse of dimensionality.
-The Fig.
-\ref{fig:sampling_efficiency} shows that MCMC and Hit\&Run have a better sampling efficiency compared to HRS and RS with decrease in informed set ratio or increase in dimensions.
-TODO: Brag about order of magnitude improvement (mostly for 6 DoF example)
+The Fig. \ref{fig:sampling_efficiency} shows that MCMC and Hit\&Run have a better sampling efficiency compared to HRS and RS with decrease in informed set ratio or increase in dimensions. 
+TODO: Brag about order of magnitude improvement!
 
-\begin{figure*}[t!]
+\begin{figure}[t!]
 	\centering
-	\begin{subfigure}[b]{0.32\textwidth}
+	\begin{subfigure}[b]{0.48\linewidth}
 		\includegraphics[width=\linewidth]{fig/sampling_efficiency/sample_efficiency_2d}
@@
 % 	\end{subfigure}	
-	\begin{subfigure}[b]{0.32\textwidth}
+	\begin{subfigure}[b]{0.48\linewidth}
 		\includegraphics[width=\linewidth]{fig/sampling_efficiency/sample_efficiency_6d}
@@
 	\end{subfigure}\\
-	\begin{subfigure}[b]{0.32\textwidth}
+	\begin{subfigure}[b]{0.48\linewidth}
 		\includegraphics[width=\linewidth]{fig/sampling_efficiency/sample_efficiency_6d}
@@
 	\end{subfigure}
-	\begin{subfigure}[b]{0.32\textwidth}
+	\begin{subfigure}[b]{0.48\linewidth}
 		\includegraphics[width=\linewidth]{fig/sampling_efficiency/sample_efficiency_6d}
@@
 	\label{fig:sampling_efficiency}
-\end{figure*}
+\end{figure}
 
@@
 
-To test the planning efficiency we run the samplers with the informed RRT* planner on 3 different problems described below and shown in Fig.
+The quality of samples determines the efficiency of resulting planning algorithms.
+To evaluate how the samplers impact the planning efficiency, we run the samplers with the informed RRT* planner~\cite{GSB14} on three different problems described below and shown in Fig.
 \ref{fig:problems}.
@@
 
+Problem 1 is a 3 DoF manipulator that moves on a plane.
+The state boundary of each join is $ [ - \pi , \pi ] $, the velocity boundary is $ [-10, 10] $, and the acceleration is $ 1 $.
+
 \subsubsection{Problem 2: 6 DoF Snake Arm}
 
+Problem 2 is a 6 DoF snake arm that moves in a 3D workspace.
+The state boundary of each join is $ [ - \pi , \pi ] $, the velocity boundary is $ [-10, 10] $, and the acceleration is $ 1 $.
+
 \subsubsection{Problem 3: 7 DoF HERB}
+
+Dimension 0 [0.541593 , 5.74159]
+Dimension 1 [-2 , 2]
+Dimension 2 [-2.8 , 2.8]
+Dimension 3 [-0.9 , 3.1]
+Dimension 4 [-4.76 , 1.24]
+Dimension 5 [-1.6 , 1.6]
+Dimension 6 [-3 , 3]
+Dimension 7 [-0.75 , 0.75]
+Dimension 8 [-0.75 , 0.75]
+Dimension 9 [-2 , 2]
+Dimension 10 [-2 , 2]
+Dimension 11 [-2.5 , 2.5]
+Dimension 12 [-2.5 , 2.5]
+Dimension 13 [-2.5 , 2.5]
 
@@
 	    \centering
-		\includegraphics[height=2.7cm]{fig/planning_efficiency/3dof_1}
-		\includegraphics[height=2.7cm]{fig/planning_efficiency/3dof_2}
-		\includegraphics[height=2.7cm]{fig/planning_efficiency/3dof_3}
-		\includegraphics[height=2.7cm]{fig/planning_efficiency/3dof_4}
-		\includegraphics[height=2.7cm]{fig/planning_efficiency/3dof_5}
+		\includegraphics[height=2.45cm]{fig/planning_efficiency/3dof_1}
+		\includegraphics[height=2.45cm]{fig/planning_efficiency/3dof_2}
+		\includegraphics[height=2.45cm]{fig/planning_efficiency/3dof_3}
+		\includegraphics[height=2.45cm]{fig/planning_efficiency/3dof_4}
+		\includegraphics[height=2.45cm]{fig/planning_efficiency/3dof_5}
 		\caption{3DOF planar}
@@
 
+The Met
+
 What MCMC algorithm is the best to use?

### 2017-09-13 code/motivation/plotdata.m

@@ -1,0 +1,46 @@
+
+fastX = [1:1:45]';
+slowX = [1:1:14]';
+
+green = [49,163,84]/255;
+red = [222 45 38]/255;
+blue = [49,130,189]/255;
+orange = [230,85,13]/255;
+purple = [117,107,177]/255;
+pink = [197,27,138]/255;
+
+
+figure(1);
+hold on;
+plot(fastX, fastpath(:,9)/1.5,'-', 'linewidth', 2, 'color', green);
+plot(fastX, fastpath(:,11)/4,'-', 'linewidth', 2, 'color',red);
+plot(fastX, fastpath(:,13)/5,'-', 'linewidth', 2, 'color', blue);
+
+plot(fastX, fastpath(:,2), '--', 'linewidth', 2, 'color', orange);
+plot(fastX, fastpath(:,4), '--', 'linewidth', 2, 'color', purple);
+plot(fastX, fastpath(:,6), '--', 'linewidth', 2,'color',pink);
+
+xlim([1,45]);
+legend('DoF2', 'DoF4', 'DoF6', 'Vel2', 'Vel4', 'Vel6');
+xlabel('Time step');
+ylabel('Value');
+hold off;
+
+
+
+figure(2);
+hold on;
+plot(slowX, slowpath(:,9)/1.5, '-', 'linewidth', 2, 'color', green);
+plot(slowX, slowpath(:,11)/4, '-', 'linewidth', 2, 'color',red);
+plot(slowX, slowpath(:,13)/5, '-', 'linewidth', 2, 'color',blue);
+
+plot(slowX, slowpath(:,2), '--', 'linewidth', 2, 'color',orange);
+plot(slowX, slowpath(:,4), '--', 'linewidth', 2, 'color',purple);
+plot(slowX, slowpath(:,6), '--', 'linewidth', 2, 'color',pink);
+hold off;
+
+xlim([1,14]);
+legend('DoF2', 'DoF4', 'DoF6', 'Vel2', 'Vel4', 'Vel6');
+xlabel('Time step');
+ylabel('Value');
+

### 2017-09-13 code/sample efficiency/6d/plot2.m

@@ -1,0 +1,30 @@
+data = sortrows(dim6, 5);
+
+%data(:,1) = log(data(:,1));
+%data(:,2) = log(data(:,2));
+%data(:,3) = log(data(:,3));
+%data(:,4) = log(data(:,4));
+
+green = [49,163,84]/255;
+red = [222 45 38]/255;
+blue = [49,130,189]/255;
+orange = [230,85,13]/255;
+purple = [117,107,177]/255;
+pink = [197,27,138]/255;
+
+figure;
+hold on;
+marker_size = 20;
+%scatter(log10(data(:,5)), log10(data(:,4)./data(:,6)), marker_size, 'MarkerFaceColor', blue, 'MarkerEdgeColor', blue, 'Marker', 's');
+%scatter((data(:,5)),log10(data(:,2)./data(:,6)), marker_size, 'MarkerFaceColor', red, 'MarkerEdgeColor', red, 'Marker', 'd');
+%scatter(log10(data(:,5)),log10(data(:,1)./data(:,6)), marker_size, 'MarkerFaceColor', green, 'MarkerEdgeColor', green, 'Marker', 'h');
+%scatter((data(:,5)),log10(data(:,3)./data(:,6)), marker_size, 'MarkerFaceColor', purple, 'MarkerEdgeColor', purple, 'Marker', 'o');
+
+
+
+%xlim([-5, -2.4]);
+xlabel('informed set volume ratio - log_1_0');
+ylabel('time per sample - log_1_0(ms)');
+%legend('Rejection', 'HRS', 'MCMC', 'Hit&Run');
+legend( 'HRS',  'Hit&Run');
+hold off;

### 2017-09-13 paper.tex
sync

@@
 
+\begin{figure*}[t!]
+	\centering
+	\begin{subfigure}[b]{\textwidth}
+		\centering
+		\includegraphics[height=3cm]{fig/motivation/slow1}
+		\includegraphics[height=3cm]{fig/motivation/slow2}
+		\includegraphics[height=3cm]{fig/motivation/slow3}
+		\includegraphics[height=3cm]{fig/motivation/slow4}
+		\includegraphics[height=3cm]{fig/motivation/slowmotion}
+		\caption{Zero goal velocity}
+		\label{fig:motivation:slow}
+	\end{subfigure}
+	\begin{subfigure}[b]{\textwidth}
+		\centering
+		\includegraphics[height=3cm]{fig/motivation/fast1}
+		\includegraphics[height=3cm]{fig/motivation/fast2}
+		\includegraphics[height=3cm]{fig/motivation/fast3}
+		\includegraphics[height=3cm]{fig/motivation/fast4}
+		\includegraphics[height=3cm]{fig/motivation/fastmotion}
+		\caption{Non-zero goal velocity}
+		\label{fig:motivation:fast}
+	\end{subfigure}
+	\caption{HERB moves right arm from a start configuration to a goal configuration, which are very close.
+    When the goal velocity is non-zero, HERB needs to move right arm further away to accelerate.
+	}
+	\label{fig:motivation}
+\end{figure*}
+
 \os{structure}
@@
 \label{sec:pdef}
+
 Let $\calX, \calU$ denote the state and controls spaces, respectively and set $\Cfree \subset \calX$ to be the set of states where the robot is collision free.
@@
 
-\section{Motivating example---Minimal-Time Double Integrator (MTDI)}
+\subsection{Motivating example---Minimal-Time Double Integrator (MTDI)}
 \label{sec:mtdi}
@@
 	    \LOOP
-		\STATE $ x_{i} \leftarrow \texttt{sample\_normal}(x_{i-1},\Sigma) $ 
+		\STATE $ x'_{i} \leftarrow \texttt{sample\_normal}(x_{i-1},\Sigma) $ 
 		\label{start}
+		\IF{ $ x'_{i} \leftarrow$ \texttt{sample\_random}$ (0.0 , 1.0) >  \pi( x'_{i} ) / \pi( x_{i} ) $  }
+		\STATE x
+ 		\ENDIF
 		\IF{ \textsc{Cost}($ x_{i} $) $ < c_{\text{best}} $  }
@@
 
+We evaluate the performance of proposed MCMC methods by comparing four types of samplers, which are rejection sampler (RS), hierarchical rejection sampler (HRS), Metropolis-Hastings sampler (MHS), and Hit-and-run sampler (HNR).
+We use different samplers to generate a fixed number of samples in different informed sets to check the sampling efficiency, especially when the sampling is harder (in a small informed set).
+We then evaluate how the samplers works with informed RRT*~\cite{GSB14}, which reflect the quality of samples in an informed set.
+
 \subsection{Sampling Efficiency}
@@
 The Fig. \ref{fig:sampling_efficiency} shows that MCMC and Hit\&Run have a better sampling efficiency compared to HRS and RS with decrease in informed set ratio or increase in dimensions. 
-TODO: Brag about order of magnitude improvement!
+Figure \ref{fig:sampling_efficiency:levelset} shows how the informed set volume ratio decreases as the level set cost $ c_{best} $ becomes smaller in problems of different dimensions.
+In a higher dimension, the informed set volume ratio falls much more quickly as the level set cost $ c_{best} $ decreases in planning process, as new better solutions are kept being found.
 
@@
 	\begin{subfigure}[b]{0.48\linewidth}
+		\includegraphics[width=\linewidth]{fig/sampling_efficiency/levelset}
+		\caption{2DoF - 4D. TODO:Time per sample vs level set}
+		\label{fig:sampling_efficiency:levelset}
+	\end{subfigure}
+	%\begin{subfigure}[b]{0.48\linewidth}
+	%	\includegraphics[width=\linewidth]{fig/sampling_efficiency/levelset_6d}
+	%	\caption{6DoF - 12D. TODO:Time per sample vs level set}
+	%	\label{fig:sampling_efficiency:6d}
+	%\end{subfigure}
+	 \\
+	\begin{subfigure}[b]{0.78\linewidth}
 		\includegraphics[width=\linewidth]{fig/sampling_efficiency/sample_efficiency_2d}
@@
 % 	\end{subfigure}	
-	\begin{subfigure}[b]{0.48\linewidth}
+	\begin{subfigure}[b]{0.78\linewidth}
 		\includegraphics[width=\linewidth]{fig/sampling_efficiency/sample_efficiency_6d}
 		\caption{6DoF - 12D. TODO: rescale x axis}
-		\label{fig:sampling_efficiency:6d}
-	\end{subfigure}\\
-	\begin{subfigure}[b]{0.48\linewidth}
-		\includegraphics[width=\linewidth]{fig/sampling_efficiency/sample_efficiency_6d}
-		\caption{2DoF - 4D. TODO:Time per sample vs level set}
-		\label{fig:sampling_efficiency:6d}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.48\linewidth}
-		\includegraphics[width=\linewidth]{fig/sampling_efficiency/sample_efficiency_6d}
-		\caption{6DoF - 12D. TODO:Time per sample vs level set}
 		\label{fig:sampling_efficiency:6d}
@@
 \end{figure} 
+vantage of sampling a near state.
+Both the per-sampling time of HRS 
+It is noticeable that both x axis and y axis are converted by $ \log_{10} () $ in Figure~\ref{fig:sampling_efficiency:2d} and Figure~\ref{fig:sampling_efficiency:6d}.
+This reserves the linearity of the data from rejection sampler, but also scales the difference in a smaller range for comparison.
+Keep in mind that the differences in unit (ms) are much bigger.
+\dy{TODO: change MCMC to MH (Metropolis Hasting) in the plots}
+Metropolis-Hasting shows consistent performance when the informed set volume ratio is decreased, because it takes the adand HNR increases with the decrease of the informed set volume ratio. 
+When informed set volume ratio is relatively high, it is easy to generate qualified samples.
+All the samplers have close performances.
+RS and HRS can be the most efficient because of its simple design.
+But when problems get harder, HNR outperforms HRS significantly.
 
@@
 
-Problem 1 is a 3 DoF manipulator that moves on a plane.
-The state boundary of each join is $ [ - \pi , \pi ] $, the velocity boundary is $ [-10, 10] $, and the acceleration is $ 1 $.
+Problem 1 is a 3 DoF manipulator that moves on a plane, which results in a 6 dimension space.
+The position boundary of each join is $ [ - \pi , \pi ] $, the velocity boundary is $ [-10, 10] $, and the acceleration is $ 1 $.
+Figure~\ref{fig:planning_efficiency:3dof:example} shows a few steps of a planned path.
 
@@
 
-Problem 2 is a 6 DoF snake arm that moves in a 3D workspace.
-The state boundary of each join is $ [ - \pi , \pi ] $, the velocity boundary is $ [-10, 10] $, and the acceleration is $ 1 $.
+Problem 2 is a 6 DoF snake arm that moves in a 3D workspace, which results in a 12 dimension space.
+The position boundary of each join is $ [ - \pi , \pi ] $, the velocity boundary is $ [-10, 10] $, and the acceleration is $ 1 $.
+Figure~\ref{fig:planning_efficiency:6dof:example} shows a few steps of a planned path.
 
@@
 
-Dimension 0 [0.541593 , 5.74159]
-Dimension 1 [-2 , 2]
-Dimension 2 [-2.8 , 2.8]
-Dimension 3 [-0.9 , 3.1]
-Dimension 4 [-4.76 , 1.24]
-Dimension 5 [-1.6 , 1.6]
-Dimension 6 [-3 , 3]
-Dimension 7 [-0.75 , 0.75]
-Dimension 8 [-0.75 , 0.75]
-Dimension 9 [-2 , 2]
-Dimension 10 [-2 , 2]
-Dimension 11 [-2.5 , 2.5]
-Dimension 12 [-2.5 , 2.5]
-Dimension 13 [-2.5 , 2.5]
+Problem 3 is a 7 DoF Barrett WAM arm of HERB that moves in a 3D workspace, which results in a 14 dimension space.
+The position boundaries of 7 joints of the arm are $  [0.541593 , 5.74159] $, $  [-2 , 2] $, $ [-2.8 , 2.8] $, $ [-0.9 , 3.1] $, $ [-4.76 , 1.24] $, $ [-1.6 , 1.6] $ and $ [-3 , 3] $.
+The velocity boundary of 7 joints of the arm are $ [-0.75 , 0.75] $, $ [-0.75 , 0.75] $, $ [-2 , 2] $, $ [-2 , 2] $, $ [-2.5 , 2.5] $, $ [-2.5 , 2.5] $ and $ [-2.5 , 2.5] $.
+The accelerations of all the joints are set to $ 1 $.
+Figure~\ref{fig:planning_efficiency:herb:example} shows a few steps of a planned path.
 
@@
 
-\begin{figure}[t!]
+\begin{figure*}[t!]
 	\centering
-	\begin{subfigure}[b]{0.5\textwidth}
+	\begin{subfigure}[b]{0.32\textwidth}
 		\includegraphics[width=\linewidth]{fig/planning_efficiency/3dof_general}
@@
 	\end{subfigure}	
-	\begin{subfigure}[b]{0.5\textwidth}
+	\begin{subfigure}[b]{0.32\textwidth}
 		\includegraphics[width=\linewidth]{fig/planning_efficiency/6dof_hammering}
@@
 	\end{subfigure}
-	\begin{subfigure}[b]{0.5\textwidth}
+	\begin{subfigure}[b]{0.32\textwidth}
 	\includegraphics[width=\linewidth]{fig/planning_efficiency/herb_batting_efficiency}
@@
 	\label{fig:planning_efficiency}
-\end{figure}
+\end{figure*}
+
+\dy{TODO: add a plot that shows the increases of samples}
+
+MHS shows the worst performance in Figure~\ref{fig:planning_efficiency:3dof:general}, \ref{fig:planning_efficiency:6dof:hammering} and \ref{fig:planning_efficiency:herb:batting}.
+Though theoretically samples converge to a target distribution, the samples could be either too correlated for exploration purpose in planning.
+If the variance of transition distribution is too high, it will then move out of the informed set too frequently, and takes longer to converge.
+Ideally we want to have markov chains are less correlated but moves in informed sets.
+
+HNR shows close performance with RS and HRS in a 6-dimension space, as in Figure~\ref{fig:planning_efficiency:3dof:general}.
+But in higher dimension performance, the advantage of HNR in sampling efficiency is shown.
+In Figure~\ref{fig:planning_efficiency:6dof:hammering} and \ref{fig:planning_efficiency:herb:batting}, the cost of current best solution by planners with HNR sampler converge significantly faster.
 

### 2017-09-13 code/motivation/plotdata.m
add phase plot

@@ -9,7 +9,7 @@ orange = [230,85,13]/255;
 purple = [117,107,177]/255;
 pink = [197,27,138]/255;
 
-
+%{
 figure(1);
 hold on;
 plot(fastX, fastpath(:,9)/1.5,'-', 'linewidth', 2, 'color', green);
@@ -27,7 +27,6 @@ ylabel('Value');
 hold off;
 
 
-
 figure(2);
 hold on;
 plot(slowX, slowpath(:,9)/1.5, '-', 'linewidth', 2, 'color', green);
@@ -43,4 +42,54 @@ xlim([1,14]);
 legend('DoF2', 'DoF4', 'DoF6', 'Vel2', 'Vel4', 'Vel6');
 xlabel('Time step');
 ylabel('Value');
+%}
+
+figure(3);
+
+step = 6;rMag = 0.1;
+fastNum = size(fastpath,1);
+slowNum = size(slowpath,1);
+fastQuiverNum = floor(fastNum/step);
+slowQuiverNum = floor(slowNum/step);
+fastV0 = zeros(fastQuiverNum,2);
+fastP = zeros(fastQuiverNum,2);
+slowV0 = zeros(slowQuiverNum,2);
+slowP = zeros(slowQuiverNum,2);
+
+for i = 1:1:fastQuiverNum
+    fastV0(i,1) = fastpath(i*step,2);
+    fastV0(i,2) = fastpath(i*step,9);
+    fastP(i,1) = (fastpath(i*step+1,2) - fastpath(i*step,2)) * rMag;
+    fastP(i,2) = (fastpath(i*step+1,9) - fastpath(i*step,9)) * rMag;
+end
+for i = 1:1:slowQuiverNum
+    slowV0(i,1) = slowpath(i*step,2);
+    slowV0(i,2) = slowpath(i*step,9);
+    slowP(i,1) = (slowpath(i*step+1,2) - slowpath(i*step,2)) * rMag;
+    slowP(i,2) = (slowpath(i*step+1,9) - slowpath(i*step,9)) * rMag;
+end
+hold on;
+h1 = plot(fastpath(:,2), fastpath(:,9), '-', 'linewidth', 2 , 'color', green);
+h2 = plot(slowpath(:,2), slowpath(:,9), '--', 'linewidth', 2, 'color', blue);
[…]

### 2017-09-13 paper.tex

@@
 \title{\LARGE \bf
-Informed sampling by Markov Chain Monte Carlo methods
+Generalizing Informed Sampling
+for Asymptotically Optimal Sampling-based Planning via Markov Chain
+Monte Carlo Methods
 }
@@
 
-\subsection{Motivating example---Minimal-Time Double Integrator (MTDI)}
+\subsection{Motivating example---Minimal-Time Double Integrator}
 \label{sec:mtdi}
+
+\os{mention~\cite{LM97} here or in related work}
 
@@
 
+\os{mention that it is AO}
+
 \begin{algorithm}[t]
@@
 (ii)~a predefined number of samples was exceeded.
+
+\os{Mention that we do not need convexity}
 
@@
 
+\os{Explain why MCMC is flat, mention strawman approach}
+
 \subsection{Planning Efficiency}
@@
 \section{Conclusion}
+\os{Discuss param tuning, we did nothing + there is a wealth of literature}
+
+\os{use with BIT*, challenge - distance function is not a metric}
 

### 2017-09-14 paper.tex
sync
add level set plot

@@
 Cole Gulino$^{}$, 
-Oren Salzman$^{}$, and
+Oren Salzman$^{}$ and
 Siddhartha Srinivasa$^{}$% <-this % stops a space
@@
 \begin{abstract}
+Asymptotically-optimal motion planners such as RRT* have been shown to incrementally approximate the shortest path between a start and goal states.
+Once an initial solution is found, their performance can be dramatically improved by restricting subsequent samples to regions of the state space that can potentially improve the current solution.
+When the motion planning problem lies in a Euclidean space, this region~$\Cinf$, called the informed set, can be sampled directly.
+However, when planning with differential constraints in non-Euclidean state spaces, no analytic solutions exists to sampling~$\Cinf$ directly.
 
+State-of-the-art approaches to sampling~$\Cinf$ in such domains such as Hierarchical Rejection Sampling (HRS) may still be slow in high-dimensional state space.
+This may cause the planning algorithm to spend most of its time trying to produces samples in~$\Cinf$ rather than explore it.
+In this paper, we suggest an alternative approach to produce samples in the informed set~\Cinf for a wide range of settings.
+Our main insight is to recast this problem as one of sampling uniformly within a level set of an implicit function.
+This recasting enables us to apply Monte Carlo sampling methods, used very effectively in the Machine Learning and Optimization communities, to solve our problem.
+We show for a wide range of scenarios that using our sampler can accelerate the convergence rate to high-quality solutions in high-dimensional problems.
 \end{abstract}
@@
 
-While our approach can be used with any Markov chain Monte Carlo (MCMC) method, it is especially suited to be used with hit and run~\cite{S84,KSZ11}.
-Roughly speaking, this is because hit and run (detailed in Sec~\ref{sec:related_work})
+While our approach can be used with any Markov chain Monte Carlo (MCMC) method, it is especially suited to be used with Hit-and-Run~\cite{S84,KSZ11}.
+Roughly speaking, this is because Hit-and-Run (detailed in Sec~\ref{sec:related_work})
 performs a series of one-dimensional rejection samples which are extremely fast to compute, even in high-dimensional spaces.
@@
 	\centering
+	\begin{minipage}[t]{0.64\linewidth}
 	\begin{subfigure}[b]{\textwidth}
 		\centering
-		\includegraphics[height=3cm]{fig/motivation/slow1}
-		\includegraphics[height=3cm]{fig/motivation/slow2}
-		\includegraphics[height=3cm]{fig/motivation/slow3}
-		\includegraphics[height=3cm]{fig/motivation/slow4}
-		\includegraphics[height=3cm]{fig/motivation/slowmotion}
+		\includegraphics[height=2.7cm]{fig/motivation/slow1}
+		\includegraphics[height=2.7cm]{fig/motivation/slow2}
+		\includegraphics[height=2.7cm]{fig/motivation/slow3}
+		\includegraphics[height=2.7cm]{fig/motivation/slow4}
+		%\includegraphics[height=3cm]{fig/motivation/slowmotion}
 		\caption{Zero goal velocity}
@@
 		\centering
-		\includegraphics[height=3cm]{fig/motivation/fast1}
-		\includegraphics[height=3cm]{fig/motivation/fast2}
-		\includegraphics[height=3cm]{fig/motivation/fast3}
-		\includegraphics[height=3cm]{fig/motivation/fast4}
-		\includegraphics[height=3cm]{fig/motivation/fastmotion}
+		\includegraphics[height=2.7cm]{fig/motivation/fast1}
+		\includegraphics[height=2.7cm]{fig/motivation/fast2}
+		\includegraphics[height=2.7cm]{fig/motivation/fast3}
+		\includegraphics[height=2.7cm]{fig/motivation/fast4}
+		%\includegraphics[height=3cm]{fig/motivation/fastmotion}
 		\caption{Non-zero goal velocity}
@@
 	\end{subfigure}
+    \end{minipage}
+    \begin{minipage}[t]{0.33\linewidth}
+    	\begin{subfigure}[c]{\textwidth}
+    		\includegraphics[width=\textwidth]{fig/motivation/phase_plot}
+    		\caption{Non-zero goal velocity}
+    		\label{fig:motivation:phase_plot}
+        \end{subfigure}
+   	\end{minipage}
 	\caption{HERB moves right arm from a start configuration to a goal configuration, which are very close.
@@
 
-\os{structure}
+The rest of the paper is structured as follows: after describing related work in Sec.~\ref{sec:related_work}, we formally define our problem in Sec.~\ref{sec:pdef}.
+We then provide in Sec.~\ref{sec:motivation} an intuitive description of the challenges faced in sampling within the informed set for our planning domains.
+We continue in Sec.~\ref{sec:algorithm} with a description of our algorithm and present experimental evaluations in Sec.~\ref{sec:eval}.
+Finally, we conclude with a discussion in Sec.~\ref{sec:future}.
 
@@
 Of specific interest to our work are approaches that produce samples in the informed set~\Cinf.
-As mentioned in Sec.~\ref{sec:intro} Gammel et al.~\cite{GSB14} describe an approach to sample uniformly in~\Cinf for the specific case of where $\calX = \R^d$ and when optimizing for path length.
-To the best of our knowledge, the only method to produce samples in non-Euclidean spaces that are applied to motion planning problems (other than rejection sampling) is HRS by Kunz et al.~\cite{KTC16}.
+As mentioned in Sec.~\ref{sec:intro} Gammel et al.~\cite{GSB14} describe an approach to sample uniformly in~\Cinf for the specific case where $\calX = \R^d$ and when optimizing for path length.
+To the best of our knowledge, the only method to produce samples in non-Euclidean spaces that can be  applied to motion planning problems (other than rejection sampling) is HRS by Kunz et al.~\cite{KTC16}.
 
@@
 One variant, which is of special interest to us is 
-hit-and-run~\cite{S84,KSZ11}.
+Hit and Run~\cite{S84,KSZ11}.
 Here, given the current point $x_i$ the next point~$x_{i+1}$ in the Markov chain is produced by sampling a random direction~$\theta$ on the surface of the unit sphere centered at $x_{i+1}$.
@@
 
-The attractiveness of hit and run for our problem domain stems from the fact that it performs a series of one-dimensional rejection samples which are extremely fast to compute, even in high-dimensional spaces.
-Finally, it is worth noting that we are not the first to apply hit and run for motion-planning problems.
+The attractiveness of Hit and Run for our problem domain stems from the fact that it performs a series of one-dimensional rejection samples which are extremely fast to compute, even in high-dimensional spaces.
+Finally, it is worth noting that we are not the first to apply Hit and Run for motion-planning problems.
 Recently~\cite{YPVA17} was used as an alternative to RRT to produce \emph{feasible motions} (and not high-quality paths). 
@@
 
-\subsection{Motivating example---Minimal-Time Double Integrator}
+In this work we consider the problem of efficiently producing samples within~$\Cinf$.
+These samples will be used within the informed RRT* framework to efficiently and incrementally compute trajectories of decreasing cost, converging to the optimal trajectory.
+\os{mention that it is AO}
+\begin{prop}
+	\dy{claim that once informed sampler provides uniform samplings in any given level set in a non-euclidean state space, the corresponding informed RRT* could asymptotically find an optimal solution.}
+\end{prop}
+
+\section{Motivation---\Cinf in kinodynamic state spaces}
 \label{sec:mtdi}
 
-\os{mention~\cite{LM97} here or in related work}
+In this section we properly motivate this work.
+Specifically, we start by describing the differences in between planning in Euclidean configuration spaces (also called geometric planning) nd non-Euclidean  state spaces.
 
+%\os{mention~\cite{LM97} here or in related work}
+\subsection{Geometric vs. Kinodynamic planning}
+
+\os{refer to Fig.~2 or the updated one.}
+
+\subsection{Minimal Time Double Integrator}
 To understand why we resort to optimization-based methods and do not attempt to provide a closed-form solution to sample $\Cinf$ we study the structure of the informed set for a simple yet important dynamical system---the double integrator minimizing time (MTDI).
@@
 \end{bmatrix}
-u
+u.
 \end{equation}
@@
 
+\dy{Do you think we should include some figures that has been commented out below to show how difficult sampling an informed set is?}
+
 \ignore{
@@
 Because the nature of this equation changes with the start and end goal, there is a curve in the input space that amounts to a switching surface that represents the boundary for the decision of the sign of $a_1$.
-This surface causes a discontinuous cost surface as shown in Fig.
-~\ref{fig:cost_surface_1d}.
+This surface causes a discontinuous cost surface as shown in Fig. ~\ref{fig:cost_surface_1d}.
 }
@@
 
-In this section we describe our approach to efficiently produce a sequence of samples in the informed set~\Cinf given a specific cost~$c_{\text{best}}$ of trajectory $x_{best}(t)$.
-Our algorithm (see Alg.~\ref{alg:mcmc_informed_sampling}) starts by randomly sampling a state~$x_\text{rand} \in \calX$ (line~2).
-This sample is used to produces a 
-sample~$x_0 \in \partial\Cinf$ 
-%sample~$x_\text{boundary} \in \partial\Cinf$ 
-which lies (approximately) on the boundary of the informed set (Sec.~\ref{subsec:grad}) by applying Newton-Raphson method~\cite{RT06} (line~3).
-Finally,~$x_0$ 
-%use~$x_\text{boundary}$ 
-is used (lines~4-6)
+In this section we describe our approach to efficiently produce new samples in an informed set ~\Cinf given a specific cost~$c_{\text{best}}$ of trajectory $x_{best}(t)$.
+The samples follow a Monte Carlo Markov Chain, in which a new sample candiate is produceded from a previous sample that also lies in the same informed set.
+It is important to note that at each iteration, we will query our algorithm for one sample. 
+However, this sample depends on the previous iterations of the algorithm which is why we describe it as a method to produce a sequence of samples.
+Furthermore, the value~$c_{\text{best}}$ can decrease between consecutive iterations.
+This will occur if the search algorithm that uses our sampler finds a path to the goal whose cost is lower than~$c_{\text{best}}$.
+
+The idea behind introducing MCMC to informed sampling is to defining a target distribution $ \pi $ as a uniform distribution in a level set $ \Cinf $.
+The sampling process consists of two stages,
+\begin{enumerate}
+	\item finding a sample in the informed same $ x_0 \in \Cinf $ as the start of a Markov chain, which is written as 
+	$ x_{0} \leftarrow \texttt{sample\_in\_informed\_space}( )$; and
+	\item sampling a new sample $ x_i $ from a previous sample $ x_{i-1} $ in the same informed set, which is written as  $x_{i} \leftarrow \texttt{MCMC\_sample} (x_{i-1}, c_{\text{best}})$.
+\end{enumerate}
+Compared with rejection samplers, a MCMC-based informed sampler takes the advantage of a previous sample in the level set $ \Cinf $ in finding a new sample, while reserves the randomness in problem space search, which builds an ``exploitation and exploration" patter in informed sampling.
+
 to initialize an MCMC algorithm which outputs a series of samples within \Cinf by constructing a Markov Chain.
@@
 
-It is important to note that at each iteration, we will query our algorithm for one sample.
-However, this sample depends on the previous iterations of the algorithm which is why we describe it as a method to produce a sequence of samples.
-Furthermore, the value~$c_{\text{best}}$ can decrease between consecutive iterations.
-This will occur if the search algorithm that uses our sampler finds a path to the goal whose cost is lower than~$c_{\text{best}}$.
+\subsection{Find a sample in a level set}
 
-\os{mention that it is AO}
+In our setting, we are only interested in points in~\Cinf, thus we can start the Markov Chain in~\Cinf and avoid this burn-in stage. 
+A new Markov chain is initialized when 
+\begin{itemize}
+	\item a new informed set is provided (e.g. a new current-best is found by the planner); or
+	\item a new sample of an existing Markov chain is outside the level set.
+\end{itemize}
+There are a few methods that provides a sample in a given level set $ \Cinf $ in a planning problem, for example
+\begin{itemize}
+	\item sampling from the start state and the goal state
+	\footnote{The start state and the goal state are guaranteed to be in any level set $ \Cinf $ because of the definition of a level set};
+	\item using a gradient descent algorithm (e.g. Newton-Raphson Method~\cite{RT06}) to find a sample in the level set $ \Cinf $; 
+	\footnote{ $ \forall x_i \in \Cinf \land x_j \not\in \Cinf, c( x_i ) > c ( x_j ) $. }
+	\item sampling from a pool of previous samples that are in the level set $ \Cinf $; and
+	\item calling a rejection sampling till one is in the level set is found.
+\end{itemize}
+
+Different methods have their pros and cons.
+For example, a gradient descent algorithm is usually efficient in finding a solution, but subject to only convex problems.
+Sampling from a pool of samples is algorithmic-free but might attract new samples near around previous samples.
+
+In theory, MCMC methods converge to the desired distribution regardless of the initial sample used to seed the chain.
+In our setting, the probability distribution~\Pinf is defined by having all points in \Cinf distributed uniformly
+while 
+the probability of sampling any configuration $x \in \calX \setminus \Cinf$ is zero.
+A common practice to avoid starting biases in MCMC-type algorithm is to discard an initial set of samples (a process referred to as ``burn-in'')~\cite{ADDJ03}.
+
+However, our cost function is not necessarily continuous (see Sec.~\ref{sec:mtdi}), thus if no sample was produced on $\partial \Cinf$ after a predefined number of steps, we restart the algorithm using a different random state~$x_\text{rand}$
+(see also Sec.~\ref{subsec:mcmc}).
+
+\subsection{Generate a new sample in a Markov chain}
+\label{mcmc}
+
+Our approach is general and can be applied to any MCMC algorithm (see Sec.~\ref{sec:related_work}).
+We demonstrate how to instantiate it with two different algorithms: 
+Metropolis-Hastings and Hit-and-Run.
 
@@
 		\LOOP
-			\STATE $x_{0} \leftarrow \texttt{sample\_in\_informed\_space}( method )$
-			\WHILE {\texttt{MCMC\_continue\_chain()}}
-			\STATE $x_{i} \leftarrow \texttt{MCMC\_sample} (x_{i-1}, c_{\text{best}})$
+		%\STATE $x_{0} \leftarrow \texttt{sample\_in\_informed\_space}( method )$
+		%\WHILE {\texttt{MCMC\_continue\_chain()}}
+		\STATE $x_{i} \leftarrow \texttt{MCMC\_sample} (x_{i-1}, c_{\text{best}})$ \label{alg:mcmc_informed_sampling:start}
+		\IF{ $ x_{i} \not\in \Cinf $ }
+			\STATE $x_{0} \leftarrow \texttt{sample\_in\_informed\_space}( )$
+			\STATE \textbf{Goto} line \ref{alg:mcmc_informed_sampling:start} 
+		\ENDIF
 		\STATE \textbf{output} $x_{i}$
-			\ENDWHILE
+		%\ENDWHILE
 		\ENDLOOP 
@@
 
-\subsection{Sampling the boundary of \Cinf}
-\label{subsec:grad}
-We can use either of the following two approaches to sample points in the informed space:
-\subsubsection{Newton-Raphson Method}
-In theory, MCMC methods converge to the desired distribution regardless of the initial sample used to seed the chain.
-In our setting, the probability distribution~\Pinf is defined by having all points in \Cinf distributed uniformly
-while 
-the probability of sampling any configuration $x \in \calX \setminus \Cinf$ is zero.
-A common practice to avoid starting biases in MCMC-type algorithm is to discard an initial set of samples (a process referred to as ``burn-in'')~\cite{ADDJ03}.
+In MCMC-based Informed Sampling, as described in Algorithm~\ref{alg:mcmc_informed_sampling}, 
+a sampler firstly 
+\begin{enumerate}
+\item generate a sample follows a Markov chain 
+(\texttt{MCMC\_sample, line 2});
+and then
+\item decide if the candidate sample is in the level set, a new Markov chain will be created as a restart
+(\texttt{sample\_in\_informed\_space, line 4}).
+\end{enumerate}
 
-In our setting, we are only interested in points in~\Cinf, thus we can start the Markov Chain in~\Cinf and avoid this burn-in stage. 
-To do so we apply  Newton-Raphson's method to obtain a sample on $\partial \Cinf$. 
-However, our cost function is not necessarily continuous (see Sec.~\ref{sec:mtdi}), thus if no sample was produced on $\partial \Cinf$ after a predefined number of steps, we restart the algorithm using a different random state~$x_\text{rand}$
-(see also Sec.~\ref{subsec:mcmc}).
+\paragraph{Metropolis-Hastings sampler}
 
-\subsubsection{Previous-Trajectory Method}
+\subsubsection{Metropolis-Hasting}
 
-\subsection{Sampling the interior of \Cinf via MCMC}
-\label{subsec:mcmc}
+The Metropolis-Hastings algorithm, describe in Alg.~\ref{alg:mh_mcmc}, also uses rejection sampling around the previously generated sample to propose the next sample of the Markov Chain.
+While the general algorithm is slightly more complex, for our setting it can be described as follows:
+We generate a new sample $ x_{i}$ around the previous sample $ x_{i-1}$ using a Gaussian distribution (line~1).
+We then check if the point lies in the informed set (lines 2-5) and if it does we return it.
+If not, we return the previous sample.
+%
+For this algorithm, we continue sampling along the Markov Chain as long as new samples are produced.
 
-Our approach is general and can be applied to any MCMC algorithm (see Sec.~\ref{sec:related_work}).
-We demonstrate how to instantiate it with two different algorithms: 
-Hit and Run and Metropolis-Hastings.
-
-For each algorithm, 
-we describe how it is used to 
-(i)~sample points 
-(\texttt{MCMC\_sample, line 5})
-and 
-(ii)~decide if to continue sampling along the Markov Chain or to restart the entire process 
-(\texttt{MCMC\_continue\_chain, line 4}).
-
-\subsubsection{Hit and Run}
+\subsubsection{Hit-and-Run sampler}
 \begin{algorithm}[t]
@@
 
+\ignore{
 \begin{algorithm}[t]
@@
 \end{algorithm}
-
-\subsubsection{Metropolis-Hasting}
-
-The Metropolis-Hastings algorithm, describe in Alg.~\ref{alg:mh_mcmc}, also uses rejection sampling around the previously generated sample to propose the next sample of the Markov Chain.
-While the general algorithm is slightly more complex, for our setting it can be described as follows:
-We generate a new sample $ x_{i}$ around the previous sample $ x_{i-1}$ using a Gaussian distribution (line~1).
-We then check if the point lies in the informed set (lines 2-5) and if it does we return it.
-If not, we return the previous sample.
-%
-For this algorithm, we continue sampling along the Markov Chain as long as new samples are produced.
+}
 
@@
 	\centering
-	\begin{subfigure}[b]{0.48\linewidth}
+	\begin{subfigure}[b]{0.78\linewidth}
 		\includegraphics[width=\linewidth]{fig/sampling_efficiency/levelset}
@@
 \section{Conclusion}
-\os{Discuss param tuning, we did nothing + there is a wealth of literature}
+\label{sec:future}
 
-\os{use with BIT*, challenge - distance function is not a metric}
-
-The Met
-
-What MCMC algorithm is the best to use?
-
-Parameter tuning
-
-Application to different state spaces
-
-Parallel chains
-
-estimating volume of informed space
+In this work we demonstrated the effectiveness of using MCMC algorithms to 
+efficiently produce samples for asymptotically-optimal motion planning algorithms.
+Clearly, there are multiple other MCMC algorithms that can be used and it is interesting to see if alternative algorithms may produce better results.
+One drawback of these approaches is that they usually incur parameters that have to be tuned.
+Indeed, in this work we did not spend effort in tuning the parameters and did not change them across the range of scenarios we tested.
+There is a wealth of literature in the optimization community regarding this topic and integrating  such tools is left for future work.
+Finally, we are interested in using this framework with alternative sampling-based algorithms such as BIT*~\cite{GSB15} or LBT-RRT~\cite{SH16} and with alternative state spaces.
+%Here, a potential challenge lies with the fact the distance function we considered is not a metric, which may require changes
 

### 2017-09-14 code/motivation/plotdata.m

@@ -80,8 +80,6 @@ hold off;
 
 
 
-
-
 %{
 figure(4);
 hold on;

### 2017-09-14 code/sample efficiency/2d/plot1.m

@@ -14,11 +14,11 @@ pink = [197,27,138]/255;
 
 figure;
 hold on;
-marker_size = 20;
-scatter(log10(data(:,5)), log10(data(:,4)./data(:,6)), marker_size, 'MarkerFaceColor', blue, 'MarkerEdgeColor', blue, 'Marker', 's');
-scatter(log10(data(:,5)),log10(data(:,2)./data(:,6)), marker_size, 'MarkerFaceColor', red, 'MarkerEdgeColor', red, 'Marker', 'd');
-scatter(log10(data(:,5)),log10(data(:,1)./data(:,6)), marker_size, 'MarkerFaceColor', green, 'MarkerEdgeColor', green, 'Marker', 'h');
-scatter(log10(data(:,5)),log10(data(:,3)./data(:,6)), marker_size, 'MarkerFaceColor', purple, 'MarkerEdgeColor', purple, 'Marker', 'o');
+marker_size = 4;
+loglog(data(:,5), log10(data(:,4)./data(:,6)), 'MarkerSize', marker_size, 'MarkerFaceColor', blue, 'MarkerEdgeColor', blue, 'Marker', 's');
+loglog(data(:,5),log10(data(:,2)./data(:,6)), 'MarkerSize', marker_size, 'MarkerFaceColor', red, 'MarkerEdgeColor', red, 'Marker', 'd');
+loglog(data(:,5),log10(data(:,1)./data(:,6)), 'MarkerSize', marker_size, 'MarkerFaceColor', green, 'MarkerEdgeColor', green, 'Marker', 'h');
+loglog(data(:,5),log10(data(:,3)./data(:,6)), 'MarkerSize', marker_size, 'MarkerFaceColor', purple, 'MarkerEdgeColor', purple, 'Marker', 'o');
 
 xlabel('informed set volume ratio - log_1_0');
 ylabel('time per sample - log_1_0(ms)');

### 2017-09-14 code/sample efficiency/volumeRatio/plot1.m

@@ -1,0 +1,30 @@
+%data = sortrows(dim3, 5);
+
+%data(:,1) = log(data(:,1));
+%data(:,2) = log(data(:,2));
+%data(:,3) = log(data(:,3));
+%data(:,4) = log(data(:,4));
+
+green = [49,163,84]/255;
+red = [222 45 38]/255;
+blue = [49,130,189]/255;
+orange = [230,85,13]/255;
+purple = [117,107,177]/255;
+pink = [197,27,138]/255;
+
+figure;
+hold on;
+marker_size = 20;
+plot(dim2(:,12), dim2(:,13), 'color', blue, 'linewidth', 4);
+plot(dim6(:,12), dim6(:,13), 'color', red, 'linewidth', 4);
+%scatter(log10(data(:,5)),log10(data(:,1)./data(:,6)), marker_size, 'MarkerFaceColor', green, 'MarkerEdgeColor', green, 'Marker', 'h');
+%scatter(log10(data(:,5)),log10(data(:,3)./data(:,6)), marker_size, 'MarkerFaceColor', purple, 'MarkerEdgeColor', purple, 'Marker', 'o');
+
+xlim([1, 1.41]);
+xlabel('informed set volume ratio');
+ylabel('level set ratio');
+%legend('Rejection', 'HRS', 'MCMC', 'Hit&Run');
+legend('4 dimension', '12 dimension');
+hold off;
+
+set(gca,'FontSize',20)

### 2017-09-14 paper.tex
new

@@
 \begin{prop}
+	\label{prop:asym_opt}
 	\dy{claim that once informed sampler provides uniform samplings in any given level set in a non-euclidean state space, the corresponding informed RRT* could asymptotically find an optimal solution.}
@@
 \os{refer to Fig.~2 or the updated one.}
+Geometric planning provides motion from a start state to a goal state.
+It is not expressive enough for a wider range of actions, because many kiondynamic features are not considered in the planning process.
+Figure \ref{fig:motivation} gives an example using HERB, which is about a swing action that a robotic arm ends with a relative high velocity towards a direction.
+Geometric planning does not consider velocities in planning, so it can be viewed as considering only zero goal velocity.
+Kinodyanic planning shall capture the velocity requirments, and generate a motion like in Figure\ref{fig:motivation:fast}.
+The difference of two are shown in a phase plot, as in Figure \ref{fig:motivation:phase_plot}.
 
@@
 
-\paragraph{Metropolis-Hastings sampler}
+\subsubsection{Metropolis-Hastings sampler}
 
-\subsubsection{Metropolis-Hasting}
-
-The Metropolis-Hastings algorithm, describe in Alg.~\ref{alg:mh_mcmc}, also uses rejection sampling around the previously generated sample to propose the next sample of the Markov Chain.
+The Metropolis-Hastings algorithm is one of the most popular MCMC samplers~\cite{CG95}, because it provides a simple and parameter-free framework that guarantees the convergence of Markov chains to a target distribution.
+Our work adopts the general Metropolis-Hasting algorithm, as described in Alg.~\ref{alg:mh_mcmc}, 
 While the general algorithm is slightly more complex, for our setting it can be described as follows:
@@
 
+\begin{algorithm}[t]
+	\begin{algorithmic}[1]
+		\STATE $ x'_{i} \leftarrow \texttt{sample\_normal}( q ( x \mid x_{i-1},\Sigma) ) $ 
+		\label{start}
+		\STATE $ \alpha \leftarrow \frac{ q ( x_{i-1} \mid x'_{i},\Sigma) \pi( x'_{i} ) }{ q ( x'_{i} \mid x_{i-1},\Sigma) \pi( x_{i-1} ) } $
+		\IF{ \texttt{sample\_random}$ (0.0 , 1.0) > \min (1, \alpha) $  }
+            \RETURN $ x'_{i} $
+		\ENDIF
+		\RETURN $ x_{i} $
+	\end{algorithmic}
+	\caption{Metropolis-Hastings MCMC $(x_{i-1}, c_{\text{best}})$}
+	\label{alg:mh_mcmc}	
+\end{algorithm}
+
+We use canonical distribution to approximate the target distribution $ \pi $, which is a uniform distribution subject to a level set.
+It means that energy function is defined from cost function that bridges cost and probability.
+The energy function's definition provides the flexibility to specify desired or more probable states (by presenting lower energies) without the need to use a formal and restrictive model.
+
+Our energy for any given cost $c$, 
+denoted by~$E\left(c,\Cbest \right)$, 
+is a function of $c$ and the current best cost~$\Cbest$.
+To consider only points in the informed set, all with equal energy, one may consider taking 
+\begin{equation}
+E_{\text{informed}}\left(c,\Cbest \right) = 
+\begin{cases}
+0,	& \text{if } c \leq \Cbest\\        
+\infty,  	& \text{otherwise}.
+\end{cases}
+\end{equation}
+To approximate that function, we propose a formula as below:
+\begin{equation}
+\hat{E}_{\text{informed}} \left( c,\Cbest \right) 
+= \beta \cdot \text{sigm}\left(\Cbest - c\right)
+\end{equation}
+penalizes states outside the informed set~$\Cinf$ using a tight sigmoid function~$\text{sigm}$ scaled by some (large\footnote{The constant~$\beta$ gives points out of~\Cinf a large energy value which in turn implies a low probability of being sampled.
+In theory, we would like to have~$\beta \approx \infty$. 
+However, choosing~$\beta$ to be too large may cause numerical instabilities.}) constant~$\beta$.
+The sigmoid can be seen as a differentiable function smoothing the boundary of~$\Cinf$.
+
 \subsubsection{Hit-and-Run sampler}
+
+\dy{Rohan, please finish this part}
+
+Also we can take other approaches that generate samples from a Markov chain without requiring an approximation of a target distribution $ \pi $.
+Hit-and-Run \cite{KSZ11} is one of them that efficiently generates uniform samples in convex regions.
+In order to generalize our sampler to a wider range of problems~\cite{KSZ11} and better efficiency
+We use the Accelerated Hit-and-Run algorithm~\cite{KSZ11}, described in Alg.~\ref{alg:hit_and_run_mcmc} that produces a series of samples $x_0, \ldots$.
+Given the previous sample~$x_{i-1}$ it first  samples a random direction on the unit sphere (line 1).
+This induces a line~$L(\lambda)$ passing through~$x_{i-1}$  in the direction sampled (line 2) parametrized by a scalar~$\lambda$.
+We obtain upper and lower bounds on $\lambda$ (line 3) that are problem dependant. 
+For example, if we have box constraints on joint limits of the robot and on maximum velocity, then bounds are given by $\lambda^{+} = -\lambda^{-} = l_{diag}$; where $l_{diag}$ is the length of the longest diagonal of the box.
+We then sample a point along~$L(\lambda)$ by sampling a scalar~$\lambda'$ within our bounds (line 5).
+This defines a point~$x_{i}$ which is a candidate for the next sample along the Markov Chain (line 6).
+We then check if the point lies in the informed set (line 7) and if it does we return it.
+If not, we update our bounds (lines~9-12) and repeat the process.
+The algorithm can be viewed as an efficient method that performs rejection sampling along a one-dimensional line passing through the previous sample parametrized by $\lambda$.
+
 \begin{algorithm}[t]
@@
 
-We use the Accelerated Hit and Run algorithm \cite{KSZ11}, described in Alg.~\ref{alg:hit_and_run_mcmc} that produces a series of samples $x_0, \ldots$.
-Given the previous sample~$x_{i-1}$ it first  samples a random direction on the unit sphere (line 1).
-This induces a line~$L(\lambda)$ passing through~$x_{i-1}$  in the direction sampled (line 2) parametrized by a scalar~$\lambda$.
-We obtain upper and lower bounds on $\lambda$ (line 3) that are problem dependant.
-For example, if we have box constraints on joint limits of the robot and on maximum velocity, then bounds are given by $\lambda^{+} = -\lambda^{-} = l_{diag}$; where $l_{diag}$ is the length of the longest diagonal of the box.
-We then sample a point along~$L(\lambda)$ by sampling a scalar~$\lambda'$ within our bounds (line 5).
-This defines a point~$x_{i}$ which is a candidate for the next sample along the Markov Chain (line 6).
-We then check if the point lies in the informed set (line 7) and if it does we return it.
-If not, we update our bounds (lines~9-12) and repeat the process.
-The algorithm can be viewed as an efficient method that performs rejection sampling along a one-dimensional line passing through the previous sample parametrized by $\lambda$.
-
 For this algorithm, we continue sampling along the Markov Chain until either 
@@
 
-\begin{algorithm}[t]
-	\begin{algorithmic}[1]
-	    \LOOP
-		\STATE $ x'_{i} \leftarrow \texttt{sample\_normal}(x_{i-1},\Sigma) $ 
-		\label{start}
-		\IF{ $ x'_{i} \leftarrow$ \texttt{sample\_random}$ (0.0 , 1.0) >  \pi( x'_{i} ) / \pi( x_{i} ) $  }
-		\STATE x
- 		\ENDIF
-		\IF{ \textsc{Cost}($ x_{i} $) $ < c_{\text{best}} $  }
-		  \RETURN $x_{i}$
-		\ENDIF 
-		\ENDLOOP
-	\end{algorithmic}
-	\caption{Metropolis-Hastings MCMC $(x_{i-1}, c_{\text{best}})$}
-	\label{alg:mh_mcmc}	
-\end{algorithm}
-
-\ignore{
-\begin{algorithm}[t]
-	\begin{algorithmic}[1]
-	\IF{ $method = \texttt{Newton-Rapson}$  }
-		\STATE $x_{\text{rand}} \leftarrow \texttt{sample\_uniform(\calX)}$
-		\STATE $x_{0} \leftarrow \texttt{newton\_raphson}(x_{\text{rand}}, c_{\text{best}})$ ; \hspace{3mm} $i\leftarrow 0$
-	\ELSIF{ $method = \texttt{Previous-Trajectory}$ }
-	    \STATE $t_{rand} \leftarrow \texttt{sample\_random\_time()}$
-	    \STATE $x_{0} \leftarrow x_{best}(t_{rand})$
-	\ENDIF
-	\RETURN $x_0$
-	\end{algorithmic}
-	\caption{sample\_in\_informed\_space$(method, c_{best})$}
-	\label{alg:sample_inf}	
-\end{algorithm}
-}
+\dy{say some Hit-and-Run's advantages over Metropolis-Hastings}
 
@@
 \subsection{Sampling Efficiency}
+
+\dy{TODO: change MCMC to MH (Metropolis Hasting) in the plots}
 
@@
 \end{figure}
-vantage of sampling a near state.
-Both the per-sampling time of HRS 
+
+\dy{shall we use informed set or level set?}
+
+\dy{going to change the tick labels so this below sentence will be replaced}
 It is noticeable that both x axis and y axis are converted by $ \log_{10} () $ in Figure~\ref{fig:sampling_efficiency:2d} and Figure~\ref{fig:sampling_efficiency:6d}.
@@
 Keep in mind that the differences in unit (ms) are much bigger.
-\dy{TODO: change MCMC to MH (Metropolis Hasting) in the plots}
-Metropolis-Hasting shows consistent performance when the informed set volume ratio is decreased, because it takes the adand HNR increases with the decrease of the informed set volume ratio. 
+
+Metropolis-Hastings shows consistent sampling time when problems get harder. 
+It takes the advantage of sampling a near state that generate samples in a level set.
+However this does not reflect the quality of the samples, though all the samples are in the level set.
+Recall in Algorithm~\ref{alg:mh_mcmc}, a new sample candidate is obtained from a Gaussian distribution $ q( x \mid x_{i-1}, \Sigma ) $.
+The best covariance $ \Sigma $ that generates faster convergence differs with problem setting.
+A small covariance tends to generate more samples near around previous samples, which a large covariance is more likely to drive a Markov chain outside of an informed set.
+In our next planning experiment setting, we use the same covariance for different problems.
+
 When informed set volume ratio is relatively high, it is easy to generate qualified samples.
 All the samplers have close performances.
-RS and HRS can be the most efficient because of its simple design.
-But when problems get harder, HNR outperforms HRS significantly.
+It actually implies rejection sampler is the best because of its simplicity in implementation.
+The sampling time of other three samplers all increase as problems get harder.
+But we can see the trend that HRS's advantage over RS is more significant , also the same for HNR's advantage over HRS.
+Moving from a 4 dimension problem in Figure \ref{fig:sampling_efficiency:2d} to a 12 dimension problem in Figure \ref{fig:sampling_efficiency:6d}, sampling in an informed set becomes even harder,
+because the informed set volume ratio becomes smaller.
+HNR and MH samplers show much better efficiency over the others.
+
+We want to point out that efficiently sampling in an informed set is not sufficient for determining the quality of a sampler.
+For example, a sampler that constantly only return the same sample in a level set might show the best sampling efficiency can be the worst sampler in a path planning problem.
+\dy{is the property that any state in a set has a chance to be sampled?}
+We hope sampler (satisfies some properties ?) that a resulting planner is asymptotically optimal.
 
 \os{Explain why MCMC is flat, mention strawman approach}
+
+\dy{do we want to say that it is hard to compare the uniformity in high dimension space}
 
@@
 The quality of samples determines the efficiency of resulting planning algorithms.
+If a sampler could provide samples with same quality as others but generate samples in a much efficiency way, we would expect that an informed RRT* with this sampler would show two properties.
+\begin{itemize}
+	\item It shall converge faster in finding the optimal solution.
+	Because sampling in an informed set is gradually becoming as new better solution reduces $ c_{best} $ which reduces the informed set volume ratio significantly.
+	\item It shall adapt better in problems defined in high dimension state space.
+	As shown in Figure \ref{fig:sampling_efficiency:levelset}, the informed set volume ratio decrease more significantly in a high-dimension state space.
+	The advantage of an informed sampler becomes more important.
+\end{itemize}
+
 To evaluate how the samplers impact the planning efficiency, we run the samplers with the informed RRT* planner~\cite{GSB14} on three different problems described below and shown in Fig.
@@
 
-\dy{TODO: add a plot that shows the increases of samples}
+\dy{TODO: add a plot that shows the increases of samples?}
 
-MHS shows the worst performance in Figure~\ref{fig:planning_efficiency:3dof:general}, \ref{fig:planning_efficiency:6dof:hammering} and \ref{fig:planning_efficiency:herb:batting}.
+MH shows the worst performance in Figure~\ref{fig:planning_efficiency:3dof:general}, \ref{fig:planning_efficiency:6dof:hammering} and \ref{fig:planning_efficiency:herb:batting}.
 Though theoretically samples converge to a target distribution, the samples could be either too correlated for exploration purpose in planning.
@@
 In Figure~\ref{fig:planning_efficiency:6dof:hammering} and \ref{fig:planning_efficiency:herb:batting}, the cost of current best solution by planners with HNR sampler converge significantly faster.
+It shows that HNR will have close performance with RS and HRS in simple problem, as in Figure \ref{fig:planning_efficiency:3dof:general}.
+But when the dimensions of problems increase, HNR shows better and steady performance.
+Also, HNR also show fast convergence to the optimal, because it is better at adapting the informed set update in planning process.
 

### 2017-09-14 code/sample efficiency/2d/plot1.m

@@ -14,14 +14,22 @@ pink = [197,27,138]/255;
 
 figure;
 hold on;
-marker_size = 4;
-loglog(data(:,5), log10(data(:,4)./data(:,6)), 'MarkerSize', marker_size, 'MarkerFaceColor', blue, 'MarkerEdgeColor', blue, 'Marker', 's');
-loglog(data(:,5),log10(data(:,2)./data(:,6)), 'MarkerSize', marker_size, 'MarkerFaceColor', red, 'MarkerEdgeColor', red, 'Marker', 'd');
-loglog(data(:,5),log10(data(:,1)./data(:,6)), 'MarkerSize', marker_size, 'MarkerFaceColor', green, 'MarkerEdgeColor', green, 'Marker', 'h');
-loglog(data(:,5),log10(data(:,3)./data(:,6)), 'MarkerSize', marker_size, 'MarkerFaceColor', purple, 'MarkerEdgeColor', purple, 'Marker', 'o');
-
-xlabel('informed set volume ratio - log_1_0');
-ylabel('time per sample - log_1_0(ms)');
-legend('Rejection', 'HRS', 'MCMC', 'Hit&Run');
+marker_size = 20;
+h1 = scatter(log10(data(:,5)),log10(data(:,4)./data(:,6)), marker_size, 'MarkerFaceColor', blue, 'MarkerEdgeColor', blue, 'Marker', 's');
+h2 = scatter(log10(data(:,5)),log10(data(:,2)./data(:,6)), marker_size, 'MarkerFaceColor', red, 'MarkerEdgeColor', red, 'Marker', 'd');
+h3 = scatter(log10(data(:,5)),log10(data(:,1)./data(:,6)), marker_size, 'MarkerFaceColor', green, 'MarkerEdgeColor', green, 'Marker', 'h');
+h4 = scatter(log10(data(:,5)),log10(data(:,3)./data(:,6)), marker_size, 'MarkerFaceColor', purple, 'MarkerEdgeColor', purple, 'Marker', 'o');
+%plot(log10(data(:,5)),log10(data(:,4)./data(:,6)), 'color', blue, 'linewidth', 1);
+%plot(log10(data(:,5)),log10(data(:,2)./data(:,6)), 'color', red, 'linewidth', 1);
+%plot(log10(data(:,5)),log10(data(:,1)./data(:,6)), 'color', green, 'linewidth', 1);
[…]

### 2017-09-14 paper.tex
sync from sharelatex

@@
 
-\dy{Rohan, please finish this part}
-
-Also we can take other approaches that generate samples from a Markov chain without requiring an approximation of a target distribution $ \pi $.
-Hit-and-Run \cite{KSZ11} is one of them that efficiently generates uniform samples in convex regions.
-In order to generalize our sampler to a wider range of problems~\cite{KSZ11} and better efficiency
-We use the Accelerated Hit-and-Run algorithm~\cite{KSZ11}, described in Alg.~\ref{alg:hit_and_run_mcmc} that produces a series of samples $x_0, \ldots$.
+Hit-and-Run~\cite{S84} MCMC sampler is known to efficiently generate uniform samples.
+Specifically, we use the Accelerated Hit-and-Run variant~\cite{KSZ11} of the algorithm i.e.
+described in Alg.~\ref{alg:hit_and_run_mcmc}.
 Given the previous sample~$x_{i-1}$ it first  samples a random direction on the unit sphere (line 1).
-This induces a line~$L(\lambda)$ passing through~$x_{i-1}$  in the direction sampled (line 2) parametrized by a scalar~$\lambda$.
+This induces a line~$L(\lambda)$ passing through~$x_{i-1}$ in the direction sampled (line 2), parametrized by a scalar~$\lambda$.
 We obtain upper and lower bounds on $\lambda$ (line 3) that are problem dependant. 
@@
 This defines a point~$x_{i}$ which is a candidate for the next sample along the Markov Chain (line 6).
-We then check if the point lies in the informed set (line 7) and if it does we return it.
+We then check if the point lies in the informed set (line 7) and if it does, we return it.
 If not, we update our bounds (lines~9-12) and repeat the process.
@@
 
-\os{Mention that we do not need convexity}
-
-\dy{say some Hit-and-Run's advantages over Metropolis-Hastings}
+The Hit-and-Run algorithm is designed specifically for uniform distributions. 
+Hence, it doesn't require an approximation of a target distribution $ \pi $ that was generated with the energy function for Metropolis-Hastings algorithm.
 
@@
 
-We evaluate the performance of proposed MCMC methods by comparing four types of samplers, which are rejection sampler (RS), hierarchical rejection sampler (HRS), Metropolis-Hastings sampler (MHS), and Hit-and-run sampler (HNR).
-We use different samplers to generate a fixed number of samples in different informed sets to check the sampling efficiency, especially when the sampling is harder (in a small informed set).
-We then evaluate how the samplers works with informed RRT*~\cite{GSB14}, which reflect the quality of samples in an informed set.
+We evaluate the performance of proposed MCMC methods by comparing four types of samplers, which are Rejection Sampler (RS), Hierarchical Rejection Sampler (HRS), Metropolis-Hastings Sampler (MHS), and Hit-and-Run Sampler (HNR).
+We use different samplers to generate a fixed number of samples in different informed sets to check the sampling efficiency. %, especially when the sampling is harder (in a small informed set).
+We then compare the quality of the samplers by evaluating how the samplers work with informed RRT*~\cite{GSB14}.
 
@@
 
-\dy{TODO: change MCMC to MH (Metropolis Hasting) in the plots}
+\dy{TODO: change MCMC to MHS (Metropolis Hasting Sampler) in the plots}
 
@@
 informed set volume ratio, i.e.
-the ratio of the volume of informed space to the volume of entire state space for 5000 samples.
-The informed set volume ratio is approximated by the ratio of the number of accepted to the total number samples obtained while running rejection sampling.
-Efficiency of rejection sampling based methods is very low for high dimesions because this ratio decreases exponentially w.r.t the dimension of the space due to the curse of dimensionality.
-The Fig. \ref{fig:sampling_efficiency} shows that MCMC and Hit\&Run have a better sampling efficiency compared to HRS and RS with decrease in informed set ratio or increase in dimensions. 
+the ratio of the volume of informed space to the volume of entire state space, for 5000 samples.
+The informed set volume ratio is approximated by the ratio of the number of accepted to the total number of samples obtained while running rejection sampling. 
+%Efficiency of rejection sampling based methods is very low for high dimensions because this ratio decreases exponentially w.r.t the dimension of the space, for a given sub-level-set of the cost function.
+Fig. \ref{fig:sampling_efficiency} shows that MHS and HNR have a better sampling efficiency compared to HRS and RS with decrease in informed set volume ratio or increase in dimensions. 
 Figure \ref{fig:sampling_efficiency:levelset} shows how the informed set volume ratio decreases as the level set cost $ c_{best} $ becomes smaller in problems of different dimensions.
@@
 The best covariance $ \Sigma $ that generates faster convergence differs with problem setting.
-A small covariance tends to generate more samples near around previous samples, which a large covariance is more likely to drive a Markov chain outside of an informed set.
+A small covariance tends to generate more samples near around previous samples, which a large covariance has better exploration but is more likely to drive a Markov chain outside of an informed set.
 In our next planning experiment setting, we use the same covariance for different problems.
@@
 We want to point out that efficiently sampling in an informed set is not sufficient for determining the quality of a sampler.
-For example, a sampler that constantly only return the same sample in a level set might show the best sampling efficiency can be the worst sampler in a path planning problem.
+For example, a sampler that constantly returns the same sample in a informed set might show the best sampling efficiency, however it is the worst sampler in a path planning problem.
 \dy{is the property that any state in a set has a chance to be sampled?}
@@
 For each problem the start and goal states (positions and velocities) are known in the joint space.
-
+\dy{TODO: Make table for limits and add units}
 \subsubsection{Problem 1: 3 DoF Planar Manipulator}
@@
 Problem 1 is a 3 DoF manipulator that moves on a plane, which results in a 6 dimension space.
-The position boundary of each join is $ [ - \pi , \pi ] $, the velocity boundary is $ [-10, 10] $, and the acceleration is $ 1 $.
+The position boundary of each join is $ [ - \pi , \pi ] $, the velocity boundary is $ [-10, 10] $, and the acceleration is $ [-1,1] $.
 Figure~\ref{fig:planning_efficiency:3dof:example} shows a few steps of a planned path.
@@
 Problem 2 is a 6 DoF snake arm that moves in a 3D workspace, which results in a 12 dimension space.
-The position boundary of each join is $ [ - \pi , \pi ] $, the velocity boundary is $ [-10, 10] $, and the acceleration is $ 1 $.
+The position boundary of each join is $ [ - \pi , \pi ] $, the velocity boundary is $ [-10, 10] $, and the acceleration is $ [-1,1] $.
 Figure~\ref{fig:planning_efficiency:6dof:example} shows a few steps of a planned path.
@@
 The velocity boundary of 7 joints of the arm are $ [-0.75 , 0.75] $, $ [-0.75 , 0.75] $, $ [-2 , 2] $, $ [-2 , 2] $, $ [-2.5 , 2.5] $, $ [-2.5 , 2.5] $ and $ [-2.5 , 2.5] $.
-The accelerations of all the joints are set to $ 1 $.
+The accelerations of all the joints are set to $ [-1,1] $.
 Figure~\ref{fig:planning_efficiency:herb:example} shows a few steps of a planned path.
@@
 HNR shows close performance with RS and HRS in a 6-dimension space, as in Figure~\ref{fig:planning_efficiency:3dof:general}.
-But in higher dimension performance, the advantage of HNR in sampling efficiency is shown.
+But in higher dimension performance, the advantage of HNR in planning efficiency is shown.
 In Figure~\ref{fig:planning_efficiency:6dof:hammering} and \ref{fig:planning_efficiency:herb:batting}, the cost of current best solution by planners with HNR sampler converge significantly faster.
@@
 But when the dimensions of problems increase, HNR shows better and steady performance.
-Also, HNR also show fast convergence to the optimal, because it is better at adapting the informed set update in planning process.
+HNR also shows faster convergence to the optimal trajectory, because it is better at adapting the informed set update in planning process.
 

### 2017-09-14 paper.tex
modify

@@
 In this paper, we suggest an alternative approach to produce samples in the informed set~\Cinf for a wide range of settings.
-Our main insight is to recast this problem as one of sampling uniformly within a level set of an implicit function.
+Our main insight is to recast this problem as one of sampling uniformly within an informed set of an implicit function.
 This recasting enables us to apply Monte Carlo sampling methods, used very effectively in the Machine Learning and Optimization communities, to solve our problem.
@@
   	Cost function is depicted using isocontours (darker shades reflect lower cost) while the boundary of the informed set is depicted in purple. 
-  	The root-finding and MCMC algorithms are depicted in blue and green, respectively.
+  	The root-finding and MCMC algorithms are depicted in red and turquoise, respectively.
   	}
@@
 \textbf{
-Our main insight is to recast this problem as one of sampling uniformly within a level set of an implicit function.
+Our main insight is to recast this problem as one of sampling uniformly within an informed set of an implicit function.
 This recasting enables us to apply Monte Carlo sampling methods, used very effectively in the Machine Learning and Optimization communities, to solve our problem.
@@
 The rest of the paper is structured as follows: after describing related work in Sec.~\ref{sec:related_work}, we formally define our problem in Sec.~\ref{sec:pdef}.
-We then provide in Sec.~\ref{sec:motivation} an intuitive description of the challenges faced in sampling within the informed set for our planning domains.
+We then provide in Sec.~\ref{sec:mtdi} an intuitive description of the challenges faced in sampling within the informed set for our planning domains.
 We continue in Sec.~\ref{sec:algorithm} with a description of our algorithm and present experimental evaluations in Sec.~\ref{sec:eval}.
@@
 These samples will be used within the informed RRT* framework to efficiently and incrementally compute trajectories of decreasing cost, converging to the optimal trajectory.
-\os{mention that it is AO}
-\begin{prop}
-	\label{prop:asym_opt}
-	\dy{claim that once informed sampler provides uniform samplings in any given level set in a non-euclidean state space, the corresponding informed RRT* could asymptotically find an optimal solution.}
-\end{prop}
 
@@
 \subsection{Geometric vs. Kinodynamic planning}
+Consider the problem depicted in Fig.~\ref{fig:motivation} where HERB is required about a swing action that a robotic arm ends with a relative high velocity towards a direction.
+One approach to address this problem is to first plan in the geometric configuration space and the re-time the algorithm.
+When the start and goal are in close proximity, a geometric planner will simply connect the two states (Fig.~\ref{fig:motivation:fast}).
+However, to adhere to the velocity constraints at the goal, the actual motion that is required is to move back the arm in order to gain speed and then reach the goal (Fig.~\ref{fig:motivation:fast}).
+In such settings, re-timing the path will not produce feasible results.
+The difference between the two motions are shown in a phase plot in Fig.~\ref{fig:motivation:phase_plot}.
 
-\os{refer to Fig.~2 or the updated one.}
-Geometric planning provides motion from a start state to a goal state.
-It is not expressive enough for a wider range of actions, because many kiondynamic features are not considered in the planning process.
-Figure \ref{fig:motivation} gives an example using HERB, which is about a swing action that a robotic arm ends with a relative high velocity towards a direction.
-Geometric planning does not consider velocities in planning, so it can be viewed as considering only zero goal velocity.
-Kinodyanic planning shall capture the velocity requirments, and generate a motion like in Figure\ref{fig:motivation:fast}.
-The difference of two are shown in a phase plot, as in Figure \ref{fig:motivation:phase_plot}.
+%Geometric planning provides motion from a start state to a goal state.
+%It is not expressive enough for a wider range of actions, because many kiondynamic features are not considered in the planning process.
+%Figure \ref{fig:motivation} gives an example using HERB, which is about a swing action that a robotic arm ends with a relative high velocity towards a direction.
+%Geometric planning does not consider velocities in planning, so it can be viewed as considering only zero goal velocity.
+%Kinodyanic planning shall capture the velocity requirments, and generate a motion like in Figure\ref{fig:motivation:fast}.
+%The difference of two are shown in a phase plot, as in Figure \ref{fig:motivation:phase_plot}.
 
@@
 
-In this section we describe our approach to efficiently produce new samples in an informed set ~\Cinf given a specific cost~$c_{\text{best}}$ of trajectory $x_{best}(t)$.
+In this section we describe our approach to efficiently produce new samples in an informed set~\Cinf given a specific cost~$c_{\text{best}}$ of trajectory $\gamma_{best}(t)$.
 The samples follow a Monte Carlo Markov Chain, in which a new sample candiate is produceded from a previous sample that also lies in the same informed set.
@@
 
-The idea behind introducing MCMC to informed sampling is to defining a target distribution $ \pi $ as a uniform distribution in a level set $ \Cinf $.
-The sampling process consists of two stages,
+The idea behind applying MCMC for informed sampling is to define a target distribution~$ \pi $ as a uniform distribution over all points in~$ \Cinf $.
+Our approach consists of two stages,
 \begin{enumerate}
-	\item finding a sample in the informed same $ x_0 \in \Cinf $ as the start of a Markov chain, which is written as 
-	$ x_{0} \leftarrow \texttt{sample\_in\_informed\_space}( )$; and
-	\item sampling a new sample $ x_i $ from a previous sample $ x_{i-1} $ in the same informed set, which is written as  $x_{i} \leftarrow \texttt{MCMC\_sample} (x_{i-1}, c_{\text{best}})$.
+	\item finding an initial sample $ x_0 \in \Cinf $ which will serve as the start of a Markov chain. This is implemented using the function 
+	$ \texttt{sample\_in\_informed\_space}( )$, and
+	\item sampling a new sample $ x_i \in \Cinf $ given a previous sample $ x_{i-1} $. This is implemented using the function $\texttt{MCMC\_sample} (x_{i-1}, c_{\text{best}})$.
 \end{enumerate}
-Compared with rejection samplers, a MCMC-based informed sampler takes the advantage of a previous sample in the level set $ \Cinf $ in finding a new sample, while reserves the randomness in problem space search, which builds an ``exploitation and exploration" patter in informed sampling.
 
-to initialize an MCMC algorithm which outputs a series of samples within \Cinf by constructing a Markov Chain.
-This is done until some termination criterion is met and the entire process is repeated (Sec.~\ref{subsec:mcmc}). 
+%Compared with rejection samplers, a MCMC-based informed sampler takes the advantage of a previous sample in the informed set $ \Cinf $ in finding a new sample, while reserves the randomness in problem space search, which builds an ``exploitation and exploration" patter in informed sampling.
+%
+%to initialize an MCMC algorithm which outputs a series of samples within \Cinf by constructing a Markov Chain.
+%This is done until some termination criterion is met and the entire process is repeated (Sec.~\ref{subsec:mcmc}). 
 %Specifically, we chose to use HMC due to its favourable properties (see Sec.~\ref{sec:intro}). 
-For a visualization of the approach, see Fig.~\ref{fig:alg}.
+Our algorithm is described in Alg.~\ref{alg:mcmc_informed_sampling} and visualized in Fig.~\ref{fig:alg}.
+We now continue to detail each of the algorithm's stages.
+%\os{Fix Alg 1 }
 
-\subsection{Find a sample in a level set}
-
-In our setting, we are only interested in points in~\Cinf, thus we can start the Markov Chain in~\Cinf and avoid this burn-in stage. 
-A new Markov chain is initialized when 
-\begin{itemize}
-	\item a new informed set is provided (e.g. a new current-best is found by the planner); or
-	\item a new sample of an existing Markov chain is outside the level set.
-\end{itemize}
-There are a few methods that provides a sample in a given level set $ \Cinf $ in a planning problem, for example
-\begin{itemize}
-	\item sampling from the start state and the goal state
-	\footnote{The start state and the goal state are guaranteed to be in any level set $ \Cinf $ because of the definition of a level set};
-	\item using a gradient descent algorithm (e.g. Newton-Raphson Method~\cite{RT06}) to find a sample in the level set $ \Cinf $; 
-	\footnote{ $ \forall x_i \in \Cinf \land x_j \not\in \Cinf, c( x_i ) > c ( x_j ) $. }
-	\item sampling from a pool of previous samples that are in the level set $ \Cinf $; and
-	\item calling a rejection sampling till one is in the level set is found.
-\end{itemize}
-
-Different methods have their pros and cons.
-For example, a gradient descent algorithm is usually efficient in finding a solution, but subject to only convex problems.
-Sampling from a pool of samples is algorithmic-free but might attract new samples near around previous samples.
-
+\subsection{Finding an initial sample in $\Cinf$}
 In theory, MCMC methods converge to the desired distribution regardless of the initial sample used to seed the chain.
@@
 
-However, our cost function is not necessarily continuous (see Sec.~\ref{sec:mtdi}), thus if no sample was produced on $\partial \Cinf$ after a predefined number of steps, we restart the algorithm using a different random state~$x_\text{rand}$
-(see also Sec.~\ref{subsec:mcmc}).
+In our setting, we are only interested in points in~\Cinf, thus we suggest to start the Markov Chain in~\Cinf and avoid this burn-in stage. 
+We restart our process and generate a new Markov chain  when 
+(i)~the cost of $\cbest$ is updated (i.e. a new solution is found by the planner) or
+(ii)~the new sample on the existing Markov chain is outside~\Cinf.
 
-\subsection{Generate a new sample in a Markov chain}
+We suggest several methods to produce an initial sample~$x_0 \in \Cinf $ 
+\begin{itemize}
+	\item randomly returning either the start state or the goal state,
+	\item randomly sampling a state $x_{\text rand} \in \Cinf$ and using a gradient descent algorithm (e.g. Newton-Raphson Method~\cite{RT06}) to find a sample in~$ \Cinf $
+%	\footnote{ $ \forall x_i \in \Cinf \land x_j \not\in \Cinf, c( x_i ) > c ( x_j ) $. }
+	\item sampling from a pool of previous samples that are in the informed set $ \Cinf $ and
+	\item applying rejection sampling until a sample in the informed set is found.
+\end{itemize}
+
+Each of the methods proposed has its own pros and cons.
+For example, a gradient-descent algorithm is usually efficient in finding a solution, but subject to only convex problems.
+Sampling from a pool of samples is algorithmic-free but biases new samples to be near previous samples.
+
+%However, our cost function is not necessarily continuous (see Sec.~\ref{sec:mtdi}), thus if no sample was produced on $\partial \Cinf$ after a predefined number of steps, we restart the algorithm using a different random state~$x_\text{rand}$
+%(see also Sec.~\ref{subsec:mcmc}).
+
+\subsection{Generating a new sample in a Markov chain}
 \label{mcmc}
@@
 Our approach is general and can be applied to any MCMC algorithm (see Sec.~\ref{sec:related_work}).
-We demonstrate how to instantiate it with two different algorithms: 
-Metropolis-Hastings and Hit-and-Run.
+The process is demonstrated in Algorithm~\ref{alg:mcmc_informed_sampling}.
+At the beginning of a Markov chain, \texttt{sample\_in\_informed\_space}() is called to generate the first sample in an informed set.
+\texttt{MCMC\_sample}() is called to generate a new sample based on a previous sample $ x_{i-1} $ and a cost $ c_{best} $ that defines an informed set.
+We demonstrate how to instantiate it with two different algorithms \emph{Metropolis-Hastings} and \emph{Hit-and-Run}, which will be described in later subsections.
+If a generated new sample candidate is in the informed set, this candidate will be returned as a new sample.
+But if a generated new sample candidate is not in the informed set, it will go back to line 2.
+A new Markov chain will be initiated by calling \texttt{sample\_in\_informed\_space}() to generate a new sample $ x_0 $.
 
@@
 		\LOOP 
-		%\STATE $x_{0} \leftarrow \texttt{sample\_in\_informed\_space}( method )$
-		%\WHILE {\texttt{MCMC\_continue\_chain()}}
-		\STATE $x_{i} \leftarrow \texttt{MCMC\_sample} (x_{i-1}, c_{\text{best}})$ \label{alg:mcmc_informed_sampling:start}
+		\IF{ $ x_{i-1} == \varnothing $ }  
+		\label{alg:mcmc_informed_sampling:start}
+			\STATE $x_{0} \leftarrow \texttt{sample\_in\_informed\_space}( )$
+		\ENDIF
+		\STATE $x_{i} \leftarrow \texttt{MCMC\_sample} (x_{i-1}, c_{\text{best}})$ 
 		\IF{ $ x_{i} \not\in \Cinf $ }
-			\STATE $x_{0} \leftarrow \texttt{sample\_in\_informed\_space}( )$
+			\STATE $ i \leftarrow 0 $; $ x_{0} \leftarrow \varnothing $
 			\STATE \textbf{Goto} line \ref{alg:mcmc_informed_sampling:start} 
 		\ENDIF
-		\STATE \textbf{output} $x_{i}$
-		%\ENDWHILE
+		\STATE \textbf{return} $x_{i}$
 		\ENDLOOP 
-		%		\STATE $x_{\text{rand}} \leftarrow \texttt{sample\_uniform(\calX)}$
-		%%		\STATE $x_{\text{boundary}} 
-		%		\STATE $x_{0} 
-		%		 \leftarrow
-		%		 \texttt{newton\_raphson}(x_{\text{rand}}, c_{\text{best}})$ ; \hspace{3mm} $i\leftarrow 0$
-		%%		\STATE $x_{0} \leftarrow x_{\text{boundary}}$
-		%		\WHILE {\texttt{MCMC\_continue\_chain()}}
-		%			\STATE $x_{i} \leftarrow \texttt{MCMC} (x_{i-1}, c_{\text{best}})$; \hspace{3mm} $i\leftarrow i+1$
-		%			\STATE \textbf{output} $x_{i}$
-		%		\ENDWHILE		
-		%		\FOR {$i = 1$ to $N$}
-		%			\STATE $x_{i} \leftarrow \texttt{MCMC} (x_{i-1}, c_{\text{best}})$
-		%			\STATE \textbf{output} $x_{i}$
-		%		\ENDFOR
 	\end{algorithmic}
-	\caption{MCMC-based Informed Sampling $(c_{\text{best}})$}
+	\caption{MCMC-based Informed Sampling $( x_{i-1}, c_{\text{best}})$}
 	\label{alg:mcmc_informed_sampling}	
@@
 
-In MCMC-based Informed Sampling, as described in Algorithm~\ref{alg:mcmc_informed_sampling}, 
-a sampler firstly 
-\begin{enumerate}
-\item generate a sample follows a Markov chain 
-(\texttt{MCMC\_sample, line 2});
-and then
-\item decide if the candidate sample is in the level set, a new Markov chain will be created as a restart
-(\texttt{sample\_in\_informed\_space, line 4}).
-\end{enumerate}
+\subsubsection{Metropolis-Hastings sampler}
 
-\subsubsection{Metropolis-Hastings sampler}
+\os{Please rewrite this entire section as well as the pseudo code. I did not understand it at all}
 
@@
 
-We use canonical distribution to approximate the target distribution $ \pi $, which is a uniform distribution subject to a level set.
+We use canonical distribution to approximate the target distribution $ \pi $, which is a uniform distribution subject to an informed set.
 It means that energy function is defined from cost function that bridges cost and probability.
@@
 
+\subsection{Asymptotic optimality}
+We note that our approach produces samples that cover the informed space. Namely, there is a non-zero probability to sample in any region of $\Cinf$.
+A direct implication of the proof of optimality presented in~\cite{KF11} is that our algorithm is asymptotic optimal:
+
+\begin{prop}
+	\label{prop:asym_opt}
+	Informed RRT*~\cite{GSB14} running with MCMC-based informed sampling is asymptotic optimal.	
+\end{prop}
+
 \section{Evaluation}
 \label{sec:eval}
-
-% \subsection{Uniformity}
-
-% (Give a set of parameters)
-% We firstly need to propose a way of measuring uniformity.
-% Then we can apply it to compare MCMC approach with rejection sampling and hierarchical rejection sampling.
-% We are interested with
-% \begin{itemize}
-% 	\item asymptotic behavior (assumption: MCMC converge to a close uniformity)
-% 	\item convergence rate (assumption: MCMC converge faster)
-% \end{itemize}
 
@@
 Fig. \ref{fig:sampling_efficiency} shows that MHS and HNR have a better sampling efficiency compared to HRS and RS with decrease in informed set volume ratio or increase in dimensions. 
-Figure \ref{fig:sampling_efficiency:levelset} shows how the informed set volume ratio decreases as the level set cost $ c_{best} $ becomes smaller in problems of different dimensions.
-In a higher dimension, the informed set volume ratio falls much more quickly as the level set cost $ c_{best} $ decreases in planning process, as new better solutions are kept being found.
+Figure \ref{fig:sampling_efficiency:levelset} shows how the informed set volume ratio decreases as the informed set cost $ c_{best} $ becomes smaller in problems of different dimensions.
+In a higher dimension, the informed set volume ratio falls much more quickly as the informed set cost $ c_{best} $ decreases in planning process, as new better solutions are kept being found.
 
@@
 		\includegraphics[width=\linewidth]{fig/sampling_efficiency/levelset}
-		\caption{2DoF - 4D. TODO:Time per sample vs level set}
+		\caption{2DoF - 4D. TODO:Time per sample vs informed set}
 		\label{fig:sampling_efficiency:levelset}
@@
 	%	\includegraphics[width=\linewidth]{fig/sampling_efficiency/levelset_6d}
-	%	\caption{6DoF - 12D. TODO:Time per sample vs level set}
+	%	\caption{6DoF - 12D. TODO:Time per sample vs informed set}
 	%	\label{fig:sampling_efficiency:6d}
@@
 
-\dy{shall we use informed set or level set?}
-
 \dy{going to change the tick labels so this below sentence will be replaced}
@@
 Metropolis-Hastings shows consistent sampling time when problems get harder. 
-It takes the advantage of sampling a near state that generate samples in a level set.
-However this does not reflect the quality of the samples, though all the samples are in the level set.
+It takes the advantage of sampling a near state that generate samples in an informed set.
+However this does not reflect the quality of the samples, though all the samples are in the informed set.
 Recall in Algorithm~\ref{alg:mh_mcmc}, a new sample candidate is obtained from a Gaussian distribution $ q( x \mid x_{i-1}, \Sigma ) $.

### 2017-09-14 code/sample efficiency/volumeRatio/plot1.m
plot code

@@ -22,7 +22,7 @@ plot(dim6(:,12), dim6(:,13), 'color', red, 'linewidth', 4);
 
 xlim([1, 1.41]);
 xlabel('informed set volume ratio');
-ylabel('level set ratio');
+ylabel(' ratio');
 %legend('Rejection', 'HRS', 'MCMC', 'Hit&Run');
 legend('4 dimension', '12 dimension');
 hold off;

### 2017-09-15 paper.tex
new plot

@@
 
-Sampling-based motion-planning algorithms~\cite{CBHKKLT05, L06} have proven to be an effective tool at solving motion-planning problems.
+Sampling-based motion-planning algorithms~\cite{L06} have proven to be an effective tool at solving motion-planning problems.
 They search through a continuous state space~$\calX$ by sampling random states and maintaining a discrete graph~$G$ called a \emph{roadmap}.
@@
 
-While our approach can be used with any Markov chain Monte Carlo (MCMC) method, it is especially suited to be used with Hit-and-Run~\cite{S84,KSZ11}.
+While our approach can be used with any Markov chain Monte Carlo (MCMC) method, it is especially suited to be used with Hit-and-Run~\cite{KSZ11}.
 Roughly speaking, this is because Hit-and-Run (detailed in Sec~\ref{sec:related_work})
@@
 
-Our approach requires that the system has a solution to the two-point boundary value problem (2pBVP)~\cite{L06, H02} and that a gradient can be defined over the cost function.
+Our approach requires that the system has a solution to the two-point boundary value problem (2pBVP)~\cite{L06} and that a gradient can be defined over the cost function.
 Indeed, we demonstrate the efficiency of our approach on a wide variety of systems and show that it enables reducing the planning time by several orders of magnitude when compared to algorithms using rejection sampling or HRS.
@@
     \end{minipage}
-    \begin{minipage}[t]{0.33\linewidth}
+    \begin{minipage}[t]{0.35\linewidth}
     	\begin{subfigure}[c]{\textwidth}
@@
 lazy dynamic programming~\cite{GSB15, JSCP15, SH15},
-relaxing optimality to near-optimality~\cite{DB14, SH16} 
+relaxing optimality to near-optimality~\cite{SH16} 
 and more.
@@
 Heuristic approaches include
-sampling on the medial axis~\cite{WAS99a, WAS99b, LTA03, YDLTA14},
-sampling near the boundary of the obstacles~\cite{ABDJV98, YTEA12},
-resampling along a given trajectory~\cite{APD11, AS11}
-and more~\cite{US03, SWT09}.
+sampling on the medial axis~\cite{WAS99a, YDLTA14},
+sampling near the boundary of the obstacles~\cite{YTEA12},
+resampling along a given trajectory~\cite{AS11}
+and more~\cite{SWT09}.
 For planning under the differential constraints,
@@
 One variant, which is of special interest to us is 
-Hit and Run~\cite{S84,KSZ11}.
+Hit and Run~\cite{KSZ11}.
 Here, given the current point $x_i$ the next point~$x_{i+1}$ in the Markov chain is produced by sampling a random direction~$\theta$ on the surface of the unit sphere centered at $x_{i+1}$.
@@
 The point $x_{i+1}$ is chosen by randomly sampling a point on $r_i$.
-This algorithm is considered to be one of the most efficient algorithms for generating an asymptotically uniform point if the set under consideration is convex~\cite{L99, LV06}
-and it can also be extended to sample points that converge to an arbitrary target distribution in total variation~\cite{BRS93, RS94}.
+This algorithm is considered to be one of the most efficient algorithms for generating an asymptotically uniform point if the set under consideration is convex~\cite{LV06}
+and it can also be extended to sample points that converge to an arbitrary target distribution in total variation~\cite{RS94}.
 
@@
 
-\dy{Do you think we should include some figures that has been commented out below to show how difficult sampling an informed set is?}
+%\dy{Do you think we should include some figures that has been commented out below to show how difficult sampling an informed set is?}
 
@@
 
-\os{Please rewrite this entire section as well as the pseudo code. I did not understand it at all}
+%\os{Please rewrite this entire section as well as the pseudo code. I did not understand it at all}
 
@@
 Our work adopts the general Metropolis-Hasting algorithm, as described in Alg.~\ref{alg:mh_mcmc}, 
-While the general algorithm is slightly more complex, for our setting it can be described as follows:
 We generate a new sample $ x_{i}$ around the previous sample $ x_{i-1}$ using a Gaussian distribution (line~1).
@@
 If not, we return the previous sample.
-%
-For this algorithm, we continue sampling along the Markov Chain as long as new samples are produced.
+An acceptance ratio $ \alpha $ is used to keep the reversibility even if the target probability $ \pi $ is asymmetric, which is needed to guarantee the convergence~\cite{CG95}.
+
+%For this algorithm, we continue sampling along the Markov Chain as long as new samples are produced.
 
@@
 Hit-and-Run~\cite{S84} MCMC sampler is known to efficiently generate uniform samples. 
-Specifically, we use the Accelerated Hit-and-Run variant~\cite{KSZ11} of the algorithm i.e.
-described in Alg.~\ref{alg:hit_and_run_mcmc}.
+Specifically, we use the Accelerated Hit-and-Run variant~\cite{KSZ11} of the algorithm i.e. described in Alg.~\ref{alg:hit_and_run_mcmc}.
 Given the previous sample~$x_{i-1}$ it first  samples a random direction on the unit sphere (line 1).
@@
 
-We evaluate the performance of proposed MCMC methods by comparing four types of samplers, which are Rejection Sampler (RS), Hierarchical Rejection Sampler (HRS), Metropolis-Hastings Sampler (MHS), and Hit-and-Run Sampler (HNR).
+We evaluate the performance of proposed MCMC methods by comparing four types of samplers, which are Rejection Sampler (RS), Hierarchical Rejection Sampler (HRS), Metropolis-Hastings Sampler (MH), and Hit-and-Run Sampler (HNR).
 We use different samplers to generate a fixed number of samples in different informed sets to check the sampling efficiency. %, especially when the sampling is harder (in a small informed set).
@@
 
-\dy{TODO: change MCMC to MHS (Metropolis Hasting Sampler) in the plots}
+%\dy{TODO: change MCMC to MHS (Metropolis Hasting Sampler) in the plots}
 
@@
 \begin{figure}[t!]
-	\centering
-	\begin{subfigure}[b]{0.78\linewidth}
-		\includegraphics[width=\linewidth]{fig/sampling_efficiency/levelset}
+	\includegraphics[width=.46\textwidth]{fig/sampling_efficiency/levelset}
 	\caption{2DoF - 4D. TODO:Time per sample vs informed set}
 	\label{fig:sampling_efficiency:levelset}
-	\end{subfigure}
+\end{figure}
+
+\begin{figure}[t!]
+	\centering
+
 	%\begin{subfigure}[b]{0.48\linewidth}
@@
 	%\end{subfigure}
-	 \\
-	\begin{subfigure}[b]{0.78\linewidth}
-		\includegraphics[width=\linewidth]{fig/sampling_efficiency/sample_efficiency_2d}
+
+	\begin{subfigure}[b]{\linewidth}
+		\centering
+		\includegraphics[width=.85\linewidth]{fig/sampling_efficiency/sample_efficiency_2d}
 		\caption{2DoF - 4D TODO: rescale x axis}
@@
 % 	\end{subfigure}	
-	\begin{subfigure}[b]{0.78\linewidth}
-		\includegraphics[width=\linewidth]{fig/sampling_efficiency/sample_efficiency_6d}
+	\begin{subfigure}[b]{\linewidth}
+		\centering
+		\includegraphics[width=.85\linewidth]{fig/sampling_efficiency/sample_efficiency_6d}
 		\caption{6DoF - 12D. TODO: rescale x axis}
@@
 
-\dy{going to change the tick labels so this below sentence will be replaced}
+%\dy{going to change the tick labels so this below sentence will be replaced}
 It is noticeable that both x axis and y axis are converted by $ \log_{10} () $ in Figure~\ref{fig:sampling_efficiency:2d} and Figure~\ref{fig:sampling_efficiency:6d}.

### 2017-09-15 code/motivation/plotdata.m

@@ -78,7 +78,7 @@ ylabel('Velocity');
 legend([h1, h2], {'non-zero goal velocity', 'zero goal velocit'});
 hold off;
 
-
+set(gca,'FontSize',16);
 
 %{
 figure(4);

### 2017-09-15 code/planning efficiency/6dof_snake/Hammer/plot_data2.m

@@ -29,8 +29,10 @@ plot(T3, mean(HRS2,1), 'o', 'MarkerFaceColor', red, 'MarkerEdgeColor', red, 'Mar
 plot(T1, mean(MCMC2,1), 'o', 'MarkerFaceColor', green, 'MarkerEdgeColor', green, 'MarkerSize', 4);
 plot(T4, mean(HNR2,1), 'o', 'MarkerFaceColor', purple, 'MarkerEdgeColor', purple, 'MarkerSize', 4);
 
-xlim([0, 8]);
-legend('RS', 'HRS', 'MCMC', 'HNR');
+xlim([0, 8]);%ylim([1,1.7]);
+legend('RS', 'HRS', 'MH', 'HNR');
 xlabel('Time - s');
 ylabel('Ratio to minimum');
 hold off;
+
+set(gca, 'FontSize', 16);

### 2017-09-15 code/planning efficiency/herb/batting/merge_planning_data2.m

@@ -1,4 +1,4 @@
-datasetSize = 10;
+datasetSize = 20;
 maxtimes = zeros(datasetSize,1);
 minvals = zeros(datasetSize,1);
 for i = 0:1:datasetSize-1
@@ -35,10 +35,10 @@ T3 = T1 + deltaStepSize*2; T3(1) = 0;
 T4 = T1 + deltaStepSize*3; T4(1) = 0; 
 
 for i = 0:1:datasetSize-1
-  mcmc_filename = sprintf('data/20s/simple_MCMC_%d.csv', i);
-  rs_filename = sprintf('data/20s/simple_RS_%d.csv', i);
-  hrs_filename = sprintf('data/20s/simple_HRS_%d.csv', i);
-  hnr_filename = sprintf('data/20s/simple_HNR_%d.csv', i);
+  mcmc_filename = sprintf('data/60s/simple_MCMC_%d.csv', i);
+  rs_filename = sprintf('data/60s/simple_RS_%d.csv', i);
+  hrs_filename = sprintf('data/60s/simple_HRS_%d.csv', i);
+  hnr_filename = sprintf('data/60s/simple_HNR_%d.csv', i);
   
   MCMC = csvread(mcmc_filename);
   RS = csvread(rs_filename);

### 2017-09-15 code/planning efficiency/herb/batting/plot_data2.m

@@ -29,8 +29,10 @@ plot(T3, mean(HRS2,1), 'o', 'MarkerFaceColor', red, 'MarkerEdgeColor', red, 'Mar
 plot(T1, mean(MCMC2,1), 'o', 'MarkerFaceColor', green, 'MarkerEdgeColor', green, 'MarkerSize', 4);
 plot(T4, mean(HNR2,1), 'o', 'MarkerFaceColor', purple, 'MarkerEdgeColor', purple, 'MarkerSize', 4);
 
-xlim([0, 20]);
-legend('RS', 'HRS', 'MCMC', 'HNR');
+xlim([0, 23]);
+legend('RS', 'HRS', 'MH', 'HNR');
 xlabel('Time - s');
 ylabel('Ratio to minimum');
 hold off;
+
+set(gca, 'FontSize', 16);

### 2017-09-15 code/planning efficiency/planar_manipulator/general/plot_data2.m

@@ -30,7 +30,10 @@ plot(T1, mean(MCMC2,1), 'o', 'MarkerFaceColor', green, 'MarkerEdgeColor', green,
 plot(T4, mean(HNR2,1), 'o', 'MarkerFaceColor', purple, 'MarkerEdgeColor', purple, 'MarkerSize', 4);
 
 xlim([0, 10]);
-legend('RS', 'HRS', 'MCMC', 'HNR');
+ylim([1,2.7]);
+legend('RS', 'HRS', 'MH', 'HNR');
 xlabel('Time - s');
 ylabel('Ratio to minimum');
 hold off;
+
+set(gca, 'FontSize', 16);

### 2017-09-15 code/sample efficiency/2d/plot1.m

@@ -25,11 +25,21 @@ h4 = scatter(log10(data(:,5)),log10(data(:,3)./data(:,6)), marker_size, 'MarkerF
 %plot(log10(data(:,5)),log10(data(:,3)./data(:,6)), 'color', purple, 'linewidth', 1);
 hold off;
 %xlim([-4, 0]);ylim([-2,1]);
+yval = -2:0.5:1;
+ytk = power(10,yval);
+ytks = cell(1,size(ytk,2));
+for i = 1:1:size(ytk,2)
+    ytks{i} = num2str(ytk(1,i),'%10.2e\n');
+end
 
 
 xlabel('informed set volume ratio');
 ylabel('time per sample - (ms)');
-legend([h1, h2, h3, h4], {'Rejection', 'HRS', 'MCMC', 'Hit&Run'});
-%set(gca, 'XTick', [-0.001 -0.001 -0.01 -0.1 1]);
-%set(gca,'XTickLabel',sprintf('%3.4f|',x))
-set(gca, 'fontsize',16);
+lgd = legend([h1, h2, h3, h4], {'RS', 'HRS', 'MH', 'HNR'});
+lgd.FontSize = 16;
+%xticks([-0.0001 -0.001 -0.01 -0.1 1]);
+set(gca, 'XTickLabel', {'0.0001','0.001','0.01', '0.1', '1'});
+set(gca,'YTickLabel',ytks);
+set(gca, 'fontsize',12);
+
+set(gca,'YTickLabelRotation',20);

### 2017-09-15 code/sample efficiency/6d/plot1.m

@@ -15,13 +15,31 @@ pink = [197,27,138]/255;
 figure;
 hold on;
 marker_size = 20;
-scatter(log10(data(:,5)), log10(data(:,4)./data(:,6)), marker_size, 'MarkerFaceColor', blue, 'MarkerEdgeColor', blue, 'Marker', 's');
-scatter(log10(data(:,5)),log10(data(:,2)./data(:,6)), marker_size, 'MarkerFaceColor', red, 'MarkerEdgeColor', red, 'Marker', 'd');
-scatter(log10(data(:,5)),log10(data(:,1)./data(:,6)), marker_size, 'MarkerFaceColor', green, 'MarkerEdgeColor', green, 'Marker', 'h');
-scatter(log10(data(:,5)),log10(data(:,3)./data(:,6)), marker_size, 'MarkerFaceColor', purple, 'MarkerEdgeColor', purple, 'Marker', 'o');
-
-xlim([-5, -2.4]);
-xlabel('informed set volume ratio - log_1_0');
-ylabel('time per sample - log_1_0(ms)');
-legend('Rejection', 'HRS', 'MCMC', 'Hit&Run');
+h1 = scatter(log10(data(:,5)),log10(data(:,4)./data(:,6)), marker_size, 'MarkerFaceColor', blue, 'MarkerEdgeColor', blue, 'Marker', 's');
+h2 = scatter(log10(data(:,5)),log10(data(:,2)./data(:,6)), marker_size, 'MarkerFaceColor', red, 'MarkerEdgeColor', red, 'Marker', 'd');
+h3 = scatter(log10(data(:,5)),log10(data(:,1)./data(:,6)), marker_size, 'MarkerFaceColor', green, 'MarkerEdgeColor', green, 'Marker', 'h');
+h4 = scatter(log10(data(:,5)),log10(data(:,3)./data(:,6)), marker_size, 'MarkerFaceColor', purple, 'MarkerEdgeColor', purple, 'Marker', 'o');
+%plot(log10(data(:,5)),log10(data(:,4)./data(:,6)), 'color', blue, 'linewidth', 1);
+%plot(log10(data(:,5)),log10(data(:,2)./data(:,6)), 'color', red, 'linewidth', 1);
+%plot(log10(data(:,5)),log10(data(:,1)./data(:,6)), 'color', green, 'linewidth', 1);
[…]

### 2017-09-15 code/sample efficiency/volumeRatio/plot1.m

@@ -21,10 +21,10 @@ plot(dim6(:,12), dim6(:,13), 'color', red, 'linewidth', 4);
 %scatter(log10(data(:,5)),log10(data(:,3)./data(:,6)), marker_size, 'MarkerFaceColor', purple, 'MarkerEdgeColor', purple, 'Marker', 'o');
 
 xlim([1, 1.41]);
-xlabel('informed set volume ratio');
-ylabel(' ratio');
+xlabel(' c_{best} / c^*_{best}');
+ylabel('informed set volume ratio');
 %legend('Rejection', 'HRS', 'MCMC', 'Hit&Run');
-legend('4 dimension', '12 dimension');
+legend('4-dimension', '12-dimension');
 hold off;
 
-set(gca,'FontSize',20)
+set(gca,'FontSize',16)

### 2017-09-15 paper.tex
sync

@@
 \usepackage{eqparbox}
+\usepackage{multirow}
+\usepackage{booktabs}
 %\hypersetup{bookmarksopen,
@@
 Generalizing Informed Sampling
-for Asymptotically Optimal Sampling-based Planning via Markov Chain
-Monte Carlo Methods
+for Asymptotically Optimal Sampling-based Kinodynamic Planning via Markov Chain
+Monte Carlo
 }
@@
 \author{
-Daqing Yi$^{*}$,
-Rohan Thakker$^{*}$,
-Cole Gulino$^{}$, 
-Oren Salzman$^{}$ and
-Siddhartha Srinivasa$^{}$% <-this % stops a space
-\thanks{*Daqing Yi and R. Thakker contributed equally to this paper.}
-\thanks{This work was (partially) funded by the National Science Foundation IIS (\#1409003), Toyota Motor Engineering \& Manufacturing (TEMA), and the Office of Naval Research.}% <-this % stops a space
-\thanks{$^{1}${\tt\small \{rthakker, cgulino, daqingy, osalzman, ss5\} @andrew.cmu.edu}}%
-%
-\\        
-Robotics Institute, Carnegie Mellon University$^{1}$
+Daqing Yi$^{*1}$,
+Rohan Thakker$^{*2}$,
+Cole Gulino$^{2}$, 
+Oren Salzman$^{2}$ and
+Siddhartha Srinivasa$^{1}$
+\thanks{$^{*}$Daqing Yi and Rohan Thakker contributed equally to this paper.}
+%\thanks{This work was (partially) funded by the National Science Foundation IIS (\#1409003), Toyota Motor Engineering \& Manufacturing (TEMA), and the Office of Naval Research.}% <-this % stops a space
+\thanks{$^{1}$Daqing Yi and Siddhartha Srinivasa are with Paul G. Allen School of Computer Science \& Engineering, University of Washington.
+{\tt\small \{dqyi, siddh\}@cs.washington.edu}}
+\thanks{$^{2}$ Rohan Thakker, Cole Gulino and Oren Salzman are with Robotics Institute, Carnegie Mellon University.
+{\tt\small \{rthakker, cgulino, osalzman\} @andrew.cmu.edu}}%
 }
@@
 \begin{abstract}
-Asymptotically-optimal motion planners such as RRT* have been shown to incrementally approximate the shortest path between a start and goal states.
+Asymptotically-optimal motion planners such as RRT* have been shown to incrementally approximate the shortest path between start and goal states.
 Once an initial solution is found, their performance can be dramatically improved by restricting subsequent samples to regions of the state space that can potentially improve the current solution.
@@
 In this paper, we suggest an alternative approach to produce samples in the informed set~\Cinf for a wide range of settings.
-Our main insight is to recast this problem as one of sampling uniformly within an informed set of an implicit function.
+%Our main insight is to recast this problem as one of sampling uniformly within an informed set of an implicit function.
+Our main insight is to recast this problem as one of sampling uniformly within the sub-level-set of an implicit non-convex function.
 This recasting enables us to apply Monte Carlo sampling methods, used very effectively in the Machine Learning and Optimization communities, to solve our problem.
@@
 \textbf{
-Our main insight is to recast this problem as one of sampling uniformly within an informed set of an implicit function.
+%Our main insight is to recast this problem as one of sampling uniformly within an informed set of an implicit function.
+Our main insight is to recast this problem as one of sampling uniformly within the sub-level-set of an implicit non-convex function.
 This recasting enables us to apply Monte Carlo sampling methods, used very effectively in the Machine Learning and Optimization communities, to solve our problem.
@@
 
-While our approach can be used with any Markov chain Monte Carlo (MCMC) method, it is especially suited to be used with Hit-and-Run~\cite{KSZ11}.
-Roughly speaking, this is because Hit-and-Run (detailed in Sec~\ref{sec:related_work})
-performs a series of one-dimensional rejection samples which are extremely fast to compute, even in high-dimensional spaces.
+While our approach can be used with any Markov Chain Monte Carlo (MCMC) method, it is especially suited to be used with Hit-and-Run~\cite{KSZ11}.
+Roughly speaking, this is because Hit-and-Run (detailed in Sec~\ref{sec:algorithm})
+produces a series of one-dimensional rejection samples which are extremely fast to compute, even in high-dimensional spaces.
 
@@
 		%\includegraphics[height=3cm]{fig/motivation/slowmotion}
-		\caption{Zero goal velocity}
+		\caption{Both start velocity and goal velocity are zero.}	\vspace{4pt}
 		\label{fig:motivation:slow}
@@
 		%\includegraphics[height=3cm]{fig/motivation/fastmotion}
-		\caption{Non-zero goal velocity}
+		\caption{Start velocity is zero but goal velocity is non-zero.}
 		\label{fig:motivation:fast}
@@
     		\includegraphics[width=\textwidth]{fig/motivation/phase_plot}
-    		\caption{Non-zero goal velocity}
+    		\caption{Phase plot of two trajectories of one of the joints.
+    		The X axis is position. The Y axis is velocity. }
     		\label{fig:motivation:phase_plot}
@@
    	\end{minipage}
-	\caption{HERB moves right arm from a start configuration to a goal configuration, which are very close.
+	\caption{HERB moves right arm from a start configuration to a goal configuration, which are in close proximity.
     When the goal velocity is non-zero, HERB needs to move right arm further away to accelerate.
@@
 Additional algorithms followed, increasing the converges rate by various techniques such as 
-lazy dynamic programming~\cite{GSB15, JSCP15, SH15},
+lazy dynamic programming~\cite{GSB15, SH15},
 relaxing optimality to near-optimality~\cite{SH16} 
@@
 sampling near the boundary of the obstacles~\cite{YTEA12},
-resampling along a given trajectory~\cite{AS11}
-and more~\cite{SWT09}.
+resampling along a given trajectory~\cite{AS11}.
+%and more~\cite{SWT09}.
 For planning under the differential constraints,
-reachability-guided sampling~\cite{SWT09, PLAEFRA17} focuses on sampling regions of the state space that are most likely to promote expansion for the given constraints.
+reachability-guided sampling~\cite{PLAEFRA17} focuses on sampling regions of the state space that are most likely to promote expansion for the given constraints.
 
@@
 \label{subsec:mcmc}
-Monte Carlo simulation is a general sampling framework widely used in various domains such as
-statistical machine learning~\cite{M97},
-motion tracking~\cite{KBD04}, 
-data regression~\cite{TL11} and 
-state estimation~\cite{ASC13}.
+Monte Carlo simulation is a general sampling framework widely used in various domains. %such as
+%statistical machine learning~\cite{M97},
+%motion tracking~\cite{KBD04}, 
+%data regression~\cite{TL11} and 
+%state estimation~\cite{ASC13}.
 Roughly speaking, Monte Carlo simulation repeatedly samples a domain at random to approximate some value or function.
@@
 Here, the samples are drawn by generating a Markov chain such that the distribution of points on the chain converges to the desired distribution.
-The Markov Chain can be generated by performing a random walk such as
-in Metropolis-Hastings~\cite{CG95}, 
-Gibbs sampling~\cite{CK94}
-or by simulating simulating Hamiltonian dynamics~\cite{N94} (instead of performing the random walk).
-
+%The Markov Chain can be generated by performing a random walk such as
+%in Metropolis-Hastings~\cite{CG95}, 
+%Gibbs sampling~\cite{CK94}
+%or by simulating simulating Hamiltonian dynamics~\cite{N94} (instead of performing the random walk).
 One variant, which is of special interest to us is 
@@
 \subsection{Geometric vs. Kinodynamic planning}
-Consider the problem depicted in Fig.~\ref{fig:motivation} where HERB is required about a swing action that a robotic arm ends with a relative high velocity towards a direction.
-One approach to address this problem is to first plan in the geometric configuration space and the re-time the algorithm.
-When the start and goal are in close proximity, a geometric planner will simply connect the two states (Fig.~\ref{fig:motivation:fast}).
-However, to adhere to the velocity constraints at the goal, the actual motion that is required is to move back the arm in order to gain speed and then reach the goal (Fig.~\ref{fig:motivation:fast}).
-In such settings, re-timing the path will not produce feasible results.
+Consider the problem depicted in Fig.~\ref{fig:motivation} where HERB is required to produce a large velocity at the end of its arm at the goal position.
+One approach to address this problem is to first plan in the geometric configuration space and then re-scale the trajectory in time.
+However, when the start and goal are in close proximity, a geometric planner will simply connect the two states (Fig.~\ref{fig:motivation:fast}).
+On re-scaling this trajectory in time, reaching the goal velocity in such short distance will require large acceleration, which will not be feasible.
+Hence, it is required to move the arm back and then reach the goal, i.e. the trajectory returned by the kinodynamic planner shown in (Fig.~\ref{fig:motivation:fast}).
 The difference between the two motions are shown in a phase plot in Fig.~\ref{fig:motivation:phase_plot}.
@@
 $u \in [\underline{u}, \overline{u}]$ 
-is the (bounded) acceleration\footnote{One can also bound the velocity of the system. However, to simplify the exposition, we only constrain the system with acceleration bounds.}.
+is the (bounded) acceleration.
+%\footnote{One can also bound the velocity of the system. However, to simplify the exposition, we only constrain the system with acceleration bounds.}.
 
@@
 %\subsection{Informed set}
-Recall that for Euclidean spaces minimizing path length, the informed set~\Cinf is a prolate hyperspheroid.
+Recall that for Euclidean spaces minimizing path length, the informed set~\Cinf is a prolate hyperspheroid~\cite{GSB14}.
 Moreover, the size and shape of the hyperspheroid is defined only be the cost $c_{\text{best}}$ of the current best solution and not by the location of the start~$x_s$ and goal~$x_g$.
@@
 Furthermore,  its boundary may not be  differentiable due to the aforementioned discontinuous.
-
-\ignore{
-See Fig. ~\ref{fig:sample_dimt} for an example motion of one joint through the $\left(q,\dot{q}\right)$ space.
-
-\begin{figure}[tb]
-  \centering
-  	\includegraphics[width=0.3\textwidth]{fig/example_motion.png}
-  \caption{
-    \captionstyle
-  	Example possible motion using the double-integrator minimum time model between start state $(x_1, \dot{x_1})$ and goal state $(x_2, \dot{x_2})$ through some intermediate state $(x_i, \dot{x_i})$.
-  	}
-   	\label{fig:sample_dimt}
-\end{figure}
-
-In order to find the minimum time, $T\left(x\right)$, of a motion like Fig.
-~\ref{fig:sample_dimt}, we can examine the paths separately with one corresponding to a motion with acceleration $a_1$ from $\left(x_1, \dot{x}_1\right)$ to $\left(x_i, \dot{x}_i\right)$ and another corresponding to motion with acceleration $a_2$ from $\left(x_i, \dot{x}_i\right)$ to $\left(x_2, \dot{x}_2\right)$.
-
-\ref{} shows that we can express total distance travelled in the joint space $x$ can be expressed in this way as:
-
-\begin{equation}
-x_2 - x_1 = d_{a_1} + d_{a_2}
-\end{equation}
-where $d_{a_1}$ is the distance travelled at max acceleration from the first path and $d_{a_2}$ is the distance travelled at max acceleration in the opposite direction.
-
-Using simple constant acceleration equations we can express this in the form:
-
-\begin{equation}
-x_2 - x_1 = \left(\dot{x}_1 t_{a_1} + \frac{1}{2} a_1 t_{a_1}^2\right) + \left(\frac{\dot{x}_2^2 - \dot{x}_i^2}{2a_2}\right)
-\end{equation}
-where $t_{a_1}$ is the time it takes to make the path from $\left(x_1, \dot{x}_1\right)$ to $\left(x_i, \dot{x}_i\right)$ at acceleration $a_1$ and $t_{a_2}$ is the time it takes to make the path from $\left(x_i, \dot{x_i}\right)$ to $\left(x_2, \dot{x}_2\right)$ at acceleration $a_2$.
-
-We can further expand the equation in order to put it into the canonical quadratic equation as follows:
-
-\begin{equation}
-a_1 t_{a_1}^2 + 2 \dot{x}_1 t_{a_1} + \frac{\dot{x}_2^2 - \dot{x}_1^2}{2a_2} - \left(x_2 - x_1\right) = 0
-\end{equation}
-
-Following ~\ref{} we solve a quadratic equation of the form $at^2+bt+c=0$ as follows:
-
-$$
-q = -\frac{1}{2}\left(b + \text{sign}\left(b\right)\sqrt{b^2 - 4ac}\right)
-$$
-$$
-t_1 = \frac{q}{a}; \hspace{5mm} t_2 = \frac{c}{q}
-$$
-where $t_1$ and $t_2$ are the two solutions to the quadratic equation.
-
-As we know, time must be positive and we are looking for minimum time.
-This leads to the fact that there is only one correct solution to the quadratic equation.
-Because of this, depending on the start and goal states, the sign of the acceleration on each path will change.
-
-Again following ~\ref{}, we programatically solve for the sign of the sign of the acceleration by analysing the start and goal position.
-Fig.
-~\ref{fig:sample_dimt} shows the determining term $\Delta x_{acc}$, which is the distance from $x_1$ to the point where $\dot{x} = \dot{x}_2$.
-
-And using constant acceleration equations with ~\ref{} again, we find that:
-
-\begin{equation}
-\Delta x_{acc} = \frac{1}{2} \left(\dot{x}_1 + \dot{x}_2\right) \frac{|\dot{x}_2 - \dot{x}_1|}{a_{max}}
-\end{equation}
-
-\begin{equation}
-a_1 = - a_2 = \text{sign}\left(x_2 - x_2 - \Delta x_{acc}\right) a_{max}
-\end{equation}
-
-From these equations it shows a fundamental difference of a kinodynamic state space compared to a geometric state space.
-Because of this the minimum time path can vary in shape depending on the start and goal state.
-The consequence of this is that the shape of the informed subset can change dramatically depending on the start and goal state of the problem definition.
-Because of this, finding a closed form solution to sampling in the informed space is not feasible.
-}
-
-%\dy{Do you think we should include some figures that has been commented out below to show how difficult sampling an informed set is?}
 
@@
 
-\ignore{
-\begin{figure}[tb]
-  \centering
-  	\includegraphics[height = 4.cm ]{fig/level_set.jpg}
-  \caption{
-    \captionstyle
-  	Level sets for the case of minimal-time double integrator.
-A point $x = (q, \dot{q})$  denote the position and velocity of the robot while the color at $x$ denotes the cost to reach $x_t$ from $x_s$ subject to passing through the state $x$.
-  	}
-   	\label{fig:informed_1d_di}
-	\vspace{-5.5mm}
-\end{figure}
-
-\begin{figure}[tb]
-  \centering
-  	\includegraphics[width=0.5\textwidth]{fig/kino_space.png}
-  \caption{
-    \captionstyle
-  	Side view of the cost surface for the case of minimal-time double integrator. The side view showcases the discontinuous nature of the cost surface.
-  	}
-   	\label{fig:cost_surface_1d}
-%	\vspace{-5.5mm}
-\end{figure}
-
-See Fig.~\ref{fig:cost_surface_1d} for a side view of the cost surface for one degree of freedom ($\left(x, \dot{x}\right)$).
-One can see a key property of the cost surface that cause serious concerns is the discontinuous nature of the surface.
-As mentioned before, finding the minimum time problem amounts to solving a quadratic equation. 
-Because the nature of this equation changes with the start and end goal, there is a curve in the input space that amounts to a switching surface that represents the boundary for the decision of the sign of $a_1$.
-This surface causes a discontinuous cost surface as shown in Fig. ~\ref{fig:cost_surface_1d}.
-}
-
 \section{MCMC-based Informed Sampling}
@@
 In this section we describe our approach to efficiently produce new samples in an informed set~\Cinf given a specific cost~$c_{\text{best}}$ of trajectory $\gamma_{best}(t)$.
-The samples follow a Monte Carlo Markov Chain, in which a new sample candiate is produceded from a previous sample that also lies in the same informed set.
-It is important to note that at each iteration, we will query our algorithm for one sample. 
-However, this sample depends on the previous iterations of the algorithm which is why we describe it as a method to produce a sequence of samples.
-Furthermore, the value~$c_{\text{best}}$ can decrease between consecutive iterations.
-This will occur if the search algorithm that uses our sampler finds a path to the goal whose cost is lower than~$c_{\text{best}}$.
+The samples follow a Markov Chain Monte Carlo, in which a new sample candidate is produced from a previous sample that also lies in the same informed set.
+%However, this sample depends on the previous iterations of the algorithm which is why we describe it as a method to produce a sequence of samples.
+Furthermore, the value~$c_{\text{best}}$ can decrease between consecutive iterations in the planning process of an informed RRT* planner.
+This will occur if the search algorithm that uses the sampler finds a path to the goal whose cost is lower than~$c_{\text{best}}$.
 
@@
 \begin{enumerate}
-	\item finding an initial sample $ x_0 \in \Cinf $ which will serve as the start of a Markov chain. This is implemented using the function 
+	\item finding an initial sample $ x_0 \in \Cinf $ which will serve as the start of a Markov chain. 
+	This is implemented using the function 
 	$ \texttt{sample\_in\_informed\_space}( )$, and
-	\item sampling a new sample $ x_i \in \Cinf $ given a previous sample $ x_{i-1} $. This is implemented using the function $\texttt{MCMC\_sample} (x_{i-1}, c_{\text{best}})$.
+	\item sampling a new sample $ x_i \in \Cinf $ given a previous sample $ x_{i-1} $. 
+	This is implemented using the function $\texttt{MCMC\_sample} (x_{i-1}, c_{\text{best}})$.
 \end{enumerate}
-
-%Compared with rejection samplers, a MCMC-based informed sampler takes the advantage of a previous sample in the informed set $ \Cinf $ in finding a new sample, while reserves the randomness in problem space search, which builds an ``exploitation and exploration" patter in informed sampling.
-%
-%to initialize an MCMC algorithm which outputs a series of samples within \Cinf by constructing a Markov Chain.
-%This is done until some termination criterion is met and the entire process is repeated (Sec.~\ref{subsec:mcmc}). 
-%Specifically, we chose to use HMC due to its favourable properties (see Sec.~\ref{sec:intro}). 
 Our algorithm is described in Alg.~\ref{alg:mcmc_informed_sampling} and visualized in Fig.~\ref{fig:alg}.
@@
 	\end{algorithmic}
-	\caption{MCMC-based Informed Sampling $( x_{i-1}, c_{\text{best}})$}
+	\caption{\captionstyle MCMC-based Informed Sampling $( x_{i-1}, c_{\text{best}})$}
 	\label{alg:mcmc_informed_sampling}	
@@
 
-We use canonical distribution to approximate the target distribution $ \pi $, which is a uniform distribution subject to an informed set.
-It means that energy function is defined from cost function that bridges cost and probability.
-The energy function's definition provides the flexibility to specify desired or more probable states (by presenting lower energies) without the need to use a formal and restrictive model.
-
-Our energy for any given cost $c$, 
-denoted by~$E\left(c,\Cbest \right)$, 
-is a function of $c$ and the current best cost~$\Cbest$.
-To consider only points in the informed set, all with equal energy, one may consider taking 
-\begin{equation}
-E_{\text{informed}}\left(c,\Cbest \right) = 
-\begin{cases}
-0,	& \text{if } c \leq \Cbest\\        
-\infty,  	& \text{otherwise}.
-\end{cases}
-\end{equation}
-To approximate that function, we propose a formula as below:
-\begin{equation}
-\hat{E}_{\text{informed}} \left( c,\Cbest \right) 
-= \beta \cdot \text{sigm}\left(\Cbest - c\right)
-\end{equation}
-penalizes states outside the informed set~$\Cinf$ using a tight sigmoid function~$\text{sigm}$ scaled by some (large\footnote{The constant~$\beta$ gives points out of~\Cinf a large energy value which in turn implies a low probability of being sampled.
-In theory, we would like to have~$\beta \approx \infty$. 
-However, choosing~$\beta$ to be too large may cause numerical instabilities.}) constant~$\beta$.
-The sigmoid can be seen as a differentiable function smoothing the boundary of~$\Cinf$.
+In implementation, we use Newton-Raphson method as a gradient descent with random restart to find $ x_0 \in \Cinf $ as the start of a Markov chain.
 
@@
 
-Hit-and-Run~\cite{S84} MCMC sampler is known to efficiently generate uniform samples. 
-Specifically, we use the Accelerated Hit-and-Run variant~\cite{KSZ11} of the algorithm i.e. described in Alg.~\ref{alg:hit_and_run_mcmc}.
+Hit-and-Run~\cite{S84} sampler is known to efficiently generate uniform samples. 
+Specifically, we use the Accelerated Hit-and-Run variant~\cite{KSZ11} of the algorithm i.e.
+described in Alg.~\ref{alg:hit_and_run_mcmc}, which also supports the uniform sampling in both convex and non-convex state space~\cite{KSZ11}.
 Given the previous sample~$x_{i-1}$ it first  samples a random direction on the unit sphere (line 1).
@@
 
-For this algorithm, we continue sampling along the Markov Chain until either 
+For this algorithm, we continue sampling along a Markov Chain until either 
 (i)~the difference between the lower and upper bounds ($\lambda^-$ and $\lambda^+)$ 
@@
 (ii)~a predefined number of samples was exceeded.
-
-The Hit-and-Run algorithm is designed specifically for uniform distributions. 
-Hence, it doesn't require an approximation of a target distribution $ \pi $ that was generated with the energy function for Metropolis-Hastings algorithm.
+We want to point out that a Hit-and-Run sampler only requires that a Markov chain starts in an informed set, and will not produce a sample outside of the informed set.
 
 \subsection{Asymptotic optimality}
-We note that our approach produces samples that cover the informed space. Namely, there is a non-zero probability to sample in any region of $\Cinf$.
+We note that our approach produces samples that cover the informed space. 
+Namely, there is a non-zero probability to sample in any region of $\Cinf$.
 A direct implication of the proof of optimality presented in~\cite{KF11} is that our algorithm is asymptotic optimal:
@@
 
-%\dy{TODO: change MCMC to MHS (Metropolis Hasting Sampler) in the plots}
+Figure \ref{fig:sampling_efficiency:levelset} shows how the informed set volume ratio decreases as the informed set cost $ c_{best} $ becomes smaller in problems of different dimensions.
+In higher dimensions, the informed set volume ratio decreases much more quickly with decrease in the informed set cost $ c_{best} $, as new cheaper trajectories are found in the planning process.
 
 Fig.
-\ref{fig:sampling_efficiency} shows the log plot of the average time taken to generate one sample in the informed space vs.
+\ref{fig:sampling_efficiency} shows the plot of the average time taken to generate one sample in the informed space vs.
 informed set volume ratio, i.e.
 the ratio of the volume of informed space to the volume of entire state space, for 5000 samples.
+The informed set volume ratio is estimated by the acceptance rate of rejection sampler.
 The informed set volume ratio is approximated by the ratio of the number of accepted to the total number of samples obtained while running rejection sampling. 
 %Efficiency of rejection sampling based methods is very low for high dimensions because this ratio decreases exponentially w.r.t the dimension of the space, for a given sub-level-set of the cost function.
-Fig. \ref{fig:sampling_efficiency} shows that MHS and HNR have a better sampling efficiency compared to HRS and RS with decrease in informed set volume ratio or increase in dimensions. 
-Figure \ref{fig:sampling_efficiency:levelset} shows how the informed set volume ratio decreases as the informed set cost $ c_{best} $ becomes smaller in problems of different dimensions.
-In a higher dimension, the informed set volume ratio falls much more quickly as the informed set cost $ c_{best} $ decreases in planning process, as new better solutions are kept being found.
+Fig. \ref{fig:sampling_efficiency} shows that MH and HNR have a better sampling efficiency compared to HRS and RS with decrease in informed set volume ratio or increase in dimensions.
 
 \begin{figure}[t!]
-	\includegraphics[width=.46\textwidth]{fig/sampling_efficiency/levelset}
-	\caption{2DoF - 4D. TODO:Time per sample vs informed set}
+    \centering
+	\includegraphics[width=.3\textwidth]{fig/sampling_efficiency/levelset}
+	\caption{\captionstyle The informed set volume ratio decrease as $ c_{best} $ decreases in the planning process in different dimensions.}
 	\label{fig:sampling_efficiency:levelset}
@@
 	\centering
-
-	%\begin{subfigure}[b]{0.48\linewidth}
-	%	\includegraphics[width=\linewidth]{fig/sampling_efficiency/levelset_6d}
-	%	\caption{6DoF - 12D. TODO:Time per sample vs informed set}
-	%	\label{fig:sampling_efficiency:6d}
-	%\end{subfigure}
-
 	\begin{subfigure}[b]{\linewidth}
@@
 		\includegraphics[width=.85\linewidth]{fig/sampling_efficiency/sample_efficiency_2d}
-		\caption{2DoF - 4D TODO: rescale x axis}
+		\caption{\captionstyle 4-dimension sampling space.}
 		\label{fig:sampling_efficiency:2d}
 	\end{subfigure}
-% 	\begin{subfigure}[b]{0.32\textwidth}
-% 		\includegraphics[width=\linewidth]{fig/sampling_efficiency/sample_efficiency_3d}
-% 		\caption{3DoF - 6D}
-% 		\label{fig:sampling_efficiency:3d}
-% 	\end{subfigure}	
 	\begin{subfigure}[b]{\linewidth}
@@
 		\includegraphics[width=.85\linewidth]{fig/sampling_efficiency/sample_efficiency_6d}
-		\caption{6DoF - 12D. TODO: rescale x axis}
+		\caption{\captionstyle 12-dimension sampling space.}
 		\label{fig:sampling_efficiency:6d}
 	\end{subfigure}
-	\caption{\captionstyle Sampling efficiency of different sampling methods}
+	\caption{\captionstyle Average sampling time vs informed set volume ratio of four samplers (RS, HRS, MH and HNR) in state spaces of different dimensions. 
+	The X axis is the ratio of informed set volume to the entire sampling space.
+	The Y axis is the average time per sample.}
 	\label{fig:sampling_efficiency}
 \end{figure}
-
-%\dy{going to change the tick labels so this below sentence will be replaced}
-It is noticeable that both x axis and y axis are converted by $ \log_{10} () $ in Figure~\ref{fig:sampling_efficiency:2d} and Figure~\ref{fig:sampling_efficiency:6d}.
-This reserves the linearity of the data from rejection sampler, but also scales the difference in a smaller range for comparison.
-Keep in mind that the differences in unit (ms) are much bigger.
 
@@
 The best covariance $ \Sigma $ that generates faster convergence differs with problem setting.
-A small covariance tends to generate more samples near around previous samples, which a large covariance has better exploration but is more likely to drive a Markov chain outside of an informed set.
+A small covariance tends to generate more samples near previous samples, while a large covariance has better exploration but is more likely to drive a markov chain outside the informed set.
 In our next planning experiment setting, we use the same covariance for different problems.
 
-When informed set volume ratio is relatively high, it is easy to generate qualified samples.
+When informed set volume ratio is relatively high, it is easy to generate samples in the informed set.
 All the samplers have close performances.
-It actually implies rejection sampler is the best because of its simplicity in implementation.
-The sampling time of other three samplers all increase as problems get harder.
-But we can see the trend that HRS's advantage over RS is more significant , also the same for HNR's advantage over HRS.
-Moving from a 4 dimension problem in Figure \ref{fig:sampling_efficiency:2d} to a 12 dimension problem in Figure \ref{fig:sampling_efficiency:6d}, sampling in an informed set becomes even harder,
-because the informed set volume ratio becomes smaller.
-HNR and MH samplers show much better efficiency over the others.
+It actually implies rejection sampler is the best because of its simplicity in implementation and minimum correlation between successive samples.
+The sampling time of all samplers except MH, increases as problems gets harder.
+Notice that the sampling efficiency of HNR scales better than HRS and HRS is scales than RS.
+Moving from a 4 dimension problem in Figure \ref{fig:sampling_efficiency:2d} to a 12 dimension problem in Figure \ref{fig:sampling_efficiency:6d}, sampling in an informed set becomes even harder, because the informed set volume ratio becomes smaller.
+Here, HNR and MH samplers show much better efficiency over the others.
 
-We want to point out that efficiently sampling in an informed set is not sufficient for determining the quality of a sampler.
+We want to point out that efficiently sampling in an informed set is not sufficient for determining the performance of a sampler.
 For example, a sampler that constantly returns the same sample in a informed set might show the best sampling efficiency, however it is the worst sampler in a path planning problem.
-\dy{is the property that any state in a set has a chance to be sampled?}
-We hope sampler (satisfies some properties ?) that a resulting planner is asymptotically optimal.
-
-\os{Explain why MCMC is flat, mention strawman approach}
-
-\dy{do we want to say that it is hard to compare the uniformity in high dimension space}
+%\dy{is the property that any state in a set has a chance to be sampled?}
+%We hope sampler (satisfies some properties ?) that a resulting planner is asymptotically optimal.
+Ideally, we want generated samples to be uniformly distributed in an informed set to get the best exploration.
+%\os{Explain why MCMC is flat, mention strawman approach}
+%\dy{do we want to say that it is hard to compare the uniformity in high dimension space}
 
@@
 	\item It shall converge faster in finding the optimal solution.
-	Because sampling in an informed set is gradually becoming as new better solution reduces $ c_{best} $ which reduces the informed set volume ratio significantly.
-	\item It shall adapt better in problems defined in high dimension state space.
+	Sampling in an informed set is gradually becoming harder as new better solution reduces $ c_{best} $ which reduces the informed set volume ratio.
+	\item Its performance should not degrade significantly in high dimensional problems.
 	As shown in Figure \ref{fig:sampling_efficiency:levelset}, the informed set volume ratio decrease more significantly in a high-dimension state space.
-	The advantage of an informed sampler becomes more important.
+	The advantage of a good informed sampler becomes evident.
 \end{itemize}
 
-To evaluate how the samplers impact the planning efficiency, we run the samplers with the informed RRT* planner~\cite{GSB14} on three different problems described below and shown in Fig.
+To evaluate the planning efficiency of the samplers, we run them with the informed RRT* planner~\cite{GSB14} in position-velocity space with MTDI as steering function, on three different problems described below and shown in Fig.
 \ref{fig:problems}.
 For each problem the start and goal states (positions and velocities) are known in the joint space.
-\dy{TODO: Make table for limits and add units}
-\subsubsection{Problem 1: 3 DoF Planar Manipulator}
+Joint velocities at start and goal are calculated from desired end-effector velocities using inverse kinematics before starting the planning.
+Table \ref{tab:params} shows the parameters used in the problems.
 
-Problem 1 is a 3 DoF manipulator that moves on a plane, which results in a 6 dimension space.
-The position boundary of each join is $ [ - \pi , \pi ] $, the velocity boundary is $ [-10, 10] $, and the acceleration is $ [-1,1] $.
-Figure~\ref{fig:planning_efficiency:3dof:example} shows a few steps of a planned path.
+\begin {table}[H]
+\caption {Parameters for the problems} \label{tab:params} 
+\begin{center}
+	\begin{tabular}{c c c c c} 
+\toprule
+\multicolumn{2}{c}{Problem} & Position  & Velocity & $|acc_{max}|$ \\ [0.5ex] 
+    &    &    $rad$       &  $rad/sec$    &  $rad/sec^2$ \\
+\midrule
+\multicolumn{2}{c}{3DoF Arm} & $[-\pi, \pi]$ & [-10, 10] & 1 \\ 
+\midrule
+\multicolumn{2}{c}{6DoF SnakeArm} & $[-\pi, \pi]$ & [-10, 10] & 1 \\
+\midrule
+\multirow{7}{*}{7DoF arm} & 1st & [0.541593 , 5.74159] & [-0.75, 0.75] & \multirow{7}{*}{1} \\
+\cmidrule{2-4}            & 2nd &  [-2 , 2]            & [-0.75, 0.75]  &  \\
+\cmidrule{2-4}            & 3rd & [-2.8, 2.8]          & [-2, 2] &  \\
+\cmidrule{2-4}            & 4th & [-0.9, 3.1]          & [-2.5, 2.5] &  \\
+\cmidrule{2-4}            & 5th & [-4.76, 1.24]        & [-2.5, 2.5] &  \\
+\cmidrule{2-4}            & 6th & [-1.6, 1.6]          & [-2.5, 2.5] &  \\
+\cmidrule{2-4}            & 7th & [-3, 3]              & [-2.5, 2.5] &  \\
+\bottomrule
+\end{tabular}
+\end{center}
+\end{table}
+\vspace{-2pt}
 
-\subsubsection{Problem 2: 6 DoF Snake Arm}
+\subsubsection{Problem 1: 6 Dimension - 3 DoF Planar Manipulator}
 
-Problem 2 is a 6 DoF snake arm that moves in a 3D workspace, which results in a 12 dimension space.
-The position boundary of each join is $ [ - \pi , \pi ] $, the velocity boundary is $ [-10, 10] $, and the acceleration is $ [-1,1] $.
-Figure~\ref{fig:planning_efficiency:6dof:example} shows a few steps of a planned path.
+The start and the goal states have zero velocities.
+%The position boundary of each join is $ [ - \pi , \pi ] $, the velocity boundary is $ [-10, 10] $, and the acceleration is $ [-1,1] $.
+Figure~\ref{fig:planning_efficiency:3dof:example} shows the planned path.
 
-\subsubsection{Problem 3: 7 DoF HERB}
+\subsubsection{Problem 2: 12 Dimension - 6 DoF Snake Arm}
 
-Problem 3 is a 7 DoF Barrett WAM arm of HERB that moves in a 3D workspace, which results in a 14 dimension space.
-The position boundaries of 7 joints of the arm are $  [0.541593 , 5.74159] $, $  [-2 , 2] $, $ [-2.8 , 2.8] $, $ [-0.9 , 3.1] $, $ [-4.76 , 1.24] $, $ [-1.6 , 1.6] $ and $ [-3 , 3] $.
-The velocity boundary of 7 joints of the arm are $ [-0.75 , 0.75] $, $ [-0.75 , 0.75] $, $ [-2 , 2] $, $ [-2 , 2] $, $ [-2.5 , 2.5] $, $ [-2.5 , 2.5] $ and $ [-2.5 , 2.5] $.
-The accelerations of all the joints are set to $ [-1,1] $.
+The objective is to hammer the end-effector into the wall while starting with zero velocity.
+%The position boundary of each join is $[-\pi,\pi]$, the velocity boundary is $[-10,10]$, and the acceleration is $[-1,1]$.
+Figure~\ref{fig:planning_efficiency:6dof:example} shows the planned path.
+
+\subsubsection{Problem 3: 14 Dimension - 7 DoF WAM Arm}
+
+%The position boundaries of 7 joints of the arm are $  [0.541593 , 5.74159] $, $  [-2 , 2] $, $ [-2.8 , 2.8] $, $ [-0.9 , 3.1] $, $ [-4.76 , 1.24] $, $ [-1.6 , 1.6] $ and $ [-3 , 3] $.
+%The velocity boundary of 7 joints of the arm are $ [-0.75 , 0.75] $, $ [-0.75 , 0.75] $, $ [-2 , 2] $, $ [-2 , 2] $, $ [-2.5 , 2.5] $, $ [-2.5 , 2.5] $ and $ [-2.5 , 2.5] $.
+%The accelerations of all the joints are set to $ [-1,1] $.
+The objective is to quickly swing away a glass on a table using the right arm.
 Figure~\ref{fig:planning_efficiency:herb:example} shows a few steps of a planned path.
@@
 		\includegraphics[height=2.45cm]{fig/planning_efficiency/3dof_5}
-		\caption{3DOF planar}
+		\caption{\captionstyle Problem 1 : 3DOF planar arm move from a start to a goal while starting and ending with zero velocities.}
+		\vspace{6pt}
 		\label{fig:planning_efficiency:3dof:example}
@@
 		\includegraphics[height=3cm]{fig/planning_efficiency/6dof_5}
-		\caption{6DOF snake}
+		\caption{\captionstyle Problem 2 : 6DOF snake hammers the end-effector into the wall while starting with zero velocity.}
+		\vspace{6pt}
 		\label{fig:planning_efficiency:6dof:example}
@@
     \includegraphics[height=2.7cm]{fig/planning_efficiency/herb_batting_5}
-	\caption{HERB}
+	\caption{Problem 3 : HERB sweeps a cup on a table, in which the right arm starts with zero velocity and ends with non-zero velocity.}
 	\label{fig:planning_efficiency:herb:example}
 	\end{subfigure}
-	\caption{Test problems to evaluate planning efficiency. TODO: Add herb and update figures}
+	\caption{\captionstyle Three problems are used to evaluate planning efficiency.
+	These problems are defined in state spaces with different dimensions and different kinodynamics.}
 	\label{fig:problems}
@@
 	\centering
-	\begin{subfigure}[b]{0.32\textwidth}
+	\begin{subfigure}[b]{0.325\textwidth}
 		\includegraphics[width=\linewidth]{fig/planning_efficiency/3dof_general}
-		\caption{\captionstyle Planning Efficiency for Problem 1: 3 DoF Manipulator}
+		\caption{\captionstyle Problem 1 - 6 Dimensions.}
 		\label{fig:planning_efficiency:3dof:general}
 	\end{subfigure}	
-	\begin{subfigure}[b]{0.32\textwidth}
+	\begin{subfigure}[b]{0.325\textwidth}
 		\includegraphics[width=\linewidth]{fig/planning_efficiency/6dof_hammering}
-		\caption{\captionstyle Planning Efficiency for Problem 2: 6DoF Hammering Task}
+		\caption{\captionstyle Problem 2 - 12 Dimensions.}
 		\label{fig:planning_efficiency:6dof:hammering}
 	\end{subfigure}
-	\begin{subfigure}[b]{0.32\textwidth}
+	\begin{subfigure}[b]{0.325\textwidth}
 	\includegraphics[width=\linewidth]{fig/planning_efficiency/herb_batting_efficiency}
-	\caption{\captionstyle Planning Efficiency for Problem 3: 7DoF HERB Batting Task}
+	\caption{\captionstyle Problem 3 - 14 Dimensions.}
 	\label{fig:planning_efficiency:herb:batting}
     \end{subfigure}
-	\caption{Planning Efficiency}
+	\caption{\captionstyle Planning Efficiency of four different samplers (RS, HRS, MH and HNR) in three problems. 
+	The X axis is the planning time. 
+	The Y axis is the ration of the current best and the optimal $ c_{best} / c^*_{best} $.}
 	\label{fig:planning_efficiency}
@@
 
-\dy{TODO: add a plot that shows the increases of samples?}
+%\dy{TODO: add a plot that shows the increases of samples?}
 
-MH shows the worst performance in Figure~\ref{fig:planning_efficiency:3dof:general}, \ref{fig:planning_efficiency:6dof:hammering} and \ref{fig:planning_efficiency:herb:batting}.
-Though theoretically samples converge to a target distribution, the samples could be either too correlated for exploration purpose in planning.
-If the variance of transition distribution is too high, it will then move out of the informed set too frequently, and takes longer to converge.
-Ideally we want to have markov chains are less correlated but moves in informed sets.
+As shown in in Figure~\ref{fig:planning_efficiency}, MH has the worst performance in all three problems, especially when the dimension increases.
+Though theoretically samples converge to a target distribution only in the limit of infinite time.
+However, in practice the samples are to close to each other and don't explore the entire informed space.
+If the variance of transition distribution is too high, it will tend to move out of the informed set too frequently, and takes longer to converge as the rejection rate is too high.
 
-HNR shows close performance with RS and HRS in a 6-dimension space, as in Figure~\ref{fig:planning_efficiency:3dof:general}.
-But in higher dimension performance, the advantage of HNR in planning efficiency is shown.
-In Figure~\ref{fig:planning_efficiency:6dof:hammering} and \ref{fig:planning_efficiency:herb:batting}, the cost of current best solution by planners with HNR sampler converge significantly faster.
-It shows that HNR will have close performance with RS and HRS in simple problem, as in Figure \ref{fig:planning_efficiency:3dof:general}.
-But when the dimensions of problems increase, HNR shows better and steady performance.
-HNR also shows faster convergence to the optimal trajectory, because it is better at adapting the informed set update in planning process.
+HNR shows close performance with RS and HRS in a 6-dimension problem, as in Figure~\ref{fig:planning_efficiency:3dof:general}. 
+As shown in Figure~\ref{fig:planning_efficiency:6dof:hammering} and \ref{fig:planning_efficiency:herb:batting}, the advantages of HNR are clearly evident in higher dimensional problems.
+The cost of best solutions generated by planner with HNR sampler converges significantly faster to a cheaper to trajectory compared to others.
 

### 2017-09-15 paper.tex
sync

@@
   \centering
-  	\includegraphics[trim={4.5cm 0 4cm 2cm},clip,height = 5.25cm ]{fig/alg.pdf}
+%  	\includegraphics[trim={4.5cm 0 4cm 2cm},clip,height = 5.25cm ]{fig/alg.pdf}
+  	\includegraphics[width=0.75\linewidth ]{fig/alg.pdf}
   \caption{
@@
 
-The idea behind applying MCMC for informed sampling is to define a target distribution~$ \pi $ as a uniform distribution over all points in~$ \Cinf $.
+The idea behind applying MCMC for informed sampling is to define a target distribution~$ \pi $ that has $p(x_{sample}\in\Cinf) \ne 0 ~\&~ p(x_{sample})\notin\Cinf = 0$. 
+This is specially useful if we want to bias the samples based on our knowledge of the environment.
+However, we make no such assumption about the environment and use a uniform distribution over all points in~$ \Cinf $. 
 Our approach consists of two stages,
@@
 \end{enumerate}
-Our algorithm is described in Alg.~\ref{alg:mcmc_informed_sampling} and visualized in Fig.~\ref{fig:alg}.
+Our framework is described in Alg.~\ref{alg:mcmc_informed_sampling} and visualized in Fig.~\ref{fig:alg}.
 We now continue to detail each of the algorithm's stages.
@@
 	\end{algorithmic}
-	\caption{Metropolis-Hastings MCMC $(x_{i-1}, c_{\text{best}})$}
+	\caption{\captionstyle Metropolis-Hastings MCMC $(x_{i-1}, c_{\text{best}})$}
 	\label{alg:mh_mcmc}	
@@
 	\end{algorithmic}
-	\caption{Hit-And-Run MCMC $(x_{i-1}, c_{\text{best}})$}
+	\caption{\captionstyle Hit-And-Run MCMC $(x_{i-1}, c_{\text{best}})$}
 	\label{alg:hit_and_run_mcmc}	
@@
 We want to point out that a Hit-and-Run sampler only requires that a Markov chain starts in an informed set, and will not produce a sample outside of the informed set.
+Also, in our implementation, we pick the start or the goal state to find $ x_0 \in \Cinf $ as the start of a Markov chain.
 
@@
 		\centering
-		\includegraphics[width=.85\linewidth]{fig/sampling_efficiency/sample_efficiency_2d}
+		\includegraphics[width=.70\linewidth]{fig/sampling_efficiency/sample_efficiency_2d}
 		\caption{\captionstyle 4-dimension sampling space.}
@@
 		\centering
-		\includegraphics[width=.85\linewidth]{fig/sampling_efficiency/sample_efficiency_6d}
+		\includegraphics[width=.70\linewidth]{fig/sampling_efficiency/sample_efficiency_6d}
 		\caption{\captionstyle 12-dimension sampling space.}
@@
 \begin {table}[H]
-\caption {Parameters for the problems} \label{tab:params} 
+\caption {\captionstyle Parameters for the problems} \label{tab:params} 
 \begin{center}

### 2017-09-15 code/sample efficiency/2d/plot1.m
new code

@@ -1,3 +1,7 @@
+% Computer Modern Font
+set(0,'DefaultTextFontname', 'CMU Serif')
+set(0,'DefaultAxesFontName', 'CMU Serif')
+
 data = sortrows(dim2, 5);
 
 %data(:,1) = log(data(:,1));

### 2017-09-15 code/sample efficiency/6d/plot1.m

@@ -1,3 +1,6 @@
+set(0,'DefaultTextFontname', 'Times New Roman')
+set(0,'DefaultAxesFontName', 'Times New Roman')
+
 data = sortrows(dim6, 5);
 
 %data(:,1) = log(data(:,1));
@@ -34,7 +37,7 @@ end
 
 
 xlabel('informed set volume ratio');
-ylabel('time per sample - (ms)');
+ylabel('time per sample (ms)');
 lgd = legend([h1, h2, h3, h4], {'RS', 'HRS', 'MH', 'HNR'});
 lgd.FontSize = 16;
 set(gca, 'XTick', [-5 -4 -3 -2 -1]);

### 2017-09-15 code/sample efficiency/6d/plot1new.m

@@ -1,0 +1,68 @@
+set(0,'DefaultTextFontname', 'Times New Roman')
+set(0,'DefaultAxesFontName', 'Times New Roman')
+
+data = sortrows(dim6, 5);
+
+%data(:,1) = log(data(:,1));
+%data(:,2) = log(data(:,2));
+%data(:,3) = log(data(:,3));
+%data(:,4) = log(data(:,4));
+
+green = [49,163,84]/255;
+red = [222 45 38]/255;
+blue = [49,130,189]/255;
+orange = [230,85,13]/255;
+purple = [117,107,177]/255;
+pink = [197,27,138]/255;
+
+
+figure(1);
+X = logspace(-1,2);
+Y = exp(X);
+hold on;
+loglog(X, Y, '-s');
+hold off;
+grid on;
+
+
+volumeRatio = data(:,5);
+RSTime = data(:,4)./data(:,6);
+HRSTime = data(:,2)./data(:,6);
+MHTime = data(:,2)./data(:,6);
+HNRTime = data(:,3)./data(:,6);
+
+
+figure(2);
+%hold on;
+marker_size = 4;
+
+loglog(volumeRatio, RSTime, 'Color', red);
+
+%h1 = loglog(data(:,5),data(:,4)./data(:,6), 'MarkerSize', marker_size, 'MarkerFaceColor', blue, 'MarkerEdgeColor', blue, 'Marker', 's');
+%h2 = loglog(data(:,5),data(:,2)./data(:,6), 'MarkerSize', marker_size, 'MarkerFaceColor', red, 'MarkerEdgeColor', red, 'Marker', 'd');
+%h3 = loglog(data(:,5),data(:,2)./data(:,6), 'MarkerSize', marker_size, 'MarkerFaceColor', green, 'MarkerEdgeColor', green, 'Marker', 'h');
+%h4 = loglog(data(:,5),data(:,3)./data(:,6), 'MarkerSize', marker_size, 'MarkerFaceColor', purple, 'MarkerEdgeColor', purple, 'Marker', 'o');
+%plot(log10(data(:,5)),log10(data(:,4)./data(:,6)), 'color', blue, 'linewidth', 1);
+%plot(log10(data(:,5)),log10(data(:,2)./data(:,6)), 'color', red, 'linewidth', 1);
[…]

### 2017-09-15 code/sample efficiency/2d/plot1new.m
new plot

@@ -1,7 +1,7 @@
 set(0,'DefaultTextFontname', 'Times New Roman')
 set(0,'DefaultAxesFontName', 'Times New Roman')
 
-data = sortrows(dim6, 5);
+data = sortrows(dim2, 5);
 
 %data(:,1) = log(data(:,1));
 %data(:,2) = log(data(:,2));

### 2017-09-16 paper.tex
update new plot

@@
 
-Given a trajectory $\gamma_{\text{best}}$ with cost $c_{\text{best}} = c(\gamma_{\text{best}})$ the \emph{informed set}~\Cinf is defined to be all states $x$  which may be on trajectories with lower cost than $c_{\text{best}}$.
+Given a trajectory $\gamma_{\rm best}$ with cost $\cbest = c(\gamma_{\rm best})$ the \emph{informed set}~\Cinf is defined to be all states $x$  which may be on trajectories with lower cost than $\cbest$.
 Specifically,
@@
 Recall that for Euclidean spaces minimizing path length, the informed set~\Cinf is a prolate hyperspheroid~\cite{GSB14}.
-Moreover, the size and shape of the hyperspheroid is defined only be the cost $c_{\text{best}}$ of the current best solution and not by the location of the start~$x_s$ and goal~$x_g$.
+Moreover, the size and shape of the hyperspheroid is defined only be the cost $\cbest$ of the current best solution and not by the location of the start~$x_s$ and goal~$x_g$.
 
@@
 Specifically, we have that 
-(i)~the structure of~\Cinf changes not only with~$c_{\text{best}}$ but also according to the specific values of~$x_s$ and~$x_g$ 
+(i)~the structure of~\Cinf changes not only with~$\cbest$ but also according to the specific values of~$x_s$ and~$x_g$ 
 and that
@@
 It is straightforward to see that both the type and the amount of acceleration applied (and hence the structure of~\Cinf) depend on the specific values of~$x_s$ and~$x_g$. 
-%Fig~\ref{fig:informed_sets} depicts two informed sets defined using the same cost~$c_{\text{best}}$ but different start and goal states. Notice the difference in structure of~\Cinf. 
+%Fig~\ref{fig:informed_sets} depicts two informed sets defined using the same cost~$\cbest$ but different start and goal states. Notice the difference in structure of~\Cinf. 
 Fig~\ref{fig:discont} depicts a simple example where the cost map is discontinuous.
@@
 
-In this section we describe our approach to efficiently produce new samples in an informed set~\Cinf given a specific cost~$c_{\text{best}}$ of trajectory $\gamma_{best}(t)$.
+In this section we describe our approach to efficiently produce new samples in an informed set~\Cinf given a specific cost~$\cbest$ of trajectory $\gamma_{\rm best}(t)$.
 The samples follow a Markov Chain Monte Carlo, in which a new sample candidate is produced from a previous sample that also lies in the same informed set.
 %However, this sample depends on the previous iterations of the algorithm which is why we describe it as a method to produce a sequence of samples.
-Furthermore, the value~$c_{\text{best}}$ can decrease between consecutive iterations in the planning process of an informed RRT* planner.
-This will occur if the search algorithm that uses the sampler finds a path to the goal whose cost is lower than~$c_{\text{best}}$.
+Furthermore, the value~$\cbest$ can decrease between consecutive iterations in the planning process of an informed RRT* planner.
+This will occur if the search algorithm that uses the sampler finds a path to the goal whose cost is lower than~$\cbest$.
 
@@
 	\item sampling a new sample $ x_i \in \Cinf $ given a previous sample $ x_{i-1} $. 
-	This is implemented using the function $\texttt{MCMC\_sample} (x_{i-1}, c_{\text{best}})$.
+	This is implemented using the function $\texttt{MCMC\_sample} (x_{i-1}, \cbest)$.
 \end{enumerate}
@@
 At the beginning of a Markov chain, \texttt{sample\_in\_informed\_space}() is called to generate the first sample in an informed set.
-\texttt{MCMC\_sample}() is called to generate a new sample based on a previous sample $ x_{i-1} $ and a cost $ c_{best} $ that defines an informed set.
+\texttt{MCMC\_sample}() is called to generate a new sample based on a previous sample $ x_{i-1} $ and a cost $ \cbest $ that defines an informed set.
 We demonstrate how to instantiate it with two different algorithms \emph{Metropolis-Hastings} and \emph{Hit-and-Run}, which will be described in later subsections.
@@
 		\ENDIF
-		\STATE $x_{i} \leftarrow \texttt{MCMC\_sample} (x_{i-1}, c_{\text{best}})$ 
+		\STATE $x_{i} \leftarrow \texttt{MCMC\_sample} (x_{i-1}, \cbest)$ 
 		\IF{ $ x_{i} \not\in \Cinf $ }
@@
 	\end{algorithmic}
-	\caption{\captionstyle MCMC-based Informed Sampling $( x_{i-1}, c_{\text{best}})$}
+	\caption{\captionstyle MCMC-based Informed Sampling $( x_{i-1}, \cbest)$}
 	\label{alg:mcmc_informed_sampling}	
@@
 	\end{algorithmic}
-	\caption{\captionstyle Metropolis-Hastings MCMC $(x_{i-1}, c_{\text{best}})$}
+	\caption{\captionstyle Metropolis-Hastings MCMC $(x_{i-1}, \cbest)$}
 	\label{alg:mh_mcmc}	
@@
 
-		\IF{ \textsc{Cost}($ x_{i} $) $ < c_{\text{best}} $ }
+		\IF{ \textsc{Cost}($ x_{i} $) $ < \cbest $ }
 		\RETURN $ x_{i}$
@@
 	\end{algorithmic}
-	\caption{\captionstyle Hit-And-Run MCMC $(x_{i-1}, c_{\text{best}})$}
+	\caption{\captionstyle Hit-And-Run MCMC $(x_{i-1}, \cbest)$}
 	\label{alg:hit_and_run_mcmc}	
@@
 
-Figure \ref{fig:sampling_efficiency:levelset} shows how the informed set volume ratio decreases as the informed set cost $ c_{best} $ becomes smaller in problems of different dimensions.
-In higher dimensions, the informed set volume ratio decreases much more quickly with decrease in the informed set cost $ c_{best} $, as new cheaper trajectories are found in the planning process.
+Figure \ref{fig:sampling_efficiency:levelset} shows how the informed set volume ratio decreases as the informed set cost $ \cbest $ becomes smaller in problems of different dimensions.
+In higher dimensions, the informed set volume ratio decreases much more quickly with decrease in the informed set cost $ \cbest $, as new cheaper trajectories are found in the planning process.
 
@@
 
-\begin{figure}[t!]
+\begin{figure*}[t!]
 	\centering
-	\includegraphics[width=.3\textwidth]{fig/sampling_efficiency/levelset}
-	\caption{\captionstyle The informed set volume ratio decrease as $ c_{best} $ decreases in the planning process in different dimensions.}
+	\begin{subfigure}[t!]{0.325\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{fig/sampling_efficiency/levelset}
+		\caption{\captionstyle The informed set volume ratio decrease as $ \cbest $ decreases in the planning process in different dimensions.}
 		\label{fig:sampling_efficiency:levelset}
-\end{figure}
-
-\begin{figure}[t!]
+	\end{subfigure}
+	\begin{subfigure}[t!]{0.325\textwidth}
 		\centering
-	\begin{subfigure}[b]{\linewidth}
-		\centering
-		\includegraphics[width=.70\linewidth]{fig/sampling_efficiency/sample_efficiency_2d}
+		\includegraphics[width=\linewidth]{fig/sampling_efficiency/sample_efficiency_2d}
 		\caption{\captionstyle 4-dimension sampling space.}
@@
 	\end{subfigure}
-	\begin{subfigure}[b]{\linewidth}
+	\begin{subfigure}[t!]{0.325\textwidth}
 		\centering
-		\includegraphics[width=.70\linewidth]{fig/sampling_efficiency/sample_efficiency_6d}
+		\includegraphics[width=\linewidth]{fig/sampling_efficiency/sample_efficiency_6d}
 		\caption{\captionstyle 12-dimension sampling space.}
@@
 	\label{fig:sampling_efficiency}
-\end{figure}
+\end{figure*}
 
@@
 	\item It shall converge faster in finding the optimal solution.
-	Sampling in an informed set is gradually becoming harder as new better solution reduces $ c_{best} $ which reduces the informed set volume ratio.
+	Sampling in an informed set is gradually becoming harder as new better solution reduces $ \cbest $ which reduces the informed set volume ratio.
 	\item Its performance should not degrade significantly in high dimensional problems.
@@
 	The X axis is the planning time. 
-	The Y axis is the ration of the current best and the optimal $ c_{best} / c^*_{best} $.}
+	The Y axis is the ration of the current best and the optimal $ \cbest / c^*_{\rm best} $.}
 	\label{fig:planning_efficiency}

### 2017-09-16 code/motivation/plotdata.m

@@ -1,3 +1,5 @@
+set(0,'DefaultTextFontname', 'Times New Roman')
+set(0,'DefaultAxesFontName', 'Times New Roman')
 
 fastX = [1:1:45]';
 slowX = [1:1:14]';
@@ -9,42 +11,7 @@ orange = [230,85,13]/255;
 purple = [117,107,177]/255;
 pink = [197,27,138]/255;
 
-%{
-figure(1);
-hold on;
-plot(fastX, fastpath(:,9)/1.5,'-', 'linewidth', 2, 'color', green);
-plot(fastX, fastpath(:,11)/4,'-', 'linewidth', 2, 'color',red);
-plot(fastX, fastpath(:,13)/5,'-', 'linewidth', 2, 'color', blue);
-
-plot(fastX, fastpath(:,2), '--', 'linewidth', 2, 'color', orange);
-plot(fastX, fastpath(:,4), '--', 'linewidth', 2, 'color', purple);
-plot(fastX, fastpath(:,6), '--', 'linewidth', 2,'color',pink);
-
-xlim([1,45]);
-legend('DoF2', 'DoF4', 'DoF6', 'Vel2', 'Vel4', 'Vel6');
-xlabel('Time step');
-ylabel('Value');
-hold off;
-
-
-figure(2);
-hold on;
-plot(slowX, slowpath(:,9)/1.5, '-', 'linewidth', 2, 'color', green);
-plot(slowX, slowpath(:,11)/4, '-', 'linewidth', 2, 'color',red);
-plot(slowX, slowpath(:,13)/5, '-', 'linewidth', 2, 'color',blue);
-
-plot(slowX, slowpath(:,2), '--', 'linewidth', 2, 'color',orange);
-plot(slowX, slowpath(:,4), '--', 'linewidth', 2, 'color',purple);
-plot(slowX, slowpath(:,6), '--', 'linewidth', 2, 'color',pink);
-hold off;
-
-xlim([1,14]);
-legend('DoF2', 'DoF4', 'DoF6', 'Vel2', 'Vel4', 'Vel6');
-xlabel('Time step');
-ylabel('Value');
-%}
-
-figure(3);
+fig = figure(3);
 
 step = 6;rMag = 0.1;
 fastNum = size(fastpath,1);
@@ -68,15 +35,80 @@ for i = 1:1:slowQuiverNum
     slowP(i,1) = (slowpath(i*step+1,2) - slowpath(i*step,2)) * rMag;
[…]

### 2017-09-16 code/planning efficiency/6dof_snake/Hammer/plot_data2.m

@@ -1,4 +1,7 @@
-figure(100);
+set(0,'DefaultTextFontname', 'Times New Roman');
+set(0,'DefaultAxesFontName', 'Times New Roman');
+
+fig = figure(100);
 hold on;
 
 %HMC2 = log(HMC1);
@@ -18,21 +21,35 @@ RS2 = RS1;
 HRS2 = HRS1;
 HNR2 = HNR1;
 
-errorbar(T2, mean(RS2,1), std(RS2), 'color', blue, 'LineWidth',2);
-errorbar(T3, mean(HRS2,1), std(HRS2), 'color', red, 'LineWidth',2);
-errorbar(T1, mean(MCMC2,1), std(MCMC2), 'color', green, 'LineWidth',2);
-errorbar(T4, mean(HNR2,1), std(HNR2), 'color', purple, 'LineWidth',2);
+RSColor = [92, 121, 157]/255.; %[69,117,180]/255.;
+HRSColor = [113, 174, 111]/255.; %[102,189,99]/255.;
+MCMCColor = [219, 176, 132]/255.; %[253,174,97]/255.;
+HNRColor = [243, 90, 83]/255.; %[215,48,39]/255.;
+
+e1 = errorbar(T2, mean(RS2,1), std(RS2), 'color', RSColor, 'LineWidth',2);
+e2 = errorbar(T3, mean(HRS2,1), std(HRS2), 'color', HRSColor, 'LineWidth',2);
+e3 = errorbar(T1, mean(MCMC2,1), std(MCMC2), 'color', MCMCColor, 'LineWidth',2);
+e4 = errorbar(T4, mean(HNR2,1), std(HNR2), 'color', HNRColor, 'LineWidth',2);
 
 
-plot(T2, mean(RS2,1), 'o', 'MarkerFaceColor', blue, 'MarkerEdgeColor', blue, 'MarkerSize', 4);
-plot(T3, mean(HRS2,1), 'o', 'MarkerFaceColor', red, 'MarkerEdgeColor', red, 'MarkerSize', 4);
-plot(T1, mean(MCMC2,1), 'o', 'MarkerFaceColor', green, 'MarkerEdgeColor', green, 'MarkerSize', 4);
-plot(T4, mean(HNR2,1), 'o', 'MarkerFaceColor', purple, 'MarkerEdgeColor', purple, 'MarkerSize', 4);
[…]

### 2017-09-16 code/planning efficiency/herb/batting/merge_planning_data2.m

@@ -21,7 +21,7 @@ end
 maxT = max(maxtimes);
 minVal = min(minvals);
 
-stepNum = 20;
+stepNum = 10;
 MCMC1 = zeros(datasetSize, stepNum+1);
 RS1 = zeros(datasetSize, stepNum+1);
 HRS1 = zeros(datasetSize, stepNum+1);

### 2017-09-16 code/planning efficiency/herb/batting/plot_data2.m

@@ -1,4 +1,7 @@
-figure(100);
+set(0,'DefaultTextFontname', 'Times New Roman');
+set(0,'DefaultAxesFontName', 'Times New Roman');
+
+fig = figure(100);
 hold on;
 
 %HMC2 = log(HMC1);
@@ -18,21 +21,35 @@ RS2 = RS1;
 HRS2 = HRS1;
 HNR2 = HNR1;
 
-errorbar(T2, mean(RS2,1), std(RS2), 'color', blue, 'LineWidth',2);
-errorbar(T3, mean(HRS2,1), std(HRS2), 'color', red, 'LineWidth',2);
-errorbar(T1, mean(MCMC2,1), std(MCMC2), 'color', green, 'LineWidth',2);
-errorbar(T4, mean(HNR2,1), std(HNR2), 'color', purple, 'LineWidth',2);
+RSColor = [92, 121, 157]/255.; %[69,117,180]/255.;
+HRSColor = [113, 174, 111]/255.; %[102,189,99]/255.;
+MCMCColor = [219, 176, 132]/255.; %[253,174,97]/255.;
+HNRColor = [243, 90, 83]/255.; %[215,48,39]/255.;
+
+e1 = errorbar(T2, mean(RS2,1), std(RS2), 'color', RSColor, 'LineWidth',2);
+e2 = errorbar(T3, mean(HRS2,1), std(HRS2), 'color', HRSColor, 'LineWidth',2);
+e3 = errorbar(T1, mean(MCMC2,1), std(MCMC2), 'color', MCMCColor, 'LineWidth',2);
+e4 = errorbar(T4, mean(HNR2,1), std(HNR2), 'color', HNRColor, 'LineWidth',2);
 
 
-plot(T2, mean(RS2,1), 'o', 'MarkerFaceColor', blue, 'MarkerEdgeColor', blue, 'MarkerSize', 4);
-plot(T3, mean(HRS2,1), 'o', 'MarkerFaceColor', red, 'MarkerEdgeColor', red, 'MarkerSize', 4);
-plot(T1, mean(MCMC2,1), 'o', 'MarkerFaceColor', green, 'MarkerEdgeColor', green, 'MarkerSize', 4);
-plot(T4, mean(HNR2,1), 'o', 'MarkerFaceColor', purple, 'MarkerEdgeColor', purple, 'MarkerSize', 4);
[…]

### 2017-09-16 code/planning efficiency/planar_manipulator/general/plot_data2.m

@@ -1,4 +1,7 @@
-figure(100);
+set(0,'DefaultTextFontname', 'Times New Roman');
+set(0,'DefaultAxesFontName', 'Times New Roman');
+
+fig = figure(100);
 hold on;
 
 %HMC2 = log(HMC1);
@@ -18,22 +21,36 @@ RS2 = RS1;
 HRS2 = HRS1;
 HNR2 = HNR1;
 
-errorbar(T2, mean(RS2,1), std(RS2), 'color', blue, 'LineWidth',2);
-errorbar(T3, mean(HRS2,1), std(HRS2), 'color', red, 'LineWidth',2);
-errorbar(T1, mean(MCMC2,1), std(MCMC2), 'color', green, 'LineWidth',2);
-errorbar(T4, mean(HNR2,1), std(HNR2), 'color', purple, 'LineWidth',2);
+RSColor = [92, 121, 157]/255.; %[69,117,180]/255.;
+HRSColor = [113, 174, 111]/255.; %[102,189,99]/255.;
+MCMCColor = [219, 176, 132]/255.; %[253,174,97]/255.;
+HNRColor = [243, 90, 83]/255.; %[215,48,39]/255.;
+
+e1 = errorbar(T2, mean(RS2,1), std(RS2), 'color', RSColor, 'LineWidth',2);
+e2 = errorbar(T3, mean(HRS2,1), std(HRS2), 'color', HRSColor, 'LineWidth',2);
+e3 = errorbar(T1, mean(MCMC2,1), std(MCMC2), 'color', MCMCColor, 'LineWidth',2);
+e4 = errorbar(T4, mean(HNR2,1), std(HNR2), 'color', HNRColor, 'LineWidth',2);
 
 
-plot(T2, mean(RS2,1), 'o', 'MarkerFaceColor', blue, 'MarkerEdgeColor', blue, 'MarkerSize', 4);
-plot(T3, mean(HRS2,1), 'o', 'MarkerFaceColor', red, 'MarkerEdgeColor', red, 'MarkerSize', 4);
-plot(T1, mean(MCMC2,1), 'o', 'MarkerFaceColor', green, 'MarkerEdgeColor', green, 'MarkerSize', 4);
-plot(T4, mean(HNR2,1), 'o', 'MarkerFaceColor', purple, 'MarkerEdgeColor', purple, 'MarkerSize', 4);
[…]

### 2017-09-16 code/sample efficiency/2d/plot1new.m

@@ -29,26 +29,33 @@ HRSTime = data(:,2)./data(:,6);
 MHTime = data(:,1)./data(:,6);
 HNRTime = data(:,3)./data(:,6);
 
+RSColor = [92, 121, 157]/255.; %[69,117,180]/255.;
+HRSColor = [113, 174, 111]/255.; %[102,189,99]/255.;
+MHColor = [219, 176, 132]/255.; %[253,174,97]/255.;
+HNRColor = [243, 90, 83]/255.; %[215,48,39]/255.;
+
 ymin = min([RSTime; HRSTime; MHTime; HNRTime]);
 ymax = max([RSTime; HRSTime; MHTime; HNRTime]);
 xmin = min(volumeRatio);
 xmax = max(volumeRatio);
 
-figure(2);
+fig = figure(2);
 %hold on;
 marker_size = 4;
 
-h1 = loglog(volumeRatio,RSTime,  'o', 'MarkerFaceColor', blue, 'MarkerEdgeColor', blue, 'MarkerSize', 4);
+h1 = loglog(volumeRatio,RSTime,  'o', 'MarkerFaceColor', RSColor, 'MarkerEdgeColor', RSColor, 'MarkerSize', 4);
 hold on;
-h2 = loglog(volumeRatio,HRSTime, 'o', 'MarkerFaceColor', red, 'MarkerEdgeColor', red, 'MarkerSize', 4);
-h3 = loglog(volumeRatio,MHTime,  'o', 'MarkerFaceColor', green, 'MarkerEdgeColor', green, 'MarkerSize', 4);
-h4 = loglog(volumeRatio,HNRTime, 'o', 'MarkerFaceColor', purple, 'MarkerEdgeColor', purple, 'MarkerSize', 4);
-
+h2 = loglog(volumeRatio,HRSTime, 'o', 'MarkerFaceColor', HRSColor, 'MarkerEdgeColor', HRSColor, 'MarkerSize', 4);
+h3 = loglog(volumeRatio,MHTime,  'o', 'MarkerFaceColor', MHColor, 'MarkerEdgeColor', MHColor, 'MarkerSize', 4);
+h4 = loglog(volumeRatio,HNRTime, 'o', 'MarkerFaceColor', HNRColor, 'MarkerEdgeColor', HNRColor, 'MarkerSize', 4);
 hold off;
-deltaXLower = 0.000001;
-deltaXUpper = 0.002;
[…]

### 2017-09-16 code/sample efficiency/6d/plot1new.m

@@ -29,22 +29,29 @@ HRSTime = data(:,2)./data(:,6);
 MHTime = data(:,1)./data(:,6);
 HNRTime = data(:,3)./data(:,6);
 
+RSColor = [92, 121, 157]/255.; %[69,117,180]/255.;
+HRSColor = [113, 174, 111]/255.; %[102,189,99]/255.;
+MHColor = [219, 176, 132]/255.; %[253,174,97]/255.;
+HNRColor = [243, 90, 83]/255.; %[215,48,39]/255.;
+
 ymin = min([RSTime; HRSTime; MHTime; HNRTime]);
 ymax = max([RSTime; HRSTime; MHTime; HNRTime]);
 xmin = min(volumeRatio);
 xmax = max(volumeRatio);
 
-figure(2);
+fig = figure(2);
 %hold on;
 marker_size = 4;
 
-h1 = loglog(volumeRatio,RSTime,  'o', 'MarkerFaceColor', blue, 'MarkerEdgeColor', blue, 'MarkerSize', 4);
+h1 = loglog(volumeRatio,RSTime,  'o', 'MarkerFaceColor', RSColor, 'MarkerEdgeColor', RSColor, 'MarkerSize', 4);
 hold on;
-h2 = loglog(volumeRatio,HRSTime, 'o', 'MarkerFaceColor', red, 'MarkerEdgeColor', red, 'MarkerSize', 4);
-h3 = loglog(volumeRatio,MHTime,  'o', 'MarkerFaceColor', green, 'MarkerEdgeColor', green, 'MarkerSize', 4);
-h4 = loglog(volumeRatio,HNRTime, 'o', 'MarkerFaceColor', purple, 'MarkerEdgeColor', purple, 'MarkerSize', 4);
-
+h2 = loglog(volumeRatio,HRSTime, 'o', 'MarkerFaceColor', HRSColor, 'MarkerEdgeColor', HRSColor, 'MarkerSize', 4);
+h3 = loglog(volumeRatio,MHTime,  'o', 'MarkerFaceColor', MHColor, 'MarkerEdgeColor', MHColor, 'MarkerSize', 4);
+h4 = loglog(volumeRatio,HNRTime, 'o', 'MarkerFaceColor', HNRColor, 'MarkerEdgeColor', HNRColor, 'MarkerSize', 4);
 hold off;
+
+h1.Color(4) = 0.9; h2.Color(4) = 0.9; h3.Color(4) = 0.9;
+
[…]

### 2017-09-16 code/sample efficiency/volumeRatio/plot1.m

@@ -5,6 +5,8 @@
 %data(:,3) = log(data(:,3));
 %data(:,4) = log(data(:,4));
 
+colororder = get(gca, 'colororder');
+
 green = [49,163,84]/255;
 red = [222 45 38]/255;
 blue = [49,130,189]/255;
@@ -12,19 +14,28 @@ orange = [230,85,13]/255;
 purple = [117,107,177]/255;
 pink = [197,27,138]/255;
 
-figure;
+lowDimColor = [102,194,164]/255.;
+highDimColor = [0,88,36]/255.;
+
+fig = figure(1);
 hold on;
 marker_size = 20;
-plot(dim2(:,12), dim2(:,13), 'color', blue, 'linewidth', 4);
-plot(dim6(:,12), dim6(:,13), 'color', red, 'linewidth', 4);
+plot(dim2(:,12), dim2(:,13), 'color', lowDimColor, 'linewidth', 4);
+plot(dim6(:,12), dim6(:,13), 'color', highDimColor, 'linewidth', 4);
 %scatter(log10(data(:,5)),log10(data(:,1)./data(:,6)), marker_size, 'MarkerFaceColor', green, 'MarkerEdgeColor', green, 'Marker', 'h');
 %scatter(log10(data(:,5)),log10(data(:,3)./data(:,6)), marker_size, 'MarkerFaceColor', purple, 'MarkerEdgeColor', purple, 'Marker', 'o');
 
 xlim([1, 1.41]);
-xlabel(' c_{best} / c^*_{best}');
+xlabel('$ c_{best} / c^*_{best} $', 'Interpreter','latex');
 ylabel('informed set volume ratio');
 %legend('Rejection', 'HRS', 'MCMC', 'Hit&Run');
-legend('4-dimension', '12-dimension');
+legend('4-dimension', '12-dimension', 'Location', 'northwest');
 hold off;
 
 set(gca,'FontSize',16)
+
+set(fig,'Units','Inches');
+figPos = get(fig,'Position');
+set(fig,'PaperPositionMode','Auto','PaperUnits','Inches','PaperSize',[figPos(3), figPos(4)+0.01])
+
+print levelset.pdf -dpdf -r0

### 2017-09-16 paper.tex
consistency

@@
 \textbf{
-%Our main insight is to recast this problem as one of sampling uniformly within an informed set of an implicit function.
 Our main insight is to recast this problem as one of sampling uniformly within the sub-level-set of an implicit non-convex function.
@@
 One variant, which is of special interest to us is 
-Hit and Run~\cite{KSZ11}.
+Hit-and-Run~\cite{KSZ11}.
 Here, given the current point $x_i$ the next point~$x_{i+1}$ in the Markov chain is produced by sampling a random direction~$\theta$ on the surface of the unit sphere centered at $x_{i+1}$.
@@
 
-The attractiveness of Hit and Run for our problem domain stems from the fact that it performs a series of one-dimensional rejection samples which are extremely fast to compute, even in high-dimensional spaces.
-Finally, it is worth noting that we are not the first to apply Hit and Run for motion-planning problems.
+The attractiveness of Hit-and-Run for our problem domain stems from the fact that it performs a series of one-dimensional rejection samples which are extremely fast to compute, even in high-dimensional spaces.
+Finally, it is worth noting that we are not the first to apply Hit-and-Run for motion-planning problems.
 Recently~\cite{YPVA17} was used as an alternative to RRT to produce \emph{feasible motions} (and not high-quality paths). 
-Interestingly the paper concludes with the statement ``\emph{One drawback is that the sample paths for Hit and-Run have no pruning and are therefore longer than the RRT paths.
+Interestingly the paper concludes with the statement ``\emph{One drawback is that the sample paths for Hit-and-Run have no pruning and are therefore longer than the RRT paths.
 Hybrid approaches that yield short paths but also explore quickly are a promising future direction.}''
@@
 %It is not expressive enough for a wider range of actions, because many kiondynamic features are not considered in the planning process.
-%Figure \ref{fig:motivation} gives an example using HERB, which is about a swing action that a robotic arm ends with a relative high velocity towards a direction.
+%Fig.~\ref{fig:motivation} gives an example using HERB, which is about a swing action that a robotic arm ends with a relative high velocity towards a direction.
 %Geometric planning does not consider velocities in planning, so it can be viewed as considering only zero goal velocity.
-%Kinodyanic planning shall capture the velocity requirments, and generate a motion like in Figure\ref{fig:motivation:fast}.
-%The difference of two are shown in a phase plot, as in Figure \ref{fig:motivation:phase_plot}.
+%Kinodyanic planning shall capture the velocity requirments, and generate a motion like in Fig.~\ref{fig:motivation:fast}.
+%The difference of two are shown in a phase plot, as in Fig.~\ref{fig:motivation:phase_plot}.
 
@@
 
-%Let $T(x_1, x_2)$ denote the minimal time to move the robot from state $x_1$ to $x_2$.
-%Furthermore, set
-%%
-%\begin{equation}
-%T(x_s, x, x_g) = T(x_s, x) + T(x, x_g).
-%\end{equation}
-%%
-%Namely, $T(x_s, x, x_g)$ is the minimal time to reach the goal from the start subject to passing through the state $x$.
-%
-%
-%\subsection{Informed set}
 Recall that for Euclidean spaces minimizing path length, the informed set~\Cinf is a prolate hyperspheroid~\cite{GSB14}.
@@
 The Metropolis-Hastings algorithm is one of the most popular MCMC samplers~\cite{CG95}, because it provides a simple and parameter-free framework that guarantees the convergence of Markov chains to a target distribution.
-Our work adopts the general Metropolis-Hasting algorithm, as described in Alg.~\ref{alg:mh_mcmc}, 
+Our work adopts the general Metropolis-Hastings algorithm, as described in Alg.~\ref{alg:mh_mcmc}, 
 We generate a new sample $ x_{i}$ around the previous sample $ x_{i-1}$ using a Gaussian distribution (line~1).
@@
 	\end{algorithmic}
-	\caption{\captionstyle Hit-And-Run MCMC $(x_{i-1}, \cbest)$}
+	\caption{\captionstyle Hit-and-Run MCMC $(x_{i-1}, \cbest)$}
 	\label{alg:hit_and_run_mcmc}	
@@
 
-Figure \ref{fig:sampling_efficiency:levelset} shows how the informed set volume ratio decreases as the informed set cost $ \cbest $ becomes smaller in problems of different dimensions.
+Fig.~\ref{fig:sampling_efficiency:levelset} shows how the informed set volume ratio decreases as the informed set cost $ \cbest $ becomes smaller in problems of different dimensions.
 In higher dimensions, the informed set volume ratio decreases much more quickly with decrease in the informed set cost $ \cbest $, as new cheaper trajectories are found in the planning process.
 
-Fig.
-\ref{fig:sampling_efficiency} shows the plot of the average time taken to generate one sample in the informed space vs.
+Fig.~\ref{fig:sampling_efficiency} shows the plot of the average time taken to generate one sample in the informed space vs.
 informed set volume ratio, i.e.
@@
 %Efficiency of rejection sampling based methods is very low for high dimensions because this ratio decreases exponentially w.r.t the dimension of the space, for a given sub-level-set of the cost function.
-Fig. \ref{fig:sampling_efficiency} shows that MH and HNR have a better sampling efficiency compared to HRS and RS with decrease in informed set volume ratio or increase in dimensions.
+Fig.~\ref{fig:sampling_efficiency} shows that MH and HNR have a better sampling efficiency compared to HRS and RS with decrease in informed set volume ratio or increase in dimensions.
 
@@
 Notice that the sampling efficiency of HNR scales better than HRS and HRS is scales than RS.
-Moving from a 4 dimension problem in Figure \ref{fig:sampling_efficiency:2d} to a 12 dimension problem in Figure \ref{fig:sampling_efficiency:6d}, sampling in an informed set becomes even harder, because the informed set volume ratio becomes smaller.
+Moving from a 4 dimension problem in Fig.~\ref{fig:sampling_efficiency:2d} to a 12 dimension problem in Fig.~\ref{fig:sampling_efficiency:6d}, sampling in an informed set becomes even harder, because the informed set volume ratio becomes smaller.
 Here, HNR and MH samplers show much better efficiency over the others.
@@
 	\item Its performance should not degrade significantly in high dimensional problems.
-	As shown in Figure \ref{fig:sampling_efficiency:levelset}, the informed set volume ratio decrease more significantly in a high-dimension state space.
+	As shown in Fig.~\ref{fig:sampling_efficiency:levelset}, the informed set volume ratio decrease more significantly in a high-dimension state space.
 	The advantage of a good informed sampler becomes evident.
@@
 
-To evaluate the planning efficiency of the samplers, we run them with the informed RRT* planner~\cite{GSB14} in position-velocity space with MTDI as steering function, on three different problems described below and shown in Fig.
-\ref{fig:problems}.
+To evaluate the planning efficiency of the samplers, we run them with the informed RRT* planner~\cite{GSB14} in position-velocity space with MTDI as steering function, on three different problems described below and shown in Fig.~\ref{fig:problems}.
 For each problem the start and goal states (positions and velocities) are known in the joint space. 
 Joint velocities at start and goal are calculated from desired end-effector velocities using inverse kinematics before starting the planning.
-Table \ref{tab:params} shows the parameters used in the problems.
+Table~\ref{tab:params} shows the parameters used in the problems.
 
@@
 %The position boundary of each join is $ [ - \pi , \pi ] $, the velocity boundary is $ [-10, 10] $, and the acceleration is $ [-1,1] $.
-Figure~\ref{fig:planning_efficiency:3dof:example} shows the planned path.
+Fig.~\ref{fig:planning_efficiency:3dof:example} shows the planned path.
 
@@
 %The position boundary of each join is $[-\pi,\pi]$, the velocity boundary is $[-10,10]$, and the acceleration is $[-1,1]$.
-Figure~\ref{fig:planning_efficiency:6dof:example} shows the planned path.
+Fig.~\ref{fig:planning_efficiency:6dof:example} shows the planned path.
 
@@
 The objective is to quickly swing away a glass on a table using the right arm.
-Figure~\ref{fig:planning_efficiency:herb:example} shows a few steps of a planned path.
+Fig.~\ref{fig:planning_efficiency:herb:example} shows a few steps of a planned path.
 
@@
 
-As shown in in Figure~\ref{fig:planning_efficiency}, MH has the worst performance in all three problems, especially when the dimension increases.
+As shown in in Fig.~\ref{fig:planning_efficiency}, MH has the worst performance in all three problems, especially when the dimension increases.
 Though theoretically samples converge to a target distribution only in the limit of infinite time.
@@
 
-HNR shows close performance with RS and HRS in a 6-dimension problem, as in Figure~\ref{fig:planning_efficiency:3dof:general}. 
-As shown in Figure~\ref{fig:planning_efficiency:6dof:hammering} and \ref{fig:planning_efficiency:herb:batting}, the advantages of HNR are clearly evident in higher dimensional problems.
+HNR shows close performance with RS and HRS in a 6-dimension problem, as in Fig.~\ref{fig:planning_efficiency:3dof:general}. 
+As shown in Fig.~\ref{fig:planning_efficiency:6dof:hammering} and \ref{fig:planning_efficiency:herb:batting}, the advantages of HNR are clearly evident in higher dimensional problems.
 The cost of best solutions generated by planner with HNR sampler converges significantly faster to a cheaper to trajectory compared to others.

### 2017-09-16 paper.tex
fix for final submission

@@
 In this paper, we suggest an alternative approach to produce samples in the informed set~\Cinf for a wide range of settings.
-%Our main insight is to recast this problem as one of sampling uniformly within an informed set of an implicit function.
 Our main insight is to recast this problem as one of sampling uniformly within the sub-level-set of an implicit non-convex function.
@@
     		\includegraphics[width=\textwidth]{fig/motivation/phase_plot}
-    		\caption{Phase plot of two trajectories of one of the joints.
-    		The X axis is position. The Y axis is velocity. }
+    		\caption{Phase plot of two trajectories of one of the joints.}
     		\label{fig:motivation:phase_plot}
@@
 Additional algorithms followed, increasing the converges rate by various techniques such as 
-lazy dynamic programming~\cite{GSB15, SH15},
-relaxing optimality to near-optimality~\cite{SH16} 
+lazy dynamic programming~\cite{GSB15,SH15},
+relaxing optimality to near-optimality~\cite{DB14,SH16} 
 and more.
@@
 sampling near the boundary of the obstacles~\cite{YTEA12},
-resampling along a given trajectory~\cite{AS11}.
-%and more~\cite{SWT09}.
+resampling along a given trajectory~\cite{AS11}
+and more~\cite{US03, SWT09}.
 For planning under the differential constraints,
@@
 
-To understand the differences recall that optimal trajectories  for MTDI follow a ``bang-bang`` controller~\cite{HN10, KS14}.
+To understand the differences recall that optimal trajectories  for MTDI follow a ``bang-bang'' controller~\cite{HN10, KS14}.
 Namely, we first apply maximal (or minimal) acceleration for some duration and then switch to applying minimal (or maximal, respectively) acceleration.
@@
 Furthermore,  its boundary may not be  differentiable due to the aforementioned discontinuous.
-
-\ignore{
-See Fig.~\ref{fig:informed_1d_di} for a visualization of the cost surface for a specific start and goal state for one degree of freedom (two dimensions $\left(x, \dot{x}\right)$).
-Lower costs are represented with cooler colors with warmer colors representing higher costs.
-One can see the minimum cost path from start to goal as the dark blue curve.
-}
 
@@
 \end{enumerate}
-Our framework is described in Alg.~\ref{alg:mcmc_informed_sampling} and visualized in Fig.~\ref{fig:alg}.
+Our framework is described in Algorithm~\ref{alg:mcmc_informed_sampling} and visualized in Fig.~\ref{fig:alg}.
 We now continue to detail each of the algorithm's stages.
@@
 The Metropolis-Hastings algorithm is one of the most popular MCMC samplers~\cite{CG95}, because it provides a simple and parameter-free framework that guarantees the convergence of Markov chains to a target distribution.
-Our work adopts the general Metropolis-Hastings algorithm, as described in Alg.~\ref{alg:mh_mcmc}, 
+Our work adopts the general Metropolis-Hastings algorithm, as described in Algorithm~\ref{alg:mh_mcmc}, 
 We generate a new sample $ x_{i}$ around the previous sample $ x_{i-1}$ using a Gaussian distribution (line~1).
@@
 Specifically, we use the Accelerated Hit-and-Run variant~\cite{KSZ11} of the algorithm i.e.
-described in Alg.~\ref{alg:hit_and_run_mcmc}, which also supports the uniform sampling in both convex and non-convex state space~\cite{KSZ11}.
-Given the previous sample~$x_{i-1}$ it first  samples a random direction on the unit sphere (line 1).
+described in Algorithm~\ref{alg:hit_and_run_mcmc}, which also supports the uniform sampling in both convex and non-convex state space~\cite{KSZ11}.
+Given the previous sample~$x_{i-1}$ it first  samples a random direction on a unit sphere (line 1).
 This induces a line~$L(\lambda)$ passing through~$x_{i-1}$ in the direction sampled (line 2), parametrized by a scalar~$\lambda$.
-We obtain upper and lower bounds on $\lambda$ (line 3) that are problem dependant. 
+We obtain upper and lower bounds on $\lambda$ (line 3) that are problem dependent. 
 For example, if we have box constraints on joint limits of the robot and on maximum velocity, then bounds are given by $\lambda^{+} = -\lambda^{-} = l_{diag}$; where $l_{diag}$ is the length of the longest diagonal of the box.
@@
 
-		\IF{ \textsc{Cost}($ x_{i} $) $ < \cbest $ }
+		\IF{ $ c( x_{i} ) $ $ < \cbest $ }
 		\RETURN $ x_{i}$
@@
 The best covariance $ \Sigma $ that generates faster convergence differs with problem setting.
-A small covariance tends to generate more samples near previous samples, while a large covariance has better exploration but is more likely to drive a markov chain outside the informed set.
+A small covariance tends to generate more samples near previous samples, while a large covariance has better exploration but is more likely to drive a Markov chain outside the informed set.
 In our next planning experiment setting, we use the same covariance for different problems.
@@
 \toprule
-\multicolumn{2}{c}{Problem} & Position  & Velocity & $|acc_{max}|$ \\ [0.5ex] 
+\multicolumn{2}{c}{Problem} & Position  & $ | v_{max} |  $ & $|acc_{max}|$ \\ [0.5ex] 
     &    &    $rad$       &  $rad/sec$    &  $rad/sec^2$ \\
 \midrule
-\multicolumn{2}{c}{3DoF Arm} & $[-\pi, \pi]$ & [-10, 10] & 1 \\ 
+\multicolumn{2}{c}{3DoF Arm} & $[-\pi, \pi]$ & 10 & 1 \\ 
 \midrule
-\multicolumn{2}{c}{6DoF SnakeArm} & $[-\pi, \pi]$ & [-10, 10] & 1 \\
+\multicolumn{2}{c}{6DoF SnakeArm} & $[-\pi, \pi]$ & 10 & 1 \\
 \midrule
-\multirow{7}{*}{7DoF arm} & 1st & [0.541593 , 5.74159] & [-0.75, 0.75] & \multirow{7}{*}{1} \\
-\cmidrule{2-4}            & 2nd &  [-2 , 2]            & [-0.75, 0.75]  &  \\
-\cmidrule{2-4}            & 3rd & [-2.8, 2.8]          & [-2, 2] &  \\
-\cmidrule{2-4}            & 4th & [-0.9, 3.1]          & [-2.5, 2.5] &  \\
-\cmidrule{2-4}            & 5th & [-4.76, 1.24]        & [-2.5, 2.5] &  \\
-\cmidrule{2-4}            & 6th & [-1.6, 1.6]          & [-2.5, 2.5] &  \\
-\cmidrule{2-4}            & 7th & [-3, 3]              & [-2.5, 2.5] &  \\
+7DoF arm                  & 1st & [0.54 , 5.74] & 0.75 & \multirow{7}{*}{1} \\
+\rule{0pt}{3ex}           & 2nd & [-2 , 2]             & 0.75 &  \\
+\rule{0pt}{3ex}           & 3rd & [-2.8, 2.8]          &  2   &  \\
+\rule{0pt}{3ex}           & 4th & [-0.9, 3.1]          & 2.5  &  \\
+\rule{0pt}{3ex}           & 5th & [-4.76, 1.24]        & 2.5  &  \\
+\rule{0pt}{3ex}           & 6th & [-1.6, 1.6]          & 2.5  &  \\
+\rule{0pt}{3ex}          & 7th & [-3, 3]              & 2.5  &  \\
 \bottomrule
@@
 
-%The position boundaries of 7 joints of the arm are $  [0.541593 , 5.74159] $, $  [-2 , 2] $, $ [-2.8 , 2.8] $, $ [-0.9 , 3.1] $, $ [-4.76 , 1.24] $, $ [-1.6 , 1.6] $ and $ [-3 , 3] $.
-%The velocity boundary of 7 joints of the arm are $ [-0.75 , 0.75] $, $ [-0.75 , 0.75] $, $ [-2 , 2] $, $ [-2 , 2] $, $ [-2.5 , 2.5] $, $ [-2.5 , 2.5] $ and $ [-2.5 , 2.5] $.
-%The accelerations of all the joints are set to $ [-1,1] $.
 The objective is to quickly swing away a glass on a table using the right arm.

### 2017-09-16 code/motivation/plotdata.m

@@ -102,7 +102,7 @@ scatter(slowStartPos, slowStartVel, 'o', 'MarkerEdgeColor', slowStartColor, 'Mar
 scatter(fastGoalPos, fastGoalVel, 's', 'MarkerEdgeColor', fastGoalColor, 'MarkerFaceColor', faceColor, 'LineWidth',2);
 scatter(slowGoalPos, slowGoalVel, 's', 'MarkerEdgeColor', slowGoalColor, 'MarkerFaceColor', faceColor, 'LineWidth',2);
 
-
+xlim([-0.32, 0.12]);
 
 xlabel('Position  $ q  $ (rad)', 'Interpreter','latex');
 ylabel('Velocity $ \dot{q} $ (rad/sec) ', 'Interpreter','latex');

### 2017-09-16 paper.tex
tiny fix

@@
 	\caption{\captionstyle Three problems are used to evaluate planning efficiency.
-	These problems are defined in state spaces with different dimensions and different kinodynamics.}
+	These problems are defined in state spaces of different dimensions and subject to different kinodynamics.}
 	\label{fig:problems}
@@
 	The X axis is the planning time. 
-	The Y axis is the ration of the current best and the optimal $ \cbest / c^*_{\rm best} $.}
+	The Y axis is the ratio of the current best and the optimal $ \cbest / c^*_{\rm best} $.}
 	\label{fig:planning_efficiency}

### 2017-09-16 code/motivation/plotdata.m
new phase plot

@@ -106,7 +106,7 @@ xlim([-0.32, 0.12]);
 
 xlabel('Position  $ q  $ (rad)', 'Interpreter','latex');
 ylabel('Velocity $ \dot{q} $ (rad/sec) ', 'Interpreter','latex');
-lgd = legend([h1, h2], {'non-zero goal velocity', 'zero goal velocity'}, 'Location', 'southeast');
+lgd = legend([h1, h2], {'non-zero goal velocity', 'zero goal velocity'}, 'Location', 'northwest');
 hold off;
 %lgd.Position = 'southeast';
 

### 2018-02-23 paper.tex
Fixed the table
new
address reviewers comments

@@
   	The root-finding and MCMC algorithms are depicted in red and turquoise, respectively.
+  	$ x_0 $ lies on the boundary of $ \Cinf $
   	}
@@
 Our approach requires that the system has a solution to the two-point boundary value problem (2pBVP)~\cite{L06} and that a gradient can be defined over the cost function.
-Indeed, we demonstrate the efficiency of our approach on a wide variety of systems and show that it enables reducing the planning time by several orders of magnitude when compared to algorithms using rejection sampling or HRS.
+Indeed, we demonstrate the efficiency of our approach in several systems and show that it has the potential of reducing the planning time by several orders of magnitude when compared to algorithms using rejection sampling or HRS.
 
@@
 $\dot{x}(t) = f( x(t) , u(t) )$.
-A trajectory is collision free if $\forall t,~\gamma(t) \in \Cfree$
+A trajectory is collision free if $\forall t,~\gamma(t) \in \Cfree$.
 
@@
 One approach to address this problem is to first plan in the geometric configuration space and then re-scale the trajectory in time.
-However, when the start and goal are in close proximity, a geometric planner will simply connect the two states (Fig.~\ref{fig:motivation:fast}).
+However, when the start and goal are in close proximity, a geometric planner will simply connect the two states (Fig.~\ref{fig:motivation:slow}).
 On re-scaling this trajectory in time, reaching the goal velocity in such short distance will require large acceleration, which will not be feasible.
@@
 To summarize, the structure of \Cinf can change given different start and goal states.
-Furthermore,  its boundary may not be  differentiable due to the aforementioned discontinuous.
+Furthermore,  its boundary may not be  differentiable due to the aforementioned discontinuity.
 
@@
 In theory, MCMC methods converge to the desired distribution regardless of the initial sample used to seed the chain.
-In our setting, the probability distribution~\Pinf is defined by having all points in \Cinf distributed uniformly
+In our setting, the probability distribution~ $ \pi $ is defined by having all points in \Cinf distributed uniformly
 while 
@@
 (ii)~the new sample on the existing Markov chain is outside~\Cinf.
-
 We suggest several methods to produce an initial sample~$x_0 \in \Cinf $ 
@@
 We demonstrate how to instantiate it with two different algorithms \emph{Metropolis-Hastings} and \emph{Hit-and-Run}, which will be described in later subsections.
-If a generated new sample candidate is in the informed set, this candidate will be returned as a new sample.
-But if a generated new sample candidate is not in the informed set, it will go back to line 2.
+If a generated new sample candidate is in the informed set, this candidate will be returned as a new sample (line~4).
+But if a generated new sample candidate is not in the informed set (line~5), it will go back to line 2.
 A new Markov chain will be initiated by calling \texttt{sample\_in\_informed\_space}() to generate a new sample $ x_0 $.
@@
 
-The Metropolis-Hastings algorithm is one of the most popular MCMC samplers~\cite{CG95}, because it provides a simple and parameter-free framework that guarantees the convergence of Markov chains to a target distribution.
+The Metropolis-Hastings algorithm is one of the most popular MCMC samplers~\cite{CG95}, because it provides a simple and framework that guarantees the convergence of Markov chains to a target distribution.
 Our work adopts the general Metropolis-Hastings algorithm, as described in Algorithm~\ref{alg:mh_mcmc}, 
 We generate a new sample $ x_{i}$ around the previous sample $ x_{i-1}$ using a Gaussian distribution (line~1).
-We then check if the point lies in the informed set (lines 2-5) and if it does we return it.
-If not, we return the previous sample.
 An acceptance ratio $ \alpha $ is used to keep the reversibility even if the target probability $ \pi $ is asymmetric, which is needed to guarantee the convergence~\cite{CG95}. 
+The calculation of the acceptance ratio $ \alpha $ is given in line~2 in Algorithm~\ref{alg:mh_mcmc}.
+A new sample will be accepted if a generated random number from a uniform distribution $[0.0, 1.0 ] $ is less than the acceptance ratio (line 3-5).
 
@@
 		\STATE $ \alpha \leftarrow \frac{ q ( x_{i-1} \mid x'_{i},\Sigma) \pi( x'_{i} ) }{ q ( x'_{i} \mid x_{i-1},\Sigma) \pi( x_{i-1} ) } $
-		\IF{ \texttt{sample\_random}$ (0.0 , 1.0) > \min (1, \alpha) $  }
+		\IF{ \texttt{sample\_random}$ (0.0 , 1.0) < \min (1, \alpha) $  }
             \RETURN $ x'_{i} $
 		\ENDIF
-		\RETURN $ x_{i} $
+		\RETURN $ x_{i-1} $
 	\end{algorithmic}
@@
 	\begin{algorithmic}[1]
-		\STATE $d \leftarrow$ \texttt{sample\_random\_direction}$()$
-		\STATE $ L(\lambda) = \{  x \mid x = x_{i-1} + \lambda d_i \} $
+		\STATE $d_i \leftarrow$ \texttt{sample\_random\_direction}$()$
+		\STATE $ L(\lambda) = \{  \lambda \in \mathbb{R} \mid c(x_{i-1} + \lambda d_i ) \leq \cbest \} $
 		\STATE $ \lambda^{+} \leftarrow \sup L(\lambda) $; 
@@
 We use different samplers to generate a fixed number of samples in different informed sets to check the sampling efficiency. %, especially when the sampling is harder (in a small informed set).
-We then compare the quality of the samplers by evaluating how the samplers work with informed RRT*~\cite{GSB14}.
+We then compare the quality of the samplers by how the samplers work with informed RRT*~\cite{GSB14}.
 
@@
 
-Fig.~\ref{fig:sampling_efficiency} shows the plot of the average time taken to generate one sample in the informed space vs.
-informed set volume ratio, i.e.
-the ratio of the volume of informed space to the volume of entire state space, for 5000 samples.
+We define the \emph{informed set volume ratio} as the ratio of the volume of informed space to the volume of entire state space.
+Fig.~\ref{fig:sampling_efficiency} shows the plot of the average time taken to generate one sample in the informed space vs. informed set volume ratio for 5000 samples. 
 The informed set volume ratio is estimated by the acceptance rate of rejection sampler.
@@
 The sampling time of all samplers except MH, increases as problems gets harder.
-Notice that the sampling efficiency of HNR scales better than HRS and HRS is scales than RS.
+Notice that the sampling efficiency of HNR scales better than HRS, and HRS scales better than RS.
 Moving from a 4 dimension problem in Fig.~\ref{fig:sampling_efficiency:2d} to a 12 dimension problem in Fig.~\ref{fig:sampling_efficiency:6d}, sampling in an informed set becomes even harder, because the informed set volume ratio becomes smaller.
@@
 We want to point out that efficiently sampling in an informed set is not sufficient for determining the performance of a sampler.
-For example, a sampler that constantly returns the same sample in a informed set might show the best sampling efficiency, however it is the worst sampler in a path planning problem.
+For example, a sampler that constantly returns the same sample in an informed set might show the best sampling efficiency, however it is the worst sampler in a path planning problem.
 %\dy{is the property that any state in a set has a chance to be sampled?}
@@
 
-\begin {table}[H]
-\caption {\captionstyle Parameters for the problems} \label{tab:params} 
-\begin{center}
-	\begin{tabular}{c c c c c} 
+\begin {table*}[t!]
+\centering
+\setlength{\tabcolsep}{0.5em}
+\begin{tabular}{r*{7}{>{[}r@{,~}l<{]}}} 
 \toprule
-\multicolumn{2}{c}{Problem} & Position  & $ | v_{max} |  $ & $|acc_{max}|$ \\ [0.5ex] 
-    &    &    $rad$       &  $rad/sec$    &  $rad/sec^2$ \\
+HERB Joint & 
+\multicolumn{2}{c}{1} & 
+\multicolumn{2}{c}{2} & 
+\multicolumn{2}{c}{3} &
+\multicolumn{2}{c}{4} &
+\multicolumn{2}{c}{5} &
+\multicolumn{2}{c}{6} &
+\multicolumn{2}{c}{7} 
+\\ 
 \midrule
-\multicolumn{2}{c}{3DoF Arm} & $[-\pi, \pi]$ & 10 & 1 \\ 
-\midrule
-\multicolumn{2}{c}{6DoF SnakeArm} & $[-\pi, \pi]$ & 10 & 1 \\
-\midrule
-7DoF arm                  & 1st & [0.54 , 5.74] & 0.75 & \multirow{7}{*}{1} \\
-\rule{0pt}{3ex}           & 2nd & [-2 , 2]             & 0.75 &  \\
-\rule{0pt}{3ex}           & 3rd & [-2.8, 2.8]          &  2   &  \\
-\rule{0pt}{3ex}           & 4th & [-0.9, 3.1]          & 2.5  &  \\
-\rule{0pt}{3ex}           & 5th & [-4.76, 1.24]        & 2.5  &  \\
-\rule{0pt}{3ex}           & 6th & [-1.6, 1.6]          & 2.5  &  \\
-\rule{0pt}{3ex}          & 7th & [-3, 3]              & 2.5  &  \\
+Joint limits ($rad$)& 
+ 0.54 & 5.74 &
+-2.00 & 2.00 &
+-2.80 & 2.80 &
+-0.90 & 3.10 &
+-4.76 & 1.24 &
+-1.60 & 1.60 &
+-3.00 & 3.00
+\\
+$| v_{max} |~(rad/s)$ &
+\multicolumn{2}{c}{0.75} &
+\multicolumn{2}{c}{0.75} &
+\multicolumn{2}{c}{2.00} &
+\multicolumn{2}{c}{2.50} &
+\multicolumn{2}{c}{2.50} &
+\multicolumn{2}{c}{2.50} &
+\multicolumn{2}{c}{2.00}
+\\
 \bottomrule
 \end{tabular}
-\end{center}
-\end{table}
-\vspace{-2pt}
+\begin{tabular}{>{[}r@{,~}l<{]}} 
+\toprule
+\multicolumn{2}{c}{3D Arm} 
+\\ 
+\midrule
+ $-\pi$ & $\pi$ 
+\\
+\multicolumn{2}{c}{10} 
+\\
+\bottomrule
+\end{tabular}
+\begin{tabular}{>{[}r@{,~}l<{]}} 
+\toprule
+\multicolumn{2}{c}{6D Snake} 
+\\ 
+\midrule
+ $-\pi$ & $\pi$ 
+\\
+\multicolumn{2}{c}{10} 
+\\
+\bottomrule
+\end{tabular}
+\caption {\captionstyle Parameters for the problems. All robots have $|a_{max}| = 1.0~rad/s^2$}.
+\label{tab:params} 
+\end{table*}
 
@@
 
+\section{Acknowledge}
+
+This work was (partially) funded by the National Science Foundation IIS ($\#1409003$), and the Office of Naval Research.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \bibliography{bibliography}
-\bibliographystyle{IEEEtran}
+\bibliographystyle{hieeetr}
 %\bibliography{IEEEabrv,bibliography}

### 2018-02-23 paper.tex
minor edits until sec VI

@@
 Generalizing Informed Sampling
-for Asymptotically Optimal Sampling-based Kinodynamic Planning via Markov Chain
+for Asymptotically-Optimal Sampling-based Kinodynamic Planning via Markov Chain
 Monte Carlo
@@
 {\tt\small \{dqyi, siddh\}@cs.washington.edu}}
-\thanks{$^{2}$ Rohan Thakker, Cole Gulino and Oren Salzman are with Robotics Institute, Carnegie Mellon University.
+\thanks{$^{2}$Rohan Thakker, Cole Gulino and Oren Salzman are with Robotics Institute, Carnegie Mellon University.
 {\tt\small \{rthakker, cgulino, osalzman\} @andrew.cmu.edu}}%
@@
 Once an initial solution is found, their performance can be dramatically improved by restricting subsequent samples to regions of the state space that can potentially improve the current solution.
-When the motion planning problem lies in a Euclidean space, this region~$\Cinf$, called the informed set, can be sampled directly.
-However, when planning with differential constraints in non-Euclidean state spaces, no analytic solutions exists to sampling~$\Cinf$ directly.
+When the motion-planning problem lies in a Euclidean space, this region~$\Cinf$, called the informed set, can be sampled directly.
+However, when planning with differential constraints in non-Euclidean state spacess, no analytic solutions exists to sampling~$\Cinf$ directly.
 
@@
 Following Gammell et al.~\cite{GSB14}, we call this subset the \emph{informed subset} and denote it~$\Cinf$.
-In this work we address the problem of efficiently producing samples in informed subset for systems with arbitrary complex costs.
+In this work we address the problem of efficiently producing samples in~$\Cinf$ for systems with arbitrary complex costs.
 
@@
   	Algorithmic approach.
-  	Cost function is depicted using isocontours (darker shades reflect lower cost) while the boundary of the informed set is depicted in purple. 
+  	Cost function is depicted using iso-contours (darker shades reflect lower cost) while the boundary of the informed set is depicted in purple. 
   	The root-finding and MCMC algorithms are depicted in red and turquoise, respectively.
@@
 }
-Specifically, our approach, depicted in Fig~\ref{fig:alg} consists of two stages:
+Specifically, our approach, depicted in Fig.~\ref{fig:alg} consists of two stages:
 in the first, a random sample $x \in \calX$ is retracted to the boundary of~$\Cinf$ by running a root-finding algorithm;
@@
 While our approach can be used with any Markov Chain Monte Carlo (MCMC) method, it is especially suited to be used with Hit-and-Run~\cite{KSZ11}.
-Roughly speaking, this is because Hit-and-Run (detailed in Sec~\ref{sec:algorithm})
+Roughly speaking, this is because Hit-and-Run (detailed in Sec.~\ref{sec:algorithm})
 produces a series of one-dimensional rejection samples which are extremely fast to compute, even in high-dimensional spaces.
@@
 The point $x_{i+1}$ is chosen by randomly sampling a point on $r_i$.
-This algorithm is considered to be one of the most efficient algorithms for generating an asymptotically uniform point if the set under consideration is convex~\cite{LV06}
+This algorithm is considered to be one of the most efficient algorithms for generating an asymptotically uniform distribution if the set under consideration is convex~\cite{LV06}
 and it can also be extended to sample points that converge to an arbitrary target distribution in total variation~\cite{RS94}.
@@
 Finally, it is worth noting that we are not the first to apply Hit-and-Run for motion-planning problems.
-Recently~\cite{YPVA17} was used as an alternative to RRT to produce \emph{feasible motions} (and not high-quality paths). 
+Recently~\cite{YPVA17} it was used as an alternative to RRT to produce \emph{feasible motions} (and not high-quality paths). 
 Interestingly the paper concludes with the statement ``\emph{One drawback is that the sample paths for Hit-and-Run have no pruning and are therefore longer than the RRT paths.
@@
 
-Given a cost function $C : \calX \times \calU \rightarrow \R$, the cost of a trajectory $ \gamma $ is the accumulated cost along the path
+Given a cost function $c : \calX \times \calU \rightarrow \R$, the cost of a trajectory $ \gamma $ is the accumulated cost along the path
 $c(\gamma) = \int_0^{T} c( x(t), u(t) ) |\dot{\gamma}(t)|dt$, 
@@
 
-Given start and target states $x_s, x_g \in \calX$, we wish to find a collision free trajectory $\gamma^*$ connecting $x_s$ to $x_g$ such that 
+Given start and target states $x_s, x_g \in \calX$, we wish to find a collision-free trajectory $\gamma^*$ connecting $x_s$ to $x_g$ such that 
 $c(\gamma^*) = \min_{\gamma \in \Gamma} c(\gamma)$, where $\Gamma$ is the set of all collision-free trajectories.
@@
 		c ( \gamma^*(x) ) < \cbest \} $~\cite{GSB14}.
-Here~$ \gamma^*(x) $ denotes the optimal trajectory  from $ x_s $ to $ x_g $ constrained to pass through $ x $.
+Here~$ \gamma^*(x) $ denotes the optimal trajectory  from $ x_s $ to $ x_g $ constrained to pass through~$x $.
 Notice that we do not require that~$ \gamma^*(x) $ is collision free.
@@
 
-In this section we properly motivate this work.
-Specifically, we start by describing the differences in between planning in Euclidean configuration spaces (also called geometric planning) nd non-Euclidean  state spaces.
+In this section we properly motivate our work.
+Specifically, we start by describing the differences in between planning in Euclidean configuration spaces (also called geometric planning) and non-Euclidean  state spaces.
 
@@
 \subsection{Geometric vs. Kinodynamic planning}
-Consider the problem depicted in Fig.~\ref{fig:motivation} where HERB is required to produce a large velocity at the end of its arm at the goal position.
+Consider the problem depicted in Fig.~\ref{fig:motivation} where HERB is required to reach a goal position with a high  velocity of its end effector.
 One approach to address this problem is to first plan in the geometric configuration space and then re-scale the trajectory in time.
@@
 %Fig~\ref{fig:informed_sets} depicts two informed sets defined using the same cost~$\cbest$ but different start and goal states. Notice the difference in structure of~\Cinf. 
-Fig~\ref{fig:discont} depicts a simple example where the cost map is discontinuous.
+Fig.~\ref{fig:discont} depicts a simple example where the cost map is discontinuous.
 
@@
 
-The idea behind applying MCMC for informed sampling is to define a target distribution~$ \pi $ that has $p(x_{sample}\in\Cinf) \ne 0 ~\&~ p(x_{sample})\notin\Cinf = 0$. 
+The idea behind applying MCMC for informed sampling is to define a target distribution~$ \pi $ that has $\text{Pr}(x_{\text{sample}}\in\Cinf) \ne 0 \text{ and } \text{Pr}(x_{\text{sample}})\notin\Cinf = 0$ (here, $\text{Pr}(\cdot)$ is the probability that an event will occur).
 This is specially useful if we want to bias the samples based on our knowledge of the environment.
@@
 	\item randomly returning either the start state or the goal state,
-	\item randomly sampling a state $x_{\text rand} \in \Cinf$ and using a gradient descent algorithm (e.g. Newton-Raphson Method~\cite{RT06}) to find a sample in~$ \Cinf $
+	\item randomly sampling a state $x_{\text {rand}} \in \calX$ and using a gradient descent algorithm (e.g. Newton-Raphson Method~\cite{RT06}) to find a sample in~$ \Cinf $
 %	\footnote{ $ \forall x_i \in \Cinf \land x_j \not\in \Cinf, c( x_i ) > c ( x_j ) $. }
@@
 At the beginning of a Markov chain, \texttt{sample\_in\_informed\_space}() is called to generate the first sample in an informed set.
-\texttt{MCMC\_sample}() is called to generate a new sample based on a previous sample $ x_{i-1} $ and a cost $ \cbest $ that defines an informed set.
+\texttt{MCMC\_sample}() is called to generate a new sample based on a previous sample~$ x_{i-1} $ and a cost $ \cbest $ that defines an informed set.
 We demonstrate how to instantiate it with two different algorithms \emph{Metropolis-Hastings} and \emph{Hit-and-Run}, which will be described in later subsections.
 If a generated new sample candidate is in the informed set, this candidate will be returned as a new sample (line~4).
-But if a generated new sample candidate is not in the informed set (line~5), it will go back to line 2.
-A new Markov chain will be initiated by calling \texttt{sample\_in\_informed\_space}() to generate a new sample $ x_0 $.
+But if a generated new sample candidate is not in the informed set (line~5), a new Markov chain will be initiated by calling \texttt{sample\_in\_informed\_space}() to generate a new sample $ x_0 $ (lines 7 and 3).
 
@@
 		\LOOP 
-		\IF{ $ x_{i-1} == \varnothing $ }  
+		\IF{ $ i = 0$ }  
 		\label{alg:mcmc_informed_sampling:start}
@@
 		\IF{ $ x_{i} \not\in \Cinf $ }
-			\STATE $ i \leftarrow 0 $; $ x_{0} \leftarrow \varnothing $
+			\STATE $ i \leftarrow 0$
+%			\STATE $ i \leftarrow 0 $; $ x_{0} \leftarrow \varnothing $
 			\STATE \textbf{Goto} line \ref{alg:mcmc_informed_sampling:start} 
@@
 
-The Metropolis-Hastings algorithm is one of the most popular MCMC samplers~\cite{CG95}, because it provides a simple and framework that guarantees the convergence of Markov chains to a target distribution.
+The Metropolis-Hastings algorithm is one of the most popular MCMC samplers~\cite{CG95} because it provides a simple  framework that guarantees the convergence of Markov chains to a target distribution.
 Our work adopts the general Metropolis-Hastings algorithm, as described in Algorithm~\ref{alg:mh_mcmc}, 
@@
 The calculation of the acceptance ratio $ \alpha $ is given in line~2 in Algorithm~\ref{alg:mh_mcmc}.
-A new sample will be accepted if a generated random number from a uniform distribution $[0.0, 1.0 ] $ is less than the acceptance ratio (line 3-5).
+A new sample will be accepted if a generated random number from a uniform distribution $[0.0, 1.0 ] $ is less than the acceptance ratio (lines~3-5).
 
@@
 		\STATE $ \alpha \leftarrow \frac{ q ( x_{i-1} \mid x'_{i},\Sigma) \pi( x'_{i} ) }{ q ( x'_{i} \mid x_{i-1},\Sigma) \pi( x_{i-1} ) } $
-		\IF{ \texttt{sample\_random}$ (0.0 , 1.0) < \min (1, \alpha) $  }
+		\IF{ \texttt{sample\_random}$ (0.0 , 1.0) < \alpha $  }
             \RETURN $ x'_{i} $
@@
 
-In implementation, we use Newton-Raphson method as a gradient descent with random restart to find $ x_0 \in \Cinf $ as the start of a Markov chain.
+In our implementation, we use the Newton-Raphson method as a gradient descent with random restart to find $ x_0 \in \Cinf $ as the start of a Markov chain.
 
@@
 
-Hit-and-Run~\cite{S84} sampler is known to efficiently generate uniform samples. 
-Specifically, we use the Accelerated Hit-and-Run variant~\cite{KSZ11} of the algorithm i.e.
-described in Algorithm~\ref{alg:hit_and_run_mcmc}, which also supports the uniform sampling in both convex and non-convex state space~\cite{KSZ11}.
+The Hit-and-Run~\cite{S84} sampler is known to efficiently generate uniform samples. 
+Specifically, we use the Accelerated Hit-and-Run variant~\cite{KSZ11} of the algorithm which is described in Algorithm~\ref{alg:hit_and_run_mcmc}.
+It allows for uniform sampling in both convex and non-convex state spaces~\cite{KSZ11}.
 Given the previous sample~$x_{i-1}$ it first  samples a random direction on a unit sphere (line 1).
-This induces a line~$L(\lambda)$ passing through~$x_{i-1}$ in the direction sampled (line 2), parametrized by a scalar~$\lambda$.
+This induces a line~$L(\lambda)$ passing through~$x_{i-1}$ in the direction sampled and parametrized by a scalar~$\lambda$ (line 2).
 We obtain upper and lower bounds on $\lambda$ (line 3) that are problem dependent. 
-For example, if we have box constraints on joint limits of the robot and on maximum velocity, then bounds are given by $\lambda^{+} = -\lambda^{-} = l_{diag}$; where $l_{diag}$ is the length of the longest diagonal of the box.
+For example, if we have box constraints on the joint limits of the robot and on the maximum velocity, then the bounds are given by $\lambda^{+} = -\lambda^{-} = l_{diag}$; where $l_{diag}$ is the length of the longest diagonal of the box.
 We then sample a point along~$L(\lambda)$ by sampling a scalar~$\lambda'$ within our bounds (line 5).
-This defines a point~$x_{i}$ which is a candidate for the next sample along the Markov Chain (line 6).
+This defines a point~$x_{i}$ which is a candidate for the next sample of the Markov Chain (line 6).
 We then check if the point lies in the informed set (line 7) and if it does, we return it.
@@
 
-		\IF{ $ c( x_{i} ) $ $ < \cbest $ }
+		\IF{ $ c( \gamma^*(x_{i}) )$ $ < \cbest $ }
 		\RETURN $ x_{i}$
@@
 
-We evaluate the performance of proposed MCMC methods by comparing four types of samplers, which are Rejection Sampler (RS), Hierarchical Rejection Sampler (HRS), Metropolis-Hastings Sampler (MH), and Hit-and-Run Sampler (HNR).
+We evaluate the performance of proposed MCMC methods by comparing four types of samplers, which are Rejection Sampler (RS), Hierarchical Rejection Sampler (HRS), Metropolis-Hastings Sampler (MH), and the Hit-and-Run Sampler (HNR).
 We use different samplers to generate a fixed number of samples in different informed sets to check the sampling efficiency. %, especially when the sampling is harder (in a small informed set).

### 2018-02-23 paper.tex
initial updates to sec VI

@@
 		\includegraphics[width=\linewidth]{fig/sampling_efficiency/sample_efficiency_2d}
-		\caption{\captionstyle 4-dimension sampling space.}
+		\caption{\captionstyle 4-dimensional state space.}
 		\label{fig:sampling_efficiency:2d}
@@
 		\includegraphics[width=\linewidth]{fig/sampling_efficiency/sample_efficiency_6d}
-		\caption{\captionstyle 12-dimension sampling space.}
+		\caption{\captionstyle 12-dimensional state space.}
 		\label{fig:sampling_efficiency:6d}
@@
 	\caption{\captionstyle Average sampling time vs informed set volume ratio of four samplers (RS, HRS, MH and HNR) in state spaces of different dimensions. 
-	The X axis is the ratio of informed set volume to the entire sampling space.
-	The Y axis is the average time per sample.}
+	The $x$-axis is the ratio of the volume of informed set and the volume of the entire state space.
+	The $y$-axis is the average time per sample.}
 	\label{fig:sampling_efficiency}
@@
 Joint velocities at start and goal are calculated from desired end-effector velocities using inverse kinematics before starting the planning.
-Table~\ref{tab:params} shows the parameters used in the problems.
+Table~\ref{tab:params} shows the parameters used in the problems and Fig.~\ref{fig:problems} depicts the planned path for the three problems.
 
@@
 
-\subsubsection{Problem 1: 6 Dimension - 3 DoF Planar Manipulator}
+\begin{enumerate}
+	\item[\textbf{P1}] \emph{6 Dimensional 3 DoF planar manipulator}---The objective is to move the arm from a start to a goal state, both with zero velocities.
 
-The start and the goal states have zero velocities.
-%The position boundary of each join is $ [ - \pi , \pi ] $, the velocity boundary is $ [-10, 10] $, and the acceleration is $ [-1,1] $.
-Fig.~\ref{fig:planning_efficiency:3dof:example} shows the planned path.
+	\item[\textbf{P2}] \emph{12 Dimensional 6 DoF snake arm}	---The objective is to hammer the end-effector into the wall while starting with zero velocity.
 
-\subsubsection{Problem 2: 12 Dimension - 6 DoF Snake Arm}
-
-The objective is to hammer the end-effector into the wall while starting with zero velocity.
-%The position boundary of each join is $[-\pi,\pi]$, the velocity boundary is $[-10,10]$, and the acceleration is $[-1,1]$.
-Fig.~\ref{fig:planning_efficiency:6dof:example} shows the planned path.
-
-\subsubsection{Problem 3: 14 Dimension - 7 DoF WAM Arm}
-
-The objective is to quickly swing away a glass on a table using the right arm.
-Fig.~\ref{fig:planning_efficiency:herb:example} shows a few steps of a planned path.
+	\item[\textbf{P3}] \emph{14 Dimensional 7 DoF WAM arm}---The objective is to  to quickly swing away a glass on a table using the right arm.
+\end{enumerate}
+%
+%
+%\subsubsection[\textbf{P1}]{\textbf{P1} 6 Dimension - 3 DoF Planar Manipulator}
+%
+%The start and the goal states have zero velocities.
+%%The position boundary of each join is $ [ - \pi , \pi ] $, the velocity boundary is $ [-10, 10] $, and the acceleration is $ [-1,1] $.
+%Fig.~\ref{fig:planning_efficiency:3dof:example} shows the planned path.
+%
+%\subsubsection{Problem 2: 12 Dimension - 6 DoF Snake Arm}
+%
+%The objective is to hammer the end-effector into the wall while starting with zero velocity.
+%%The position boundary of each join is $[-\pi,\pi]$, the velocity boundary is $[-10,10]$, and the acceleration is $[-1,1]$.
+%Fig.~\ref{fig:planning_efficiency:6dof:example} shows the planned path.
+%
+%\subsubsection{Problem 3: 14 Dimension - 7 DoF WAM Arm}
+%
+%The objective is to quickly swing away a glass on a table using the right arm.
+%Fig.~\ref{fig:planning_efficiency:herb:example} shows a few steps of a planned path.
 
@@
 		\includegraphics[height=2.45cm]{fig/planning_efficiency/3dof_5}
-		\caption{\captionstyle Problem 1 : 3DOF planar arm move from a start to a goal while starting and ending with zero velocities.}
+		\caption{\captionstyle Problem \textbf{P1} : 3DOF planar arm moving from a start state to a goal state, both with zero velocities.}
 		\vspace{6pt}
@@
 		\includegraphics[height=3cm]{fig/planning_efficiency/6dof_5}
-		\caption{\captionstyle Problem 2 : 6DOF snake hammers the end-effector into the wall while starting with zero velocity.}
+		\caption{\captionstyle Problem \textbf{P2} : 6DOF snake hammers the end-effector into the wall while starting with zero velocity.}
 		\vspace{6pt}
@@
     \includegraphics[height=2.7cm]{fig/planning_efficiency/herb_batting_5}
-	\caption{Problem 3 : HERB sweeps a cup on a table, in which the right arm starts with zero velocity and ends with non-zero velocity.}
+	\caption{Problem \textbf{P3} : HERB sweeps a cup on a table, in which the right arm starts with zero velocity and ends with non-zero velocity.}
 	\label{fig:planning_efficiency:herb:example}
 	\end{subfigure}
-	\caption{\captionstyle Three problems are used to evaluate planning efficiency.
-	These problems are defined in state spaces of different dimensions and subject to different kinodynamics.}
+	\caption{\captionstyle Three problems in different state spaces and subject to different dynamic constraints used to evaluate planning efficiency.}
 	\label{fig:problems}
@@
 		\includegraphics[width=\linewidth]{fig/planning_efficiency/3dof_general}
-		\caption{\captionstyle Problem 1 - 6 Dimensions.}
+		\caption{\captionstyle Problem \textbf{P1} - 6 dimensions.}
 		\label{fig:planning_efficiency:3dof:general}
@@
 		\includegraphics[width=\linewidth]{fig/planning_efficiency/6dof_hammering}
-		\caption{\captionstyle Problem 2 - 12 Dimensions.}
+		\caption{\captionstyle Problem \textbf{P2} - 12 dimensions.}
 		\label{fig:planning_efficiency:6dof:hammering}
@@
 	\includegraphics[width=\linewidth]{fig/planning_efficiency/herb_batting_efficiency}
-	\caption{\captionstyle Problem 3 - 14 Dimensions.}
+	\caption{\captionstyle Problem \textbf{P3} - 14 dimensions.}
 	\label{fig:planning_efficiency:herb:batting}
@@
 	\caption{\captionstyle Planning Efficiency of four different samplers (RS, HRS, MH and HNR) in three problems. 
-	The X axis is the planning time. 
-	The Y axis is the ratio of the current best and the optimal $ \cbest / c^*_{\rm best} $.}
+	The $x$-axis is the planning time. 
+	The $y$-axis is the ratio of the current best and the optimal $ \cbest / c^*_{\rm best} $.}
 	\label{fig:planning_efficiency}
@@
 
-\section{Acknowledge}
+\section{Acknowledgements}
 

### 2018-02-23 code/sample efficiency/2d/plot1new.m
update figure

@@ -59,8 +59,8 @@ deltaYUpper = 2;
 xlim([xmin-deltaXLower,xmax+deltaXUpper]);
 ylim([ymin-deltaYLower,ymax+deltaYUpper]);
 
-xlabel('informed set volume ratio');
-ylabel('time per sample (ms)');
+xlabel('Informed set volume ratio');
+ylabel('Time per sample (ms)');
 lgd = legend([h1, h2, h3, h4], {'RS', 'HRS', 'MH', 'HNR'});
 lgd.FontSize = 16;
 set(gca, 'fontsize',16);

### 2018-02-23 code/sample efficiency/6d/plot1new.m

@@ -59,8 +59,8 @@ deltaYUpper = 2000;
 xlim([xmin-deltaXLower,xmax+deltaXUpper]);
 ylim([ymin-deltaYLower,ymax+deltaYUpper]);
 
-xlabel('informed set volume ratio');
-ylabel('time per sample (ms)');
+xlabel('Informed set volume ratio');
+ylabel('Time per sample (ms)');
 lgd = legend([h1, h2, h3, h4], {'RS', 'HRS', 'MH', 'HNR'});
 lgd.FontSize = 16;
 set(gca, 'fontsize',16);

### 2018-02-23 code/sample efficiency/volumeRatio/plot1.m

@@ -27,7 +27,7 @@ plot(dim6(:,12), dim6(:,13), 'color', highDimColor, 'linewidth', 4);
 
 xlim([1, 1.41]);
 xlabel('$ c_{best} / c^*_{best} $', 'Interpreter','latex');
-ylabel('informed set volume ratio');
+ylabel('Informed set volume ratio');
 %legend('Rejection', 'HRS', 'MCMC', 'Hit&Run');
 legend('4-dimension', '12-dimension', 'Location', 'northwest');
 hold off;

### 2018-02-24 paper.tex
update table
updated eval section

@@
 When the motion-planning problem lies in a Euclidean space, this region~$\Cinf$, called the informed set, can be sampled directly.
-However, when planning with differential constraints in non-Euclidean state spacess, no analytic solutions exists to sampling~$\Cinf$ directly.
+However, when planning with differential constraints in non-Euclidean state spaces, no analytic solutions exists to sampling~$\Cinf$ directly.
 
@@
 \subsection{Sampling Efficiency}
+We define the \emph{informed set volume ratio} as the ratio of the volume of informed space to the volume of entire state space.
+This serves as a measure of how hard it is for a rejection sampler to sample within $\Cinf$.
+We plot (Fig.~\ref{fig:sampling_efficiency:levelset}) the informed set volume ratio decreases as the informed set cost $ \cbest $ becomes smaller in problems of different dimensions.
+As the dimension increases, the informed set volume ratio decreases much more quickly with the decrease in the informed set cost $ \cbest $, as new cheaper trajectories are found in the planning process.
+This implies that as the current solution improves, the problem of sampling within $\Cinf$ significantly increases.
 
-Fig.~\ref{fig:sampling_efficiency:levelset} shows how the informed set volume ratio decreases as the informed set cost $ \cbest $ becomes smaller in problems of different dimensions.
-In higher dimensions, the informed set volume ratio decreases much more quickly with decrease in the informed set cost $ \cbest $, as new cheaper trajectories are found in the planning process.
-
-We define the \emph{informed set volume ratio} as the ratio of the volume of informed space to the volume of entire state space.
-Fig.~\ref{fig:sampling_efficiency} shows the plot of the average time taken to generate one sample in the informed space vs. informed set volume ratio for 5000 samples. 
-The informed set volume ratio is estimated by the acceptance rate of rejection sampler.
-The informed set volume ratio is approximated by the ratio of the number of accepted to the total number of samples obtained while running rejection sampling. 
+We next move to evaluate the average time taken to generate one sample in the informed space as a function informed set volume ratio.
+Fig.~\ref{fig:sampling_efficiency} depicts this value averaged over 5000 samples; here, the informed set volume ratio is estimated by the acceptance rate of rejection sampler.
+%The informed set volume ratio is approximated by the ratio of the number of accepted to the total number of samples obtained while running rejection sampling. 
 %Efficiency of rejection sampling based methods is very low for high dimensions because this ratio decreases exponentially w.r.t the dimension of the space, for a given sub-level-set of the cost function.
-Fig.~\ref{fig:sampling_efficiency} shows that MH and HNR have a better sampling efficiency compared to HRS and RS with decrease in informed set volume ratio or increase in dimensions.
+%Fig.~\ref{fig:sampling_efficiency} 
+When the informed set volume ratio is high, it is relatively easy to generate samples in the informed set and all the samplers have comparable performances.
+This implies that rejection sampler may be the preferable sampler due to its simplicity and the fact that it indeed produces uniform samples in $\Cinf$.
+The sampling time of HRS and HNR, increases as problems gets harder.
+Notice that the sampling efficiency of HNR scales better than HRS, and HRS scales better than RS.
+Moving from a 4-dimensional problem in Fig.~\ref{fig:sampling_efficiency:2d} to a 12-dimensional problem in Fig.~\ref{fig:sampling_efficiency:6d}, sampling in $\Cinf$ becomes even harder, because the informed set volume ratio becomes smaller.
+Here, HNR and MH samplers show much better efficiency over the others.
 
@@
 
-Metropolis-Hastings shows consistent sampling time when problems get harder. 
-It takes the advantage of sampling a near state that generate samples in an informed set.
-However this does not reflect the quality of the samples, though all the samples are in the informed set.
-Recall in Algorithm~\ref{alg:mh_mcmc}, a new sample candidate is obtained from a Gaussian distribution $ q( x \mid x_{i-1}, \Sigma ) $.
+Roughly speaking, the average time to produce a sample remains constant for MH, regardless of the problem's difficulty.
+This is due to the fact that every sample is produced in the vicinity of a previously-generated sample.
+%It takes the advantage of sampling a near state that generate samples in an informed set.
+However this does not reflect the \emph{quality} of the samples---namely the distribution of the samples in $\Cinf$.
+Recall (Algorithm~\ref{alg:mh_mcmc}) that a new sample candidate is obtained from a Gaussian distribution $ q( x \mid x_{i-1}, \Sigma ) $.
 The best covariance $ \Sigma $ that generates faster convergence differs with problem setting.
@@
 
-When informed set volume ratio is relatively high, it is easy to generate samples in the informed set.
-All the samplers have close performances.
-It actually implies rejection sampler is the best because of its simplicity in implementation and minimum correlation between successive samples.
-The sampling time of all samplers except MH, increases as problems gets harder.
-Notice that the sampling efficiency of HNR scales better than HRS, and HRS scales better than RS.
-Moving from a 4 dimension problem in Fig.~\ref{fig:sampling_efficiency:2d} to a 12 dimension problem in Fig.~\ref{fig:sampling_efficiency:6d}, sampling in an informed set becomes even harder, because the informed set volume ratio becomes smaller.
-Here, HNR and MH samplers show much better efficiency over the others.
-
 We want to point out that efficiently sampling in an informed set is not sufficient for determining the performance of a sampler.
-For example, a sampler that constantly returns the same sample in an informed set might show the best sampling efficiency, however it is the worst sampler in a path planning problem.
+For example, a sampler that constantly returns the same sample in an informed set might exhibit the best sampling efficiency, however it is the worst sampler in a path planning problem.
 %\dy{is the property that any state in a set has a chance to be sampled?}
@@
 
-The quality of samples determines the efficiency of resulting planning algorithms.
-If a sampler could provide samples with same quality as others but generate samples in a much efficiency way, we would expect that an informed RRT* with this sampler would show two properties.
+The quality of samples determines the efficiency of planning algorithm using that sampler.
+If a sampler could provide samples with the same quality as others but generate samples in a much more efficient way, we expect that an informed RRT* with this sampler would show two properties:
 \begin{itemize}
-	\item It shall converge faster in finding the optimal solution.
-	Sampling in an informed set is gradually becoming harder as new better solution reduces $ \cbest $ which reduces the informed set volume ratio.
-	\item Its performance should not degrade significantly in high dimensional problems.
-	As shown in Fig.~\ref{fig:sampling_efficiency:levelset}, the informed set volume ratio decrease more significantly in a high-dimension state space.
-	The advantage of a good informed sampler becomes evident.
+	\item It shall converge faster to the optimal solution as sampling in $\Cfree$ becoming harder as new and better solution reduces $ \cbest $ (which,  in turn reduces the informed set volume ratio).
+	\item Its performance should not degrade significantly in high-dimensional problems.
+	As shown in Fig.~\ref{fig:sampling_efficiency:levelset}, the informed set volume ratio decrease more significantly in high-dimension state spaces, making the problem significantly more challenging.
+%	The advantage of a good informed sampler becomes evident.
 \end{itemize}
@@
 \setlength{\tabcolsep}{0.5em}
-\begin{tabular}{r*{7}{>{[}r@{,~}l<{]}}} 
+\begin{tabular}{>{[}r@{,~}l<{]}} 
+	\toprule
+	\multicolumn{2}{c}{3D Arm} 
+	\\ 
+	\midrule
+	$-\pi$ & $\pi$ 
+	\\
+	\multicolumn{2}{c}{10} 
+	\\
+	\bottomrule
+\end{tabular}
+\begin{tabular}{>{[}r@{,~}l<{]}} 
+	\toprule
+	\multicolumn{2}{c}{6D Snake} 
+	\\ 
+	\midrule
+	$-\pi$ & $\pi$ 
+	\\
+	\multicolumn{2}{c}{10} 
+	\\
+	\bottomrule
+\end{tabular}
+\begin{tabular}{l*{7}{>{[}r@{,~}l<{]}}} 
 \toprule
@@
 \multicolumn{2}{c}{2.00}
-\\
-\bottomrule
-\end{tabular}
-\begin{tabular}{>{[}r@{,~}l<{]}} 
-\toprule
-\multicolumn{2}{c}{3D Arm} 
-\\ 
-\midrule
- $-\pi$ & $\pi$ 
-\\
-\multicolumn{2}{c}{10} 
-\\
-\bottomrule
-\end{tabular}
-\begin{tabular}{>{[}r@{,~}l<{]}} 
-\toprule
-\multicolumn{2}{c}{6D Snake} 
-\\ 
-\midrule
- $-\pi$ & $\pi$ 
-\\
-\multicolumn{2}{c}{10} 
 \\
@@
 
-As shown in in Fig.~\ref{fig:planning_efficiency}, MH has the worst performance in all three problems, especially when the dimension increases.
-Though theoretically samples converge to a target distribution only in the limit of infinite time.
-However, in practice the samples are to close to each other and don't explore the entire informed space.
-If the variance of transition distribution is too high, it will tend to move out of the informed set too frequently, and takes longer to converge as the rejection rate is too high.
+As shown in in Fig.~\ref{fig:planning_efficiency}, MH has the worst performance in all three problems and this is accentuated as the dimension increases.
+Though theoretically, the samples it priduces converge to a target distribution only,  this occurs only as the number of samples tend to infinity.
+In practice, the samples are to close to each other and don't explore the entire informed space.
+A possible remedy would be to increase the variance of transition distribution.
+However, this may cause samples to exit $\Cinf$ too frequently, and would result in larger sampling times as the rejection rate would be too high.
 
-HNR shows close performance with RS and HRS in a 6-dimension problem, as in Fig.~\ref{fig:planning_efficiency:3dof:general}. 
-As shown in Fig.~\ref{fig:planning_efficiency:6dof:hammering} and \ref{fig:planning_efficiency:herb:batting}, the advantages of HNR are clearly evident in higher dimensional problems.
-The cost of best solutions generated by planner with HNR sampler converges significantly faster to a cheaper to trajectory compared to others.
+HNR shows similar  performance with RS and HRS in a 6-dimensional problem, as depicted in Fig.~\ref{fig:planning_efficiency:3dof:general}. 
+However, in higher dimensions 
+(Fig.~\ref{fig:planning_efficiency:6dof:hammering} and \ref{fig:planning_efficiency:herb:batting}), , the cost of the solutions generated by Informed RRT* with HNR as a sampler converges significantly faster to a cheaper to trajectory compared to the other methods.
 
@@
 In this work we demonstrated the effectiveness of using MCMC algorithms to 
-efficiently produce samples for asymptotically-optimal motion planning algorithms.
+efficiently produce samples for asymptotically-optimal motion-planning algorithms.
 Clearly, there are multiple other MCMC algorithms that can be used and it is interesting to see if alternative algorithms may produce better results.
